### 2022-07-11 Models.Rmd
summary

---
title: "Summary of models"
output: pdf_document
date: '2022-07-08'
---

Summary of models for seed numbers per plant species

# Richness
```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
library(knitr)
library(dplyr)
library(kableExtra)
library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)

Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
Pollinator_Plant<-Pollinator_Plant[,-1]

#Species out
spp_out <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  summarise(Unique_Id = n_distinct(Site_ID)) %>%
  filter(Unique_Id == 1) %>%
  select(Plant_gen_sp) %>% pull(Plant_gen_sp)

#Data with species in more than 1 site
Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)

#Models _ Seed numbers 
# richness
ta_seed<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
  summarise(broom.mixed::tidy(model)) %>%
  ungroup()

opts <- options(knitr.kable.NA = "")

ta_seed<-ta_seed %>%
  select(-effect, -group)  %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

ta_seed<-filter(ta_seed, !term == "sd__(Intercept)" & !term =="sd__Observation")

ta_seed %>% 
kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
column_spec(7, bold = ifelse(ta_seed$p.value < 0.05, T, F) )

```

\newpage
visitation rate

```{r, echo=FALSE}
load(".RData")
opts <- options(knitr.kable.NA = "")
knitr::kable(ta_seed2, digits = 4)
```

### 2022-07-12 models.R
correlation and models

@@ -1,0 +1,136 @@
+
+
+library(tidyverse)
+#install.packages("broom.mixed")
+library(broom.mixed)
+library(broom)
+#install.packages("lmerTest")
+library(lmerTest)
+library(dplyr)
+
+
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
+str(Pollinator_Plant)
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+
+# correlation
+a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
+a <- mutate_all(a, ~replace(., is.na(.), 0))
+
+#by(a[,2:7], a$Plant_gen_sp, cor)
+
+a_cor <- a %>%
+  group_by(Plant_gen_sp) %>%
+  do(cormat = cor(select(., -matches("Plant_gen_sp")))) 
+
+a_cor[[2]]
+
+list_1 <- a_cor[[2]]
+
+a_cor[[1]]
+
+v <- a_cor[[1]]
+str(v)
+names(list_1) <- v
+
+str(list_1)
+data2 <- do.call(rbind.data.frame, list_1)
+
+data2 %>%
+mutate(newcolum = rownames(data2))%>%
+separate(newcolum, into=c('species', 'rows'), extra = "merge", sep = "\\.")%>%
+select(species, rows,everything())  %>%
+remove_rownames() %>%
+  mutate(species = replace(species, duplicated(species), ""))
+
+
+
+
+#Models _ Seed numbers 
+
+require("lattice")
+xyplot(Seeds ~ visitatio_rate|Plant_gen_sp, data = Pollinator_Plant, type = c("p", "r"))
+xyplot(Seeds ~ richness|Plant_gen_sp, data = Pollinator_Plant, type = c("p", "r"))
+
+# richness
[…]

### 2022-07-12 script/models.R
correlation and models

@@ -6,6 +6,7 @@ library(broom.mixed)
 library(broom)
 #install.packages("lmerTest")
 library(lmerTest)
+library(dplyr)
 
 
 
@@ -27,14 +28,51 @@ spp_out <- Pollinator_Plant %>%
 Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
 
 
+# correlation
+a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
+a <- mutate_all(a, ~replace(., is.na(.), 0))
+
+#by(a[,2:7], a$Plant_gen_sp, cor)
+
+a_cor <- a %>%
+  group_by(Plant_gen_sp) %>%
+  do(cormat = cor(select(., -matches("Plant_gen_sp")))) 
+
+a_cor[[2]]
+
+list_1 <- a_cor[[2]]
+
+a_cor[[1]]
+
+v <- a_cor[[1]]
+str(v)
+names(list_1) <- v
+
+str(list_1)
+data2 <- do.call(rbind.data.frame, list_1)
+
+data2 %>%
+mutate(newcolum = rownames(data2))%>%
+separate(newcolum, into=c('species', 'rows'), extra = "merge", sep = "\\.")%>%
+select(species, rows,everything())  %>%
+remove_rownames() %>%
+  mutate(species = replace(species, duplicated(species), ""))
+
+
+
+
 #Models _ Seed numbers 
+
+require("lattice")
+xyplot(Seeds ~ visitatio_rate|Plant_gen_sp, data = Pollinator_Plant, type = c("p", "r"))
+xyplot(Seeds ~ richness|Plant_gen_sp, data = Pollinator_Plant, type = c("p", "r"))
+
 # richness
 ta_seed<-Pollinator_Plant %>%
   nest_by(Plant_gen_sp) %>%
   mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
   summarise(broom.mixed::tidy(model)) %>%
   ungroup()
-
 
 
 # visistation rate
@@ -46,6 +84,11 @@ ta_seed2<-Pollinator_Plant %>%
 
 
 #Models _ Seed weight 
+
+require("lattice")
+xyplot(Seed_weight ~ visitatio_rate|Plant_gen_sp, data = Pollinator_Plant, type = c("p", "r"))
[…]

### 2022-07-12 models.R
.

@@ -1,136 +1,0 @@
-
-
-library(tidyverse)
-#install.packages("broom.mixed")
-library(broom.mixed)
-library(broom)
-#install.packages("lmerTest")
-library(lmerTest)
-library(dplyr)
-
-
-
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
-str(Pollinator_Plant)
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-
-# correlation
-a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
-a <- mutate_all(a, ~replace(., is.na(.), 0))
-
-#by(a[,2:7], a$Plant_gen_sp, cor)
-
-a_cor <- a %>%
-  group_by(Plant_gen_sp) %>%
-  do(cormat = cor(select(., -matches("Plant_gen_sp")))) 
-
-a_cor[[2]]
-
-list_1 <- a_cor[[2]]
-
-a_cor[[1]]
-
-v <- a_cor[[1]]
-str(v)
-names(list_1) <- v
-
-str(list_1)
-data2 <- do.call(rbind.data.frame, list_1)
-
-data2 %>%
-mutate(newcolum = rownames(data2))%>%
-separate(newcolum, into=c('species', 'rows'), extra = "merge", sep = "\\.")%>%
-select(species, rows,everything())  %>%
-remove_rownames() %>%
-  mutate(species = replace(species, duplicated(species), ""))
-
-
-
-
-#Models _ Seed numbers 
-
-require("lattice")
-xyplot(Seeds ~ visitatio_rate|Plant_gen_sp, data = Pollinator_Plant, type = c("p", "r"))
-xyplot(Seeds ~ richness|Plant_gen_sp, data = Pollinator_Plant, type = c("p", "r"))
-
-# richness
[…]

### 2022-07-12 Models.Rmd
correlation and summary of models

@@
 
-Summary of models for seed numbers per plant species
+# Correlation
 
-# Richness
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+library(tidyverse)
+#install.packages("broom.mixed")
+library(broom.mixed)
+library(broom)
+#install.packages("lmerTest")
+library(lmerTest)
+library(dplyr)
+library(knitr)
+library(kableExtra)
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# correlation
+a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
+a <- mutate_all(a, ~replace(., is.na(.), 0))
+
+a_cor <- a %>%
+  group_by(Plant_gen_sp) %>%
+  do(cormat = cor(select(., -matches("Plant_gen_sp"))))
+
+list_1 <- a_cor[[2]]
+
+v <- a_cor[[1]]
+names(list_1) <- v
+
+data2 <- do.call(rbind.data.frame, list_1)
+
+corre<-data2 %>%
+mutate(newcolum = rownames(data2))%>%
+separate(newcolum, into=c('species', 'rows'), extra = "merge", sep = "\\.")%>%
+select(species, rows,everything())  %>%
+remove_rownames() %>%
+  mutate(species = replace(species, duplicated(species), ""))
+
+corre %>% 
+   kable(booktabs = TRUE,digits =  4,longtable = T,linesep = c("","","","","","\\addlinespace"),align = "llcccccc") %>%
+  kable_styling(font_size = 9,full_width = F)
+
+```
+
+\newpage
+
+# Fruit proportion
+
+Summary of models for fruit proportion per plant species
+
+**Richness**
+
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
@@
 library(lmerTest)
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+#Models _ fruit proportion 
+# richnes
+ta_f<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f<-ta_f %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f<-filter(ta_f, !term == "sd__(Intercept)")
+
+ta_f %>% 
+    kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f$p.value < 0.05, T, F) )
+
+```
+
+\newpage
+**Visitation rate**
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# visistation rate
+ta_f2<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f2<-ta_f2 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f2<-filter(ta_f2, !term == "sd__(Intercept)")
+
+ta_f2 %>% 
+kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f2$p.value < 0.05, T, F) )
+
+```
+
+\newpage
+
+# Seed numbers
+
+Summary of models for seed numbers per plant species
+
+**Richness**
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
 
@@
 \newpage
-visitation rate
+**Visitation rate**
 
-```{r, echo=FALSE}
-load(".RData")
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# visitation rate
+ta_seed2<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
 opts <- options(knitr.kable.NA = "")
-knitr::kable(ta_seed2, digits = 4)
+
+ta_seed2<-ta_seed2 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed2<-filter(ta_seed2, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed2 %>% 
+kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed2$p.value < 0.05, T, F) )
 ```
+
+\newpage
+
+# Seed weight
+
+Summary of models for seed weight per plant species
+
+**Richness**
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+#Models _ Seed weight 
+# richnes
+ta_weight<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~richness+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight<-ta_weight %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight<-filter(ta_weight, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight %>% 
+kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight$p.value < 0.05, T, F) )
+
+```
+
+\newpage
+
+**Visitation rate**
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+#Models _ Seed weight 
+# visistation rate
+ta_weight2<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~visitatio_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight2<-ta_weight2 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight2<-filter(ta_weight2, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight2 %>% 
+kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight2$p.value < 0.05, T, F) )
+
+```

### 2022-07-13 script/Fruit_set.R
new pollinator-plant

@@ -417,8 +417,8 @@ levels(factor(cole$Pollinator_genus))
 
 # remove Anthrenus
 focal<-subset(focal, Pollinator_genus != 'Anthrenus' | is.na(Orden))
-sum(is.na(focal$Orden))
 
+sum(is.na(focal$Orden)) # 702 obser con pollinator sp NANA
 
 
 # Plant species #
@@ -426,11 +426,12 @@ sum(is.na(focal$Orden))
 # Plant species in focal #
 levels(factor(focal$Plant_gen_sp))
 
-#select plant species in focal present in reproductive success (todas:19 especies)
-levels(factor(reprod_success0$Plant_gen_sp)) 
+#select plant species in focal present in reproductive success (todas:18 especies)
+# reproductive success with data of fruit and seed
+levels(factor(reprod_success$Plant_gen_sp)) 
 
 plant<-c("Anchusa azurea","Asphodelus fistulosus","Cistus crispus","Cistus ladanifer","Cistus libanotis",
-      "Cistus monspeliensis","Cistus salviifolius","Erica ciliaris","Erophaca baetica","Halimium calycinum",
+      "Cistus monspeliensis","Cistus salviifolius","Erophaca baetica","Halimium calycinum",
       "Halimium halimifolium","Lavandula pedunculata","Lavandula stoechas","Phlomis purpurea","Retama sphaerocarpa",
       "Salvia rosmarinus","Spartium junceum","Teucrium fruticans","Ulex australis")
 
@@ -503,8 +504,11 @@ Pol_frequency<-aggregate(Frequency ~ Year+Site_ID+Plant_gen_sp+plant_id, data = 
 #link flower_abun and Pol_frequency (dejando individuos que tienen flores pero no visitas)
 visitation<-merge(x=flower_abun,y=Pol_frequency,by=c("Year","Site_ID", "Plant_gen_sp","plant_id" ),all.x=T, all.y=F)
 
-sum(is.na(visitation$Frequency)) # 45 observ no tienen visitas polinizador
+sum(is.na(visitation$Frequency)) # 45 observ (plant id) no tienen visitas polinizador
 
+
+visitation<-visitation%>%
+   filter(!Flower_abundance==0) # eliminar 4 observaciones con flower abundance=0
 
 # frequency/ flower abundance
 visitation<-visitation %>% mutate(visitatio_rate = Frequency/Flower_abundance)
[…]

### 2022-07-13 script/correlacion.R
.

@@ -1,2650 +1,0 @@
-
-getwd()
-
-library(readr)
-library(dplyr)
-#install.packages("PerformanceAnalytics")
-library(PerformanceAnalytics)
-library(ggplot2)
-library(nlme)
-library(lme4)
-#install.packages("AICcmodavg")
-library(AICcmodavg)
-library(MASS)
-library(psych)
-#install.packages("corrplot")
-library(corrplot)
-#install.packages("DHARMa")
-library(DHARMa)
-
-
-total <- read.csv("Data/Frequency-Fruit.csv")
-View(total)
-str(total)
-total<-total[,-1]
-
-
-total$Year= factor(total$Year)
-
-# removed lines with all=0 (5 obser)
-total<-total[!apply(total[,5:21] == 0, 1, all), ]
-
-
-#total <- total[!(total$Frequency == 0),]
-
-
-
-par(mfrow=c(3,3))
-boxplot(total$Fruit_proportion)
-boxplot(Fruit_proportion~Year, data = total)
-boxplot(Fruit_proportion~Site_ID, data = total)
-boxplot(total$seed_number)
-boxplot(seed_number~Year, data = total)
-boxplot(seed_number~Site_ID, data = total)
-boxplot(total$Seed_weight)
-boxplot(Seed_weight~Year, data = total)
-boxplot(Seed_weight~Site_ID, data = total)
-dev.off()
-
-
-require(car)
-#scatterplot(Fruit_proportion ~ Frequency, reg.line = lm, smooth = F, data=total)
-scatterplot(Fruit_proportion ~ Frequency|Plant_sp, reg.line = lm, smooth = F, data=total)
-
-
-require("lattice")
-xyplot(Fruit_proportion ~ Frequency, data = total, type = c("p", "r"))
-xyplot(Fruit_proportion ~ Frequency|Plant_sp, data = total, type = c("p", "r"))
-xyplot(Fruit_proportion ~ richness|Plant_sp, data = total, type = c("p", "r"))
-
-xyplot(seed_number ~ Frequency, data = total, type = c("p", "r"))
[…]

### 2022-07-13 models.R
correlation and models

@@ -1,0 +1,182 @@
+
+
+library(tidyverse)
+#install.packages("broom.mixed")
+library(broom.mixed)
+library(broom)
+#install.packages("lmerTest")
+library(lmerTest)
+library(dplyr)
+
+
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
+str(Pollinator_Plant)
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+
+# correlation
+a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
+a <- mutate_all(a, ~replace(., is.na(.), 0))
+
+a_cor <- a %>%
+  group_by(Plant_gen_sp) %>%
+  do(cormat = cor(select(., -matches("Plant_gen_sp")))) 
+
+a_cor[[2]]
+
+list_1 <- a_cor[[2]]
+
+a_cor[[1]]
+
+v <- a_cor[[1]]
+str(v)
+names(list_1) <- v
+
+str(list_1)
+data2 <- do.call(rbind.data.frame, list_1)
+
+corre<-data2 %>%
+mutate(newcolum = rownames(data2))%>%
+separate(newcolum, into=c('species', 'rows'), extra = "merge", sep = "\\.")%>%
+select(species, rows,everything())  %>%
+remove_rownames() %>%
+  mutate(species = replace(species, duplicated(species), ""))
+
+
+#corrplot 
+a %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ corrplot::corrplot(cor(select(.x, where(is.numeric)),
+  use = "complete.obs"),method="number",type="upper",
+  tl.cex=0.8,title = first(.x$Plant_gen_sp)), .keep = TRUE)
+   
+
+library(tidyverse)
[…]

### 2022-07-13 Models.Rmd
correlation and summary of models

@@
 date: '2022-07-08'
+
 ---
@@
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
 library(tidyverse)
@@
    kable(booktabs = TRUE,digits =  4,longtable = T,linesep = c("","","","","","\\addlinespace"),align = "llcccccc") %>%
-  kable_styling(font_size = 9,full_width = F)
+  kable_styling(font_size = 9,full_width = F, position="left")
 
@@
 
+```{r, echo=FALSE, warning=FALSE,message=FALSE, figures-side, out.width="100%",fig.fullwidth=TRUE}
+
+library(tidyverse)
+#install.packages("broom.mixed")
+library(broom.mixed)
+library(broom)
+#install.packages("lmerTest")
+library(lmerTest)
+library(dplyr)
+library(knitr)
+library(kableExtra)
+library(patchwork)
+library(ggcorrplot)
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# correlation
+a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
+a <- mutate_all(a, ~replace(., is.na(.), 0))
+
+df_with_plots <- a %>%
+  group_by(Plant_gen_sp) %>%
+  nest() %>%
+  mutate(plot = map(data, function(.x) {
+    .x  %>%
+      cor() %>%
+      ggcorrplot::ggcorrplot()
+  }))
+
+plots1 <- map2(df_with_plots$plot, df_with_plots$Plant_gen_sp, ~(.x + labs(title = .y)))
+
+plots1[[1]] + plots1[[2]] + plots1[[2]] + plots1[[2]]
+
+```
+
+\clearpage
+
 # Fruit proportion
 
-Summary of models for fruit proportion per plant species
+Summary of models for fruit proportion per plant species. Binomial cbind(fruit_formado, Fruit_No). Site_ID as factor random
 
-**Richness**
+## Richness
 
@@
 
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
 Pollinator_Plant<-Pollinator_Plant[,-1]
@@
 ta_f %>% 
-    kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f$p.value < 0.05, T, F) )
+    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
 
@@
 \newpage
-**Visitation rate**
+
+## Visitation rate
 
@@
 ta_f2 %>% 
-kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f2$p.value < 0.05, T, F) )
+kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f2$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Frequency
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# frequency
+ta_f3<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f3<-ta_f3 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f3<-filter(ta_f3, !term == "sd__(Intercept)")
+
+ta_f3 %>% 
+kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f3$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
 
@@
 
-Summary of models for seed numbers per plant species
+Summary of models for seed numbers per plant species (LMM). Site_ID as factor random
 
-**Richness**
+## Richness
+
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
@@
 ta_seed %>% 
-kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed$p.value < 0.05, T, F) )
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
 
@@
 \newpage
-**Visitation rate**
+## Visitation rate
 
@@
 ta_seed2 %>% 
-kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed2$p.value < 0.05, T, F) )
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed2$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+```
+
+\newpage
+## Visitation rate
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# Frequency
+ta_seed3<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed3<-ta_seed3 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed3<-filter(ta_seed3, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed3 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed3$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
 ```
@@
 
-Summary of models for seed weight per plant species
+Summary of models for seed weight per plant species (LMM). Site_ID as factor random
 
-**Richness**
+## Richness
 
@@
 ta_weight %>% 
-kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_weight$p.value < 0.05, T, F) )
+kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
 
@@
 
-**Visitation rate**
+## Visitation rate
 
@@
 ta_weight2 %>% 
-kable(booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_weight2$p.value < 0.05, T, F) )
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight2$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
 
 ```
+
+\newpage
+
+## Frequency
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+#Models _ Seed weight 
+# frequency
+ta_weight3<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Frequency+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight3<-ta_weight3 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight3<-filter(ta_weight3, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight3 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight3$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```

### 2022-07-13 models.R
correlations

@@ -66,9 +66,7 @@ a %>%
    
 
 library(tidyverse)
-install.packages("patchwork")
 library(patchwork)
-install.packages("ggcorrplot")
 library(ggcorrplot)
 
 df_with_plots <- a %>%

### 2022-07-13 script/models.R
correlation and models

@@ -10,7 +10,7 @@ library(dplyr)
 
 
 
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
 str(Pollinator_Plant)
 Pollinator_Plant<-Pollinator_Plant[,-1]
 
@@ -32,8 +32,6 @@ Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
 a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
 a <- mutate_all(a, ~replace(., is.na(.), 0))
 
-#by(a[,2:7], a$Plant_gen_sp, cor)
-
 a_cor <- a %>%
   group_by(Plant_gen_sp) %>%
   do(cormat = cor(select(., -matches("Plant_gen_sp")))) 
@@ -51,13 +49,38 @@ names(list_1) <- v
 str(list_1)
 data2 <- do.call(rbind.data.frame, list_1)
 
-data2 %>%
+corre<-data2 %>%
 mutate(newcolum = rownames(data2))%>%
 separate(newcolum, into=c('species', 'rows'), extra = "merge", sep = "\\.")%>%
 select(species, rows,everything())  %>%
 remove_rownames() %>%
   mutate(species = replace(species, duplicated(species), ""))
 
+
+#corrplot 
+a %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ corrplot::corrplot(cor(select(.x, where(is.numeric)),
+  use = "complete.obs"),method="number",type="upper",
+  tl.cex=0.8,title = first(.x$Plant_gen_sp)), .keep = TRUE)
+   
+
+library(tidyverse)
+library(patchwork)
+library(ggcorrplot)
+
+df_with_plots <- a %>%
+  group_by(Plant_gen_sp) %>%
+  nest() %>%
+  mutate(plot = map(data, function(.x) {
+    .x  %>%
+      cor() %>%
+      ggcorrplot::ggcorrplot()
+  }))
+
+plots1 <- map2(df_with_plots$plot, df_with_plots$Plant_gen_sp, ~(.x + labs(title = .y)))
+
[…]

### 2022-07-13 models.R
.

@@ -1,180 +1,0 @@
-
-
-library(tidyverse)
-#install.packages("broom.mixed")
-library(broom.mixed)
-library(broom)
-#install.packages("lmerTest")
-library(lmerTest)
-library(dplyr)
-
-
-
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
-str(Pollinator_Plant)
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-
-# correlation
-a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
-a <- mutate_all(a, ~replace(., is.na(.), 0))
-
-a_cor <- a %>%
-  group_by(Plant_gen_sp) %>%
-  do(cormat = cor(select(., -matches("Plant_gen_sp")))) 
-
-a_cor[[2]]
-
-list_1 <- a_cor[[2]]
-
-a_cor[[1]]
-
-v <- a_cor[[1]]
-str(v)
-names(list_1) <- v
-
-str(list_1)
-data2 <- do.call(rbind.data.frame, list_1)
-
-corre<-data2 %>%
-mutate(newcolum = rownames(data2))%>%
-separate(newcolum, into=c('species', 'rows'), extra = "merge", sep = "\\.")%>%
-select(species, rows,everything())  %>%
-remove_rownames() %>%
-  mutate(species = replace(species, duplicated(species), ""))
-
-
-#corrplot 
-a %>%
-  group_by(Plant_gen_sp) %>%
-  group_map(~ corrplot::corrplot(cor(select(.x, where(is.numeric)),
-  use = "complete.obs"),method="number",type="upper",
-  tl.cex=0.8,title = first(.x$Plant_gen_sp)), .keep = TRUE)
-   
-
-library(tidyverse)
-library(patchwork)
[…]

### 2022-07-14 script/models.R
correlation and models

@@ -9,11 +9,9 @@ library(lmerTest)
 library(dplyr)
 
 
-
 Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
 str(Pollinator_Plant)
 Pollinator_Plant<-Pollinator_Plant[,-1]
-
 
 
 #Species out
@@ -65,7 +63,6 @@ a %>%
   tl.cex=0.8,title = first(.x$Plant_gen_sp)), .keep = TRUE)
    
 
-library(tidyverse)
 library(patchwork)
 library(ggcorrplot)
 
@@ -75,14 +72,22 @@ df_with_plots <- a %>%
   mutate(plot = map(data, function(.x) {
     .x  %>%
       cor() %>%
-      ggcorrplot::ggcorrplot()
+      ggcorrplot::ggcorrplot(show.diag = F, type="lower",lab=TRUE)
   }))
 
 plots1 <- map2(df_with_plots$plot, df_with_plots$Plant_gen_sp, ~(.x + labs(title = .y)))
 
-plots1[[1]] + plots1[[2]] + plots1[[2]] + plots1[[2]]
+install.packages("ggpubr")
+library(ggpubr)
+
+plots1[[1]] + plots1[[2]] + plots1[[3]] + plots1[[4]]+plots1[[5]]+plots1[[6]]+plots1[[7]]+
+  plots1[[8]]+plots1[[9]]+plots1[[10]]+plots1[[11]]+plots1[[12]]
 
 
+ggarrange(plots1[[1]], plots1[[2]], plots1[[3]], plots1[[4]], ncol=2, nrow=2, common.legend = TRUE, legend="bottom")
+
+
+#df_with_plots$plot %>% wrap_plots(ncol = 2)
 
 #Models _ Seed numbers 
 
@@ -174,7 +179,81 @@ ta_f3<-Pollinator_Plant %>%
   ungroup()
 
 
+#########
+# Lavandula species together (L.peduncalata (49 obs) and L.stoechas (24 obs))
+
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+#seed number
+# richness
+ta_seed_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
[…]

### 2022-07-14 Models.Rmd
correlation and summary of models

@@
 
+header-includes:
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
 ---
+
+Data base from beefun: plant individuals per sites (13 sites) for five years (2015-2019). Data base has 400 observation, only matching individuals, some with no pollinator frequency (16 observations).
+Fruit proportions, seed numbers and seed weight are calculated for each plant individual per plant species in site and year.
+Richness, visitation rate and frequency of pollinators are also calculated for plant individual per plant species.
+16 plant species but 4 are removed because they are present only one site.
 
@@
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE, figures-side, out.width="100%",fig.fullwidth=TRUE}
+\blandscape
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, figures-side,fig.height = 13,fig.width=18, out.width="100%",fig.fullwidth=TRUE}
 
 library(tidyverse)
-#install.packages("broom.mixed")
 library(broom.mixed)
 library(broom)
-#install.packages("lmerTest")
 library(lmerTest)
@@
 library(ggcorrplot)
+library(ggpubr)
 
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
 Pollinator_Plant<-Pollinator_Plant[,-1]
@@
       cor() %>%
-      ggcorrplot::ggcorrplot()
+      ggcorrplot::ggcorrplot(show.diag = F, type="lower",lab=TRUE,lab_size=4,tl.cex=12)
   }))
@@
 
-plots1[[1]] + plots1[[2]] + plots1[[2]] + plots1[[2]]
+ggarrange(plots1[[1]], plots1[[2]], plots1[[3]], plots1[[4]],plots1[[5]],plots1[[6]], plots1[[7]], plots1[[8]], plots1[[9]], plots1[[10]],plots1[[11]],plots1[[12]], ncol=4, nrow=3, common.legend = TRUE, legend="right")
 
 ```
+
+\elandscape
 
@@
 \newpage
-## Visitation rate
+## Frequency
 
@@
 ```
+
+\newpage
+
+## join together Lavandula species 
+(L.peduncalata (49 obs) and L.stoechas (24 obs))
+
+## Fruit proportion - richness
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# richnes
+ta_f_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f_la<-ta_f_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f_la<-filter(ta_f_la, !term == "sd__(Intercept)")
+
+ta_f_la %>% 
+    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Fruit proportion - visitation rate
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# visistation rate
+ta_f2_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f2_la<-ta_f2_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f2_la<-filter(ta_f2_la, !term == "sd__(Intercept)")
+
+ta_f2_la %>% 
+    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f2_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Fruit proportion - frequency
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# frequency
+ta_f3_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f3_la<-ta_f3_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f3_la<-filter(ta_f3_la, !term == "sd__(Intercept)")
+
+ta_f3_la %>% 
+    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f3_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed number - richness
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# richness
+ta_seed_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed_la<-ta_seed_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed_la<-filter(ta_seed_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed number - visitation rate
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# visistation rate
+ta_seed2_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed2_la<-ta_seed2_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed2_la<-filter(ta_seed2_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed2_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed2_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed number - frequency
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# Frequency
+ta_seed3_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed3_la<-ta_seed3_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed3_la<-filter(ta_seed3_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed3_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed3_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed weight - richness
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# richnes
+ta_weight_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~richness+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight_la<-ta_weight_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight_la<-filter(ta_weight_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed weight - visitation rate
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# visistation rate
+ta_weight2_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~visitatio_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight2_la<-ta_weight2_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight2_la<-filter(ta_weight2_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight2_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight2_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed weight - frequency
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# frequency
+ta_weight3_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Frequency+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight3_la<-ta_weight3_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight3_la<-filter(ta_weight3_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight3_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight3_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```

### 2022-07-20 Models.Rmd
correlation and summary of models

@@
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-library(knitr)
-library(dplyr)
-library(kableExtra)
-library(tidyverse)
-#install.packages("broom.mixed")
-library(broom.mixed)
-library(broom)
-#install.packages("lmerTest")
-library(lmerTest)
 
@@
 column_spec(6, bold = ifelse(ta_f2$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Hymenoptera visitation
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+#Models _ fruit proportion 
+# hymenoptera visitation
+ta_f4<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f4<-ta_f4 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f4<-filter(ta_f4, !term == "sd__(Intercept)")
+
+ta_f4 %>% 
+    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f4$p.value < 0.05, T, F) )%>%
   kable_styling(position="center", latex_option="hold_position")
@@
 \newpage
+## Hymenoptera visitation
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# hymenoptera visitation
+ta_seed4<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed4<-ta_seed4 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed4<-filter(ta_seed4, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed4 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed4$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
 ## Frequency
@@
 column_spec(7, bold = ifelse(ta_weight2$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Hymenoptera visitation
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+#Models _ Seed weight 
+# Hymenoptera visitation
+ta_weight4<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight4<-ta_weight4 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight4<-filter(ta_weight4, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight4 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight4$p.value < 0.05, T, F) )%>%
   kable_styling(position="center", latex_option="hold_position")
@@
 
+## Fruit proportion - hymenoptera visitation
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# hymenoptera visitation
+ta_f4_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f4_la<-ta_f4_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f4_la<-filter(ta_f4_la, !term == "sd__(Intercept)")
+
+ta_f4_la %>% 
+    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f4_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
 ## Fruit proportion - frequency
@@
 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
 # richness
@@
 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
 # visistation rate
@@
 
+## Seed number - hymenoptera visitation
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# hymenoptera visitation
+ta_seed4_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed4_la<-ta_seed4_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed4_la<-filter(ta_seed4_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed4_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed4_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
 ## Seed number - frequency
@@
 Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
 
@@
 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
 # richnes
@@
 column_spec(7, bold = ifelse(ta_weight2_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed weight - hymenoptera visitation
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# hymenoptera visitation
+ta_weight4_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight4_la<-ta_weight4_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight4_la<-filter(ta_weight4_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight4_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight4_la$p.value < 0.05, T, F) )%>%
   kable_styling(position="center", latex_option="hold_position")

### 2022-07-20 script/models.R
correlation and models

@@ -77,7 +77,7 @@ df_with_plots <- a %>%
 
 plots1 <- map2(df_with_plots$plot, df_with_plots$Plant_gen_sp, ~(.x + labs(title = .y)))
 
-install.packages("ggpubr")
+
 library(ggpubr)
 
 plots1[[1]] + plots1[[2]] + plots1[[3]] + plots1[[4]]+plots1[[5]]+plots1[[6]]+plots1[[7]]+
@@ -117,6 +117,12 @@ ta_seed3<-Pollinator_Plant %>%
   summarise(broom.mixed::tidy(model)) %>%
   ungroup()
 
+# hymenoptera visitation
+ta_seed4<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
 
 #Models _ Seed weight 
 
@@ -145,6 +151,13 @@ ta_weight3<-Pollinator_Plant %>%
   summarise(broom.mixed::tidy(model)) %>%
   ungroup()
 
+
+# Hymenoptera visitation
+ta_weight4<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
 
 #Models _ fruit proportion 
 
@@ -178,6 +191,12 @@ ta_f3<-Pollinator_Plant %>%
   summarise(broom.mixed::tidy(model)) %>%
   ungroup()
 
+# hymenoptera visitation
+ta_f4<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
 
 #########
 # Lavandula species together (L.peduncalata (49 obs) and L.stoechas (24 obs))
@@ -208,6 +227,13 @@ ta_seed3_la<-lavan_tog %>%
   summarise(broom.mixed::tidy(model)) %>%
   ungroup()
 
+# hymenoptera visitation
[…]

### 2022-07-20 script/models.R
correlation and models

@@ -89,6 +89,11 @@ ggarrange(plots1[[1]], plots1[[2]], plots1[[3]], plots1[[4]], ncol=2, nrow=2, co
 
 #df_with_plots$plot %>% wrap_plots(ncol = 2)
 
+
+# replace NAs by 0
+Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
+
+
 #Models _ Seed numbers 
 
 require("lattice")

### 2022-07-27 script/stability.R
stability

@@ -1,0 +1,63 @@
+
+library(tidyverse)
+#install.packages("broom.mixed")
+library(broom.mixed)
+library(broom)
+#install.packages("lmerTest")
+library(lmerTest)
+library(dplyr)
+
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+str(Pollinator_Plant)
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# replace NAs by 0
+Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
+
+# fruit proportion stability for each plant species per site
+cv_1Fruit<-Pollinator_Plant %>%
+  group_by(Plant_gen_sp,Site_ID) %>%
+  summarise_at(vars(fruit_proportion),cv_1 <- function(x, ...) {
+    ( mean(x, ...)/sd(x, ...) )
+  })
+
+# seed number stability for each plant species per site
+cv_1Seed<-Pollinator_Plant %>%
+  group_by(Plant_gen_sp,Site_ID) %>%
+  summarise_at(vars(Seeds),cv_1 <- function(x, ...) {
+    ( mean(x, ...)/sd(x, ...) )
+  })
+
+#visitation rate stability for each plant species per site (all pollinators)
+cv_1pollinator<-Pollinator_Plant %>%
+  group_by(Plant_gen_sp,Site_ID) %>%
+  summarise_at(vars(visitatio_rate),cv_1 <- function(x, ...) {
+    ( mean(x, ...)/sd(x, ...) )
+  })
+
+
+#  pollinator richness for each plant species per site
+S<-aggregate(richness ~ Plant_gen_sp+Site_ID, data = Pollinator_Plant,FUN = sum)
+
+
+# join tables 
+full=full_join(cv_1Fruit, cv_1Seed, by = c('Plant_gen_sp', 'Site_ID'))%>%
[…]

### 2022-07-27 Rmd/Stability.Rmd
stability

---
title: "Stability"
output: pdf_document
date: '2022-07-27'
---

```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
library(tidyverse)
#install.packages("broom.mixed")
library(broom.mixed)
library(broom)
#install.packages("lmerTest")
library(lmerTest)
library(dplyr)
library(kableExtra)

Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
Pollinator_Plant<-Pollinator_Plant[,-1]

#Species out
spp_out <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  summarise(Unique_Id = n_distinct(Site_ID)) %>%
  filter(Unique_Id == 1) %>%
  select(Plant_gen_sp) %>% pull(Plant_gen_sp)

#Data with species in more than 1 site
Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)

# replace NAs by 0
Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))

# fruit proportion stability for each plant species per site
cv_1Fruit<-Pollinator_Plant %>%
  group_by(Plant_gen_sp,Site_ID) %>%
  summarise_at(vars(fruit_proportion),cv_1 <- function(x, ...) {
    ( mean(x, ...)/sd(x, ...) )
  })

# seed number stability for each plant species per site
cv_1Seed<-Pollinator_Plant %>%
  group_by(Plant_gen_sp,Site_ID) %>%
  summarise_at(vars(Seeds),cv_1 <- function(x, ...) {
    ( mean(x, ...)/sd(x, ...) )
  })

#visitation rate stability for each plant species per site (all pollinators)
cv_1pollinator<-Pollinator_Plant %>%
  group_by(Plant_gen_sp,Site_ID) %>%
  summarise_at(vars(visitatio_rate),cv_1 <- function(x, ...) {
    ( mean(x, ...)/sd(x, ...) )
  })

#  pollinator richness for each plant species per site
S<-aggregate(richness ~ Plant_gen_sp+Site_ID, data = Pollinator_Plant,FUN = sum)

# join tables 
full=full_join(cv_1Fruit, cv_1Seed, by = c('Plant_gen_sp', 'Site_ID'))%>%
  full_join (., cv_1pollinator, by=c('Plant_gen_sp', 'Site_ID')) %>%
  full_join (., S, by=c('Plant_gen_sp', 'Site_ID'))%>%
  rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds, cv_1_visitation=visitatio_rate)

full %>% 
    kable("latex",booktabs = TRUE,longtable = T,linesep = "")
```

### 2022-07-29 Rmd/Models.Rmd
correlation and models

--- 2022-07-20 Models.Rmd
@@
 
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
 Pollinator_Plant<-Pollinator_Plant[,-1]
@@
 
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# replace NAs by 0
+Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
 
@@
 
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #402 observaciones
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") #402 observaciones
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# replace NAs by 0
+Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
 
@@
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# replace NAs by 0
+Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
 
@@
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+# replace NAs by 0
+Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
+
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
 

### 2022-07-29 script/synchrony.R
synchrony

@@ -1,0 +1,84 @@
+library(tidyverse)
+#install.packages("broom.mixed")
+library(broom.mixed)
+library(broom)
+#install.packages("lmerTest")
+library(lmerTest)
+library(dplyr)
+library(reshape2)
+
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
+str(Pollinator_Plant)
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+
+focal<- read.csv("Data/focal.csv") 
+focal<-focal[,-1]
+
+#Data with species in more than 1 site
+focal = focal %>% filter(!Plant_gen_sp %in% spp_out)
+
+focal_0 <- focal[!(focal$Pollinator_gen_sp == "NA NA"),] #eliminar polinizadores NA NA
+
+
+levels(factor(focal_0$Plant_gen_sp))
+
+focal_0<-subset(focal_0, Plant_gen_sp != 'Ulex australis') #remove ulex
+
+
+plant_polli<-data.frame(focal_0[,c(1,2,6,29)])
+
+plant_polli1 <- dcast(plant_polli, formula = Site_ID + Year +Plant_gen_sp ~ Pollinator_gen_sp)
+
+
+#variance ratio
+#(Var over the Sum of abundances of all species over time/ Sum of the variance of each species over time)
+
+var_ratio <- function(x){
+  out <- (var(rowSums(x))) / (sum(apply(x, MARGIN = 2, FUN = var))) 
+  out                               
+}
+
+asy=plant_polli1%>% 
+  group_by(Plant_gen_sp,Site_ID)%>% 
+  do(var_ratio=var_ratio(.[4:139]))
+
+# Loreau & Mazancourt syncrony index
+#sum of the tempotral covariances of all species / sum of sqrt of the variances squared
+syncLM <- function(x){
+  out <- (sum(cov(x))) / (sum(sqrt(diag(cov(x))))^2)
+  out
+}
+
+asy_2=plant_polli1%>% 
[…]

### 2022-09-08 Rmd/Stability.Rmd
stability
stability analysis

@@
 date: '2022-07-27'
+
+header-includes:
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
 ---
+
+For each plant species per site, stability (inverse of the coefficient of variation) of the visitation rate of pollinators (visitation rate calculated like frequency/flower abundance) and also of the fruit proportion and the seed numbers were calculated.
+Pollinator richness was obtained and furthermore, the log of variance ratio (Lepš et al., 2018) and Loreau & Mazancourt syncrony index were calculated.
+
+Positive values of log var ratio signify synchronization, negative values indicate compensatory dynamics (Lepš et al., 2018).
+Loreau & Mazancourt index is standardized between 0 (perfect asynchrony) and 1 (perfect synchrony).
+
+note: NA= one data per year
 
@@
 library(kableExtra)
+library(reshape2)
 
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") #400 observaciones
 Pollinator_Plant<-Pollinator_Plant[,-1]
@@
     ( mean(x, ...)/sd(x, ...) )
-  })
+  })%>%
+  ungroup()
 
@@
 
+## Synchrony ###
+
+focal<- read.csv("../Data/focal.csv") 
+focal<-focal[,-1]
+
+focal_0 <- focal[!(focal$Pollinator_gen_sp == "NA NA"),] #eliminar polinizadores NA NA
+
+#Data with species in more than 1 site
+focal_0 = focal_0 %>% filter(!Plant_gen_sp %in% spp_out)
+
+focal_0<-subset(focal_0, Plant_gen_sp != 'Ulex australis') #remove ulex
+plant_polli<-data.frame(focal_0[,c(1,2,6,29,30)])
+
+df.result <- left_join(Pollinator_Plant, plant_polli, c('Plant_gen_sp', 'Site_ID','Year','plant_id'))
+df.result1<-data.frame(df.result[,c(1,2,3,4,25)])
+df.result2 <- dcast(df.result, formula = Site_ID + Year +plant_id+Plant_gen_sp ~ Pollinator_gen_sp)
+
+# log variance ratio (Lepš et al., 2018)
+#log (Var over the Sum of abundances of all species over time/ Sum of the variance of each species over time)
+# Positive values of log var ratio signify synchronization, negative values indicate compensatory dynamics
+
+log_VR <- function(x){
+  out <- log((var(rowSums(x))) / (sum(apply(x, MARGIN = 2, FUN = var)))) 
+  out                               
+}
+
+syn=df.result2%>% 
+  group_by(Plant_gen_sp,Site_ID)%>% 
+  do(log_VR=log_VR(.[5:129]))
+
+# Loreau & Mazancourt syncrony index
+#sum of the tempotral covariances of all species / sum of sqrt of the variances squared
+syncLM <- function(x){
+  out <- (sum(cov(x))) / (sum(sqrt(diag(cov(x))))^2)
+  out
+}
+
+syn_2=df.result2%>% 
+  group_by(Plant_gen_sp,Site_ID)%>% 
+  do(syncLM=syncLM(.[5:129]))
+
+# join tables 
 # join tables 
@@
   full_join (., S, by=c('Plant_gen_sp', 'Site_ID'))%>%
+  full_join (., syn, by=c('Plant_gen_sp', 'Site_ID'))%>%
+  full_join (., syn_2, by=c('Plant_gen_sp', 'Site_ID'))%>%
   rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds, cv_1_visitation=visitatio_rate)
 
+full$log_VR <- unlist(full$log_VR)
+full$syncLM <- unlist(full$syncLM)
+
 full %>% 
-    kable("latex",booktabs = TRUE,longtable = T,linesep = "")
+    kable("latex",booktabs = TRUE, digits =  4,longtable = T,linesep = "")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
 ```
+
+\newpage
+
+\blandscape
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, figures-side,fig.height = 13,fig.width=18, out.width="100%",fig.fullwidth=TRUE}
+
+library(tidyverse)
+library(broom.mixed)
+library(broom)
+library(lmerTest)
+library(dplyr)
+library(knitr)
+library(kableExtra)
+library(patchwork)
+library(ggcorrplot)
+library(ggpubr)
+
+a<-full %>% select(Plant_gen_sp,cv_1_fruit, cv_1_seed,cv_1_visitation,richness,log_VR,syncLM)
+
+## Replace Inf and -Inf with NA
+a[is.na(a) | a == "Inf"] <- NA 
+a[is.na(a) | a == "-Inf"] <- NA 
+a <- mutate_all(a, ~replace(., is.na(.), 0))
+
+df_with_plots <- a %>%
+  group_by(Plant_gen_sp) %>%
+  nest() %>%
+  mutate(plot = map(data, function(.x) {
+    .x  %>%
+      cor() %>%
+      ggcorrplot::ggcorrplot(show.diag = F, type="lower",lab=TRUE,lab_size=4,tl.cex=12)
+  }))
+
+plots1 <- map2(df_with_plots$plot, df_with_plots$Plant_gen_sp, ~(.x + labs(title = .y)))
+
+ggarrange(plots1[[1]], plots1[[2]], plots1[[3]], plots1[[4]],plots1[[5]],plots1[[6]], plots1[[7]], plots1[[8]], plots1[[9]], plots1[[10]],plots1[[11]],plots1[[12]], ncol=4, nrow=3, common.legend = TRUE, legend="right")
+
+```
+
+\elandscape
+
+\newpage
+
+Data with species in more than 3 sites. I removed 4 plant species (A.fistulosus, C.libanotis, c.monspeliensis, T.fructicans)
+
+We analysed whether the visitation rate stability is affected by richness and synchrony for each plant species separately.
+
+A) richness + log VR
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+library(tidyr)
+
+sp_out2=full %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id <= 3) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 3 sites
+full1 = full %>% filter(!Plant_gen_sp %in% sp_out2)
+
+## Replace Inf and -Inf with NA
+full1[is.na(full1) | full1 == "Inf"] <- NA 
+full1[is.na(full1) | full1 == "-Inf"] <- NA
+
+sta_polli<-full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+sta_polli<-sta_polli %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_polli %>% 
+    kable("latex",booktabs = TRUE, digits =  4, linesep = c("","","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_polli$p.value < 0.05| is.na(sta_polli$p.value), T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+Goodness of fit measures, p-values for hypothesis tests on residuals, and model convergence information.
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+library(tidyr)
+
+#goodness of fit measures, p-values for hypothesis tests on residuals, or model convergence information.
+sta_polli_glance<-full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table<-sta_polli_glance %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Salvia rosmarinus', 'S.rosmarinus', Plant_gen_sp))
+
+table %>% 
+    kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+library(ggeffects)
+library(patchwork)
+
+sta_polli2 <- full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "richness"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)))
+
+p1=sta_polli2$plots[[1]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+labs(x = "Richness",y="visitation rate stability",subtitle = "C.crispus")+ 
+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli2$plots[[2]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+labs(x = "Richness",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli2$plots[[3]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+labs(x = "Richness",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=sta_polli2$plots[[4]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+labs(x = "Richness",y="visitation rate stability",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli2$plots[[5]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+labs(x = "Richness",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli2$plots[[6]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+labs(x = "Richness",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_polli2$plots[[7]] + geom_point(data = na.omit( full1 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+labs(x = "Richness",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot (cv_1_visitation~log_VR)
+sta_polli2.1 <- full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)))
+
+p1=sta_polli2.1$plots[[1]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log VR",y="visitation rate stability",subtitle = "C.crispus")+
+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli2.1$plots[[2]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log VR",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli2.1$plots[[3]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log VR",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=sta_polli2.1$plots[[4]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log VR",y="visitation rate stability",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli2.1$plots[[5]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log VR",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli2.1$plots[[6]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log VR",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_polli2.1$plots[[7]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log VR",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7
+
+```
+
+\newpage
+
+B) richness + Lorea and Mazancourt index
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#model 2: richness + Lorea and Mazancourt index
+sta_polli3<-full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+syncLM,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+sta_polli3<-sta_polli3 %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_polli3 %>% 
+    kable("latex",booktabs = TRUE, digits =  4, linesep = c("","","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_polli3$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures, p-values for hypothesis tests on residuals, or model convergence information.
+sta_polli_glance3<-full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+syncLM,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table2<-sta_polli_glance3 %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Salvia rosmarinus', 'S.rosmarinus', Plant_gen_sp))
+
+table2 %>% 
+    kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model2 plot (cv_1_visitation~richness)
+sta_polli3.1 <- full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+syncLM,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "richness"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)))
+
+p1=sta_polli3.1$plots[[1]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Richness",y="visitation rate stability",subtitle = "C.crispus")+
+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli3.1$plots[[2]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Richness",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli3.1$plots[[3]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Richness",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=sta_polli3.1$plots[[4]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Richness",y="visitation rate stability",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli3.1$plots[[5]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Richness",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli3.1$plots[[6]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Richness",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_polli3.1$plots[[7]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Richness",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+# model2 plot (cv_1_visitation~syncLM)
+sta_polli3.2 <- full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+syncLM,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)))
+
+p1=sta_polli3.2$plots[[1]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Lorea and Mazancourt index",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli3.2$plots[[2]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Lorea and Mazancourt index",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli3.2$plots[[3]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Lorea and Mazancourt index",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=sta_polli3.2$plots[[4]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Lorea and Mazancourt index",y="visitation rate stability",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli3.2$plots[[5]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Lorea and Mazancourt index",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli3.2$plots[[6]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Lorea and Mazancourt index",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_polli3.2$plots[[7]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "Lorea and Mazancourt index",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7
+```
+
+\newpage
+
+We analysed the relationship between fruit proportion stability and visitation rate stability
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+# Relationship between fruit proportion stability and visitation rate stability
+
+sta_fruit<-full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+sta_fruit<-sta_fruit %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_fruit %>% 
+    kable("latex",booktabs = TRUE, digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_fruit$p.value < 0.05| is.na(sta_fruit$p.value), T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures, p-values for hypothesis tests on residuals, or model convergence information.
+sta_fruit_glance<-full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table3<-sta_fruit_glance %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Salvia rosmarinus', 'S.rosmarinus', Plant_gen_sp))
+
+table3 %>% 
+    kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot (fruit proportion stability and visitation rate stability)
+sta_fruit.1 <- full1 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "cv_1_visitation"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)))
+
+p1=sta_fruit.1$plots[[1]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_fruit.1$plots[[2]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_fruit.1$plots[[3]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_fruit.1$plots[[5]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_fruit.1$plots[[6]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_fruit.1$plots[[7]] + geom_point(data = full1 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=sta_fruit.1$plots[[8]] + geom_point(data = na.omit(full1 %>% filter(Plant_gen_sp == "Salvia rosmarinus")), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6+p7+p8
+```

### 2022-09-08 script/stability.R
stability analysis

@@ -6,6 +6,11 @@ library(broom)
 #install.packages("lmerTest")
 library(lmerTest)
 library(dplyr)
+library(reshape2)
+library(tidyr)
+library(ggplot2)
+#install.packages("ggeffects")
+library(ggeffects)
 
 
 Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
@@ -27,27 +32,38 @@ Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
 # replace NAs by 0
 Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
 
+
+## Stability ##
+
 # fruit proportion stability for each plant species per site
 cv_1Fruit<-Pollinator_Plant %>%
   group_by(Plant_gen_sp,Site_ID) %>%
   summarise_at(vars(fruit_proportion),cv_1 <- function(x, ...) {
     ( mean(x, ...)/sd(x, ...) )
-  })
+  })%>%
+  ungroup()
+
+
 
 # seed number stability for each plant species per site
 cv_1Seed<-Pollinator_Plant %>%
   group_by(Plant_gen_sp,Site_ID) %>%
   summarise_at(vars(Seeds),cv_1 <- function(x, ...) {
     ( mean(x, ...)/sd(x, ...) )
-  })
+  })%>%
+  ungroup()
+
 
 #visitation rate stability for each plant species per site (all pollinators)
 cv_1pollinator<-Pollinator_Plant %>%
   group_by(Plant_gen_sp,Site_ID) %>%
   summarise_at(vars(visitatio_rate),cv_1 <- function(x, ...) {
     ( mean(x, ...)/sd(x, ...) )
-  })
+  })%>%
+  ungroup()
 
+
+## Richness ##
 
 #  pollinator richness for each plant species per site
 S<-aggregate(richness ~ Plant_gen_sp+Site_ID, data = Pollinator_Plant,FUN = sum)
@@ -60,4 +76,368 @@ full=full_join(cv_1Fruit, cv_1Seed, by = c('Plant_gen_sp', 'Site_ID'))%>%
   rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds, cv_1_visitation=visitatio_rate)
 
 
+## Synchrony ###
+
+focal<- read.csv("Data/focal.csv") 
+focal<-focal[,-1]
+
+
[…]

### 2022-09-08 script/synchrony.R
.

@@ -1,84 +1,0 @@
-library(tidyverse)
-#install.packages("broom.mixed")
-library(broom.mixed)
-library(broom)
-#install.packages("lmerTest")
-library(lmerTest)
-library(dplyr)
-library(reshape2)
-
-
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
-str(Pollinator_Plant)
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-
-focal<- read.csv("Data/focal.csv") 
-focal<-focal[,-1]
-
-#Data with species in more than 1 site
-focal = focal %>% filter(!Plant_gen_sp %in% spp_out)
-
-focal_0 <- focal[!(focal$Pollinator_gen_sp == "NA NA"),] #eliminar polinizadores NA NA
-
-
-levels(factor(focal_0$Plant_gen_sp))
-
-focal_0<-subset(focal_0, Plant_gen_sp != 'Ulex australis') #remove ulex
-
-
-plant_polli<-data.frame(focal_0[,c(1,2,6,29)])
-
-plant_polli1 <- dcast(plant_polli, formula = Site_ID + Year +Plant_gen_sp ~ Pollinator_gen_sp)
-
-
-#variance ratio
-#(Var over the Sum of abundances of all species over time/ Sum of the variance of each species over time)
-
-var_ratio <- function(x){
-  out <- (var(rowSums(x))) / (sum(apply(x, MARGIN = 2, FUN = var))) 
-  out                               
-}
-
-asy=plant_polli1%>% 
-  group_by(Plant_gen_sp,Site_ID)%>% 
-  do(var_ratio=var_ratio(.[4:139]))
-
-# Loreau & Mazancourt syncrony index
-#sum of the tempotral covariances of all species / sum of sqrt of the variances squared
-syncLM <- function(x){
-  out <- (sum(cov(x))) / (sum(sqrt(diag(cov(x))))^2)
-  out
-}
-
-asy_2=plant_polli1%>% 
[…]

### 2022-09-14 Rmd/Stability.Rmd
stability analysis

--- 2022-07-27 Rmd/Stability.Rmd
@@
 date: '2022-07-27'
+
+header-includes:
+- \usepackage{pdflscape}
+- \newcommand{\blandscape}{\begin{landscape}}
+- \newcommand{\elandscape}{\end{landscape}}
 ---
+
+For each plant species per site, stability (inverse of the coefficient of variation) of the visitation rate of pollinators (visitation rate calculated like frequency/flower abundance) and also of the fruit proportion and the seed numbers were calculated.
+Total of pollinator richness (sum) was obtained and furthermore, the log of variance ratio (Lepš et al., 2018) and Loreau & Mazancourt syncrony index were calculated.
+
+Positive values of log var ratio signify synchronization, negative values indicate compensatory dynamics (Lepš et al., 2018).
+Loreau & Mazancourt index is standardized between 0 (perfect asynchrony) and 1 (perfect synchrony).
+
+note: NA= one data per year
 
@@
 
-# fruit proportion stability for each plant species per site
-cv_1Fruit<-Pollinator_Plant %>%
+# datos sin plant_id (mean de las variables porque hay plantas con 2 indv, otras 3, etc)
+pol_plant2=Pollinator_Plant %>%
+  group_by(Site_ID,Year, Plant_gen_sp) %>%
+  summarise_if(is.numeric, mean)
+
+# datos por año y sitio para cada sp de planta (sin plant_id)
+cv_1Fruit2<-pol_plant2 %>%
   group_by(Plant_gen_sp,Site_ID) %>%
@@
     ( mean(x, ...)/sd(x, ...) )
-  })
+  })%>%
+  ungroup()
 
-# seed number stability for each plant species per site
-cv_1Seed<-Pollinator_Plant %>%
+# datos por año y sitio para cada sp de planta (sin plant_id)
+cv_1Seed2<-pol_plant2 %>%
   group_by(Plant_gen_sp,Site_ID) %>%
@@
     ( mean(x, ...)/sd(x, ...) )
-  })
+  })%>%
+  ungroup()
 
-#visitation rate stability for each plant species per site (all pollinators)
-cv_1pollinator<-Pollinator_Plant %>%
+# datos por año y sitio para cada sp de planta (sin plant_id)
+cv_1pollinator2<-pol_plant2 %>%
   group_by(Plant_gen_sp,Site_ID) %>%
@@
     ( mean(x, ...)/sd(x, ...) )
-  })
+  })%>%
+  ungroup()
 
-#  pollinator richness for each plant species per site
-S<-aggregate(richness ~ Plant_gen_sp+Site_ID, data = Pollinator_Plant,FUN = sum)
+#suma de la riqueza media por año para cada plant sp y sitio
+S2<-aggregate(richness ~ Plant_gen_sp+Site_ID, data = pol_plant2,FUN = sum)
+
+## Synchrony ###
+
+focal<- read.csv("../Data/focal.csv") 
+focal<-focal[,-1]
+
+focal_0 <- focal[!(focal$Pollinator_gen_sp == "NA NA"),] #eliminar polinizadores NA NA
+
+#Data with species in more than 1 site
+focal_0 = focal_0 %>% filter(!Plant_gen_sp %in% spp_out)
+
+focal_0<-subset(focal_0, Plant_gen_sp != 'Ulex australis') #remove ulex
+plant_polli<-data.frame(focal_0[,c(1,2,6,29,30)])
+
+df.result <- left_join(Pollinator_Plant, plant_polli, c('Plant_gen_sp', 'Site_ID','Year','plant_id'))
+df.result1<-data.frame(df.result[,c(1,2,3,4,25)])
+df.result2 <- dcast(df.result, formula = Site_ID + Year +plant_id+Plant_gen_sp ~ Pollinator_gen_sp)
+
+# sin plant_id
+prueba=df.result2 %>%
+  group_by(Site_ID,Year, Plant_gen_sp) %>%
+  summarise_if(is.numeric, sum)
+
+# log variance ratio (Lepš et al., 2018)
+#log (Var over the Sum of abundances of all species over time/ Sum of the variance of each species over time)
+# Positive values of log var ratio signify synchronization, negative values indicate compensatory dynamics
+
+log_VR <- function(x){
+  out <- log((var(rowSums(x))) / (sum(apply(x, MARGIN = 2, FUN = var)))) 
+  out                               
+}
+
+# un dato por sp planta, sitio y año (sin plant_id)
+syn_2=prueba%>% 
+  group_by(Plant_gen_sp,Site_ID)%>% 
+  do(log_VR=log_VR(.[4:127]))
+
+# Loreau & Mazancourt syncrony index
+#sum of the tempotral covariances of all species / sum of sqrt of the variances squared
+syncLM <- function(x){
+  out <- (sum(cov(x))) / (sum(sqrt(diag(cov(x))))^2)
+  out
+}
+
+# un dato por sp planta, sitio y año (sin plant_id)
+syn_LM2=prueba%>% 
+  group_by(Plant_gen_sp,Site_ID)%>% 
+  do(syncLM=syncLM(.[4:127]))
 
 # join tables 
-full=full_join(cv_1Fruit, cv_1Seed, by = c('Plant_gen_sp', 'Site_ID'))%>%
-  full_join (., cv_1pollinator, by=c('Plant_gen_sp', 'Site_ID')) %>%
-  full_join (., S, by=c('Plant_gen_sp', 'Site_ID'))%>%
+full2=full_join(cv_1Fruit2, cv_1Seed2, by = c('Plant_gen_sp', 'Site_ID'))%>%
+  full_join (., cv_1pollinator2, by=c('Plant_gen_sp', 'Site_ID')) %>%
+  full_join (., S2, by=c('Plant_gen_sp', 'Site_ID'))%>%
+  full_join (., syn_2, by=c('Plant_gen_sp', 'Site_ID'))%>%
+  full_join (., syn_LM2, by=c('Plant_gen_sp', 'Site_ID'))%>%
   rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds, cv_1_visitation=visitatio_rate)
 
-full %>% 
-    kable("latex",booktabs = TRUE,longtable = T,linesep = "")
+full2$log_VR <- unlist(full2$log_VR)
+full2$syncLM <- unlist(full2$syncLM)
+
+full2 %>% 
+    kable("latex",booktabs = TRUE, digits =  4,longtable = T,linesep = "")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
 ```
+
+Correlation 
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+tr2<-full2 %>% select(cv_1_fruit, cv_1_seed,cv_1_visitation,richness)
+
+## Replace Inf and -Inf with NA
+tr2[is.na(tr2) | tr2 == "Inf"] <- 0 
+tr2[is.na(tr2) | tr2 == "-Inf"] <- 0
+
+tr2 <- mutate_all(tr2, ~replace(., is.na(.), 0))
+
+cr=cor(tr2)
+
+cr %>% 
+    kable("latex",booktabs = TRUE, digits =  4)
+
+```
+
+\newpage
+
+\blandscape
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, figures-side,fig.height = 13,fig.width=18, out.width="100%",fig.fullwidth=TRUE}
+
+library(tidyverse)
+library(broom.mixed)
+library(broom)
+library(lmerTest)
+library(dplyr)
+library(knitr)
+library(kableExtra)
+library(patchwork)
+library(ggcorrplot)
+library(ggpubr)
+
+# correlacion con nuevos calculos (full2 = sin plant_id)
+b<-full2 %>% select(Plant_gen_sp,cv_1_fruit, cv_1_seed,cv_1_visitation,richness,log_VR,syncLM)
+
+## Replace Inf and -Inf with NA
+b[is.na(b) | b == "Inf"] <- NA 
+b[is.na(b) | b == "-Inf"] <- NA
+
+b <- mutate_all(b, ~replace(., is.na(.), 0))
+
+df_with_plotsb <- b %>%
+  group_by(Plant_gen_sp) %>%
+  nest() %>%
+  mutate(plot = map(data, function(.x) {
+    .x  %>%
+      cor() %>%
+      ggcorrplot::ggcorrplot(show.diag = F, type="lower",lab=TRUE)
+  }))
+
+plots1 <- map2(df_with_plotsb$plot, df_with_plotsb$Plant_gen_sp, ~(.x + labs(title = .y)))
+
+ggarrange(plots1[[1]], plots1[[2]], plots1[[3]], plots1[[4]],plots1[[5]],plots1[[6]], plots1[[7]], plots1[[8]], plots1[[9]], plots1[[10]],plots1[[11]],plots1[[12]], ncol=4, nrow=3, common.legend = TRUE, legend="right")
+
+```
+
+\elandscape
+
+\newpage
+
+Data with species in more than 3 sites. I removed 4 plant species (A.fistulosus, C.libanotis, c.monspeliensis, T.fructicans)
+
+Salvia rosmarinus = only one year per site (remove)
+
+We analysed the relationship between fruit proportion stability and visitation rate stability
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+# 4 plant species are in 2-3 site (A.fistulosus, C.libanotis, c.monspeliensis, T.fructicans)
+
+# eliminar plant species en new data
+sp_out2=full2 %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id <= 3) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in more than 3 sites
+full_2 = full2 %>% filter(!Plant_gen_sp %in% sp_out2)
+
+# Salvia rosmarinus solo un dato por año(estabilidad y sincronia =NA). Eliminar
+
+full_2<-subset(full_2, Plant_gen_sp != 'Salvia rosmarinus')
+
+## Replace Inf and -Inf with NA
+full_2[is.na(full_2) | full_2 == "Inf"] <- NA 
+full_2[is.na(full_2) | full_2 == "-Inf"] <- NA
+
+sta_fruit<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+sta_fruit<-sta_fruit %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_fruit %>% 
+    kable("latex",booktabs = TRUE, digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_fruit$p.value < 0.05| is.na(sta_fruit$p.value), T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+```
+
+Goodness of fit measures, p-values for hypothesis tests on residuals, and model convergence information.
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures, p-values for hypothesis tests on residuals, or model convergence information.
+sta_fruit_glance<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table3<-sta_fruit_glance %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table3 %>% 
+    kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot (fruit proportion stability and visitation rate stability)
+sta_fruit.1 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_fruit~cv_1_visitation,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "cv_1_visitation"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_fruit.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_fruit.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_fruit.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_fruit.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_fruit.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_fruit.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  cv_1_visitation, y = cv_1_fruit),shape=20)+ 
+  labs(x = "visitation rate stability",y="fruit proportion stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6+p7
+
+```
+
+\newpage
+
+We analysed the relationship between seed number stability and visitation rate stability
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+# Relationship between seed number stability and visitation rate stability
+
+sta_seed<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_seed~cv_1_visitation,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+sta_seed<-sta_seed %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_seed %>% 
+kable("latex",booktabs = TRUE, digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_seed$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+
+sta_seed_glance<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_seed~cv_1_visitation,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table4<-sta_seed_glance %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Salvia rosmarinus', 'S.rosmarinus', Plant_gen_sp))
+
+table4 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot (seed number stability and visitation rate stability)
+sta_seed.1 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_seed~cv_1_visitation,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "cv_1_visitation"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_seed.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
+  labs(x = "visitation rate stability",y="seed number stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_seed.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
+  labs(x = "visitation rate stability",y="seed number stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_seed.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
+  labs(x = "visitation rate stability",y="seed number stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=sta_seed.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
+  labs(x = "visitation rate stability",y="seed number stability",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_seed.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
+  labs(x = "visitation rate stability",y="seed number stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_seed.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
+  labs(x = "visitation rate stability",y="seed number stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_seed.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  cv_1_visitation, y = cv_1_seed),shape=20)+ 
+  labs(x = "visitation rate stability",y="seed number stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7
+```
+
+\newpage
+
+Relationship between richness-synchrony with different synchrony indice.
+
+A- Richness ~ log VR
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+rich<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(richness~log_VR,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+rich<-rich %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+rich %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(rich$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+
+rich_glance<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(richness~log_VR,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table5<-rich_glance %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table5 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+rich.1 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(richness~log_VR,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=rich.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = richness),shape=20)+ 
+  labs(x = "log_VR",y="richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = richness),shape=20)+ 
+  labs(x = "log_VR",y="richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = richness),shape=20)+ 
+  labs(x = "log_VR",y="richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=rich.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = richness),shape=20)+ 
+  labs(x = "log_VR",y="richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = richness),shape=20)+ 
+  labs(x = "log_VR",y="richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = richness),shape=20)+ 
+  labs(x = "log_VR",y="richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=rich.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = richness),shape=20)+ 
+  labs(x = "log_VR",y="richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7
+```
+
+\newpage
+A- Richness ~ Loreau & Mazancourt syncrony index
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+rich2<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(richness~syncLM,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+rich2<-rich2 %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+rich2 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(rich2$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+rich2_glance<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(richness~syncLM,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table6<-rich2_glance %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table6 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+rich.2 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(richness~syncLM,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=rich.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = richness),shape=20)+ 
+  labs(x = "syncLM",y="richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = richness),shape=20)+ 
+  labs(x = "syncLM",y="richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = richness),shape=20)+ 
+  labs(x = "syncLM",y="richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = richness),shape=20)+ 
+  labs(x = "syncLM",y="richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = richness),shape=20)+ 
+  labs(x = "syncLM",y="richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = richness),shape=20)+ 
+  labs(x = "syncLM",y="richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = richness),shape=20)+ 
+  labs(x = "syncLM",y="richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7
+```
+
+\newpage
+
+We analysed whether the visitation rate stability is affected by richness and synchrony for each plant species separately
+
+A) richness + log VR
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+#model 1: richness + log VR
+sta_polli<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+sta_polli<-sta_polli %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_polli %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_polli$p.value < 0.05| is.na(sta_polli$p.value), T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+sta_polli_glance<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table7<-sta_polli_glance %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table7 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot (cv_1_visitation~richness)
+sta_polli2 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "richness"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "richness",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli2$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "richness",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli2$plots[[3]] + geom_point(data = na.omit (full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "richness",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "richness",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
+  labs(x = "richness",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```

### 2022-09-14 script/stability.R
stability analysis

@@ -33,9 +33,16 @@ Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
 Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
 
 
+# datos sin plant_id (mean de las variables porque hay plantas con 2 indv, otras 3, etc)
+pol_plant2=Pollinator_Plant %>%
+  group_by(Site_ID,Year, Plant_gen_sp) %>%
+  summarise_if(is.numeric, mean)
+
+
 ## Stability ##
 
-# fruit proportion stability for each plant species per site
+# fruit proportion stability for each plant species per site #
+# con colum plant_id
 cv_1Fruit<-Pollinator_Plant %>%
   group_by(Plant_gen_sp,Site_ID) %>%
   summarise_at(vars(fruit_proportion),cv_1 <- function(x, ...) {
@@ -44,8 +51,16 @@ cv_1Fruit<-Pollinator_Plant %>%
   ungroup()
 
 
+# datos por año y sitio para cada sp de planta (sin plant_id)
+cv_1Fruit2<-pol_plant2 %>%
+  group_by(Plant_gen_sp,Site_ID) %>%
+  summarise_at(vars(fruit_proportion),cv_1 <- function(x, ...) {
+    ( mean(x, ...)/sd(x, ...) )
+  })%>%
+  ungroup()
 
-# seed number stability for each plant species per site
+
+# seed number stability for each plant species per site #
 cv_1Seed<-Pollinator_Plant %>%
   group_by(Plant_gen_sp,Site_ID) %>%
   summarise_at(vars(Seeds),cv_1 <- function(x, ...) {
@@ -53,9 +68,24 @@ cv_1Seed<-Pollinator_Plant %>%
   })%>%
   ungroup()
 
+# datos por año y sitio para cada sp de planta (sin plant_id)
+cv_1Seed2<-pol_plant2 %>%
+  group_by(Plant_gen_sp,Site_ID) %>%
+  summarise_at(vars(Seeds),cv_1 <- function(x, ...) {
+    ( mean(x, ...)/sd(x, ...) )
+  })%>%
+  ungroup()
 
-#visitation rate stability for each plant species per site (all pollinators)
[…]

### 2022-09-26 script/models.R
plots and checking residuals

@@ -7,12 +7,15 @@ library(broom)
 #install.packages("lmerTest")
 library(lmerTest)
 library(dplyr)
+library(patchwork)
+library(ggcorrplot)
+library(ggpubr)
 
 
 Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
 str(Pollinator_Plant)
 Pollinator_Plant<-Pollinator_Plant[,-1]
-
+head(Pollinator_Plant)
 
 #Species out
 spp_out <- Pollinator_Plant %>%
@@ -34,6 +37,38 @@ a_cor <- a %>%
   group_by(Plant_gen_sp) %>%
   do(cormat = cor(select(., -matches("Plant_gen_sp")))) 
 
+
+#######
+# correlacion por sitios en lugar de por plant species
+b<-Pollinator_Plant %>% select(Site_ID,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
+b <- mutate_all(b, ~replace(., is.na(.), 0))
+
+b_cor <- b %>%
+  group_by(Site_ID) %>%
+  do(cormat = cor(select(., -matches("Site_ID")))) 
+
+b_cor[[2]]
+
+list_1 <- b_cor[[2]]
+
+b_cor[[1]]
+
+v <- b_cor[[1]]
+str(v)
+names(list_1) <- v
+
+str(list_1)
+data2 <- do.call(rbind.data.frame, list_1)
+
+corre<-data2 %>%
+  mutate(newcolum = rownames(data2))%>%
+  separate(newcolum, into=c('species', 'rows'), extra = "merge", sep = "\\.")%>%
+  select(species, rows,everything())  %>%
+  remove_rownames() %>%
+  mutate(species = replace(species, duplicated(species), ""))
+
+
+#####
 a_cor[[2]]
 
 list_1 <- a_cor[[2]]
@@ -63,8 +98,7 @@ a %>%
   tl.cex=0.8,title = first(.x$Plant_gen_sp)), .keep = TRUE)
    
 
-library(patchwork)
-library(ggcorrplot)
+
 
 df_with_plots <- a %>%
   group_by(Plant_gen_sp) %>%
@@ -78,7 +112,7 @@ df_with_plots <- a %>%
 plots1 <- map2(df_with_plots$plot, df_with_plots$Plant_gen_sp, ~(.x + labs(title = .y)))
 
 
[…]

### 2022-09-26 Rmd/Models.Rmd
added plots

@@
 - \newcommand{\elandscape}{\end{landscape}}
+
 ---
@@
 
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# correlation
-a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
-a <- mutate_all(a, ~replace(., is.na(.), 0))
-
 df_with_plots <- a %>%
@@
 
-\clearpage
-
 # Fruit proportion
 
-Summary of models for fruit proportion per plant species. Binomial cbind(fruit_formado, Fruit_No). Site_ID as factor random
-
 ## Richness
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+# replace NAs by 0
+# hay especies de plantas que presentan datos de fruit y seed pero no de polinizador (durante el tiempo observado no se ve ningun polinizador )
+Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
+
+#plot
+plots_fruitproportion <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=richness, y=fruit_proportion) + 
+   geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_fruitproportion[[1]],plots_fruitproportion[[2]],plots_fruitproportion[[3]],plots_fruitproportion[[4]],plots_fruitproportion[[5]],plots_fruitproportion[[6]],plots_fruitproportion[[7]],plots_fruitproportion[[8]],plots_fruitproportion[[9]],plots_fruitproportion[[10]],plots_fruitproportion[[11]],plots_fruitproportion[[12]], ncol=3, nrow=4)
+
+```
+
+\newpage
+
+Summary of models for fruit proportion ~ pollinator richness per plant species.
+Binomial cbind(fruit_formado, Fruit_No), fruit formada= Fruit yes + fruit preyed + fruit dispersed.
+Site_ID as factor random
+
+Note: NAs is replaced by zero. The plant species have fruit and seed data but no pollinator visiting were registered. No pollinator visit the plant species during observed time
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
 
@@
 # richnes
-ta_f<-Pollinator_Plant %>%
+
+mod_fruitproportion<-Pollinator_Plant %>%
   nest_by(Plant_gen_sp) %>%
@@
 
-ta_f<-ta_f %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_f<-filter(ta_f, !term == "sd__(Intercept)")
-
-ta_f %>% 
+mod_fruitproportion<-mod_fruitproportion %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruitproportion<-filter(mod_fruitproportion, !term == "sd__(Intercept)")
+
+mod_fruitproportion %>% 
     kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
+column_spec(6, bold = ifelse(mod_fruitproportion$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_fruitproportion_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_fruitproportion_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot
+mod_fruitproportion.1 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "richness"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1= mod_fruitproportion.1$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2= mod_fruitproportion.1$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3= mod_fruitproportion.1$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  richness, y = fruit_proportion),shape=20)+labs(x = "richness",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4= mod_fruitproportion.1$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5= mod_fruitproportion.1$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  richness, y = fruit_proportion),shape=20)+labs(x = "richness",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6= mod_fruitproportion.1$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7= mod_fruitproportion.1$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8= mod_fruitproportion.1$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9= mod_fruitproportion.1$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10= mod_fruitproportion.1$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11= mod_fruitproportion.1$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12= mod_fruitproportion.1$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  richness, y = fruit_proportion),shape=20)+ labs(x = "richness",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
 
@@
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_fruitproportion_2 <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=visitatio_rate, y=fruit_proportion) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_fruitproportion_2[[1]],plots_fruitproportion_2[[2]],plots_fruitproportion_2[[3]],plots_fruitproportion_2[[4]],plots_fruitproportion_2[[5]],plots_fruitproportion_2[[6]],plots_fruitproportion_2[[7]],plots_fruitproportion_2[[8]],plots_fruitproportion_2[[9]],plots_fruitproportion_2[[10]],plots_fruitproportion_2[[11]],plots_fruitproportion_2[[12]], ncol=3, nrow=4)
+
+```
+
+\newpage
+
+Summary of models for fruit proportion ~ visitation rate per plant species. Binomial cbind(fruit_formado, Fruit_No), fruit formada= Fruit yes + fruit preyed + fruit dispersed. Site_ID as factor random
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
 
 # visistation rate
-ta_f2<-Pollinator_Plant %>%
+mod_fruitproportion_2<-Pollinator_Plant %>%
   nest_by(Plant_gen_sp) %>%
@@
 
-ta_f2<-ta_f2 %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_f2<-filter(ta_f2, !term == "sd__(Intercept)")
-
-ta_f2 %>% 
+mod_fruitproportion_2<-mod_fruitproportion_2 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruitproportion_2<-filter(mod_fruitproportion_2, !term == "sd__(Intercept)")
+
+mod_fruitproportion_2 %>% 
 kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f2$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
+column_spec(6, bold = ifelse(mod_fruitproportion_2$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_fruitproportion_2_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_fruitproportion_2_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_fruitproportion.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "visitatio_rate"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1= mod_fruitproportion.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2= mod_fruitproportion.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_fruitproportion.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4= mod_fruitproportion.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5= mod_fruitproportion.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6= mod_fruitproportion.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7= mod_fruitproportion.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8= mod_fruitproportion.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9= mod_fruitproportion.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10= mod_fruitproportion.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_fruitproportion.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+ labs(x = "visitation_rate",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12= mod_fruitproportion.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  visitatio_rate, y = fruit_proportion),shape=20)+labs(x = "visitation_rate",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
 

### 2022-09-27 script/models.R
plots and checking residuals

@@ -29,7 +29,7 @@ spp_out <- Pollinator_Plant %>%
 Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
 
 
-# correlation
+# correlation ----
 a<-Pollinator_Plant %>% select(Plant_gen_sp,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
 a <- mutate_all(a, ~replace(., is.na(.), 0))
 
@@ -38,7 +38,7 @@ a_cor <- a %>%
   do(cormat = cor(select(., -matches("Plant_gen_sp")))) 
 
 
-#######
+#+++++++++++++++++++++
 # correlacion por sitios en lugar de por plant species
 b<-Pollinator_Plant %>% select(Site_ID,fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
 b <- mutate_all(b, ~replace(., is.na(.), 0))
@@ -68,7 +68,7 @@ corre<-data2 %>%
   mutate(species = replace(species, duplicated(species), ""))
 
 
-#####
+#+++++++++++++++++++++++++++++++++
 a_cor[[2]]
 
 list_1 <- a_cor[[2]]
@@ -121,7 +121,6 @@ plots1[[1]] + plots1[[2]] + plots1[[3]] + plots1[[4]]+plots1[[5]]+plots1[[6]]+pl
 ggarrange(plots1[[1]], plots1[[2]], plots1[[3]], plots1[[4]], ncol=2, nrow=2, common.legend = TRUE, legend="bottom")
 
 
-#df_with_plots$plot %>% wrap_plots(ncol = 2)
 
 
 # replace NAs by 0
@@ -129,81 +128,776 @@ ggarrange(plots1[[1]], plots1[[2]], plots1[[3]], plots1[[4]], ncol=2, nrow=2, co
 #(durante el tiempo observado no se ve ningun polinizador )
 Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
 
+#correlacion general, no por especie de plantas 
+cor_general<-Pollinator_Plant %>% 
+  select(fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
 
-#Models _ Seed numbers---- 
+corr <- round(cor(cor_general), 4)
+p.mat <- cor_pmat(cor_general)
+ggcorrplot(corr, hc.order = TRUE, type = "lower",
[…]

### 2022-09-27 Rmd/Models.Rmd
added plots

@@
 
+## general correlation 
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+# replace NAs by 0
+# hay especies de plantas que presentan datos de fruit y seed pero no de polinizador (durante el tiempo observado no se ve ningun polinizador )
+Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
+
+cor_general<-Pollinator_Plant %>% 
+  select(fruit_proportion, Seeds,Seed_weight,richness,visitatio_rate,Frequency)
+
+corr <- round(cor(cor_general), 4)
+
+corr %>% 
+    kable("latex",booktabs = TRUE,linesep = "")
+
+```
+
+```{r,,echo=FALSE, warning=FALSE,message=FALSE, out.width="89%"}
+ggcorrplot(corr, hc.order = TRUE, type = "lower",
+           lab = TRUE)
+```
+
+\newpage
+
 # Fruit proportion
@@
 
+visitation rate is calculated like frequency/ flower abundance
+
 ```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
@@
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-
+Hymenoptera visitation is calculated like hymenoptera frequency / Flower abundance
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_fruitproportion_3 <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=Hym_visit, y=fruit_proportion) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_fruitproportion_3[[1]],plots_fruitproportion_3[[2]],plots_fruitproportion_3[[3]],plots_fruitproportion_3[[4]],plots_fruitproportion_3[[5]],plots_fruitproportion_3[[6]],plots_fruitproportion_3[[7]],plots_fruitproportion_3[[8]],plots_fruitproportion_3[[9]],plots_fruitproportion_3[[10]],plots_fruitproportion_3[[11]],plots_fruitproportion_3[[12]], ncol=3, nrow=4)
+
+```
+
+\newpage
+
+Summary of models for fruit proportion ~ Hymenoptera visitation per plant species.
+Binomial cbind(fruit_formado, Fruit_No), fruit formada= Fruit yes + fruit preyed + fruit dispersed.
+Site_ID as factor random
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#Models _ fruit proportion 
+# hymenoptera visitation
+mod_plots_fruitproportion_3<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_plots_fruitproportion_3<-mod_plots_fruitproportion_3 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_plots_fruitproportion_3<-filter(mod_plots_fruitproportion_3, !term == "sd__(Intercept)")
+
+mod_plots_fruitproportion_3 %>% 
+    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(mod_plots_fruitproportion_3$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_fruitproportion_3_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_fruitproportion_3_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_fruitproportion.3 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Hym_visit"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_fruitproportion.3$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=mod_fruitproportion.3$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_fruitproportion.3$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=mod_fruitproportion.3$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_fruitproportion.3$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_fruitproportion.3$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7= mod_fruitproportion.3$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=mod_fruitproportion.3$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_fruitproportion.3$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_fruitproportion.3$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_fruitproportion.3$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_fruitproportion.3$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Hym_visit, y = fruit_proportion),shape=20)+ labs(x = "Hymenotera_visit",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+## Pollinator frequency
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_fruitproportion_4 <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=Frequency, y=fruit_proportion) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_fruitproportion_4[[1]],plots_fruitproportion_4[[2]],plots_fruitproportion_4[[3]],plots_fruitproportion_4[[4]],plots_fruitproportion_4[[5]],plots_fruitproportion_4[[6]],plots_fruitproportion_4[[7]],plots_fruitproportion_4[[8]],plots_fruitproportion_4[[9]],plots_fruitproportion_4[[10]],plots_fruitproportion_4[[11]],plots_fruitproportion_4[[12]], ncol=3, nrow=4)
+
+```
+
+\newpage
+
+Summary of models for fruit proportion ~ pollinator frequency per plant species.
+Binomial cbind(fruit_formado, Fruit_No), fruit formada= Fruit yes + fruit preyed + fruit dispersed.
+Site_ID as factor random
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# frequency
+mod_fruitproportion_4<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_fruitproportion_4<-mod_fruitproportion_4 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruitproportion_4<-filter(mod_fruitproportion_4, !term == "sd__(Intercept)")
+
+mod_fruitproportion_4 %>% 
+kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(mod_fruitproportion_4$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_fruitproportion_4_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_fruitproportion_4_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_fruitproportion.4 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Frequency"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+ geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_fruitproportion.4$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=mod_fruitproportion.4$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_fruitproportion.4$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+P4=mod_fruitproportion.4$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_fruitproportion.4$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Frequency, y = fruit_proportion),shape=20)+labs(x = "Frequency",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_fruitproportion.4$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Frequency, y = fruit_proportion),shape=20)+labs(x = "Frequency",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=mod_fruitproportion.4$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Frequency, y = fruit_proportion),shape=20)+labs(x = "Frequency",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8= mod_fruitproportion.4$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Frequency, y = fruit_proportion),shape=20)+labs(x = "Frequency",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_fruitproportion.4$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_fruitproportion.4$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_fruitproportion.4$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Frequency, y = fruit_proportion),shape=20)+ labs(x = "Frequency",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_fruitproportion.4$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Frequency, y = fruit_proportion),shape=20)+  labs(x = "Frequency",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+# Seed number
+
+seed number is calculated like seed number mean per fruit in plant individual per plant species
+
+## Richness
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_seed <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=richness, y=Seeds) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_seed[[1]],plots_seed[[2]],plots_seed[[3]],plots_seed[[4]],plots_seed[[5]],plots_seed[[6]],plots_seed[[7]],plots_seed[[8]],plots_seed[[9]],plots_seed[[10]],plots_seed[[11]],plots_seed[[12]], ncol=3, nrow=4)
+
+```
+
+\newpage
+
+Summary of models for seed numbers ~ richness per plant species (LMM). Site_ID as factor random
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#Models _ Seed numbers 
+# richness
+mod_seed<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed<-mod_seed %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed<-filter(mod_seed, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_seed.1 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "richness"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+ geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_seed.1$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=mod_seed.1$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_seed.1$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=mod_seed.1$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_seed.1$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_seed.1$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=mod_seed.1$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=mod_seed.1$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_seed.1$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_seed.1$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  richness, y = Seeds),shape=20)+labs(x = "richness",y="seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_seed.1$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_seed.1$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  richness, y = Seeds),shape=20)+ labs(x = "richness",y="seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+## Visitation rate
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_seed_2 <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=visitatio_rate, y=Seeds) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_seed_2[[1]],plots_seed_2[[2]],plots_seed_2[[3]],plots_seed_2[[4]],plots_seed_2[[5]],plots_seed_2[[6]],plots_seed_2[[7]],plots_seed_2[[8]],plots_seed_2[[9]],plots_seed_2[[10]],plots_seed_2[[11]],plots_seed_2[[12]], ncol=3,nrow=4)
+
+```
+
+\newpage
+
+Summary of models for seed number ~ visitation rate per plant species (LMM). Site_ID as factor random
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# visitation rate
+mod_seed2<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed2<-mod_seed2 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed2<-filter(mod_seed2, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed2 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed2$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed2_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed2_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_seed.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "visitatio_rate")))  %>%  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_seed.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=mod_seed.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_seed.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=mod_seed.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_seed.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_seed.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=mod_seed.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=mod_seed.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  visitatio_rate, y = Seeds),shape=20)+labs(x = "visitation_rate",y="seed_number",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_seed.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  visitatio_rate, y = Seeds),shape=20)+labs(x = "visitation_rate",y="seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_seed.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11= mod_seed.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_seed.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ labs(x = "visitation_rate",y="seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+## Hymenoptera visitation
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_seed_3 <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=Hym_visit, y=Seeds) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_seed_3[[1]],plots_seed_3[[2]],plots_seed_3[[3]],plots_seed_3[[4]],plots_seed_3[[5]],plots_seed_3[[6]],plots_seed_3[[7]],plots_seed_3[[8]],plots_seed_3[[9]],plots_seed_3[[10]],plots_seed_3[[11]],plots_seed_3[[12]], ncol=3,nrow=4)
+
+```
+
+\newpage
+
+Summary of models for seed number ~ Hymenoptera visitation per plant species (LMM). Site_ID as factor random
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# hymenoptera visitation
+mod_seed3<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed3<-mod_seed3 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed3<-filter(mod_seed3, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed3 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed3$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed3_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed3_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_seed.3 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Hym_visit"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_seed.3$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Hym_visit, y = Seeds),shape=20)+  labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=mod_seed.3$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_seed.3$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=mod_seed.3$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_seed.3$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_seed.3$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=mod_seed.3$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=mod_seed.3$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Hym_visit, y = Seeds),shape=20)+labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_seed.3$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_seed.3$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Hym_visit, y = Seeds),shape=20)+  labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_seed.3$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Hym_visit, y = Seeds),shape=20)+ labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_seed.3$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Hym_visit, y = Seeds),shape=20)+  labs(x = "Hymenoptera_visit",y="seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+## Pollinator frequency
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_seed_4 <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=Frequency, y=Seeds) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_seed_4[[1]],plots_seed_4[[2]],plots_seed_4[[3]],plots_seed_4[[4]],plots_seed_4[[5]],plots_seed_4[[6]],plots_seed_4[[7]],plots_seed_4[[8]],plots_seed_4[[9]],plots_seed_4[[10]],plots_seed_4[[11]],plots_seed_4[[12]], ncol=3,nrow=4)
+
+```
+
+\newpage
+
+Summary of models for seed number ~ pollinator frequency per plant species (LMM). Site_ID as factor random
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# Frequency
+mod_seed4<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed4<-mod_seed4 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed4<-filter(mod_seed4, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed4 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed4$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed4_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed4_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+mod_seed.4 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Frequency"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_seed.4$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=mod_seed.4$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Frequency, y = Seeds),shape=20)+labs(x = "Frequency",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_seed.4$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Frequency, y = Seeds),shape=20)+labs(x = "Frequency",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=mod_seed.4$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_seed.4$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_seed.4$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=mod_seed.4$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=mod_seed.4$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_seed.4$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_seed.4$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_seed.4$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_seed.4$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Frequency, y = Seeds),shape=20)+ labs(x = "Frequency",y="seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+# Seed weight
+
+seed weight mean per fruit in plant individual per plant species
+
+## Richness
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_seed_weight <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=richness, y=Seed_weight) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_seed_weight[[1]],plots_seed_weight[[2]],plots_seed_weight[[3]],plots_seed_weight[[4]],plots_seed_weight[[5]],plots_seed_weight[[6]],plots_seed_weight[[7]],plots_seed_weight[[8]],plots_seed_weight[[9]],plots_seed_weight[[10]],plots_seed_weight[[11]],plots_seed_weight[[12]], ncol=3,nrow=4)
+
+```
+
+\newpage
+
+Summary of models for seed weight ~ richness per plant species (LMM). Site_ID as factor random
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#Models _ Seed weight 
+# richnes
+mod_seed_weight<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~richness+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_weight<-mod_seed_weight %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_weight<-filter(mod_seed_weight, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_weight %>% 
+kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(mod_seed_weight$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_weight_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~richness+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_weight_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+mod_seed_weight.1 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~richness+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "richness"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_seed_weight.1$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2= mod_seed_weight.1$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_seed_weight.1$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=mod_seed_weight.1$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_seed_weight.1$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  richness, y = Seed_weight),shape=20)+labs(x = "richness",y="Seed_weight",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_seed_weight.1$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=mod_seed_weight.1$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=mod_seed_weight.1$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_seed_weight.1$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_seed_weight.1$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_seed_weight.1$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  richness, y = Seed_weight),shape=20)+ labs(x = "richness",y="Seed_weight",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_seed_weight.1$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  richness, y = Seed_weight),shape=20)+  labs(x = "richness",y="Seed_weight",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+## Visitation rate
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_seed_weight2 <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=visitatio_rate, y=Seed_weight) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_seed_weight2[[1]],plots_seed_weight2[[2]],plots_seed_weight2[[3]],plots_seed_weight2[[4]],plots_seed_weight2[[5]],plots_seed_weight2[[6]],plots_seed_weight2[[7]],plots_seed_weight2[[8]],plots_seed_weight2[[9]],plots_seed_weight2[[10]],plots_seed_weight2[[11]],plots_seed_weight2[[12]], ncol=3,nrow=4)
+
+```
+
+\newpage
+
+Summary of models for seed weight ~ visitation rate per plant species (LMM). Site_ID as factor random
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#Models _ Seed weight 
+# visistation rate
+mod_seed_weight2<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~visitatio_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_weight2<-mod_seed_weight2 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_weight2<-filter(mod_seed_weight2, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_weight2 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_weight2$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_weight2_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~visitatio_rate+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_weight2_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+mod_seed_weight.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~visitatio_rate+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "visitatio_rate"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_seed_weight.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=mod_seed_weight.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_seed_weight.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=mod_seed_weight.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_seed_weight.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_seed_weight.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=mod_seed_weight.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=mod_seed_weight.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+labs(x = "visitation_rate",y="Seed_weight",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_seed_weight.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_seed_weight.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_seed_weight.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_seed_weight.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  visitatio_rate, y = Seed_weight),shape=20)+ labs(x = "visitation_rate",y="Seed_weight",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+## Hymenoptera visitation
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_seed_weight3 <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=Hym_visit, y=Seed_weight) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_seed_weight3[[1]],plots_seed_weight3[[2]],plots_seed_weight3[[3]],plots_seed_weight3[[4]],plots_seed_weight3[[5]],plots_seed_weight3[[6]],plots_seed_weight3[[7]],plots_seed_weight3[[8]],plots_seed_weight3[[9]],plots_seed_weight3[[10]],plots_seed_weight3[[11]],plots_seed_weight3[[12]], ncol=3,nrow=4)
+
+```
+
+\newpage
+
+Summary of models for seed weight ~ hymenoptera visitation per plant species (LMM). Site_ID as factor random
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#Models _ Seed weight 
+# Hymenoptera visitation
+mod_seed_weight3<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_weight3<-mod_seed_weight3 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_weight3<-filter(mod_seed_weight3, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_weight3 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_weight3$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_weight3_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_weight3_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+mod_seed_weight.3 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Hym_visit"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+   geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_seed_weight.3$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=mod_seed_weight.3$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_seed_weight.3$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=mod_seed_weight.3$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_seed_weight.3$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_seed_weight.3$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=mod_seed_weight.3$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=mod_seed_weight.3$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_seed_weight.3$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_seed_weight.3$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_seed_weight.3$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_seed_weight.3$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Hym_visit, y = Seed_weight),shape=20)+ labs(x = "Hymenoptera_visit",y="Seed_weight",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+## Frequency
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_seed_weight4 <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=Frequency, y=Seed_weight) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_seed_weight4[[1]],plots_seed_weight4[[2]],plots_seed_weight4[[3]],plots_seed_weight4[[4]],plots_seed_weight4[[5]],plots_seed_weight4[[6]],plots_seed_weight4[[7]],plots_seed_weight4[[8]],plots_seed_weight4[[9]],plots_seed_weight4[[10]],plots_seed_weight4[[11]],plots_seed_weight4[[12]], ncol=3,nrow=4)
+
+```
+
+\newpage
+
+Summary of models for seed weight ~ pollinator frequency per plant species (LMM). Site_ID as factor random
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#Models _ Seed weight 
+# frequency
+mod_seed_weight4<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Frequency+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_weight4<-mod_seed_weight4 %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_weight4<-filter(mod_seed_weight4, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_weight4 %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_weight4$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_weight4_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Frequency+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_weight4_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+mod_seed_weight.4 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Frequency+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Frequency"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=mod_seed_weight.4$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=mod_seed_weight.4$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_seed_weight.4$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=mod_seed_weight.4$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=mod_seed_weight.4$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=mod_seed_weight.4$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=mod_seed_weight.4$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Frequency, y = Seed_weight),shape=20)+ 
+  labs(x = "Frequency",y="Seed_weight",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8=mod_seed_weight.4$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9=mod_seed_weight.4$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10=mod_seed_weight.4$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_seed_weight.4$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12=mod_seed_weight.4$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Frequency, y = Seed_weight),shape=20)+ labs(x = "Frequency",y="Seed_weight",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+## join together Lavandula species 
+(L.peduncalata (49 obs) and L.stoechas (24 obs))
+
+## Fruit proportion - richness
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
 Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
@@
 
-#Models _ fruit proportion 
-# hymenoptera visitation
-ta_f4<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_f4<-ta_f4 %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_f4<-filter(ta_f4, !term == "sd__(Intercept)")
-
-ta_f4 %>% 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# richnes
+ta_f_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f_la<-ta_f_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f_la<-filter(ta_f_la, !term == "sd__(Intercept)")
+
+ta_f_la %>% 
     kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f4$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Frequency
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-
+column_spec(6, bold = ifelse(ta_f_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Fruit proportion - visitation rate
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
 Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
@@
 
-# frequency
-ta_f3<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data)))%>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_f3<-ta_f3 %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_f3<-filter(ta_f3, !term == "sd__(Intercept)")
-
-ta_f3 %>% 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# visistation rate
+ta_f2_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f2_la<-ta_f2_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f2_la<-filter(ta_f2_la, !term == "sd__(Intercept)")
+
+ta_f2_la %>% 
     kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f3$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-# Seed numbers
-
-Summary of models for seed numbers per plant species (LMM). Site_ID as factor random
-
-## Richness
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") #402 observaciones
+column_spec(6, bold = ifelse(ta_f2_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Fruit proportion - hymenoptera visitation
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
 Pollinator_Plant<-Pollinator_Plant[,-1]
@@
 
-#Models _ Seed numbers 
-# richness
-ta_seed<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_seed<-ta_seed %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_seed<-filter(ta_seed, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_seed %>% 
-kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-## Visitation rate
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# hymenoptera visitation
+ta_f4_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f4_la<-ta_f4_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f4_la<-filter(ta_f4_la, !term == "sd__(Intercept)")
+
+ta_f4_la %>% 
+    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f4_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Fruit proportion - frequency
 
@@
 
-# visitation rate
-ta_seed2<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_seed2<-ta_seed2 %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_seed2<-filter(ta_seed2, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_seed2 %>% 
-kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed2$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-```
-
-\newpage
-## Hymenoptera visitation
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# frequency
+ta_f3_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_f3_la<-ta_f3_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_f3_la<-filter(ta_f3_la, !term == "sd__(Intercept)")
+
+ta_f3_la %>% 
+    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(ta_f3_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed number - richness
+
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
@@
 
-# hymenoptera visitation
-ta_seed4<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_seed4<-ta_seed4 %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_seed4<-filter(ta_seed4, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_seed4 %>% 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# richness
+ta_seed_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed_la<-ta_seed_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed_la<-filter(ta_seed_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed_la %>% 
 kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed4$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-## Frequency
+column_spec(7, bold = ifelse(ta_seed_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed number - visitation rate
 
@@
 
-# Frequency
-ta_seed3<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_seed3<-ta_seed3 %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_seed3<-filter(ta_seed3, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_seed3 %>% 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# visistation rate
+ta_seed2_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed2_la<-ta_seed2_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed2_la<-filter(ta_seed2_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed2_la %>% 
 kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed3$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-# Seed weight
-
-Summary of models for seed weight per plant species (LMM). Site_ID as factor random
-
-## Richness
+column_spec(7, bold = ifelse(ta_seed2_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed number - hymenoptera visitation
 
@@
 
-#Models _ Seed weight 
-# richnes
-ta_weight<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seed_weight~richness+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_weight<-ta_weight %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_weight<-filter(ta_weight, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_weight %>% 
-kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_weight$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Visitation rate
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# hymenoptera visitation
+ta_seed4_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed4_la<-ta_seed4_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed4_la<-filter(ta_seed4_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed4_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_seed4_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed number - frequency
 
@@
 
-#Models _ Seed weight 
-# visistation rate
-ta_weight2<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seed_weight~visitatio_rate+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_weight2<-ta_weight2 %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_weight2<-filter(ta_weight2, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_weight2 %>% 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# Frequency
+ta_seed3_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_seed3_la<-ta_seed3_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_seed3_la<-filter(ta_seed3_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_seed3_la %>% 
 kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_weight2$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Hymenoptera visitation
+column_spec(7, bold = ifelse(ta_seed3_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed weight - richness
+
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
@@
 
-#Models _ Seed weight 
-# Hymenoptera visitation
-ta_weight4<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_weight4<-ta_weight4 %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_weight4<-filter(ta_weight4, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_weight4 %>% 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# richnes
+ta_weight_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~richness+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight_la<-ta_weight_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight_la<-filter(ta_weight_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight_la %>% 
 kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_weight4$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Frequency
+column_spec(7, bold = ifelse(ta_weight_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed weight - visitation rate
 
@@
 
-#Models _ Seed weight 
-# frequency
-ta_weight3<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seed_weight~Frequency+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_weight3<-ta_weight3 %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_weight3<-filter(ta_weight3, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_weight3 %>% 
+lavan_tog=Pollinator_Plant %>%
+  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
+
+# visistation rate
+ta_weight2_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~visitatio_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight2_la<-ta_weight2_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight2_la<-filter(ta_weight2_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight2_la %>% 
 kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_weight3$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## join together Lavandula species 
-(L.peduncalata (49 obs) and L.stoechas (24 obs))
-
-## Fruit proportion - richness
+column_spec(7, bold = ifelse(ta_weight2_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed weight - hymenoptera visitation
 
@@
 
-# richnes
-ta_f_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~richness + (1|Site_ID),family=binomial,data)))%>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_f_la<-ta_f_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_f_la<-filter(ta_f_la, !term == "sd__(Intercept)")
-
-ta_f_la %>% 
-    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Fruit proportion - visitation rate
+# hymenoptera visitation
+ta_weight4_la<-lavan_tog %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+ta_weight4_la<-ta_weight4_la %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+ta_weight4_la<-filter(ta_weight4_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+ta_weight4_la %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(7, bold = ifelse(ta_weight4_la$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+## Seed weight - frequency
 
@@
 
-# visistation rate
-ta_f2_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate + (1|Site_ID),family=binomial,data)))%>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_f2_la<-ta_f2_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_f2_la<-filter(ta_f2_la, !term == "sd__(Intercept)")
-
-ta_f2_la %>% 
-    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f2_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Fruit proportion - hymenoptera visitation
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
-# hymenoptera visitation
-ta_f4_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit + (1|Site_ID),family=binomial,data)))%>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_f4_la<-ta_f4_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_f4_la<-filter(ta_f4_la, !term == "sd__(Intercept)")
-
-ta_f4_la %>% 
-    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f4_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Fruit proportion - frequency
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
-# frequency
-ta_f3_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Frequency + (1|Site_ID),family=binomial,data)))%>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_f3_la<-ta_f3_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_f3_la<-filter(ta_f3_la, !term == "sd__(Intercept)")
-
-ta_f3_la %>% 
-    kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(6, bold = ifelse(ta_f3_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Seed number - richness
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
-# richness
-ta_seed_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seeds~richness+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_seed_la<-ta_seed_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_seed_la<-filter(ta_seed_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_seed_la %>% 
-kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Seed number - visitation rate
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
-# visistation rate
-ta_seed2_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seeds~visitatio_rate+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_seed2_la<-ta_seed2_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_seed2_la<-filter(ta_seed2_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_seed2_la %>% 
-kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed2_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Seed number - hymenoptera visitation
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
-# hymenoptera visitation
-ta_seed4_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seeds~Hym_visit+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_seed4_la<-ta_seed4_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_seed4_la<-filter(ta_seed4_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_seed4_la %>% 
-kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed4_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Seed number - frequency
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
-# Frequency
-ta_seed3_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seeds~Frequency+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_seed3_la<-ta_seed3_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_seed3_la<-filter(ta_seed3_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_seed3_la %>% 
-kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_seed3_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Seed weight - richness
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
-# richnes
-ta_weight_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seed_weight~richness+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_weight_la<-ta_weight_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_weight_la<-filter(ta_weight_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_weight_la %>% 
-kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_weight_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Seed weight - visitation rate
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
-# visistation rate
-ta_weight2_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seed_weight~visitatio_rate+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_weight2_la<-ta_weight2_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_weight2_la<-filter(ta_weight2_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_weight2_la %>% 
-kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_weight2_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Seed weight - hymenoptera visitation
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
-# hymenoptera visitation
-ta_weight4_la<-lavan_tog %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lmer(Seed_weight~Hym_visit+(1|Site_ID),data))) %>%
-  summarise(broom.mixed::tidy(model)) %>%
-  ungroup()
-
-opts <- options(knitr.kable.NA = "")
-
-ta_weight4_la<-ta_weight4_la %>%
-  select(-effect, -group)  %>%
-  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
-
-ta_weight4_la<-filter(ta_weight4_la, !term == "sd__(Intercept)" & !term =="sd__Observation")
-
-ta_weight4_la %>% 
-kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
-column_spec(7, bold = ifelse(ta_weight4_la$p.value < 0.05, T, F) )%>%
-  kable_styling(position="center", latex_option="hold_position")
-
-```
-
-\newpage
-
-## Seed weight - frequency
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
-Pollinator_Plant<-Pollinator_Plant[,-1]
-
-#Species out
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in more than 1 site
-Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-# replace NAs by 0
-Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
-
-lavan_tog=Pollinator_Plant %>%
-  mutate(Plant_gen_sp = recode(Plant_gen_sp, "Lavandula pedunculata" = "Lavandula","Lavandula stoechas" = "Lavandula"))
-
 # frequency

### 2022-09-28 Rmd/Stability.Rmd
added plots

@@
 
-For each plant species per site, stability (inverse of the coefficient of variation) of the visitation rate of pollinators (visitation rate calculated like frequency/flower abundance) and also of the fruit proportion and the seed numbers were calculated.
-Total of pollinator richness (sum) was obtained and furthermore, the log of variance ratio (Lepš et al., 2018) and Loreau & Mazancourt syncrony index were calculated.
+Plots of fruit proportion and year for each plant species and site
 
-Positive values of log var ratio signify synchronization, negative values indicate compensatory dynamics (Lepš et al., 2018).
-Loreau & Mazancourt index is standardized between 0 (perfect asynchrony) and 1 (perfect synchrony).
-
-note: NA= one data per year
-
-```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
 library(tidyverse)
@@
 library(dplyr)
+library(reshape2)
+library(tidyr)
+library(ggplot2)
+#install.packages("ggeffects")
+library(ggeffects)
+library(patchwork)
+library(ggcorrplot)
+library(ggpubr)
 library(kableExtra)
-library(reshape2)
 
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") #400 observaciones
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
 Pollinator_Plant<-Pollinator_Plant[,-1]
@@
   summarise_if(is.numeric, mean)
+
+pol_plant2$Year <- factor(pol_plant2$Year)
+
+plots3 <- pol_plant2 %>%
+group_by(Plant_gen_sp) %>%
+group_map(~ ggplot(.) + aes(x=Year, y=fruit_proportion, col =factor(Site_ID))+ theme_bw()+geom_point(size = 5,alpha = 0.5)+  theme(axis.title = element_text(size = 20))+ theme(axis.text = element_text(size = 15)) + theme(plot.title = element_text(size = 20)) + theme(legend.text = element_text(size = 13)) + ggtitle(.y[[1]]))
+
+ggarrange(plots3[[1]],plots3[[2]],plots3[[3]],plots3[[4]],plots3[[5]],plots3[[6]], plots3[[7]],plots3[[8]],plots3[[9]],plots3[[10]],plots3[[11]],plots3[[12]],ncol=3,nrow = 4)
+
+```
+
+\newpage
+
+Plots of seed number and year for each plant species and site
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+plots3_seed <- pol_plant2 %>%
+group_by(Plant_gen_sp) %>%
+group_map(~ ggplot(.) + aes(x=Year, y=Seeds, col =factor(Site_ID))+ theme_bw()+geom_point(size = 5,alpha = 0.5)+  theme(axis.title = element_text(size = 20))+ theme(axis.text = element_text(size = 15)) + theme(plot.title = element_text(size = 20)) + theme(legend.text = element_text(size = 13)) + ggtitle(.y[[1]]))
+
+ggarrange(plots3_seed[[1]],plots3_seed[[2]],plots3_seed[[3]],plots3_seed[[4]],plots3_seed[[5]],plots3_seed[[6]],plots3_seed[[7]],plots3_seed[[8]],plots3_seed[[9]],plots3_seed[[10]],plots3_seed[[11]],plots3_seed[[12]],ncol=3,nrow = 4)
+
+```
+
+\newpage
+
+Plots of visitation rate and year for each plant species and site
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+plots3_visitation_rate <- pol_plant2 %>%
+group_by(Plant_gen_sp) %>%
+group_map(~ ggplot(.) + aes(x=Year, y=visitatio_rate, col =factor(Site_ID))+ theme_bw()+geom_point(size = 5,alpha = 0.5)+  theme(axis.title = element_text(size = 20))+ theme(axis.text = element_text(size = 15)) + theme(plot.title = element_text(size = 20)) + theme(legend.text = element_text(size = 13)) + ggtitle(.y[[1]]))
+
+ggarrange(plots3_visitation_rate[[1]],plots3_visitation_rate[[2]],plots3_visitation_rate[[3]],plots3_visitation_rate[[4]],plots3_visitation_rate[[5]],plots3_visitation_rate[[6]],plots3_visitation_rate[[7]],plots3_visitation_rate[[8]],plots3_visitation_rate[[9]],plots3_visitation_rate[[10]],plots3_visitation_rate[[11]],plots3_visitation_rate[[12]],ncol=3,nrow = 4)
+
+```
+
+\newpage
+For each plant species per site, stability (inverse of the coefficient of variation) of the visitation rate of pollinators (visitation rate calculated like frequency/flower abundance) and also of the fruit proportion and the seed numbers were calculated.
+Pollinator richness (total and mean) was obtained and furthermore, the log of variance ratio (Lepš et al., 2018) and Loreau & Mazancourt syncrony index were calculated.
+
+Positive values of log var ratio signify synchronization, negative values indicate compensatory dynamics (Lepš et al., 2018).
+Loreau & Mazancourt index is standardized between 0 (perfect asynchrony) and 1 (perfect synchrony).
+
+note: NA= one data per year
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
 
@@
   ungroup()
+
+#  pollinator richness for each plant species per site (Total)
+S<-aggregate(richness ~ Plant_gen_sp+Site_ID, data = Pollinator_Plant,FUN = sum)
 
@@
   full_join (., cv_1pollinator2, by=c('Plant_gen_sp', 'Site_ID')) %>%
+  full_join (., S, by=c('Plant_gen_sp', 'Site_ID'))%>%
   full_join (., S2, by=c('Plant_gen_sp', 'Site_ID'))%>%
@@
   full_join (., syn_LM2, by=c('Plant_gen_sp', 'Site_ID'))%>%
-  rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds, cv_1_visitation=visitatio_rate)
+  rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds,   cv_1_visitation=visitatio_rate,S_total=richness.x, S_mean=richness.y)
 
@@
 
-tr2<-full2 %>% select(cv_1_fruit, cv_1_seed,cv_1_visitation,richness)
+tr2<-full2 %>% select(cv_1_fruit, cv_1_seed,cv_1_visitation,S_total, S_mean)
 
@@
 # correlacion con nuevos calculos (full2 = sin plant_id)
-b<-full2 %>% select(Plant_gen_sp,cv_1_fruit, cv_1_seed,cv_1_visitation,richness,log_VR,syncLM)
+b<-full2 %>% select(Plant_gen_sp,cv_1_fruit, cv_1_seed,cv_1_visitation,S_total,S_mean,log_VR,syncLM)
 
@@
 
+Replace Inf and -Inf with NA
+
 We analysed the relationship between fruit proportion stability and visitation rate stability
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
 # 4 plant species are in 2-3 site (A.fistulosus, C.libanotis, c.monspeliensis, T.fructicans)
@@
 
+#plot
+plots_sta_fruit <- full_2 %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=cv_1_visitation, y=cv_1_fruit) + 
+ theme_bw()+ geom_point(size = 5) + labs(x = "visitation rate  stability",y="fruit proportion stability")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))
+
+ggarrange(plots_sta_fruit[[1]],plots_sta_fruit[[2]],plots_sta_fruit[[3]],plots_sta_fruit[[4]],plots_sta_fruit[[5]],plots_sta_fruit[[6]],plots_sta_fruit[[7]], ncol=3, nrow=3)
+
+```
+
+Halimium calycinum only one observation
+
+\newpage
+
+Summary of model per plant species
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#model
 sta_fruit<-full_2 %>%
@@
 
+checking residuals, I detect problems with the homogeneity of variance for all plant species
+
 \newpage
@@
 We analysed the relationship between seed number stability and visitation rate stability
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#plot
+plots_sta_seed <- full_2 %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=cv_1_visitation, y=cv_1_seed) + 
+ theme_bw()+ geom_point(size = 5) + labs(x = "visitation rate  stability",y="seed stability")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))
+
+ggarrange(plots_sta_seed[[1]],plots_sta_seed[[2]],plots_sta_seed[[3]],plots_sta_seed[[4]],plots_sta_seed[[5]],plots_sta_seed[[6]],plots_sta_seed[[7]], ncol=3, nrow=3)
+
+```
+
+\newpage
+
+Summary of model
 
@@
 
-A- Richness ~ log VR
+A- Total richness ~ log VR
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#plot
+plots_rich <- full_2 %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=log_VR, y=S_total) + 
+ theme_bw()+ geom_point(size = 5) + labs(x = "log VR",y="Total richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))
+
+ggarrange(plots_rich[[1]],plots_rich[[2]],plots_rich[[3]],plots_rich[[4]],plots_rich[[5]],plots_rich[[6]],plots_rich[[7]], ncol=3, nrow=3)
+
+```
+
+\newpage
+
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(richness~log_VR,data))) %>%
+  mutate(mod = list(lm(S_total~log_VR,data))) %>%
   summarize(tidy(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(richness~log_VR,data))) %>%
+  mutate(mod = list(lm(S_total~log_VR,data))) %>%
   summarize(glance(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(richness~log_VR,data))) %>%
+  mutate(mod = list(lm(S_total~log_VR,data))) %>%
   mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
@@
 
-p1=rich.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = richness),shape=20)+ 
-  labs(x = "log_VR",y="richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+p1=rich.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_total),shape=20)+ 
+  labs(x = "log_VR",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
 
-p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = richness),shape=20)+ 
-  labs(x = "log_VR",y="richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_total),shape=20)+ 
+  labs(x = "log_VR",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = richness),shape=20)+ 
-  labs(x = "log_VR",y="richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_total),shape=20)+ 
+  labs(x = "log_VR",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p4=rich.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = richness),shape=20)+ 
-  labs(x = "log_VR",y="richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p4=rich.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_total),shape=20)+ 
+  labs(x = "log_VR",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = richness),shape=20)+ 
-  labs(x = "log_VR",y="richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_total),shape=20)+ 
+  labs(x = "log_VR",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = richness),shape=20)+ 
-  labs(x = "log_VR",y="richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_total),shape=20)+ 
+  labs(x = "log_VR",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p7=rich.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = richness),shape=20)+ 
-  labs(x = "log_VR",y="richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p7=rich.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_total),shape=20)+ 
+  labs(x = "log_VR",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
@@
 \newpage
-A- Richness ~ Loreau & Mazancourt syncrony index
+B- total richness ~ Loreau & Mazancourt syncrony index
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(richness~syncLM,data))) %>%
+  mutate(mod = list(lm(S_total~syncLM,data))) %>%
   summarize(tidy(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(richness~syncLM,data))) %>%
+  mutate(mod = list(lm(S_total~syncLM,data))) %>%
   summarize(glance(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(richness~syncLM,data))) %>%
+  mutate(mod = list(lm(S_total~syncLM,data))) %>%
   mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
@@
 
-p1=rich.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = richness),shape=20)+ 
-  labs(x = "syncLM",y="richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+p1=rich.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_total),shape=20)+ 
+  labs(x = "syncLM",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
 
-p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = richness),shape=20)+ 
-  labs(x = "syncLM",y="richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_total),shape=20)+ 
+  labs(x = "syncLM",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = richness),shape=20)+ 
-  labs(x = "syncLM",y="richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_total),shape=20)+ 
+  labs(x = "syncLM",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = richness),shape=20)+ 
-  labs(x = "syncLM",y="richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_total),shape=20)+ 
+  labs(x = "syncLM",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p5=rich.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = richness),shape=20)+ 
-  labs(x = "syncLM",y="richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p5=rich.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_total),shape=20)+ 
+  labs(x = "syncLM",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = richness),shape=20)+ 
-  labs(x = "syncLM",y="richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_total),shape=20)+ 
+  labs(x = "syncLM",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = richness),shape=20)+ 
-  labs(x = "syncLM",y="richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_total),shape=20)+ 
+  labs(x = "syncLM",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7
+```
+
+\newpage
+
+C- mean richness ~ log VR
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+rich3<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+rich3<-rich3 %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+rich3 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(rich3$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+
+rich3_glance<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table5<-rich3_glance %>%
+  mutate(Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table5 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+rich.3 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=rich.3$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=rich.3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich.3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=rich.3$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich.3$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=rich.3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=rich.3$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7
+```
+
+\newpage
+
+D- mean richness ~ Loreau & Mazancourt syncrony index
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+rich4<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+rich4<-rich4 %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+rich4 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(rich4$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+
+rich4_glance<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table6<-rich4_glance %>%
+  mutate(Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table6 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+rich.4 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=rich.4$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_mean),shape=20)+ 
+  labs(x = "syncLM",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=rich.4$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_mean),shape=20)+ 
+  labs(x = "syncLM",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich.4$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_mean),shape=20)+ 
+  labs(x = "syncLM",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=rich.4$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_mean),shape=20)+ 
+  labs(x = "syncLM",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich.4$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_mean),shape=20)+ 
+  labs(x = "syncLM",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=rich.4$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_mean),shape=20)+ 
+  labs(x = "syncLM",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=rich.4$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_mean),shape=20)+ 
+  labs(x = "syncLM",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
@@
 
-A) richness + log VR
+A) total richness + log VR
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
   summarize(tidy(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
   summarize(glance(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(cv_1_visitation~richness+log_VR,data))) %>%
-  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "richness"))) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
   mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
@@
 
-p1=sta_polli2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
-  labs(x = "richness",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+p1=sta_polli2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
 
-p2=sta_polli2$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
-  labs(x = "richness",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p2=sta_polli2$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p3=sta_polli2$plots[[3]] + geom_point(data = na.omit (full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
-  labs(x = "richness",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p3=sta_polli2$plots[[3]] + geom_point(data = na.omit (full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p5=sta_polli2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
-  labs(x = "richness",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p5=sta_polli2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p6=sta_polli2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  richness, y = cv_1_visitation),shape=20)+ 
-  labs(x = "richness",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p6=sta_polli2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
@@
 ```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot (cv_1_visitation~log_VR)
+sta_polli2.1 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+log_VR,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli2.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log_VR",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli2.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log_VR",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli2.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log_VR",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli2.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log_VR",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli2.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ 
+  labs(x = "log_VR",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```
+
+\newpage
+
+B) total richness + Lorea and Mazancourt index
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+#model 2: total richness + Lorea and Mazancourt index
+sta_polli3<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+syncLM,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+sta_polli3<-sta_polli3 %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_polli3 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_polli3$p.value < 0.05|is.na(sta_polli3$p.value), T, F))%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+sta_polli_glance3<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+syncLM,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table8<-sta_polli_glance3 %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table8 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot (cv_1_visitation~ total richness)
+sta_polli3.1 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+syncLM,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli3.1$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli3.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli3.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli3.1$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli3.1$plots[[6]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_polli3.1$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_total, y = cv_1_visitation),shape=20)+ 
+  labs(x = "S_total",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6+p7
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model2 plot (cv_1_visitation~syncLM)
+sta_polli3.2 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+syncLM,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli3.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "syncLM",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli3.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "syncLM",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli3.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "syncLM",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli3.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "syncLM",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli3.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "syncLM",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_polli3.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ 
+  labs(x = "syncLM",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6+p7
+```
+
+\newpage
+
+C) mean richness + log VR
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+#model 3: mean richness + log VR
+sta_polli_Smean<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+log_VR,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+sta_polli_Smean<-sta_polli_Smean %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_polli_Smean %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_polli_Smean$p.value < 0.05|is.na(sta_polli_Smean$p.value), T, F))%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+sta_polli_glance_mod3<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+log_VR,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table9<-sta_polli_glance_mod3 %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table9 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model3 plot (cv_1_visitation~ mean richness)
+sta_polli_Smean_plot <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+log_VR,data))) %>%
+  mutate(mod = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
+  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli_Smean_plot$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli_Smean_plot$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli_Smean_plot$plots[[3]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli_Smean_plot$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli_Smean_plot$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model3 plot (cv_1_visitation~log_VR)
+sta_polli_Smean_plot2 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+log_VR,data))) %>%
+  mutate(mod = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
+  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli_Smean_plot2$plots[[1]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli_Smean_plot2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli_Smean_plot2$plots[[3]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli_Smean_plot2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli_Smean_plot2$plots[[6]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  log_VR, y = cv_1_visitation),shape=20)+ labs(x = "log_VR",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```
+
+\newpage
+
+D) mean richness + Lorea & Mazancourt index
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+#model 3: mean richness + log VR
+sta_polli_Smean2<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+syncLM,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+sta_polli_Smean2<-sta_polli_Smean2 %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_polli_Smean2 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_polli_Smean2$p.value <0.05|is.na(sta_polli_Smean2$p.value), T, F))%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+sta_polli_glance_mod4<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+syncLM,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table10<-sta_polli_glance_mod4 %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table10 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model4 plot (cv_1_visitation~ mean richness)
+sta_polli_Smean_plot4 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+syncLM,data))) %>%
+  mutate(mod = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
+  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli_Smean_plot4$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli_Smean_plot4$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli_Smean_plot4$plots[[3]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli_Smean_plot4$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli_Smean_plot4$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_polli_Smean_plot4$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6+p7
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model3 plot (cv_1_visitation~syncLM)
+sta_polli_Smean_plot4.2 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+syncLM,data))) %>%
+  mutate(mod = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
+  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
+                        geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli_Smean_plot4.2$plots[[1]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli_Smean_plot4.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli_Smean_plot4.2$plots[[3]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli_Smean_plot4.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli_Smean_plot4.2$plots[[6]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=sta_polli_Smean_plot4.2$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  syncLM, y = cv_1_visitation),shape=20)+ labs(x = "syncLM",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6+p7
+```

### 2022-09-28 script/stability.R
checking residuals and plots

@@ -11,7 +11,11 @@ library(tidyr)
 library(ggplot2)
 #install.packages("ggeffects")
 library(ggeffects)
-
+library(patchwork)
+library(ggcorrplot)
+library(ggpubr)
+#install.packages("qqplotr")
+library(qqplotr)
 
 Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
 str(Pollinator_Plant)
@@ -34,21 +38,59 @@ Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
 
 
 # datos sin plant_id (mean de las variables porque hay plantas con 2 indv, otras 3, etc)
+#nos quedamos con sitio - año - plant species
 pol_plant2=Pollinator_Plant %>%
   group_by(Site_ID,Year, Plant_gen_sp) %>%
   summarise_if(is.numeric, mean)
 
+levels(factor(pol_plant2$Plant_gen_sp)) #12 plant species 
+
+
+pol_plant2$Year <- factor(pol_plant2$Year)
+
+# plot fruit proportion and year for each plant species and site 
+plots3 <- pol_plant2 %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=Year, y=fruit_proportion, col =factor(Site_ID), shape=factor(Site_ID)) + 
+              scale_shape_manual(values = c(15,16,17,18,6,7,8,9,10,11,12,13,14))+ geom_point(size = 3) + ggtitle(.y[[1]]))
+
+plots3[[1]]+plots3[[2]]+plots3[[3]]+plots3[[4]]
+plots3[[5]]+plots3[[6]]+plots3[[7]]+plots3[[8]] 
+plots3[[9]]+plots3[[10]]+plots3[[11]]+plots3[[12]]
+
+
+# plot seed number and year for each plant species and site 
+plots3_seed <- pol_plant2 %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=Year, y=Seeds, col =factor(Site_ID), shape=factor(Site_ID)) + 
+              scale_shape_manual(values = c(15,16,17,18,6,7,8,9,10,11,12,13,14))+ geom_point(size = 3) + ggtitle(.y[[1]]))
+
[…]

### 2022-09-29 Rmd/Stability.Rmd
edit plots

@@
 
-Relationship between richness-synchrony with different synchrony indice.
-
-A- Total richness ~ log VR
+Relationship between synchrony ~ richness with different synchrony indice.
+
+A- log VR ~ Total richness
 
@@
   group_by(Plant_gen_sp) %>%
-  group_map(~ ggplot(.) + aes(x=log_VR, y=S_total) + 
- theme_bw()+ geom_point(size = 5) + labs(x = "log VR",y="Total richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))
+  group_map(~ ggplot(.) + aes(x=S_total, y=log_VR) + 
+ theme_bw()+ geom_point(size = 5) + labs(y = "log VR",x="Total richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))
 
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_total~log_VR,data))) %>%
+  mutate(mod = list(lm(log_VR~S_total,data))) %>%
   summarize(tidy(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_total~log_VR,data))) %>%
+  mutate(mod = list(lm(log_VR~S_total,data))) %>%
   summarize(glance(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_total~log_VR,data))) %>%
-  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
+  mutate(mod = list(lm(log_VR~S_total,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
   mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
@@
 
-p1=rich.1$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_total),shape=20)+ 
-  labs(x = "log_VR",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
-
-p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_total),shape=20)+ 
-  labs(x = "log_VR",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_total),shape=20)+ 
-  labs(x = "log_VR",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p4=rich.1$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_total),shape=20)+ 
-  labs(x = "log_VR",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_total),shape=20)+ 
-  labs(x = "log_VR",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_total),shape=20)+ 
-  labs(x = "log_VR",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p7=rich.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_total),shape=20)+ 
-  labs(x = "log_VR",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p1=rich.1$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = log_VR),shape=20)+ 
+  labs(x = "total_richness",y="log_VR",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=rich.1$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_total, y = log_VR),shape=20)+ 
+  labs(x = "total_richness",y="log_VR",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich.1$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_total, y = log_VR),shape=20)+ 
+  labs(x = "total_richness",y="log_VR",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=rich.1$plots[[4]] + geom_point(data =full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  S_total, y = log_VR),shape=20)+ 
+  labs(x = "total_richness",y="log_VR",subtitle = "H.calycinum")+scale_x_continuous(limits = c(4, 7))+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich.1$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  S_total, y = log_VR),shape=20)+ 
+  labs(x = "total_richness",y="log_VR",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=rich.1$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_total, y = log_VR),shape=20)+ 
+  labs(x = "total_richness",y="log_VR",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=rich.1$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_total, y = log_VR),shape=20)+ 
+  labs(x = "total_richness",y="log_VR",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
@@
 \newpage
-B- total richness ~ Loreau & Mazancourt syncrony index
+B- Loreau & Mazancourt syncrony index ~ total richness
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#plot
+plots_rich2 <- full_2 %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=S_total, y=syncLM) + 
+ theme_bw()+ geom_point(size = 5) + labs(x="Total richness",y = "syncLM")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))
+
+ggarrange(plots_rich2[[1]],plots_rich2[[2]],plots_rich2[[3]],plots_rich2[[4]],plots_rich2[[5]],plots_rich2[[6]],plots_rich2[[7]], ncol=3, nrow=3)
+
+```
+
+\newpage
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_total~syncLM,data))) %>%
+  mutate(mod = list(lm(syncLM ~S_total,data))) %>%
   summarize(tidy(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_total~syncLM,data))) %>%
+  mutate(mod = list(lm(syncLM ~S_total,data))) %>%
   summarize(glance(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_total~syncLM,data))) %>%
-  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
+  mutate(mod = list(lm(syncLM ~S_total,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
   mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
@@
 
-p1=rich.2$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_total),shape=20)+ 
-  labs(x = "syncLM",y="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
-
-p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_total),shape=20)+ 
-  labs(x = "syncLM",y="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_total),shape=20)+ 
-  labs(x = "syncLM",y="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_total),shape=20)+ 
-  labs(x = "syncLM",y="total richness",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p5=rich.2$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_total),shape=20)+ 
-  labs(x = "syncLM",y="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_total),shape=20)+ 
-  labs(x = "syncLM",y="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_total),shape=20)+ 
-  labs(x = "syncLM",y="total richness",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p1=rich.2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = syncLM),shape=20)+ 
+  labs(y = "syncLM",x="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=rich.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_total, y = syncLM),shape=20)+ 
+  labs(y = "syncLM",x="total richness",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_total, y = syncLM),shape=20)+ 
+  labs(y = "syncLM",x="total richness",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=rich.2$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  S_total, y = syncLM),shape=20)+ 
+  labs(y = "syncLM",x="total richness",subtitle = "H.calycinum") + scale_x_continuous(limits = c(4, 7)) +  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_total, y = syncLM),shape=20)+ 
+  labs(y = "syncLM",x="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=rich.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_total, y = syncLM),shape=20)+ 
+  labs(y = "syncLM",x="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=rich.2$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  S_total, y = syncLM),shape=20)+ 
+  labs(y = "syncLM",x="total richness",subtitle = "L.stoechas")+ scale_x_continuous(limits = c(5, 13))+  theme_classic()+theme(text = element_text(size=rel(3)))
 
@@
 
-C- mean richness ~ log VR
+C- log VR ~ mean richness
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#plot
+plots_rich3 <- full_2 %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes( x=S_mean, y=log_VR) + 
+ theme_bw()+ geom_point(size = 5) + labs(y = "log_VR",x="mean richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))
+
+ggarrange(plots_rich3[[1]],plots_rich3[[2]],plots_rich3[[3]],plots_rich3[[4]],plots_rich3[[5]],plots_rich3[[6]],plots_rich3[[7]], ncol=3, nrow=3)
+
+```
+
+\newpage
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
+  mutate(mod = list(lm(log_VR ~ S_mean,data))) %>%
   summarize(tidy(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
+  mutate(mod = list(lm(log_VR ~ S_mean,data))) %>%
   summarize(glance(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_mean~log_VR,data))) %>%
-  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
+  mutate(mod = list(lm(log_VR ~ S_mean,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
   mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
@@
 
-p1=rich.3$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  log_VR, y = S_mean),shape=20)+ 
-  labs(x = "log_VR",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
-
-p2=rich.3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  log_VR, y = S_mean),shape=20)+ 
-  labs(x = "log_VR",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p3=rich.3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  log_VR, y = S_mean),shape=20)+ 
-  labs(x = "log_VR",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p4=rich.3$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  log_VR, y = S_mean),shape=20)+ 
-  labs(x = "log_VR",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p5=rich.3$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+p1=rich.3$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = log_VR),shape=20)+ 
+  labs(y = "log_VR",x="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=rich.3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_mean, y = log_VR),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "C.ladanifer") + scale_x_continuous(limits = c(4, 11)) +  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich.3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_mean, y = log_VR),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "C.salviifolius")+ scale_x_continuous(limits = c(3, 12))+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=rich.3$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  S_mean, y = log_VR),shape=20)+ 
+  labs(x = "log_VR",y="S_mean",subtitle = "H.calycinum")+ scale_x_continuous(limits = c(2, 5.5))+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich.3$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  S_mean, y = log_VR),shape=20)+ 
   labs(x = "log_VR",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p6=rich.3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+p6=rich.3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = log_VR),shape=20)+ 
   labs(x = "log_VR",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
-p7=rich.3$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  log_VR, y = S_mean),shape=20)+ 
+p7=rich.3$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_mean, y = log_VR),shape=20)+ 
   labs(x = "log_VR",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
@@
 
-D- mean richness ~ Loreau & Mazancourt syncrony index
+D- Loreau & Mazancourt syncrony index ~  mean richness
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#plot
+plots_rich4 <- full_2 %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes( x=S_mean, y=syncLM) + 
+ theme_bw()+ geom_point(size = 5) + labs(y = "syncLM",x="mean richness")+ ggtitle(.y[[1]])+theme(text = element_text(size=18)))
+
+ggarrange(plots_rich4[[1]],plots_rich4[[2]],plots_rich4[[3]],plots_rich4[[4]],plots_rich4[[5]],plots_rich4[[6]],plots_rich4[[7]], ncol=3, nrow=3)
+
+```
+
+\newpage
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
+  mutate(mod = list(lm(syncLM ~ S_mean,data))) %>%
   summarize(tidy(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
+  mutate(mod = list(lm(syncLM ~ S_mean,data))) %>%
   summarize(glance(mod))%>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_mean~syncLM,data))) %>%
-  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "syncLM"))) %>%
+  mutate(mod = list(lm(syncLM ~ S_mean,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
   mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
@@
 
-p1=rich.4$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  syncLM, y = S_mean),shape=20)+ 
-  labs(x = "syncLM",y="S_mean",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
-
-p2=rich.4$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  syncLM, y = S_mean),shape=20)+ 
-  labs(x = "syncLM",y="S_mean",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p3=rich.4$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  syncLM, y = S_mean),shape=20)+ 
-  labs(x = "syncLM",y="S_mean",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p4=rich.4$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  syncLM, y = S_mean),shape=20)+ 
-  labs(x = "syncLM",y="S_mean",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p5=rich.4$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  syncLM, y = S_mean),shape=20)+ 
-  labs(x = "syncLM",y="S_mean",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p6=rich.4$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  syncLM, y = S_mean),shape=20)+ 
-  labs(x = "syncLM",y="S_mean",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
-
-p7=rich.4$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  syncLM, y = S_mean),shape=20)+ 
-  labs(x = "syncLM",y="S_mean",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p1=rich.4$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = syncLM),shape=20)+ 
+  labs(x = "S_mean",y="syncLM",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=rich.4$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_mean, y = syncLM),shape=20)+ 
+  labs(x = "S_mean",y="syncLM",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich.4$plots[[3]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_mean, y = syncLM),shape=20)+ 
+  labs(x = "S_mean",y="syncLM",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4=rich.4$plots[[4]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  S_mean, y = syncLM),shape=20)+ 
+  labs(x = "S_mean",y="syncLM",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich.4$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  S_mean, y = syncLM),shape=20)+ 
+  labs(x = "S_mean",y="syncLM",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=rich.4$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = syncLM),shape=20)+ 
+  labs(x = "S_mean",y="syncLM",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7=rich.4$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_mean, y = syncLM),shape=20)+ 
+  labs(x = "S_mean",y="syncLM",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
@@
 
-p7=sta_polli_Smean_plot4$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+p7=sta_polli_Smean_plot4$plots[[7]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula stoechas")), aes(x =  S_mean, y = cv_1_visitation),shape=20)+ labs(x = "S_mean",y="visitation rate stability",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
 

### 2022-09-29 script/stability.R
plots and residuals

@@ -510,7 +510,7 @@ sta_seed.1$plots[[7]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lav
 
 plots_rich <- full_2 %>%
   group_by(Plant_gen_sp) %>%
-  group_map(~ ggplot(.) + aes(x=log_VR, y=S_total) + 
+  group_map(~ ggplot(.) + aes(y=log_VR, x=S_total) + 
               geom_point() + ggtitle(.y[[1]]))
 
 plots_rich[[1]]+plots_rich[[2]]+plots_rich[[3]]+plots_rich[[4]]
@@ -519,13 +519,13 @@ plots_rich[[5]]+plots_rich[[6]]+plots_rich[[7]]
 #model
 rich<-full_2 %>%
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_total~log_VR,data))) %>%
+  mutate(mod = list(lm(log_VR ~S_total,data))) %>%
   summarize(tidy(mod))%>%
   ungroup()
 
 rich_glance<-full_2 %>%
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_total~log_VR,data))) %>%
+  mutate(mod = list(lm(log_VR ~S_total,data))) %>%
   summarize(glance(mod))%>%
   ungroup()
 
@@ -533,7 +533,7 @@ rich_glance<-full_2 %>%
 #checking residuals
 rich_resid<-full_2 %>%
   nest_by(Plant_gen_sp) %>%
-  mutate(model = list(lm(S_total~log_VR,data)))%>%
+  mutate(model = list(lm(log_VR ~S_total,data)))%>%
   mutate(plots = list(performance::check_model(model))) %>%
   ungroup()
 
@@ -548,123 +548,186 @@ plot(rich_resid$plots[[7]]) # Lavandula stoechas
 # model plot
 rich.1 <- full_2 %>%
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(S_total~log_VR,data))) %>%
-  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "log_VR"))) %>%
+  mutate(mod = list(lm(log_VR ~S_total,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
   mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
[…]

### 2022-09-30 script/Fruit_set.R
A.mellifera visitation rate and no apis (pollinator and hymenoptera)

@@ -109,7 +109,7 @@ levels(factor(fruit$plant_id))
 
 # sum fruit yes,fruit no, fruit preyed and fruit dispersed per individual plant 
 #(2015 and 2016 fruit is counted by branch, 2017-2018 no)
-#thus each individual plant in 2015-2016 has a number of fruit yes and fruit no (same that 2017-2018)
+
 fruit_yes<-aggregate(Fruit_Yes ~ Year+Site_ID+Plant_gen_sp+plant_id, data = fruit,FUN = sum)
 fruit_no<-aggregate(Fruit_No ~ Year+Site_ID+Plant_gen_sp+plant_id, data = fruit, FUN = sum)
 fruit_preyed<-aggregate(Fruit_preyed ~ Year+Site_ID+Plant_gen_sp+plant_id, data = fruit, FUN = sum)
@@ -393,11 +393,11 @@ levels(factor(focal$Orden))
 hym= focal %>% filter(Orden %in% "Hymenoptera")
 levels(factor(hym$Pollinator_genus))
 
-h<-c("Bembix","Chrysididae","Chrysis","Formiciidae","Megalodontes","Pemphredon","Philantus",
+hyme<-c("Bembix","Chrysididae","Chrysis","Formiciidae","Megalodontes","Pemphredon","Philantus",
      "Polistes","Sphecodes","Tachysphex","Thyreus","Vespula")
 
 
-focal = focal %>% filter(!Pollinator_genus %in% h)
+focal = focal %>% filter(!Pollinator_genus %in% hyme)
 
 
 #Diptera
@@ -405,10 +405,10 @@ Dipt= focal %>% filter(Orden %in% "Diptera")
 levels(factor(Dipt$Pollinator_genus))
 
 # remove all that is not Bombilidos, sirfidos and rhyncomyia (Diptera)
-d<-c("Bibio","Bibionidae", "Dasypogon","Dilophus","Empis","Lucilia","Sarcophaga",
+dip<-c("Bibio","Bibionidae", "Dasypogon","Dilophus","Empis","Lucilia","Sarcophaga",
      "Stomorhina","Stratyiomis")
 
-focal = focal %>% filter(!Pollinator_genus %in% d)
+focal = focal %>% filter(!Pollinator_genus %in% dip)
 
 
 #Coleoptera
@@ -491,6 +491,9 @@ focal$plant_id = ifelse(focal$Plant_individual=="AFE" |focal$Plant_individual== 
 
[…]

### 2022-10-05 script/models.R
Apis-no Apis and yearlike fixed factor

@@ -10,9 +10,10 @@ library(dplyr)
 library(patchwork)
 library(ggcorrplot)
 library(ggpubr)
+library (lme4)
 
 
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant_Apis_separada.csv") #400 observaciones
 str(Pollinator_Plant)
 Pollinator_Plant<-Pollinator_Plant[,-1]
 head(Pollinator_Plant)
@@ -136,6 +137,7 @@ corr <- round(cor(cor_general), 4)
 p.mat <- cor_pmat(cor_general)
 ggcorrplot(corr, hc.order = TRUE, type = "lower",
            lab = TRUE)
+
 
 
 # Models _ Seed numbers---- 
@@ -328,6 +330,169 @@ mod_seed.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen
 mod_seed.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  visitatio_rate, y = Seeds),shape=20)+ 
   labs(x = "visitation_rate",y="seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
+# visitation rate without Apis mellifera
+
+#plot
+plots_Visitation_rate_no_apis <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=No_Apis_visit_rate, y=Seeds) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+plots_Visitation_rate_no_apis[[1]]+plots_Visitation_rate_no_apis[[2]]+plots_Visitation_rate_no_apis[[3]]+plots_Visitation_rate_no_apis[[4]]
+plots_Visitation_rate_no_apis[[5]]+plots_Visitation_rate_no_apis[[6]]+plots_Visitation_rate_no_apis[[7]]+plots_Visitation_rate_no_apis[[8]] 
+plots_Visitation_rate_no_apis[[9]]+plots_Visitation_rate_no_apis[[10]]+plots_Visitation_rate_no_apis[[11]]+plots_Visitation_rate_no_apis[[12]]
+
+#model
[…]

### 2022-10-05 Rmd/model_with_year.Rmd
models with year

---
title: "Models with year"
output: pdf_document
date: '2022-10-05'
---

# Seed number

we analyse whether the visitation rate of all pollinators, years and their interaction affect to the seed number for each plant species

A- linear model: lm(Seeds~visitatio_rate * Year 
```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}

library(tidyverse)
library(broom.mixed)
library(broom)
library(lmerTest)
library(dplyr)
library(tidyr)
library(ggplot2)
library(ggeffects)
library(patchwork)
library(ggcorrplot)
library(ggpubr)
library(kableExtra)
library(sjPlot)

Pollinator_Plant<- read.csv("../Data/Pollinator_Plant_Apis_separada.csv") 
Pollinator_Plant<-Pollinator_Plant[,-1]

#Species out
spp_out <- Pollinator_Plant %>%
  group_by(Plant_gen_sp) %>%
  summarise(Unique_Id = n_distinct(Site_ID)) %>%
  filter(Unique_Id == 1) %>%
  select(Plant_gen_sp) %>% pull(Plant_gen_sp)

#Data with species in more than 1 site
Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)

# replace NAs by 0
# hay especies de plantas que presentan datos de fruit y seed pero no de polinizador (durante el tiempo observado no se ve ningun polinizador )
Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))

Pollinator_Plant$Year <- factor(Pollinator_Plant$Year)

#model
mod_seed_year<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(Seeds~visitatio_rate * Year,data))) %>%
  summarize(tidy(mod))%>%
  ungroup()

mod_seed_year<-mod_seed_year %>%
  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))

mod_seed_year %>% 
 kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
column_spec(6, bold = ifelse(mod_seed_year$p.value < 0.05| is.na(mod_seed_year$p.value), T, F) )%>%
  kable_styling(position="left")

```

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}

mod_seed_year_glance<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(Seeds~visitatio_rate * Year,data))) %>%
  summarize(glance(mod))%>%
  ungroup()

table1<-mod_seed_year_glance %>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Asphodelus fistulosus','A.fistulosus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus libanotis', 'C.libanotis', Plant_gen_sp))%>%
   mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus monspeliensis', 'C.monspeliensis', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Salvia rosmarinus', 'S.rosmarinus', Plant_gen_sp))%>%
  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Teucrium fruticans', 'T.fructicans', Plant_gen_sp))

table1 %>% 
    kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc") %>%
  kable_styling(font_size = 7,full_width = F, position="left")

```

\newpage

```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
mod_seed_year.1<-Pollinator_Plant %>%
  nest_by(Plant_gen_sp) %>%
  mutate(mod = list(lm(Seeds~visitatio_rate * Year,data)))

ggarrange(plot_model(mod_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus"),plot_model(mod_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus"),plot_model(mod_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer "),plot_model(mod_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis"),plot_model(mod_seed_year.1$mod[[5]], type = "int", title = "Cistus monspeliensis"),plot_model(mod_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius"),plot_model(mod_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum"),plot_model(mod_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium "),plot_model(mod_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata"),plot_model(mod_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas"),plot_model(mod_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus"),plot_model(mod_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans"),ncol=3,nrow = 4)

```

*Cistus monspeliensis* - *Halimium halimifolium* - *Teucrium fructicans*
Warning message:
In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,: prediction from a rank-deficient fit may be misleading

**Importante**: Cistus crispus en 2015 solo tiene dos valores, uno con 0 semillas y visitation rate 0.214; y otro con casi 40 semillas y visitation rate 0

### 2022-10-05 Rmd/Models.Rmd
visitation rate (Apis and no Apis)

@@
 
-Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") 
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant_Apis_separada.csv") 
 Pollinator_Plant<-Pollinator_Plant[,-1]
@@
 
-visitation rate is calculated like frequency/ flower abundance
+Visitation rate of all pollinators (hymenoptera, diptera and coleoptera) is calculated like frequency/ flower abundance
 
@@
 
+## Visitation rate of pollinators without Apis mellifera
+
+visitation rate (frequency/ flower abundance) is calculated to all pollinators no apis mellifera.
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+mod_fruitproportion_polli_no_api<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~No_Apis_visit_rate + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_fruitproportion_polli_no_api<-mod_fruitproportion_polli_no_api %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruitproportion_polli_no_api<-filter(mod_fruitproportion_polli_no_api, !term == "sd__(Intercept)")
+
+mod_fruitproportion_polli_no_api %>% 
+kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(mod_fruitproportion_polli_no_api$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_fruitproportion_polli_no_api_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~No_Apis_visit_rate + (1|Site_ID),family=binomial,data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_fruitproportion_polli_no_api_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_fruitproportion_polli_no_api.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~No_Apis_visit_rate + (1|Site_ID),family=binomial,data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "No_Apis_visit_rate"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1= mod_fruitproportion_polli_no_api.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2= mod_fruitproportion_polli_no_api.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_fruitproportion_polli_no_api.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4= mod_fruitproportion_polli_no_api.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5= mod_fruitproportion_polli_no_api.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6= mod_fruitproportion_polli_no_api.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7= mod_fruitproportion_polli_no_api.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8= mod_fruitproportion_polli_no_api.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9= mod_fruitproportion_polli_no_api.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10= mod_fruitproportion_polli_no_api.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_fruitproportion_polli_no_api.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12= mod_fruitproportion_polli_no_api.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  No_Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "visit_rate(no A.mellifera)",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+## Apis mellifera visitation rate
+
+Only data of Apis mellifera
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# visistation rate A.mellifera
+mod_fruitproportion__apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_fruitproportion__apis<-mod_fruitproportion__apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruitproportion__apis<-filter(mod_fruitproportion__apis, !term == "sd__(Intercept)")
+
+mod_fruitproportion__apis %>% 
+kable("latex",booktabs = TRUE, digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(mod_fruitproportion__apis$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_fruitproportion__apis_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate + (1|Site_ID),family=binomial,data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_fruitproportion__apis_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_fruitproportion__apis.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate + (1|Site_ID),family=binomial,data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms ="Apis_visit_rate")))   %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1= mod_fruitproportion__apis.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2= mod_fruitproportion__apis.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=mod_fruitproportion__apis.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4= mod_fruitproportion__apis.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5= mod_fruitproportion__apis.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6= mod_fruitproportion__apis.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7= mod_fruitproportion__apis.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8= mod_fruitproportion__apis.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9= mod_fruitproportion__apis.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10= mod_fruitproportion__apis.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11=mod_fruitproportion__apis.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+ labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12= mod_fruitproportion__apis.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Apis_visit_rate, y = fruit_proportion),shape=20)+labs(x = "Apis_visit_rate",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
 ## Hymenoptera visitation
@@
 
+\newpage
+
+## Hymenoptera visitation rate without A.mellifera
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+mod_fruitproportion_hyme_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit_sin_apis + (1|Site_ID),family=binomial,data)))%>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_fruitproportion_hyme_no_apis<-mod_fruitproportion_hyme_no_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruitproportion_hyme_no_apis<-filter(mod_fruitproportion_hyme_no_apis, !term == "sd__(Intercept)")
+
+mod_fruitproportion_hyme_no_apis %>% 
+kable("latex",booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(mod_fruitproportion_hyme_no_apis$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_fruitproportion_hyme_no_apis_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit_sin_apis + (1|Site_ID),family=binomial,data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_fruitproportion_hyme_no_apis_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_fruitproportion_hyme_no_apis.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit_sin_apis + (1|Site_ID),family=binomial,data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Hym_visit_sin_apis"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1 = mod_fruitproportion_hyme_no_apis.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2 = mod_fruitproportion_hyme_no_apis.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3 = mod_fruitproportion_hyme_no_apis.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4 = mod_fruitproportion_hyme_no_apis.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5 = mod_fruitproportion_hyme_no_apis.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6 = mod_fruitproportion_hyme_no_apis.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7 = mod_fruitproportion_hyme_no_apis.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+ 
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8 = mod_fruitproportion_hyme_no_apis.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9 = mod_fruitproportion_hyme_no_apis.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10 = mod_fruitproportion_hyme_no_apis.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11 = mod_fruitproportion_hyme_no_apis.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12 = mod_fruitproportion_hyme_no_apis.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Hym_visit_sin_apis, y = fruit_proportion),shape=20)+
+  labs(x = "Hym_visit_sin_apis",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
 ## Pollinator frequency
@@
 ## Visitation rate
+Visitation rate of all pollinators (hymenoptera, diptera and coleoptera)
 
@@
 
-## Hymenoptera visitation
+## Visitation rate of pollinators without Apis mellifera
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+mod_seed_Vr_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~No_Apis_visit_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_Vr_no_apis<-mod_seed_Vr_no_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_Vr_no_apis<-filter(mod_seed_Vr_no_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_Vr_no_apis %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_Vr_no_apis$p.value < 0.05, T, F)) %>% kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_Vr_no_apis_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~No_Apis_visit_rate+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_Vr_no_apis_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%  kable_styling(font_size = 8,full_width = F, position="center")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_seed_Vr_no_apis_trial.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~No_Apis_visit_rate+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "No_Apis_visit_rate"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1 = mod_seed_Vr_no_apis_trial.2 $ plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x = No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate",y ="seed_number",subtitle = "A.fistulosus") + theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2 = mod_seed_Vr_no_apis_trial.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "C.crispus")+ theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3 = mod_seed_Vr_no_apis_trial.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "C.ladanifer")+ theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4 = mod_seed_Vr_no_apis_trial.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate", y ="seed_number",subtitle = "C.libanotis")+ theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5 = mod_seed_Vr_no_apis_trial.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate", y = "seed_number", subtitle = "C.monspeliensis")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6 = mod_seed_Vr_no_apis_trial.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate", y = "seed_number",subtitle = "C.salviifolius")+ theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7 = mod_seed_Vr_no_apis_trial.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate", y = "seed_number",subtitle = "H.calycinum") + theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8 = mod_seed_Vr_no_apis_trial.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20) + labs(x = "No_Apis_visit_rate", y = "seed_number",subtitle = "H.halimifolium")+ theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9 = mod_seed_Vr_no_apis_trial.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10 = mod_seed_Vr_no_apis_trial.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11 = mod_seed_Vr_no_apis_trial.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12 = mod_seed_Vr_no_apis_trial.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  No_Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "No_Apis_visit_rate",y = "seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
+\newpage
+
+## Visitation rate of Apis mellifera
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+mod_seed_Vr_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Apis_visit_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_Vr_apis<-mod_seed_Vr_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_Vr_apis<-filter(mod_seed_Vr_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_Vr_apis %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_Vr_apis$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_Vr_apis_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Apis_visit_rate+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_Vr_apis_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_seed_Vr_apis_trial.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Apis_visit_rate+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Apis_visit_rate"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1 = mod_seed_Vr_apis_trial.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2 = mod_seed_Vr_apis_trial.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+  labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3 = mod_seed_Vr_apis_trial.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4 = mod_seed_Vr_apis_trial.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5 = mod_seed_Vr_apis_trial.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6 = mod_seed_Vr_apis_trial.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7 = mod_seed_Vr_apis_trial.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8 = mod_seed_Vr_apis_trial.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9 = mod_seed_Vr_apis_trial.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10 = mod_seed_Vr_apis_trial.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11 = mod_seed_Vr_apis_trial.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12 = mod_seed_Vr_apis_trial.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Apis_visit_rate, y = Seeds),shape=20)+ labs(x = "Apis_visit_rate",y="seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+## Hymenoptera visitation rate
 
@@
 
+## Hymenoptera visitation rate without A.mellifera
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#model
+mod_seed_hym_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit_sin_apis+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_hym_no_apis<-mod_seed_hym_no_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_hym_no_apis<-filter(mod_seed_hym_no_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_hym_no_apis %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_hym_no_apis$p.value < 0.05, T, F) ) %>%  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_hym_no_apis_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit_sin_apis+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_hym_no_apis_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_seedhym_no_apis.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds~Hym_visit_sin_apis+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Hym_visit_sin_apis"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1 = mod_seedhym_no_apis.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+ labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2 = mod_seedhym_no_apis.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+ labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3 = mod_seedhym_no_apis.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4 = mod_seedhym_no_apis.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+ labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5 = mod_seedhym_no_apis.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+ labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6 = mod_seedhym_no_apis.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+ labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7 = mod_seedhym_no_apis.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+ labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8 = mod_seedhym_no_apis.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+ labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9 = mod_seedhym_no_apis.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10 = mod_seedhym_no_apis.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+ labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11 = mod_seedhym_no_apis.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12 = mod_seedhym_no_apis.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Hym_visit_sin_apis, y = Seeds),shape=20)+ labs(x = "Hym_visit_sin_apis",y="seed_number",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+
 ## Pollinator frequency
@@
 
-## Hymenoptera visitation
+\newpage 
+## Visitation rate of pollinator without Apis mellifera
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
+
+mod_seed_weight_VR_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~No_Apis_visit_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_weight_VR_no_apis<-mod_seed_weight_VR_no_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_weight_VR_no_apis<-filter(mod_seed_weight_VR_no_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_weight_VR_no_apis %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_weight_VR_no_apis$p.value < 0.05, T, F) )%>% kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_weight_VR_no_apis_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~No_Apis_visit_rate+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_weight_VR_no_apis_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+mod_seed_weight_VR_no_apis.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~No_Apis_visit_rate+(1|Site_ID),data))) %>%  mutate(model1 = list(ggeffects::ggpredict(model, terms = "No_Apis_visit_rate"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+ geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1 = mod_seed_weight_VR_no_apis.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2 = mod_seed_weight_VR_no_apis.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3 = mod_seed_weight_VR_no_apis.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4 = mod_seed_weight_VR_no_apis.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5 = mod_seed_weight_VR_no_apis.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6 = mod_seed_weight_VR_no_apis.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7 = mod_seed_weight_VR_no_apis.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8 = mod_seed_weight_VR_no_apis.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9 = mod_seed_weight_VR_no_apis.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10 = mod_seed_weight_VR_no_apis.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11 = mod_seed_weight_VR_no_apis.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12 = mod_seed_weight_VR_no_apis.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  No_Apis_visit_rate, y = Seed_weight),shape=20)+ 
+  labs(x = "No_Apis_visit_rate",y="Seed_weight",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+\newpage
+## Visitation rate of Apis mellifera
+
+```{r echo=FALSE, message=FALSE, warning=FALSE, out.width="100%"}
+
+#model
+mod_seed_weight_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Apis_visit_rate+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_weight_apis<-mod_seed_weight_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_weight_apis<-filter(mod_seed_weight_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_weight_apis %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_weight_apis$p.value < 0.05, T, F) )%>% kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_weight_apis_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Apis_visit_rate+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_weight_apis_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+mod_seed_weight_apis.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Apis_visit_rate+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Apis_visit_rate"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1 = mod_seed_weight_apis.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2 = mod_seed_weight_apis.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+ labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3 = mod_seed_weight_apis.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4 = mod_seed_weight_apis.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+ labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5 = mod_seed_weight_apis.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6 = mod_seed_weight_apis.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7 = mod_seed_weight_apis.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+ labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8 = mod_seed_weight_apis.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9 = mod_seed_weight_apis.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10 = mod_seed_weight_apis.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+ labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11 = mod_seed_weight_apis.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+ labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12 = mod_seed_weight_apis.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Apis_visit_rate, y = Seed_weight),shape=20)+ labs(x = "Apis_visit_rate",y="Seed_weight",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
+## Hymenoptera visitation rate
 
@@
 
+\newpage
+## Hymenoptera visitation rate without A.mellifera
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+#model
+mod_seed_weight_hym_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit_sin_apis+(1|Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+mod_seed_weight_hym_no_apis<-mod_seed_weight_hym_no_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_weight_hym_no_apis<-filter(mod_seed_weight_hym_no_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_seed_weight_hym_no_apis %>% 
+kable("latex", booktabs = TRUE,digits =  4, linesep = c("","\\addlinespace")) %>% column_spec(7, bold = ifelse(mod_seed_weight_hym_no_apis$p.value < 0.05, T, F) )%>%  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%"}
+
+mod_seed_weight_hym_no_apis_glance<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit_sin_apis+(1|Site_ID),data))) %>%
+  summarize(glance(model))%>%
+  ungroup()
+
+mod_seed_weight_hym_no_apis_glance %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="center")
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot 
+mod_seed_weight_hym_no_apis.2 <- Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seed_weight~Hym_visit_sin_apis+(1|Site_ID),data))) %>%
+  mutate(model1 = list(ggeffects::ggpredict(model, terms = "Hym_visit_sin_apis"))) %>%
+  mutate(plots = list(ggplot(model1, aes(x, predicted)) + geom_line() +
+ geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1 = mod_seed_weight_hym_no_apis.2$plots[[1]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Asphodelus fistulosus"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "A.fistulosus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2 = mod_seed_weight_hym_no_apis.2$plots[[2]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "C.crispus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3 = mod_seed_weight_hym_no_apis.2$plots[[3]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p4 = mod_seed_weight_hym_no_apis.2$plots[[4]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus libanotis"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "C.libanotis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5 = mod_seed_weight_hym_no_apis.2$plots[[5]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus monspeliensis"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "C.monspeliensis")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6 = mod_seed_weight_hym_no_apis.2$plots[[6]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p7 = mod_seed_weight_hym_no_apis.2$plots[[7]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium calycinum"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "H.calycinum")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p8 = mod_seed_weight_hym_no_apis.2$plots[[8]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p9 = mod_seed_weight_hym_no_apis.2$plots[[9]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p10 = mod_seed_weight_hym_no_apis.2$plots[[10]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Lavandula stoechas"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "L.stoechas")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p11 = mod_seed_weight_hym_no_apis.2$plots[[11]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Salvia rosmarinus"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+  labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "S.rosmarinus")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p12 = mod_seed_weight_hym_no_apis.2$plots[[12]] + geom_point(data = Pollinator_Plant %>% filter(Plant_gen_sp == "Teucrium fruticans"), aes(x =  Hym_visit_sin_apis, y = Seed_weight),shape=20)+ 
+labs(x = "Hym_visit_sin_apis",y="Seed_weight",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p4+p5+p6+p7+p8+p9+p10+p11+p12
+
+```
+
 ## Frequency
@@
 
-## join together Lavandula species 
+# join together Lavandula species 
 (L.peduncalata (49 obs) and L.stoechas (24 obs))

### 2022-10-06 script/models.R
interaction of visitation rate and year analysed on seed

@@ -2038,7 +2038,7 @@ mod_fruitproportion.4$plots[[12]] + geom_point(data = Pollinator_Plant %>% filte
 ##############################
 
 # Incluyeno año como factor fijo ----
-# seed number
+# seed number----
 str(Pollinator_Plant)
 
 Pollinator_Plant$Year <- factor(Pollinator_Plant$Year)
@@ -2080,22 +2080,41 @@ mod_seed_year.1<-Pollinator_Plant %>%
   nest_by(Plant_gen_sp) %>%
   mutate(mod = list(lm(Seeds~visitatio_rate * Year,data)))
 
-plot_model(mod_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+plot_model(mod_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
 get_model_data(mod_seed_year.1$mod[[1]], type = "int")
 
 plot_model(mod_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
 get_model_data(mod_seed_year.1$mod[[2]], type = "int")
 
-plot_model(mod_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer ")
-plot_model(mod_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis")
-plot_model(mod_seed_year.1$mod[[5]], type = "int", title = "Cistus monspeliensis")
-plot_model(mod_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius")
-plot_model(mod_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum")
-plot_model(mod_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium ")
-plot_model(mod_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
-plot_model(mod_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas")
-plot_model(mod_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
-plot_model(mod_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+plot_model(mod_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
[…]

### 2022-10-06 Rmd/model_with_year.Rmd
models with year

@@
 
+**Visitation rate (all pollinators)**
+
 we analyse whether the visitation rate of all pollinators, years and their interaction affect to the seed number for each plant species
 
-A- linear model: lm(Seeds~visitatio_rate * Year 
+**A-** linear model: lm(Seeds~visitatio_rate * Year)
+
 ```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
@@
 \newpage
-
 ```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
@@
 
-ggarrange(plot_model(mod_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus"),plot_model(mod_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus"),plot_model(mod_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer "),plot_model(mod_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis"),plot_model(mod_seed_year.1$mod[[5]], type = "int", title = "Cistus monspeliensis"),plot_model(mod_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius"),plot_model(mod_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum"),plot_model(mod_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium "),plot_model(mod_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata"),plot_model(mod_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas"),plot_model(mod_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus"),plot_model(mod_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans"),ncol=3,nrow = 4)
+# estimates of model 
+ggarrange(plot_model(mod_seed_year.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3), ncol=3,nrow = 4)
+
+```
+
+\newpage
+Predicte values of seed number
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+mod_seed_year.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds~visitatio_rate * Year,data)))
+
+ggarrange(plot_model(mod_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[5]], type = "int", title = "Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE), ncol=3,nrow = 4)
 
@@
 **Importante**: Cistus crispus en 2015 solo tiene dos valores, uno con 0 semillas y visitation rate 0.214; y otro con casi 40 semillas y visitation rate 0
+
+\newpage
+
+Predicted values of Seeds for *Cistus crispus*
+```{r,echo=FALSE, warning=FALSE,message=FALSE}
+get_model_data(mod_seed_year.1$mod[[2]], type = "int")
+
+```
+
+\newpage
+
+**B-** linear mixed model with site ID like random factor
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#model
+mod_mix_seed_year<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds ~ visitatio_rate * Year + (1 | Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+mod_mix_seed_year<-mod_mix_seed_year %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_seed_year<-filter(mod_mix_seed_year, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_mix_seed_year %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(7, bold = ifelse(mod_mix_seed_year$p.value < 0.05, T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+#model plot
+mod_mix_seed_year.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lmer(Seeds ~ visitatio_rate * Year + (1 | Site_ID),data)))
+
+# estimates of model 
+ggarrange(plot_model(mod_mix_seed_year.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3), ncol=3,nrow = 4)
+
+```
+
+\newpage
+Predicted values of Seeds
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_mix_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis", show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum", show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_mix_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+,ncol=3,nrow = 4)
+
+```
+
+*Cistus monspeliensis* - *Halimium halimifolium* - *Teucrium fructicans* 
+Could not compute variance-covariance matrix of predictions. No confidence intervals are returned.
+
+**se prueban modelos con year like random slope**
+
+Hay especies que dan problema porque hay menos observaciones que 
+random effect.
+El error dice:  the random-effects parameters and the residual variance (or scale parameter) are probably unidentifiable.
+Las especies que dan problema y habria que eliminar son: Halimium calycinum, Lavandula pedunculata, Lavandula stoechas, Salvia rosmarinus
+
+\newpage
+**Visitation rate of *Apis mellifera* **
+
+**A-** linear model: lm(Seeds ~ Apis_visitatio_rate * Year)
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#model
+mod_seed_year_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ Apis_visit_rate * Year,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_seed_year_apis<-mod_seed_year_apis %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_year_apis %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_seed_year_apis$p.value < 0.05| is.na(mod_seed_year_apis$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+mod_seed_year_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ Apis_visit_rate * Year,data)))
+
+ggarrange(plot_model(mod_seed_year_apis.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_apis.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3), ncol=3,nrow = 4)
+
+```
+
+\newpage
+
+Predicted values of Seeds 
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE), ncol=3,nrow = 4)
+
+```
+
+*Asphodelus fistulosus* - *Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans*
+
+Warning message: In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,: prediction from a rank-deficient fit may be misleading
+
+\newpage
+**B-** linear mixed model with site ID like random factor
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#model
+mod_mix_seed_year_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds ~ Apis_visit_rate * Year + (1 | Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+mod_mix_seed_year_apis<-mod_mix_seed_year_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_seed_year_apis<-filter(mod_mix_seed_year_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_mix_seed_year_apis %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(7, bold = ifelse(mod_mix_seed_year_apis$p.value < 0.05, T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+#model plot
+mod_mix_seed_year_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lmer(Seeds ~ Apis_visit_rate * Year + (1 | Site_ID),data)))
+
+ggarrange(plot_model(mod_mix_seed_year_apis.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_apis.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_mix_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_mix_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+```
+
+*Asphodelus fistulosus* - *Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans*
+
+Could not compute variance-covariance matrix of predictions. No confidence intervals are returned
+
+\newpage
+**Visitation rate of pollinator without *Apis mellifera* **
+
+**A-** linear model: lm(Seeds ~ No_Apis_visitatio_rate * Year)
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#model
+mod_seed_year_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ No_Apis_visit_rate * Year,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_seed_year_no_apis<-mod_seed_year_no_apis %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_year_no_apis %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_seed_year_no_apis$p.value < 0.05| is.na(mod_seed_year_no_apis$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+#model plot
+mod_seed_year_no_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ No_Apis_visit_rate * Year,data)))
+
+ggarrange(plot_model(mod_seed_year_no_apis.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_no_apis.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+```
+
+*Cistus monspeliensis* - *Halimium halimifolium* - *Teucrium fructicans* 
+Warning message:
+In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,: prediction from a rank-deficient fit may be misleading
+
+\newpage
+
+**B-** linear mixed model with site ID like random factor
+
+Warning messages:Some predictor variables are on very different scales: consider rescaling. The warning occurred in Salvia rosmarinus
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#model
+mod_mix_seed_year_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds ~ No_Apis_visit_rate * Year + (1 | Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+mod_mix_seed_year_no_apis<-mod_mix_seed_year_no_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_seed_year_no_apis<-filter(mod_mix_seed_year_no_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_mix_seed_year_no_apis %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(7, bold = ifelse(mod_mix_seed_year_no_apis$p.value < 0.05, T, F) )%>%  kable_styling(position="left")
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+#model plot
+mod_mix_seed_year_no_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lmer(Seeds ~ No_Apis_visit_rate * Year + (1 | Site_ID),data)))
+
+ggarrange(plot_model(mod_mix_seed_year_no_apis.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[2]], title = "Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_mix_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_mix_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+```
+
+\newpage
+**Visitation rate of hymenoptera **
+
+**A-** linear model: lm(Seeds ~ No_Apis_visitatio_rate * Year)
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#model
+mod_seed_year_hym<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ Hym_visit * Year,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_seed_year_hym<-mod_seed_year_hym %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_year_hym %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_seed_year_hym$p.value < 0.05| is.na(mod_seed_year_hym$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+mod_seed_year_hym.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ Hym_visit * Year,data)))
+
+ggarrange(plot_model(mod_seed_year_hym.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_seed_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_seed_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+```
+
+\newpage
+
+**B-** linear mixed model with site ID like random factor
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#model
+mod_mix_seed_year_hym<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds ~ Hym_visit * Year + (1 | Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+mod_mix_seed_year_hym<-mod_mix_seed_year_hym %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_seed_year_hym<-filter(mod_mix_seed_year_hym, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_mix_seed_year_hym %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(7, bold = ifelse(mod_mix_seed_year_hym$p.value < 0.05, T, F) )%>%  kable_styling(position="left")
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+#model plot
+mod_mix_seed_year_hym.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lmer(Seeds ~ Hym_visit * Year + (1 | Site_ID),data)))
+
+ggarrange(plot_model(mod_mix_seed_year_hym.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_mix_seed_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+```
+
+\newpage
+**Visitation rate of hymenoptera without A.mellifera **
+
+**A-** linear model: lm(Seeds ~ No_Apis_visitatio_rate * Year)
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+# linear model 
+mod_seed_year_hym_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ Hym_visit_sin_apis * Year,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_seed_year_hym_no_apis<-mod_seed_year_hym_no_apis %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_year_hym_no_apis %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_seed_year_hym_no_apis$p.value < 0.05| is.na(mod_seed_year_hym_no_apis$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+#model plot
+mod_seed_year_hym_no_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ Hym_visit_sin_apis * Year,data)))
+
+ggarrange(plot_model(mod_seed_year_hym_no_apis.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_seed_year_hym_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_seed_year_hym_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+```
+
+\newpage
+
+**B-** linear mixed model with site ID like random factor
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#model
+mod_mix_seed_year_hym_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds ~ Hym_visit_sin_apis * Year + (1 | Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+mod_mix_seed_year_hym_no_apis<-mod_mix_seed_year_hym_no_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_seed_year_hym_no_apis<-filter(mod_mix_seed_year_hym_no_apis, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_mix_seed_year_hym_no_apis %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(7, bold = ifelse(mod_mix_seed_year_hym_no_apis$p.value < 0.05, T, F) )%>%  kable_styling(position="left")
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+#model plot
+mod_mix_seed_year_hym_no_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lmer(Seeds ~ Hym_visit_sin_apis * Year + (1 | Site_ID),data)))
+
+ggarrange(plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+```

### 2022-10-07 script/models.R
fruit proportion and year analysed

@@ -2097,6 +2097,21 @@ plot_model(mod_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas"
 plot_model(mod_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
 plot_model(mod_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
 
+
+plot_model(mod_seed_year.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[2]], type = "pred", title = " Cistus crispus",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[4]], type = "pred",title = "Cistus libanotis",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[5]], type = "pred", title = "Cistus monspeliensis",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[7]], type = "pred",title = " Halimium calycinum",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus",show.data = TRUE)
+plot_model(mod_seed_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans",show.data = TRUE)
+
+
 # estimates of model 
 plot_model(mod_seed_year.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3)
 plot_model(mod_seed_year.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3)
[…]

### 2022-10-07 Rmd/model_with_year.Rmd
fruit proportion and year

@@
 Predicte values of seed number
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-mod_seed_year.1<-Pollinator_Plant %>%
-  nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(Seeds~visitatio_rate * Year,data)))
-
-ggarrange(plot_model(mod_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[5]], type = "int", title = "Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE), ncol=3,nrow = 4)
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_seed_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus",show.data = TRUE)
+p2=plot_model(mod_seed_year.1$mod[[2]], type = "pred", title = " Cistus crispus",show.data = TRUE)
+p3=plot_model(mod_seed_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer",show.data = TRUE)
+p4=plot_model(mod_seed_year.1$mod[[4]], type = "pred",title = "Cistus libanotis",show.data = TRUE)
+p5=plot_model(mod_seed_year.1$mod[[5]], type = "pred", title = "Cistus monspeliensis",show.data = TRUE)
+p6=plot_model(mod_seed_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius",show.data = TRUE)
+
+p1.1=plot_model(mod_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_seed_year.1$mod[[5]], type = "int", title = "Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$visitatio_rate,p1$Year,p1.1,
+p2$visitatio_rate,p2$Year,p2.1,
+p3$visitatio_rate,p3$Year,p3.1,
+p4$visitatio_rate,p4$Year,p4.1,
+p5$visitatio_rate,p5$Year,p5.1,
+p6$visitatio_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_seed_year.1$mod[[7]], type = "pred",title = " Halimium calycinum",show.data = TRUE)
+p8=plot_model(mod_seed_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium",show.data = TRUE)
+p9=plot_model(mod_seed_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata",show.data = TRUE)
+p10=plot_model(mod_seed_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas",show.data = TRUE)
+p11=plot_model(mod_seed_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus",show.data = TRUE)
+p12=plot_model(mod_seed_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans",show.data = TRUE)
+
+p7.1=plot_model(mod_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$visitatio_rate,p7$Year,p7.1,
+p8$visitatio_rate,p8$Year,p8.1,
+p9$visitatio_rate,p9$Year,p9.1,
+p10$visitatio_rate,p10$Year,p10.1,
+p11$visitatio_rate,p11$Year,p11.1,
+p12$visitatio_rate,p12$Year,p12.1,ncol=3,nrow = 6)
 
@@
 ```
+
+\newpage
+**Richness **
+
+**A-** linear model: lm(Seeds ~ richness * Year)
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+# linear model 
+mod_seed_year_richness<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ richness * Year,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_seed_year_richness<-mod_seed_year_richness %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_seed_year_richness %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_seed_year_richness$p.value < 0.05| is.na(mod_seed_year_richness$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+#model plot
+mod_seed_year_richness.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(Seeds ~ richness * Year,data)))
+
+ggarrange(plot_model(mod_seed_year_richness.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_seed_year_richness.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_seed_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_seed_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+```
+
+\newpage
+
+**B-** linear mixed model with site ID like random factor
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+#model
+mod_mix_seed_year_richness<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(model = list(lmer(Seeds ~ richness * Year + (1 | Site_ID),data))) %>%
+  summarise(broom.mixed::tidy(model)) %>%
+  ungroup()
+
+mod_mix_seed_year_richness<-mod_mix_seed_year_richness %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_seed_year_richness<-filter(mod_mix_seed_year_richness, !term == "sd__(Intercept)" & !term =="sd__Observation")
+
+mod_mix_seed_year_richness %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(7, bold = ifelse(mod_mix_seed_year_richness$p.value < 0.05, T, F) )%>%  kable_styling(position="left")
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+#model plot
+mod_mix_seed_year_richness.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lmer(Seeds ~ richness * Year + (1 | Site_ID),data)))
+
+ggarrange(plot_model(mod_mix_seed_year_richness.1$mod[[1]], title = " Asphodelus fistulosus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[2]], title = "  Cistus crispus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[3]], title = " Cistus ladanifer",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[4]], title = "Cistus libanotis",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[5]], title = "Cistus monspeliensis",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[6]], title = " Cistus salviifolius",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[7]], title = " Halimium calycinum",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[8]], title = " Halimium halimifolium",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[9]], title = " Lavandula pedunculata",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[10]], title = " Lavandula stoechas",show.values = TRUE,value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[11]], title = " Salvia rosmarinus",show.values = TRUE, value.offset = .3),
+plot_model(mod_mix_seed_year_richness.1$mod[[12]], title = " Teucrium fruticans",show.values = TRUE, value.offset = .3),ncol=3,nrow = 4)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
+
+ggarrange(plot_model(mod_mix_seed_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
+plot_model(mod_mix_seed_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+```
+
+\newpage
+
+# Fruit proportion
+
+**visitation rate (all pollinator)**
+
+**A-** GLM binomial (cbind(fruit_formado, Fruit_No))
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+mod_fruit_year<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ visitatio_rate * Year,data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_fruit_year<-mod_fruit_year %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruit_year %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_fruit_year$p.value < 0.05| is.na(mod_fruit_year$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+mod_fruit_year.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ visitatio_rate * Year,data,family = binomial)))
+
+p1=plot_model(mod_fruit_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_fruit_year.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_fruit_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_fruit_year.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_fruit_year.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_fruit_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_fruit_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_fruit_year.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_fruit_year.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_fruit_year.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_fruit_year.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_fruit_year.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$visitatio_rate,p1$Year,p1.1,
+p2$visitatio_rate,p2$Year,p2.1,
+p3$visitatio_rate,p3$Year,p3.1,
+p4$visitatio_rate,p4$Year,p4.1,
+p5$visitatio_rate,p5$Year,p5.1,
+p6$visitatio_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_fruit_year.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_fruit_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_fruit_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_fruit_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_fruit_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_fruit_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_fruit_year.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_fruit_year.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_fruit_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_fruit_year.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_fruit_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_fruit_year.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$visitatio_rate,p7$Year,p7.1,
+p8$visitatio_rate,p8$Year,p8.1,
+p9$visitatio_rate,p9$Year,p9.1,
+p10$visitatio_rate,p10$Year,p10.1,
+p11$visitatio_rate,p11$Year,p11.1,
+p12$visitatio_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+\newpage
+
+**B-** GLMM binomial (ramdon= Site_ID)
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# glmm binomial
+mod_mix_fruit_year<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate *Year + (1|Site_ID),data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_mix_fruit_year<-mod_mix_fruit_year %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_fruit_year<-filter(mod_mix_fruit_year, !term == "sd__(Intercept)")
+
+mod_mix_fruit_year %>% 
+kable("latex",booktabs = TRUE,digits =  4,longtable = T, linesep = "") %>% column_spec(6, bold = ifelse(mod_mix_fruit_year$p.value < 0.05, T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+mod_mix_fruit_year.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~visitatio_rate *Year + (1|Site_ID),data,family = binomial)))
+
+p1=plot_model(mod_mix_fruit_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_mix_fruit_year.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_fruit_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_fruit_year.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_fruit_year.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_mix_fruit_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_fruit_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_mix_fruit_year.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_mix_fruit_year.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_mix_fruit_year.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_mix_fruit_year.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_mix_fruit_year.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$visitatio_rate,p1$Year,p1.1,
+p2$visitatio_rate,p2$Year,p2.1,
+p3$visitatio_rate,p3$Year,p3.1,
+p4$visitatio_rate,p4$Year,p4.1,
+p5$visitatio_rate,p5$Year,p5.1,
+p6$visitatio_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_fruit_year.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_fruit_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_fruit_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_fruit_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_fruit_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_fruit_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_fruit_year.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_mix_fruit_year.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_mix_fruit_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_mix_fruit_year.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_mix_fruit_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_mix_fruit_year.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$visitatio_rate,p7$Year,p7.1,
+p8$visitatio_rate,p8$Year,p8.1,
+p9$visitatio_rate,p9$Year,p9.1,
+p10$visitatio_rate,p10$Year,p10.1,
+p11$visitatio_rate,p11$Year,p11.1,
+p12$visitatio_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**visitation rate of *Apis mellifera* **
+
+**A-** GLM binomial (cbind(fruit_formado, Fruit_No))
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+# glm binomial
+mod_fruit_year_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ Apis_visit_rate * Year,data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_fruit_year_apis<-mod_fruit_year_apis %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruit_year_apis %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_fruit_year_apis$p.value < 0.05| is.na(mod_fruit_year_apis$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#model plot
+mod_fruit_year_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ Apis_visit_rate * Year,data,family = binomial)))
+
+p1=plot_model(mod_fruit_year_apis.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_fruit_year_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_fruit_year_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_fruit_year_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_fruit_year_apis.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_fruit_year_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_fruit_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_fruit_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_fruit_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_fruit_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_fruit_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_fruit_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$Apis_visit_rate,p1$Year,p1.1,
+p2$Apis_visit_rate,p2$Year,p2.1,
+p3$Apis_visit_rate,p3$Year,p3.1,
+p4$Apis_visit_rate,p4$Year,p4.1,
+p5$Apis_visit_rate,p5$Year,p5.1,
+p6$Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_fruit_year_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_fruit_year_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_fruit_year_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_fruit_year_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_fruit_year_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_fruit_year_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_fruit_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_fruit_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_fruit_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_fruit_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_fruit_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_fruit_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$Apis_visit_rate,p7$Year,p7.1,
+p8$Apis_visit_rate,p8$Year,p8.1,
+p9$Apis_visit_rate,p9$Year,p9.1,
+p10$Apis_visit_rate,p10$Year,p10.1,
+p11$Apis_visit_rate,p11$Year,p11.1,
+p12$Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**B-** GLMM binomial (ramdon= Site_ID)
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# glmm binomial
+mod_mix_fruit_year_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate *Year + (1|Site_ID),data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_mix_fruit_year_apis<-mod_mix_fruit_year_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_fruit_year_apis<-filter(mod_mix_fruit_year_apis, !term == "sd__(Intercept)")
+
+mod_mix_fruit_year_apis %>% 
+kable("latex",booktabs = TRUE,digits =  4, longtable = T,linesep ="") %>% 
+column_spec(6, bold = ifelse(mod_mix_fruit_year_apis$p.value < 0.05, T, F) )%>%  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#model plot
+mod_mix_fruit_year_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~Apis_visit_rate *Year + (1|Site_ID),data,family = binomial)))
+
+p1=plot_model(mod_mix_fruit_year_apis.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_mix_fruit_year_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_fruit_year_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_fruit_year_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_fruit_year_apis.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_mix_fruit_year_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_fruit_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_mix_fruit_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_mix_fruit_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_mix_fruit_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_mix_fruit_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_mix_fruit_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$Apis_visit_rate,p1$Year,p1.1,
+p2$Apis_visit_rate,p2$Year,p2.1,
+p3$Apis_visit_rate,p3$Year,p3.1,
+p4$Apis_visit_rate,p4$Year,p4.1,
+p5$Apis_visit_rate,p5$Year,p5.1,
+p6$Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_fruit_year_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_fruit_year_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_fruit_year_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_fruit_year_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_fruit_year_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p11=plot_model(mod_mix_fruit_year_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_fruit_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_mix_fruit_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_mix_fruit_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_mix_fruit_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_mix_fruit_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_mix_fruit_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$Apis_visit_rate,p7$Year,p7.1,
+p8$Apis_visit_rate,p8$Year,p8.1,
+p9$Apis_visit_rate,p9$Year,p9.1,
+p10$Apis_visit_rate,p10$Year,p10.1,
+p11$Apis_visit_rate,p11$Year,p11.1,
+p12$Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**visitation rate of pollinator without *Apis mellifera* **
+
+**A-** GLM binomial (cbind(fruit_formado, Fruit_No))
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+# glm binomial
+mod_fruit_year_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ No_Apis_visit_rate * Year,data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_fruit_year_no_apis<-mod_fruit_year_no_apis %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruit_year_no_apis %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_fruit_year_no_apis$p.value < 0.05| is.na(mod_fruit_year_no_apis$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#model plot
+mod_fruit_year_no_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ No_Apis_visit_rate * Year,data,family = binomial)))
+
+p1=plot_model(mod_fruit_year_no_apis.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_fruit_year_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_fruit_year_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_fruit_year_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_fruit_year_no_apis.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_fruit_year_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_fruit_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_fruit_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_fruit_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_fruit_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_fruit_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_fruit_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$No_Apis_visit_rate,p1$Year,p1.1,
+p2$No_Apis_visit_rate,p2$Year,p2.1,
+p3$No_Apis_visit_rate,p3$Year,p3.1,
+p4$No_Apis_visit_rate,p4$Year,p4.1,
+p5$No_Apis_visit_rate,p5$Year,p5.1,
+p6$No_Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_fruit_year_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_fruit_year_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_fruit_year_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_fruit_year_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_fruit_year_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_fruit_year_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_fruit_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_fruit_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_fruit_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_fruit_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_fruit_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_fruit_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$No_Apis_visit_rate,p7$Year,p7.1,
+p8$No_Apis_visit_rate,p8$Year,p8.1,
+p9$No_Apis_visit_rate,p9$Year,p9.1,
+p10$No_Apis_visit_rate,p10$Year,p10.1,
+p11$No_Apis_visit_rate,p11$Year,p11.1,
+p12$No_Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**B-** GLMM binomial (ramdon= Site_ID)
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# glmm binomial
+mod_mix_fruit_year_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~No_Apis_visit_rate *Year + (1|Site_ID),data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_mix_fruit_year_no_apis<-mod_mix_fruit_year_no_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_fruit_year_no_apis<-filter(mod_mix_fruit_year_no_apis, !term == "sd__(Intercept)")
+
+mod_mix_fruit_year_no_apis %>% 
+kable("latex",booktabs = TRUE,digits =  4, longtable = T,linesep ="") %>% 
+column_spec(6, bold = ifelse(mod_mix_fruit_year_no_apis$p.value < 0.05, T, F) )%>%  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#model plot
+mod_mix_fruit_year_no_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~No_Apis_visit_rate *Year + (1|Site_ID),data,family = binomial)))
+
+p1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_mix_fruit_year_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_fruit_year_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_fruit_year_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_fruit_year_no_apis.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_mix_fruit_year_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$No_Apis_visit_rate,p1$Year,p1.1,
+p2$No_Apis_visit_rate,p2$Year,p2.1,
+p3$No_Apis_visit_rate,p3$Year,p3.1,
+p4$No_Apis_visit_rate,p4$Year,p4.1,
+p5$No_Apis_visit_rate,p5$Year,p5.1,
+p6$No_Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_fruit_year_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_fruit_year_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_fruit_year_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_fruit_year_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_fruit_year_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_fruit_year_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_mix_fruit_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$No_Apis_visit_rate,p7$Year,p7.1,
+p8$No_Apis_visit_rate,p8$Year,p8.1,
+p9$No_Apis_visit_rate,p9$Year,p9.1,
+p10$No_Apis_visit_rate,p10$Year,p10.1,
+p11$No_Apis_visit_rate,p11$Year,p11.1,
+p12$No_Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**visitation rate of hymenoptera **
+
+**A-** GLM binomial (cbind(fruit_formado, Fruit_No))
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+# glm binomial
+mod_fruit_year_hym<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ Hym_visit * Year,data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_fruit_year_hym<-mod_fruit_year_hym %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruit_year_hym %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_fruit_year_hym$p.value < 0.05| is.na(mod_fruit_year_hym$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#model plot
+mod_fruit_year_hym.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ Hym_visit * Year,data,family = binomial)))
+
+p1=plot_model(mod_fruit_year_hym.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_fruit_year_hym.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_fruit_year_hym.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_fruit_year_hym.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_fruit_year_hym.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_fruit_year_hym.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_fruit_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_fruit_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_fruit_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_fruit_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_fruit_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_fruit_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$Hym_visit,p1$Year,p1.1,
+p2$Hym_visit,p2$Year,p2.1,
+p3$Hym_visit,p3$Year,p3.1,
+p4$Hym_visit,p4$Year,p4.1,
+p5$Hym_visit,p5$Year,p5.1,
+p6$Hym_visit,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_fruit_year_hym.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_fruit_year_hym.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_fruit_year_hym.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_fruit_year_hym.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_fruit_year_hym.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_fruit_year_hym.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_fruit_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_fruit_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_fruit_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_fruit_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_fruit_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_fruit_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$Hym_visit,p7$Year,p7.1,
+p8$Hym_visit,p8$Year,p8.1,
+p9$Hym_visit,p9$Year,p9.1,
+p10$Hym_visit,p10$Year,p10.1,
+p11$Hym_visit,p11$Year,p11.1,
+p12$Hym_visit,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**B-** GLMM binomial (ramdon= Site_ID)
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# glmm binomial
+mod_mix_fruit_year_hym<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit *Year + (1|Site_ID),data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_mix_fruit_year_hym<-mod_mix_fruit_year_hym %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_fruit_year_hym<-filter(mod_mix_fruit_year_hym, !term == "sd__(Intercept)")
+
+mod_mix_fruit_year_hym %>% 
+kable("latex",booktabs = TRUE,digits =  4, longtable = T,linesep ="") %>% 
+column_spec(6, bold = ifelse(mod_mix_fruit_year_hym$p.value < 0.05, T, F) )%>%  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#plot
+mod_mix_fruit_year_hym.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit *Year + (1|Site_ID),data,family = binomial)))
+
+p1=plot_model(mod_mix_fruit_year_hym.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_mix_fruit_year_hym.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_fruit_year_hym.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_fruit_year_hym.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_fruit_year_hym.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_mix_fruit_year_hym.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_fruit_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_mix_fruit_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_mix_fruit_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_mix_fruit_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_mix_fruit_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_mix_fruit_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$Hym_visit,p1$Year,p1.1,
+p2$Hym_visit,p2$Year,p2.1,
+p3$Hym_visit,p3$Year,p3.1,
+p4$Hym_visit,p4$Year,p4.1,
+p5$Hym_visit,p5$Year,p5.1,
+p6$Hym_visit,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_fruit_year_hym.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_fruit_year_hym.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_fruit_year_hym.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_fruit_year_hym.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_fruit_year_hym.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_fruit_year_hym.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_fruit_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_mix_fruit_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_mix_fruit_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_mix_fruit_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_mix_fruit_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_mix_fruit_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$Hym_visit,p7$Year,p7.1,
+p8$Hym_visit,p8$Year,p8.1,
+p9$Hym_visit,p9$Year,p9.1,
+p10$Hym_visit,p10$Year,p10.1,
+p11$Hym_visit,p11$Year,p11.1,
+p12$Hym_visit,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**visitation rate of hymenoptera without *A. mellifera* **
+
+**A-** GLM binomial (cbind(fruit_formado, Fruit_No))
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+# glm binomial
+mod_fruit_year_hym_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ Hym_visit_sin_apis * Year,data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_fruit_year_hym_no_apis<-mod_fruit_year_hym_no_apis %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruit_year_hym_no_apis %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_fruit_year_hym_no_apis$p.value < 0.05| is.na(mod_fruit_year_hym_no_apis$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#model plot
+mod_fruit_year_hym_no_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ Hym_visit_sin_apis * Year,data,family = binomial)))
+
+p1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_fruit_year_hym_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_fruit_year_hym_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_fruit_year_hym_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_fruit_year_hym_no_apis.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_fruit_year_hym_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$Hym_visit_sin_apis,p1$Year,p1.1,
+p2$Hym_visit_sin_apis,p2$Year,p2.1,
+p3$Hym_visit_sin_apis,p3$Year,p3.1,
+p4$Hym_visit_sin_apis,p4$Year,p4.1,
+p5$Hym_visit_sin_apis,p5$Year,p5.1,
+p6$Hym_visit_sin_apis,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_fruit_year_hym_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_fruit_year_hym_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_fruit_year_hym_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_fruit_year_hym_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_fruit_year_hym_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_fruit_year_hym_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_fruit_year_hym_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$Hym_visit_sin_apis,p7$Year,p7.1,
+p8$Hym_visit_sin_apis,p8$Year,p8.1,
+p9$Hym_visit_sin_apis,p9$Year,p9.1,
+p10$Hym_visit_sin_apis,p10$Year,p10.1,
+p11$Hym_visit_sin_apis,p11$Year,p11.1,
+p12$Hym_visit_sin_apis,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**B-** GLMM binomial (ramdon= Site_ID)
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# glmm binomial
+mod_mix_fruit_year_hym_no_apis<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit_sin_apis *Year + (1|Site_ID),data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_mix_fruit_year_hym_no_apis<-mod_mix_fruit_year_hym_no_apis %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_fruit_year_hym_no_apis<-filter(mod_mix_fruit_year_hym_no_apis, !term == "sd__(Intercept)")
+
+mod_mix_fruit_year_hym_no_apis %>% 
+kable("latex",booktabs = TRUE,digits =  4, longtable = T,linesep ="") %>% 
+column_spec(6, bold = ifelse(mod_mix_fruit_year_hym_no_apis$p.value < 0.05, T, F) )%>%  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#plot
+mod_mix_fruit_year_hym_no_apis.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~Hym_visit_sin_apis *Year + (1|Site_ID),data,family = binomial)))
+
+p1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$Hym_visit_sin_apis,p1$Year,p1.1,
+p2$Hym_visit_sin_apis,p2$Year,p2.1,
+p3$Hym_visit_sin_apis,p3$Year,p3.1,
+p4$Hym_visit_sin_apis,p4$Year,p4.1,
+p5$Hym_visit_sin_apis,p5$Year,p5.1,
+p6$Hym_visit_sin_apis,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_mix_fruit_year_hym_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$Hym_visit_sin_apis,p7$Year,p7.1,
+p8$Hym_visit_sin_apis,p8$Year,p8.1,
+p9$Hym_visit_sin_apis,p9$Year,p9.1,
+p10$Hym_visit_sin_apis,p10$Year,p10.1,
+p11$Hym_visit_sin_apis,p11$Year,p11.1,
+p12$Hym_visit_sin_apis,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**Richness**
+
+**A-** GLM binomial (cbind(fruit_formado, Fruit_No))
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+
+# glm binomial
+mod_fruit_year_richness<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ richness * Year,data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_fruit_year_richness<-mod_fruit_year_richness %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_fruit_year_richness %>% 
+ kable("latex",booktabs = TRUE, digits =  4,longtable = T, linesep = "") %>% 
+column_spec(6, bold = ifelse(mod_fruit_year_richness$p.value < 0.05| is.na(mod_fruit_year_richness$p.value), T, F) )%>%
+  kable_styling(position="left")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#model plot
+mod_fruit_year_richness.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glm(cbind(fruit_formado,Fruit_No) ~ richness * Year,data,family = binomial)))
+
+p1=plot_model(mod_fruit_year_richness.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_fruit_year_richness.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_fruit_year_richness.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_fruit_year_richness.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_fruit_year_richness.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_fruit_year_richness.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_fruit_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_fruit_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_fruit_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_fruit_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_fruit_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_fruit_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$richness,p1$Year,p1.1,
+p2$richness,p2$Year,p2.1,
+p3$richness,p3$Year,p3.1,
+p4$richness,p4$Year,p4.1,
+p5$richness,p5$Year,p5.1,
+p6$richness,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_fruit_year_richness.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_fruit_year_richness.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_fruit_year_richness.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_fruit_year_richness.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_fruit_year_richness.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_fruit_year_richness.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_fruit_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_fruit_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_fruit_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_fruit_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_fruit_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_fruit_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$richness,p7$Year,p7.1,
+p8$richness,p8$Year,p8.1,
+p9$richness,p9$Year,p9.1,
+p10$richness,p10$Year,p10.1,
+p11$richness,p11$Year,p11.1,
+p12$richness,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+**B-** GLMM binomial (ramdon= Site_ID)
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+
+# glmm binomial
+mod_mix_fruit_year_richness<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~richness *Year + (1|Site_ID),data,family = binomial))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+mod_mix_fruit_year_richness<-mod_mix_fruit_year_richness %>%
+  select(-effect, -group)  %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+mod_mix_fruit_year_richness<-filter(mod_mix_fruit_year_richness, !term == "sd__(Intercept)")
+
+mod_mix_fruit_year_richness %>% 
+kable("latex",booktabs = TRUE,digits =  4, longtable = T,linesep ="") %>% 
+column_spec(6, bold = ifelse(mod_mix_fruit_year_richness$p.value < 0.05, T, F) )%>%  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+#plot
+mod_mix_fruit_year_richness.1<-Pollinator_Plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(glmer(cbind(fruit_formado, Fruit_No)~richness *Year + (1|Site_ID),data,family = binomial)))
+
+p1=plot_model(mod_mix_fruit_year_richness.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_mix_fruit_year_richness.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_fruit_year_richness.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_fruit_year_richness.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_fruit_year_richness.1$mod[[5]], type = "pred", title = " Cistus monspeliensis")
+p6=plot_model(mod_mix_fruit_year_richness.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_fruit_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus")
+p2.1=plot_model(mod_mix_fruit_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus")
+p3.1=plot_model(mod_mix_fruit_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer")
+p4.1=plot_model(mod_mix_fruit_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis")
+p5.1=plot_model(mod_mix_fruit_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis")
+p6.1=plot_model(mod_mix_fruit_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius")
+
+ggarrange(p1$richness,p1$Year,p1.1,
+p2$richness,p2$Year,p2.1,
+p3$richness,p3$Year,p3.1,
+p4$richness,p4$Year,p4.1,
+p5$richness,p5$Year,p5.1,
+p6$richness,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_fruit_year_richness.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_fruit_year_richness.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_fruit_year_richness.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_fruit_year_richness.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_fruit_year_richness.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_fruit_year_richness.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_fruit_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum")
+p8.1=plot_model(mod_mix_fruit_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium")
+p9.1=plot_model(mod_mix_fruit_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata")
+p10.1=plot_model(mod_mix_fruit_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas")
+p11.1=plot_model(mod_mix_fruit_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus")
+p12.1=plot_model(mod_mix_fruit_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans")
+
+ggarrange(p7$richness,p7$Year,p7.1,
+p8$richness,p8$Year,p8.1,
+p9$richness,p9$Year,p9.1,
+p10$richness,p10$Year,p10.1,
+p11$richness,p11$Year,p11.1,
+p12$richness,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```

### 2022-10-11 script/models.R
plots added

@@ -11,6 +11,7 @@ library(patchwork)
 library(ggcorrplot)
 library(ggpubr)
 library (lme4)
+library(sjPlot)
 
 
 Pollinator_Plant<- read.csv("Data/Pollinator_Plant_Apis_separada.csv") #400 observaciones
@@ -1458,7 +1459,6 @@ mod_fruitproportion.1$plots[[12]] + geom_point(data = Pollinator_Plant %>% filte
   labs(x = "richness",y="fruit proportion",subtitle = "T.fruticans")+  theme_classic()+theme(text = element_text(size=rel(3)))
 
 
-
 # visistation rate (all pollinators)
 
 #plot
@@ -1572,7 +1572,34 @@ mod_fruitproportion_polli_no_api<-Pollinator_Plant %>%
   summarise(broom.mixed::tidy(model)) %>%
   ungroup()
 
+# modelo salvia  
+salvia=Pollinator_Plant %>%
+  filter(Plant_gen_sp == "Salvia rosmarinus") 
 
+plot(salvia$No_Apis_visit_rate,salvia$fruit_proportion)
+
+plot(salvia$Apis_visit_rate,salvia$fruit_proportion)
+
+mod= glmer(cbind(fruit_formado, Fruit_No) ~ No_Apis_visit_rate + (1|Site_ID), family = binomial, data= salvia)
+summary(mod)
+
+mod_apis= glmer(cbind(fruit_formado, Fruit_No) ~ Apis_visit_rate + (1|Site_ID), family = binomial, data= salvia)
+summary(mod_apis)
+
+plot_model(mod, type = "pred", show.ci = TRUE)
+get_model_data(mod, type = "pred")
+
+plot_model(mod_apis, type = "pred", show.ci = TRUE)
+get_model_data(mod_apis, type = "pred")
+
+library(effects)
+plot (allEffects(mod))
+library(ggeffects)
+ggpredict(mod, "No_Apis_visit_rate")
+me <- ggpredict(mod, "No_Apis_visit_rate")
+plot(me)
+
+#
 mod_fruitproportion_polli_no_api_glance<-Pollinator_Plant %>%
   nest_by(Plant_gen_sp) %>%
   mutate(model = list(glmer(cbind(fruit_formado, Fruit_No)~No_Apis_visit_rate + (1|Site_ID),family=binomial,data))) %>%
[…]

### 2022-10-11 script/stability.R
Gross index analysed

@@ -245,41 +245,90 @@ syn_LM2=prueba%>%
 
 ### IMPORTANTE: se obtiene todo NA, consultar que puede estar pasando
 
-#av_sync <- function(x, w = TRUE){
-#  S <- ncol(x) #num sp
-#  total <- rowSums(x)
-#  p <- colSums(x)/sum(colSums(x)) #rel abund
-#  cors <- c()
-#  for(i in 1:ncol(x)) cors[i] <- cor(x[,i],total-x[,i])
-# if(w){
-#    out <- sum(p * cors) #a--b, a-c, ...
-#  }else{
-#    out <- (1/S) * sum(cors) #a--b, a-c, ...
-#  }
-#  out
-#}
+av_sync <- function(x, w = TRUE){
+ xx<-x[,which(colSums(x) > 0)]
+ S <- ncol(xx) #num sp
+ total <- rowSums(xx)
+ p <- colSums(xx)/sum(colSums(xx)) #rel abund
+ cors <- c()
+ for(i in 1:ncol(xx)) cors[i] <- cor(xx[,i],total-xx[,i])
+if(w){
+   out <- sum(p * cors) #a--b, a-c, ...
+ }else{
+   out <- (1/S) * sum(cors) #a--b, a-c, ...
+ }
+ out
+}
 
-#syn_G2=prueba%>% 
-#  group_by(Plant_gen_sp,Site_ID)%>% 
-#  do(av_sync=av_sync(.[4:127]))
+av_sync_spearma <- function(x, w = TRUE){
+  xx<-x[,which(colSums(x) > 0)]
+  S <- ncol(xx) #num sp
+  total <- rowSums(xx)
+  p <- colSums(xx)/sum(colSums(xx)) #rel abund
+  cors <- c()
+  for(i in 1:ncol(xx)) cors[i] <- cor(xx[,i],total-xx[,i],method = "spearman")
+  if(w){
+    out <- sum(p * cors) #a--b, a-c, ...
+  }else{
+    out <- (1/S) * sum(cors) #a--b, a-c, ...
+  }
+  out
+}
+
+# test <- prueba%>%
+#   filter( Plant_gen_sp == "Asphodelus fistulosus",Site_ID == "Aznalcazar")
+# 
+# test <- prueba%>%
+#   filter( Plant_gen_sp == "Cistus crispus",Site_ID == "Aznalcazar")
+# 
+# test <- prueba%>%
[…]

### 2022-10-11 script/Fruit_set.R
Apis and no apis

@@ -546,10 +546,24 @@ visitation<-merge(x=visitation,y=Hym,by=c("Year","Site_ID", "Plant_gen_sp","plan
 visitation<-visitation %>% mutate(Hym_visit = Hym_freq/Flower_abundance)
 
 
-# hymenoptera sin A. mellifera
+# solo hymenoptera sin A. mellifera
+
+sin_apis=focal %>%
+   filter(!Pollinator_gen_sp=="Apis mellifera")
+
+levels(factor(sin_apis$Pollinator_gen_sp))
+
+# frecuencia de hymnenopteros sin A. mellifera
+Hym_no_apis<-aggregate(Frequency ~ Year+Site_ID+Plant_gen_sp+plant_id, sin_apis[sin_apis$Orden %in% c("Hymenoptera"),], sum)
+names(Hym_no_apis)[names(Hym_no_apis) == "Frequency"] <- "Hym_freq_sin_apis"
+
+# hymenopter visitation sin A. mellifera
+visitation<-merge(x=visitation,y=Hym_no_apis,by=c("Year","Site_ID", "Plant_gen_sp","plant_id" ),all.x=T, all.y=F)
+visitation<-visitation %>% mutate(Hym_visit_sin_apis = Hym_freq_sin_apis/Flower_abundance)
 
 
-
+# nota: si sumo Apis_freq y no_apis_freq es igual a frequency (todos los polinizadores)
+# si sumo Apis_freq y Hym_freq_sin-apis es igual a Hym_freq (solo Hymenoptero, sin dipteros y coleopteros)
 
 # Diptera frequency
 dip<-aggregate(Frequency ~ Year+Site_ID+Plant_gen_sp+plant_id, focal[focal$Orden %in% c("Diptera"),], sum)
@@ -658,6 +672,8 @@ visitation<-arrange(visitation,Site_ID, Plant_gen_sp)
 
 #to <- mutate_at(to,"richness08", ~replace(., is.na(.), 0))
 
+
+
 # join visitation and reproductive success
 #solo individuos coincidentes
 total<-merge(x=reprod_success,y=visitation,by=c("Year","Site_ID", "Plant_gen_sp","plant_id"),all.x=F, all.y=F)
@@ -670,7 +686,7 @@ total<-arrange(total,Site_ID, Plant_gen_sp)
 
 
 write_xlsx(total, "C:/Users/estef/git/stability-and-function/Data/Pollinator_Plant.xlsx")
[…]

### 2022-10-11 Rmd/model_with_year.Rmd
plot_models

@@
 Predicte values of seed number
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
-
-p1=plot_model(mod_seed_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus",show.data = TRUE)
-p2=plot_model(mod_seed_year.1$mod[[2]], type = "pred", title = " Cistus crispus",show.data = TRUE)
-p3=plot_model(mod_seed_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer",show.data = TRUE)
-p4=plot_model(mod_seed_year.1$mod[[4]], type = "pred",title = "Cistus libanotis",show.data = TRUE)
-p5=plot_model(mod_seed_year.1$mod[[5]], type = "pred", title = "Cistus monspeliensis",show.data = TRUE)
-p6=plot_model(mod_seed_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius",show.data = TRUE)
+
+*Cistus monspeliensis* - *Halimium halimifolium* - *Teucrium fructicans* 
+Warning message:
+In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,: prediction from a rank-deficient fit may be misleading
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_seed_year.1$mod[[1]], type = "pred", title = " Asphodelus fistulosus")
+p2=plot_model(mod_seed_year.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_seed_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_seed_year.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_seed_year.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_seed_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
 
@@
 
-p7=plot_model(mod_seed_year.1$mod[[7]], type = "pred",title = " Halimium calycinum",show.data = TRUE)
-p8=plot_model(mod_seed_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium",show.data = TRUE)
-p9=plot_model(mod_seed_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata",show.data = TRUE)
-p10=plot_model(mod_seed_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas",show.data = TRUE)
-p11=plot_model(mod_seed_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus",show.data = TRUE)
-p12=plot_model(mod_seed_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans",show.data = TRUE)
+p7=plot_model(mod_seed_year.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_seed_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_seed_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_seed_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_seed_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_seed_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
 
@@
 
-*Cistus monspeliensis* - *Halimium halimifolium* - *Teucrium fructicans* 
-Warning message:
-In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,: prediction from a rank-deficient fit may be misleading
-
 **Importante**: Cistus crispus en 2015 solo tiene dos valores, uno con 0 semillas y visitation rate 0.214; y otro con casi 40 semillas y visitation rate 0
@@
 Predicted values of Seeds for *Cistus crispus*
+
 ```{r,echo=FALSE, warning=FALSE,message=FALSE}
@@
 
-\newpage
+elimana algunos valores de interacciones en *C.monspeliensis*, *H.halimifolium* y *T.fructicans*: fixed-effect model matrix is rank deficient so dropping 3 columns / coefficients - 1 column / coefficient - 1 column / coefficient
+
+Además boundary (singular) fit: see help('isSingular')
+
 ```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
@@
 Predicted values of Seeds
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_mix_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis", show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum", show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_mix_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
-,ncol=3,nrow = 4)
-
-```
 
@@
 Could not compute variance-covariance matrix of predictions. No confidence intervals are returned.
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_mix_seed_year.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_mix_seed_year.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_seed_year.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_seed_year.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_seed_year.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_mix_seed_year.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_seed_year.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_mix_seed_year.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_mix_seed_year.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_mix_seed_year.1$mod[[4]], type = "int",title = "Cistus libanotis", show.data = TRUE)
+p5.1=plot_model(mod_mix_seed_year.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_mix_seed_year.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$visitatio_rate,p1$Year,p1.1,
+p2$visitatio_rate,p2$Year,p2.1,
+p3$visitatio_rate,p3$Year,p3.1,
+p4$visitatio_rate,p4$Year,p4.1,
+p5$visitatio_rate,p5$Year,p5.1,
+p6$visitatio_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_seed_year.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_seed_year.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_seed_year.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_seed_year.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_seed_year.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_seed_year.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_seed_year.1$mod[[7]], type = "int",title = " Halimium calycinum", show.data = TRUE)
+p8.1=plot_model(mod_mix_seed_year.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_mix_seed_year.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_mix_seed_year.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_mix_seed_year.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_mix_seed_year.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$visitatio_rate,p7$Year,p7.1,
+p8$visitatio_rate,p8$Year,p8.1,
+p9$visitatio_rate,p9$Year,p9.1,
+p10$visitatio_rate,p10$Year,p10.1,
+p11$visitatio_rate,p11$Year,p11.1,
+p12$visitatio_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
 
@@
 Predicted values of Seeds
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE), ncol=3,nrow = 4)
-
-```
 
@@
 Warning message: In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,: prediction from a rank-deficient fit may be misleading
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_seed_year_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_seed_year_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_seed_year_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_seed_year_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_seed_year_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_seed_year_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$Apis_visit_rate,p1$Year,p1.1,
+p2$Apis_visit_rate,p2$Year,p2.1,
+p3$Apis_visit_rate,p3$Year,p3.1,
+p4$Apis_visit_rate,p4$Year,p4.1,
+p5$Apis_visit_rate,p5$Year,p5.1,
+p6$Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_seed_year_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_seed_year_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_seed_year_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_seed_year_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_seed_year_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_seed_year_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$Apis_visit_rate,p7$Year,p7.1,
+p8$Apis_visit_rate,p8$Year,p8.1,
+p9$Apis_visit_rate,p9$Year,p9.1,
+p10$Apis_visit_rate,p10$Year,p10.1,
+p11$Apis_visit_rate,p11$Year,p11.1,
+p12$Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
 
@@
 ```
+
+elimana algunos valores de interacciones en *Asphodelus fistulosus* - *Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans*: fixed-effect model matrix is rank deficient so dropping 3 columns / coefficients - 1 column / coefficient - 1 column / coefficient
+
+Además boundary (singular) fit: see help('isSingular')
 
@@
 \newpage
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_mix_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_mix_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
-
-```
+
+Predicted values of Seeds
 
 *Asphodelus fistulosus* - *Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans* 
-
 Could not compute variance-covariance matrix of predictions. No confidence intervals are returned
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_mix_seed_year_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_mix_seed_year_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_seed_year_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_seed_year_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_seed_year_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_mix_seed_year_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_seed_year_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_mix_seed_year_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_mix_seed_year_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_mix_seed_year_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_mix_seed_year_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_mix_seed_year_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$Apis_visit_rate,p1$Year,p1.1,
+p2$Apis_visit_rate,p2$Year,p2.1,
+p3$Apis_visit_rate,p3$Year,p3.1,
+p4$Apis_visit_rate,p4$Year,p4.1,
+p5$Apis_visit_rate,p5$Year,p5.1,
+p6$Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_seed_year_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_seed_year_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_seed_year_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_seed_year_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_seed_year_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_seed_year_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_seed_year_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_mix_seed_year_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_mix_seed_year_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_mix_seed_year_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_mix_seed_year_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_mix_seed_year_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$Apis_visit_rate,p7$Year,p7.1,
+p8$Apis_visit_rate,p8$Year,p8.1,
+p9$Apis_visit_rate,p9$Year,p9.1,
+p10$Apis_visit_rate,p10$Year,p10.1,
+p11$Apis_visit_rate,p11$Year,p11.1,
+p12$Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
 
@@
 \newpage
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
-
-```
+
+Predicted values of Seeds
 
@@
 
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_seed_year_no_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_seed_year_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_seed_year_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_seed_year_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_seed_year_no_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_seed_year_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$No_Apis_visit_rate,p1$Year,p1.1,
+p2$No_Apis_visit_rate,p2$Year,p2.1,
+p3$No_Apis_visit_rate,p3$Year,p3.1,
+p4$No_Apis_visit_rate,p4$Year,p4.1,
+p5$No_Apis_visit_rate,p5$Year,p5.1,
+p6$No_Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_seed_year_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_seed_year_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_seed_year_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_seed_year_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_seed_year_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_seed_year_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$No_Apis_visit_rate,p7$Year,p7.1,
+p8$No_Apis_visit_rate,p8$Year,p8.1,
+p9$No_Apis_visit_rate,p9$Year,p9.1,
+p10$No_Apis_visit_rate,p10$Year,p10.1,
+p11$No_Apis_visit_rate,p11$Year,p11.1,
+p12$No_Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
+
 \newpage
@@
 Warning messages:Some predictor variables are on very different scales: consider rescaling. The warning occurred in Salvia rosmarinus
+No_Apis_visit_rate:Year2016 -> 364.706 (Estimate); 813.126 (std.error)
+
+elimana algunos valores de interacciones en *C.monspeliensis*, *H.halimifolium* y *T.fructicans*: fixed-effect model matrix is rank deficient so dropping 3 columns / coefficients - 1 column / coefficient - 1 column / coefficient
 
@@
 \newpage
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_mix_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_mix_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+Predicted values of Seeds
+
+*C.monspeliensis*, *H.halimifolium* y *T.fructicans*
+Could not compute variance-covariance matrix of predictions. No confidence intervals are returned
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_mix_seed_year_no_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_mix_seed_year_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_seed_year_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_seed_year_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_seed_year_no_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_mix_seed_year_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = T)
+p2.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = T)
+p3.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = T)
+p4.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = T)
+p5.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = T)
+p6.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = T)
+
+ggarrange(p1$No_Apis_visit_rate,p1$Year,p1.1,
+p2$No_Apis_visit_rate,p2$Year,p2.1,
+p3$No_Apis_visit_rate,p3$Year,p3.1,
+p4$No_Apis_visit_rate,p4$Year,p4.1,
+p5$No_Apis_visit_rate,p5$Year,p5.1,
+p6$No_Apis_visit_rate,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_seed_year_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_seed_year_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_seed_year_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_seed_year_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_seed_year_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_seed_year_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = T)
+p8.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = T)
+p9.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = T)
+p10.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = T)
+p11.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = T)
+p12.1=plot_model(mod_mix_seed_year_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = T)
+
+ggarrange(p7$No_Apis_visit_rate,p7$Year,p7.1,
+p8$No_Apis_visit_rate,p8$Year,p8.1,
+p9$No_Apis_visit_rate,p9$Year,p9.1,
+p10$No_Apis_visit_rate,p10$Year,p10.1,
+p11$No_Apis_visit_rate,p11$Year,p11.1,
+p12$No_Apis_visit_rate,p12$Year,p12.1,ncol=3,nrow = 6)
 
@@
 \newpage
+
 ```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
@@
 \newpage
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_seed_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_seed_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+Predicted values of Seeds
+
+*Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans* 
+Warning message:
+In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,:  prediction from a rank-deficient fit may be misleading
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_seed_year_hym.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_seed_year_hym.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_seed_year_hym.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_seed_year_hym.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_seed_year_hym.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_seed_year_hym.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_seed_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_seed_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_seed_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_seed_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_seed_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_seed_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$Hym_visit,p1$Year,p1.1,
+p2$Hym_visit,p2$Year,p2.1,
+p3$Hym_visit,p3$Year,p3.1,
+p4$Hym_visit,p4$Year,p4.1,
+p5$Hym_visit,p5$Year,p5.1,
+p6$Hym_visit,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_seed_year_hym.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_seed_year_hym.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_seed_year_hym.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_seed_year_hym.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_seed_year_hym.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_seed_year_hym.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_seed_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_seed_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_seed_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_seed_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_seed_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_seed_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$Hym_visit,p7$Year,p7.1,
+p8$Hym_visit,p8$Year,p8.1,
+p9$Hym_visit,p9$Year,p9.1,
+p10$Hym_visit,p10$Year,p10.1,
+p11$Hym_visit,p11$Year,p11.1,
+p12$Hym_visit,p12$Year,p12.1,ncol=3,nrow = 6)
 
@@
 **B-** linear mixed model with site ID like random factor
+fixed-effect model matrix is rank deficient so dropping 1 column / coefficient de varia especies
+
 ```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
@@
 \newpage
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_mix_seed_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+Predicted values of Seeds
+
+*Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans* 
+Could not compute variance-covariance matrix of predictions. No confidence intervals are returned.
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_mix_seed_year_hym.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_mix_seed_year_hym.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_seed_year_hym.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_seed_year_hym.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_seed_year_hym.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_mix_seed_year_hym.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_seed_year_hym.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_mix_seed_year_hym.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_mix_seed_year_hym.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_mix_seed_year_hym.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_mix_seed_year_hym.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_mix_seed_year_hym.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$Hym_visit,p1$Year,p1.1,
+p2$Hym_visit,p2$Year,p2.1,
+p3$Hym_visit,p3$Year,p3.1,
+p4$Hym_visit,p4$Year,p4.1,
+p5$Hym_visit,p5$Year,p5.1,
+p6$Hym_visit,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_seed_year_hym.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_seed_year_hym.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_seed_year_hym.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_seed_year_hym.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_seed_year_hym.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_seed_year_hym.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_seed_year_hym.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_mix_seed_year_hym.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_mix_seed_year_hym.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_mix_seed_year_hym.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_mix_seed_year_hym.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_mix_seed_year_hym.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$Hym_visit,p7$Year,p7.1,
+p8$Hym_visit,p8$Year,p8.1,
+p9$Hym_visit,p9$Year,p9.1,
+p10$Hym_visit,p10$Year,p10.1,
+p11$Hym_visit,p11$Year,p11.1,
+p12$Hym_visit,p12$Year,p12.1,ncol=3,nrow = 6)
 
@@
 \newpage
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_seed_year_hym_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_seed_year_hym_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+
+Predicted values of Seeds
+
+*Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans* 
+Warning message:
+In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,:  prediction from a rank-deficient fit may be misleading
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_seed_year_hym_no_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_seed_year_hym_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_seed_year_hym_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_seed_year_hym_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_seed_year_hym_no_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_seed_year_hym_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$Hym_visit_sin_apis,p1$Year,p1.1,
+p2$Hym_visit_sin_apis,p2$Year,p2.1,
+p3$Hym_visit_sin_apis,p3$Year,p3.1,
+p4$Hym_visit_sin_apis,p4$Year,p4.1,
+p5$Hym_visit_sin_apis,p5$Year,p5.1,
+p6$Hym_visit_sin_apis,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_seed_year_hym_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_seed_year_hym_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_seed_year_hym_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_seed_year_hym_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_seed_year_hym_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_seed_year_hym_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_seed_year_hym_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$Hym_visit_sin_apis,p7$Year,p7.1,
+p8$Hym_visit_sin_apis,p8$Year,p8.1,
+p9$Hym_visit_sin_apis,p9$Year,p9.1,
+p10$Hym_visit_sin_apis,p10$Year,p10.1,
+p11$Hym_visit_sin_apis,p11$Year,p11.1,
+p12$Hym_visit_sin_apis,p12$Year,p12.1,ncol=3,nrow = 6)
 
@@
 **B-** linear mixed model with site ID like random factor
+
+Warning messages:Some predictor variables are on very different scales: consider rescaling. The warning occurred in Salvia rosmarinus
+
+fixed-effect model matrix is rank deficient so dropping 1 column / coefficient
+
 ```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
@@
 \newpage
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+Predicted values of Seeds
+
+*Cistus libanotis*- *Cistus monspeliensis* - *Halimium calycinum* - *Halimium halimifolium* - *Teucrium fructicans* 
+Could not compute variance-covariance matrix of predictions. No confidence intervals are returned.
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$Hym_visit_sin_apis,p1$Year,p1.1,
+p2$Hym_visit_sin_apis,p2$Year,p2.1,
+p3$Hym_visit_sin_apis,p3$Year,p3.1,
+p4$Hym_visit_sin_apis,p4$Year,p4.1,
+p5$Hym_visit_sin_apis,p5$Year,p5.1,
+p6$Hym_visit_sin_apis,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_mix_seed_year_hym_no_apis.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$Hym_visit_sin_apis,p7$Year,p7.1,
+p8$Hym_visit_sin_apis,p8$Year,p8.1,
+p9$Hym_visit_sin_apis,p9$Year,p9.1,
+p10$Hym_visit_sin_apis,p10$Year,p10.1,
+p11$Hym_visit_sin_apis,p11$Year,p11.1,
+p12$Hym_visit_sin_apis,p12$Year,p12.1,ncol=3,nrow = 6)
 
@@
 \newpage
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_seed_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_seed_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
+Predicted values of Seeds
+
+*Aspodelus fistulosus* - *Cistus libanotis*- *Cistus monspeliensis* - *Halimium halimifolium* - *Lavandula stoechas* - *Teucrium fructicans* 
+Warning message: In predict.lm(model, newdata = fitfram, type = "response", se.fit = se,:  prediction from a rank-deficient fit may be misleading
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_seed_year_richness.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_seed_year_richness.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_seed_year_richness.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_seed_year_richness.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_seed_year_richness.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_seed_year_richness.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_seed_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_seed_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_seed_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_seed_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_seed_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_seed_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$richness,p1$Year,p1.1,
+p2$richness,p2$Year,p2.1,
+p3$richness,p3$Year,p3.1,
+p4$richness,p4$Year,p4.1,
+p5$richness,p5$Year,p5.1,
+p6$richness,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_seed_year_richness.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_seed_year_richness.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_seed_year_richness.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_seed_year_richness.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_seed_year_richness.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_seed_year_richness.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_seed_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_seed_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_seed_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_seed_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_seed_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_seed_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$richness,p7$Year,p7.1,
+p8$richness,p8$Year,p8.1,
+p9$richness,p9$Year,p9.1,
+p10$richness,p10$Year,p10.1,
+p11$richness,p11$Year,p11.1,
+p12$richness,p12$Year,p12.1,ncol=3,nrow = 6)
 
@@
 \newpage
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 20,fig.width=22, out.width="100%"}
-
-ggarrange(plot_model(mod_mix_seed_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE),
-plot_model(mod_mix_seed_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE),ncol=3,nrow = 4)
-
-```
-
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p1=plot_model(mod_mix_seed_year_richness.1$mod[[1]], type = "pred", title = "Asphodelus fistulosus")
+p2=plot_model(mod_mix_seed_year_richness.1$mod[[2]], type = "pred", title = " Cistus crispus")
+p3=plot_model(mod_mix_seed_year_richness.1$mod[[3]], type = "pred", title = " Cistus ladanifer")
+p4=plot_model(mod_mix_seed_year_richness.1$mod[[4]], type = "pred",title = "Cistus libanotis")
+p5=plot_model(mod_mix_seed_year_richness.1$mod[[5]], type = "pred", title = "Cistus monspeliensis")
+p6=plot_model(mod_mix_seed_year_richness.1$mod[[6]], type = "pred",title = " Cistus salviifolius")
+
+p1.1=plot_model(mod_mix_seed_year_richness.1$mod[[1]], type = "int", title = " Asphodelus fistulosus",show.data = TRUE)
+p2.1=plot_model(mod_mix_seed_year_richness.1$mod[[2]], type = "int", title = " Cistus crispus",show.data = TRUE)
+p3.1=plot_model(mod_mix_seed_year_richness.1$mod[[3]], type = "int", title = " Cistus ladanifer",show.data = TRUE)
+p4.1=plot_model(mod_mix_seed_year_richness.1$mod[[4]], type = "int",title = "Cistus libanotis",show.data = TRUE)
+p5.1=plot_model(mod_mix_seed_year_richness.1$mod[[5]], type = "int", title = " Cistus monspeliensis",show.data = TRUE)
+p6.1=plot_model(mod_mix_seed_year_richness.1$mod[[6]], type = "int",title = " Cistus salviifolius",show.data = TRUE)
+
+ggarrange(p1$richness,p1$Year,p1.1,
+p2$richness,p2$Year,p2.1,
+p3$richness,p3$Year,p3.1,
+p4$richness,p4$Year,p4.1,
+p5$richness,p5$Year,p5.1,
+p6$richness,p6$Year,p6.1,ncol=3,nrow = 6)
+
+```
+
+\newpage
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 30,fig.width=25, out.width="100%"}
+
+p7=plot_model(mod_mix_seed_year_richness.1$mod[[7]], type = "pred",title = " Halimium calycinum")
+p8=plot_model(mod_mix_seed_year_richness.1$mod[[8]], type = "pred",title = " Halimium halimifolium")
+p9=plot_model(mod_mix_seed_year_richness.1$mod[[9]], type = "pred",title = " Lavandula pedunculata")
+p10=plot_model(mod_mix_seed_year_richness.1$mod[[10]], type = "pred",title = " Lavandula stoechas")
+p11=plot_model(mod_mix_seed_year_richness.1$mod[[11]], type = "pred",title = " Salvia rosmarinus")
+p12=plot_model(mod_mix_seed_year_richness.1$mod[[12]], type = "pred",title = " Teucrium fruticans")
+
+p7.1=plot_model(mod_mix_seed_year_richness.1$mod[[7]], type = "int",title = " Halimium calycinum",show.data = TRUE)
+p8.1=plot_model(mod_mix_seed_year_richness.1$mod[[8]], type = "int",title = " Halimium halimifolium",show.data = TRUE)
+p9.1=plot_model(mod_mix_seed_year_richness.1$mod[[9]], type = "int",title = " Lavandula pedunculata",show.data = TRUE)
+p10.1=plot_model(mod_mix_seed_year_richness.1$mod[[10]], type = "int",title = " Lavandula stoechas",show.data = TRUE)
+p11.1=plot_model(mod_mix_seed_year_richness.1$mod[[11]], type = "int",title = " Salvia rosmarinus",show.data = TRUE)
+p12.1=plot_model(mod_mix_seed_year_richness.1$mod[[12]], type = "int",title = " Teucrium fruticans",show.data = TRUE)
+
+ggarrange(p7$richness,p7$Year,p7.1,
+p8$richness,p8$Year,p8.1,
+p9$richness,p9$Year,p9.1,
+p10$richness,p10$Year,p10.1,
+p11$richness,p11$Year,p11.1,
+p12$richness,p12$Year,p12.1,ncol=3,nrow = 6)
+
+```
 \newpage
@@
 \newpage
+*C.crispus*, *C.ladanifer*, *C.salviifolius*, *H.halimifolium*, *L.pedunculata*, *L.stoechas* -> Data were 'prettified'. Consider using terms="visitatio_rate [all] to get smooth plots.
 
@@
 
-\newpage
+boundary (singular) fit: see help('isSingular')
+fixed-effect model matrix is rank deficient so dropping 3 columns / coefficients
+
+ademas There were 30 warnings (use warnings() to see them)
+*Asphodelus* unable to evaluate scaled gradient and Hessian is numerically singular: parameters are not uniquely determined 
+*C.crispus* Model failed to converge with max|grad| = 0.00813624 (tol = 0.002, component 1)
+*Cistus ladanifer* unable to evaluate scaled gradient and Model failed to converge: degenerate Hessian with 1 negative eigenvalues
+*Cistus monspeliensis* unable to evaluate scaled gradient and Hessian is numerically singular: parameters are not uniquely determined
+*Cistus salviifolius* unable to evaluate scaled gradient and Model failed to converge: degenerate Hessian with 3 negative eigenvalues
+*Halimium halimifolium* unable to evaluate scaled gradient and Hessian is numerically singular: parameters are not uniquely determined
+*Lavandula stoechas* Model is nearly unidentifiable: large eigenvalue ratio - Rescale variables?
+*Salvia rosmarinu* unable to evaluate scaled gradient and Hessian is numerically singular: parameters are not uniquely determined
+
+\newpage
+
+*C.crispus*, *C.ladanifer*, *C.salviifolius*, *H.halimifolium*, *L.pedunculata*, *L.stoechas* -> Data were 'prettified'. Consider using terms="visitatio_rate [all] to get smooth plots.
+Could not compute variance-covariance matrix of predictions. No confidence intervals are returned
 

### 2022-10-11 Rmd/Stability.Rmd
Gross index analysed

@@
 
+#Gross et al. 2014
+av_sync <- function(x, w = TRUE){
+ xx<-x[,which(colSums(x) > 0)]
+ S <- ncol(xx) #num sp
+ total <- rowSums(xx)
+ p <- colSums(xx)/sum(colSums(xx)) #rel abund
+ cors <- c()
+ for(i in 1:ncol(xx)) cors[i] <- cor(xx[,i],total-xx[,i])
+if(w){
+   out <- sum(p * cors) #a--b, a-c, ...
+ }else{
+   out <- (1/S) * sum(cors) #a--b, a-c, ...
+ }
+ out
+}
+
+syn_G2=prueba%>%
+ group_by(Plant_gen_sp,Site_ID)%>%
+ do(av_sync=av_sync(.[4:ncol(prueba)]))
+
 # join tables 
@@
   full_join (., syn_LM2, by=c('Plant_gen_sp', 'Site_ID'))%>%
+  full_join (., syn_G2, by=c('Plant_gen_sp', 'Site_ID'))%>%
   rename(cv_1_fruit=fruit_proportion, cv_1_seed=Seeds,   cv_1_visitation=visitatio_rate,S_total=richness.x, S_mean=richness.y)
@@
 full2$syncLM <- unlist(full2$syncLM)
+full2$ av_sync <- unlist(full2$ av_sync)
 
@@
 cr %>% 
+    kable("latex",booktabs = TRUE, digits =  4)
+
+```
+
+Correlacion indices sincronia
+```{r,echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+# correlacion indices de sincronia
+
+syn_cor<-full2 %>% select(log_VR,syncLM,av_sync)
+
+## Replace Inf and -Inf with NA
+syn_cor[is.na(syn_cor) | syn_cor == "Inf"] <- 0 
+syn_cor[is.na(syn_cor) | syn_cor == "-Inf"] <- 0
+
+syn_cor <- mutate_all(syn_cor, ~replace(., is.na(.), 0))
+
+cr_syn=cor(syn_cor)
+
+cr_syn %>% 
     kable("latex",booktabs = TRUE, digits =  4)
@@
 
-C- log VR ~ mean richness
+C- Gross index ~ Total richness
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+rich_Gross<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(av_sync ~ S_total,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+rich_Gross<-rich_Gross %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+rich_Gross %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(rich_Gross$p.value < 0.05| is.na(rich_Gross$p.value), T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+#model plot
+rich_Gross.2 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(av_sync ~ S_total,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=rich_Gross.2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(y =  av_sync, x = S_total))+ 
+  labs(y = "av_sync",x="total richness",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=rich_Gross.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(y =  av_sync, x = S_total))+ 
+  labs(y = "av_sync",x="total richness",subtitle = "C.ladanifer")+ scale_x_continuous(limits = c(9, 27))+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich_Gross.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(y =  av_sync, x = S_total))+ 
+  labs(y = "av_sync",x="total richness",subtitle = "C.salviifolius")+ scale_x_continuous(limits = c(7, 31))+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich_Gross.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(y =  av_sync, x = S_total))+ labs(y = "av_sync",x="total richness",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=rich_Gross.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(y =  av_sync, x = S_total))+ 
+  labs(y = "av_sync",x="total richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```
+
+\newpage
+
+D- log VR ~ mean richness
 
@@
 
-D- Loreau & Mazancourt syncrony index ~  mean richness
+E- Loreau & Mazancourt syncrony index ~  mean richness
 
@@
 
+C- Gross index ~ mean richness
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+#model
+rich_mean_Gross<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(av_sync ~ S_mean,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+opts <- options(knitr.kable.NA = "")
+
+rich_mean_Gross<-rich_mean_Gross %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+rich_mean_Gross %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(rich_mean_Gross$p.value < 0.05| is.na(rich_mean_Gross$p.value), T, F) )%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+#model plot
+rich_mean_Gross.2 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(av_sync ~ S_mean,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=rich_mean_Gross.2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(y =  av_sync, x = S_mean))+ 
+labs(y = "av_sync",x="mean richness",subtitle = "C.crispus")+theme_classic() +theme(text = element_text(size=rel(3)))
+
+p2=rich_mean_Gross.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(y =  av_sync, x = S_mean))+ 
+  labs(y = "av_sync",x="mean richness",subtitle = "C.ladanifer") + scale_x_continuous(limits = c(4.5, 11)) + theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=rich_mean_Gross.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(y =  av_sync, x = S_mean))+ labs(y = "av_sync",x="mean richness",subtitle = "C.salviifolius")+ scale_x_continuous(limits = c(4, 12))+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=rich_mean_Gross.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(y =  av_sync, x = S_mean))+labs(y = "av_sync",x="mean richness",subtitle = "H.halimifolium")+  theme_classic() +theme(text = element_text(size=rel(3)))
+
+p6=rich_mean_Gross.2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(y =  av_sync, x = S_mean))+ labs(y = "av_sync",x="mean richness",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```
+
+\newpage
+
 We analysed whether the visitation rate stability is affected by richness and synchrony for each plant species separately
@@
 
-C) mean richness + log VR
+C) total richness + Gross index
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+#model: total richness + Gross index
+sta_polli_Gross<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+av_sync,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+sta_polli_Gross<-sta_polli_Gross %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_polli_Gross %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_polli_Gross$p.value < 0.05|is.na(sta_polli_Gross$p.value), T, F))%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+sta_polli_Gross_glance<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+av_sync,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table9<-sta_polli_Gross_glance %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table9 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot (cv_1_visitation~total richness)
+sta_polli_Gross.2 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+av_sync,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)))
+
+p1=sta_polli_Gross.2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_total, y = cv_1_visitation))+ labs(x = "S_total",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli_Gross.2$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  S_total, y = cv_1_visitation))+ labs(x = "S_total",y="visitation rate stability",subtitle = "C.ladanifer") + scale_x_continuous(limits = c(9, 27))+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli_Gross.2$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  S_total, y = cv_1_visitation))+  labs(x = "S_total",y="visitation rate stability",subtitle = "C.salviifolius") + scale_x_continuous(limits = c(7, 31))+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli_Gross.2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_total, y = cv_1_visitation))+ labs(x = "S_total",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic() +theme(text = element_text(size=rel(3)))
+
+p6=sta_polli_Gross.2$plots[[6]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata")), aes(x =  S_total, y = cv_1_visitation))+ labs(x = "S_total",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+# model plot (cv_1_visitation~av_sync)
+sta_polli_Gross.3 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+av_sync,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "av_sync"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line() +
+ geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .1)))
+
+p1=sta_polli_Gross.3$plots[[1]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus crispus"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.crispus")+ theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli_Gross.3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli_Gross.3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.salviifolius")+ theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli_Gross.3$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli_Gross.3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```
+
+\newpage
+
+D) mean richness + log VR
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
 
-D) mean richness + Lorea & Mazancourt index
+E) mean richness + Lorea & Mazancourt index
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
 ```
+
+\newpage
+
+F) mean richness + Gross index
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+#model: mean richness + Gross index
+sta_polli_Smean_Gross<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+av_sync,data))) %>%
+  summarize(tidy(mod))%>%
+  ungroup()
+
+sta_polli_Smean_Gross<-sta_polli_Smean_Gross %>%
+  mutate(Plant_gen_sp = replace(Plant_gen_sp, duplicated(Plant_gen_sp), ""))
+
+sta_polli_Smean_Gross %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = c("","","\\addlinespace")) %>% 
+column_spec(6, bold = ifelse(sta_polli_Smean_Gross$p.value <0.05|is.na(sta_polli_Smean_Gross$p.value), T, F))%>%
+  kable_styling(position="center", latex_option="hold_position")
+
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="80%", fig.align='left'}
+
+#goodness of fit measures
+sta_polli_Smean_Gross_glance<-full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+av_sync,data))) %>%
+  summarize(glance(mod))%>%
+  ungroup()
+
+table11<-sta_polli_Smean_Gross_glance %>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus crispus', 'C.crispus', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus ladanifer', 'C.ladanifer', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Cistus salviifolius', 'C.salviifolius', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium calycinum', 'H. calycinum', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Halimium halimifolium', 'H.halimifolium', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula pedunculata', 'L.pedunculata', Plant_gen_sp))%>%
+  mutate( Plant_gen_sp = if_else(Plant_gen_sp == 'Lavandula stoechas', 'L.stoechas', Plant_gen_sp))
+
+table11 %>% 
+ kable("latex",booktabs = TRUE, digits =  3,linesep = "",align = "lcccccccccccc")%>%
+  kable_styling(font_size = 8,full_width = F, position="left")
+
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+sta_polli_Smean_Gross2 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+av_sync,data))) %>%
+  mutate(mod = list(ggeffects::ggpredict(mod, terms = "S_mean"))) %>%
+  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli_Smean_Gross2$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "C.crispus")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli_Smean_Gross2$plots[[2]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer")), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic() +theme(text = element_text(size=rel(3)))
+
+p3=sta_polli_Smean_Gross2$plots[[3]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius")), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli_Smean_Gross2$plots[[5]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium")), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "H.halimifolium")+theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli_Smean_Gross2$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  S_mean, y = cv_1_visitation))+ labs(x = "mean richness",y="visitation rate stability",subtitle = "L.pedunculata")+ theme_classic()+theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```
+
+\newpage
+```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
+
+sta_polli_Smean_Gross3 <- full_2 %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_mean+av_sync,data))) %>%
+  mutate(mod = list(ggeffects::ggpredict(mod, terms = "av_sync"))) %>%
+  mutate(plots = list(ggplot(mod, aes(x, predicted)) + geom_line() +
+ geom_ribbon(aes(ymin = conf.low, ymax = conf.high), alpha = .2)))
+
+p1=sta_polli_Smean_Gross3$plots[[1]] + geom_point(data = na.omit(full_2 %>% filter(Plant_gen_sp == "Cistus crispus")), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.crispus")+ theme_classic()+theme(text = element_text(size=rel(3)))
+
+p2=sta_polli_Smean_Gross3$plots[[2]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus ladanifer"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.ladanifer")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p3=sta_polli_Smean_Gross3$plots[[3]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Cistus salviifolius"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "C.salviifolius")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p5=sta_polli_Smean_Gross3$plots[[5]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Halimium halimifolium"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "H.halimifolium")+  theme_classic()+theme(text = element_text(size=rel(3)))
+
+p6=sta_polli_Smean_Gross3$plots[[6]] + geom_point(data = full_2 %>% filter(Plant_gen_sp == "Lavandula pedunculata"), aes(x =  av_sync, y = cv_1_visitation))+ labs(x = "av_sync",y="visitation rate stability",subtitle = "L.pedunculata")+  theme_classic() +theme(text = element_text(size=rel(3)))
+
+p1+p2+p3+p5+p6
+```

### 2022-10-11 Rmd/Models.Rmd
apis and no apis

@@
 
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+#plot
+plots_fruitproportion_polli_no_apis <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=No_Apis_visit_rate, y=fruit_proportion) + 
+  geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_fruitproportion_polli_no_apis[[1]],plots_fruitproportion_polli_no_apis[[2]],plots_fruitproportion_polli_no_apis[[3]],plots_fruitproportion_polli_no_apis[[4]],plots_fruitproportion_polli_no_apis[[5]],plots_fruitproportion_polli_no_apis[[6]],plots_fruitproportion_polli_no_apis[[7]],plots_fruitproportion_polli_no_apis[[8]],plots_fruitproportion_polli_no_apis[[9]],plots_fruitproportion_polli_no_apis[[10]],plots_fruitproportion_polli_no_apis[[11]],plots_fruitproportion_polli_no_apis[[12]], ncol=3, nrow=4)
+
+```
+
+\newpage
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
@@
 
+\newpage
+Data were 'prettified'. Consider using `terms="No_Apis_visit_rate [all]"` to get smooth plots.
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
 
+Problemas C.libanotis 
+Warning messages:
+1: In vcov.merMod(object, use.hessian = use.hessian) :
+  variance-covariance matrix computed from finite-difference Hessian is
+not positive definite or contains NA values: falling back to var-cov estimated from RX
+2: In vcov.merMod(object, correlation = correlation, sigm = sig) :
+  variance-covariance matrix computed from finite-difference Hessian is
+not positive definite or contains NA values: falling back to var-cov estimated from RX
+
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
@@
 
+\newpage
+Data were 'prettified'. Consider using `terms="Apis_visit_rate [all]"` to get smooth plots.
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}
@@
 ## Hymenoptera visitation rate without A.mellifera
-
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=15, out.width="100%"}
+#plot
+plots_fruitproportion_hyme_no_apis <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  group_map(~ ggplot(.) + aes(x=Hym_visit_sin_apis, y=fruit_proportion) + 
+              geom_point() + ggtitle(.y[[1]]))
+
+ggarrange(plots_fruitproportion_hyme_no_apis[[1]],plots_fruitproportion_hyme_no_apis[[2]],plots_fruitproportion_hyme_no_apis[[3]],plots_fruitproportion_hyme_no_apis[[4]],plots_fruitproportion_hyme_no_apis[[5]],plots_fruitproportion_hyme_no_apis[[6]],plots_fruitproportion_hyme_no_apis[[7]],plots_fruitproportion_hyme_no_apis[[8]],plots_fruitproportion_hyme_no_apis[[9]],plots_fruitproportion_hyme_no_apis[[10]],plots_fruitproportion_hyme_no_apis[[11]],plots_fruitproportion_hyme_no_apis[[12]], ncol=3, nrow=4)
+
+```
+
+\newpage
+
+Problemas H.calycinum: unable to evaluate scaled gradient and Hessian is numerically singular: parameters are not uniquely determined
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
@@
 
+\newpage
+Data were 'prettified'. Consider using `terms="Hym_visit_sin_apis [all]"` to get smooth plots
 ```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%", fig.align='center'}

### 2022-10-26 Figures/Plot_1.R
Plot 1

@@ -1,0 +1,60 @@
+
+library(tidyverse)
+library(lme4)
+library(effects)
+library(patchwork)
+
+
+
+# stability data for five plant species present at least in five sites
+# C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata
+
+data_plant<- read.csv("Data/Stability_fivespecies.csv")
+data_plant<-data_plant[,-1]
+
+
+# Replace inf with NA
+data_plant[sapply(data_plant, is.infinite)] <- NA
+
+# We can express asynchrony as 1 - φ, 
+#where φ is Loreau and de Mazancourt’s (2008)
+data_plant$asynchrony= 1-data_plant$syncLM
+
+
+#model 
+mod1_sta= lmer (cv_1_visitation ~ S_total + asynchrony + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+
+
+
+#getting effects for asynchrony
+effe_mod_sta <-data.frame( effect("asynchrony", mod1_sta, se = TRUE))
+
+
+#plot model of asynchrony
+p1=ggplot(effe_mod_sta, aes(asynchrony, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.1, colour = "black")+
+  scale_y_continuous(limits = c(-0.14, 6))+ labs(color='Plant species')+
+  geom_point(data = data_plant, aes(x =  asynchrony, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
+  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
+  labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")
+
+
+#getting effects for richness
+effe2_mod_sta <-data.frame( effect("S_total", mod1_sta, se = TRUE))
+
+
+#plot model of richness
+p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.1, colour = "black")+
+  scale_y_continuous(limits = c(-0.14, 6))+  labs(color='Plant species')+
+  geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
+  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
[…]

### 2022-10-26 Figures/Plot_1.R
.

@@ -1,60 +1,0 @@
-
-library(tidyverse)
-library(lme4)
-library(effects)
-library(patchwork)
-
-
-
-# stability data for five plant species present at least in five sites
-# C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata
-
-data_plant<- read.csv("Data/Stability_fivespecies.csv")
-data_plant<-data_plant[,-1]
-
-
-# Replace inf with NA
-data_plant[sapply(data_plant, is.infinite)] <- NA
-
-# We can express asynchrony as 1 - φ, 
-#where φ is Loreau and de Mazancourt’s (2008)
-data_plant$asynchrony= 1-data_plant$syncLM
-
-
-#model 
-mod1_sta= lmer (cv_1_visitation ~ S_total + asynchrony + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
-
-
-
-#getting effects for asynchrony
-effe_mod_sta <-data.frame( effect("asynchrony", mod1_sta, se = TRUE))
-
-
-#plot model of asynchrony
-p1=ggplot(effe_mod_sta, aes(asynchrony, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.1, colour = "black")+
-  scale_y_continuous(limits = c(-0.14, 6))+ labs(color='Plant species')+
-  geom_point(data = data_plant, aes(x =  asynchrony, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
-  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
-  labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")
-
-
-#getting effects for richness
-effe2_mod_sta <-data.frame( effect("S_total", mod1_sta, se = TRUE))
-
-
-#plot model of richness
-p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.1, colour = "black")+
-  scale_y_continuous(limits = c(-0.14, 6))+  labs(color='Plant species')+
-  geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
-  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
[…]

### 2022-10-26 Manuscript/Manuscript.Rmd
Material and method

---
title: "Title"
output: pdf_document
date: '2022-10-26'
---

# Material and method

Our study was conducted in the southwest of the Iberian Peninsula (Huelva and Seville - Spain). We selected 16 (13) sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby. These sites had similarity in plant community composition and some of most abundance plant species provide nectar and pollen that attract flower visitors. Each site was surveyed at least 7 times per year during the flowering season from 2015 to 2019 (from March to June). Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean  ± standard error: 5.92  ± 0.54 plant species per site). All the floral visitors (from now on referred to as pollinators) that contacted with their flowers  were registered over 5 minutes. Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory. For each plant individual, we counted the total number of flowers and at the end of the season, we recorded the number of fruit and the seeds per fruit.
For each site and year, we calculated the visitation rate of pollinators as the number of visits divided by the number of flowers, pollinator richness, the fruit set as the proportion of fruit, and the seed set as number of seed for each plant individual sampled per site.

## Stability
For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were present in at least 5 sites during the 5 years. The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot. To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot during the five years. To synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018). All of them were positively correlation in each plant species, therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses. This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous. Finally, we express asynchrony as 1-Loreau and de Mazancourt’s index of synchrony.
We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.

## Statistical analysis
To evaluate the main drivers of visitation rate stability, we employed linear mixed model to test for relationships between stability and richness and asynchrony including site and plant species as random factor. We used variance inflation factors to check for collinearity between explanatory variables. For a deeper understanding, we also analyzed the respond of the stability for each plant species separately.
For our aim to study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run  linear mixed models using as response variables the stability of fruit proportion or stability of seed number and as explanatory variable the visitation rate stability. Site and plant species were included as factor random.
To detect whether the effect of pollinator richness and visitation rate  is different across the years, we use all plant species sampled. We analyzed the interaction effect richness and year, and visitation rate and year on fruit proportion using  binomial generalized linear mixed models, and on the number of seeds employing linear mixed model. The number of seeds per fruit was centered and scaled to allow meaningful comparisons across species. For all models, we included plant species identity nested within site and site as random effects because of multiple individuals of the same plant species are measured at each site.

# Results

Stability of visitation rate ranged from 0.71 to 5.63 (mean ± SE: 1.715 ± 0.135), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.98 (0.689 ± 0.036).
Our results showed that the stability of visitation rate was positively related with de asynchorny (Estimate: 1.236; standard error: 0.658) (Fig 1A), and it was not influenced by the pollinator richness (Estimate: 0.021; standard error: 0.034) (Fig 1B).
when we analyzed the plant species separately, we observed that the relationship between stability of visitation rate and richness is different in function of plant species. *Cistus crispus* and *Cistus salviifolius* showed a negative relation whereas *Cistus ladanifer* and *Lavandula pedunculata* was positive. The tendency of the asynchrony was positive in all plant species except to the *Lavandula pedunculata*. (Supplementary material-Fig1)

```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}

library(tidyverse)
library(lme4)
library(effects)
library(patchwork)

# stability data for five plant species present at least in five sites
# C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata

data_plant<- read.csv("../Data/Stability_fivespecies.csv")
data_plant<-data_plant[,-1]

# Replace inf with NA
data_plant[sapply(data_plant, is.infinite)] <- NA

# We can express asynchrony as 1 - φ, 
#where φ is Loreau and de Mazancourt’s (2008)
data_plant$asynchrony= 1-data_plant$syncLM

#model 
mod1_sta= lmer (cv_1_visitation ~ S_total + asynchrony + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)

#getting effects for asynchrony
effe_mod_sta <-data.frame( effect("asynchrony", mod1_sta, se = TRUE))

#plot model of asynchrony
p1=ggplot(effe_mod_sta, aes(asynchrony, fit)) + geom_line(size=1)+
  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.1, colour = "black")+
  scale_y_continuous(limits = c(-0.14, 6))+ labs(color='Plant species')+
  geom_point(data = data_plant, aes(x =  asynchrony, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
  labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")

#getting effects for richness
effe2_mod_sta <-data.frame( effect("S_total", mod1_sta, se = TRUE))

#plot model of richness
p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.1, colour = "black")+
  scale_y_continuous(limits = c(-0.14, 6))+  labs(color='Plant species')+
  geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
  labs(x = "Richness of pollinator",y="")

#join plots
p_cv_visit=p1+p2+ 
  plot_annotation(tag_levels = "A")& 
  theme(plot.tag.position = c(0, 1),
        plot.tag = element_text(hjust = -3.5, vjust = 1.5, size=15))& theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))
p_cv_visit+ plot_layout(guides = "collect")

```

### 2022-10-26 Manuscript/Figures/Suplementary_Fig1.R
Suplementary Fig 1

@@ -1,0 +1,105 @@
+
+library(tidyverse)
+library(effects)
+library(patchwork)
+
+# stability data for five plant species present at least in five sites
+# C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata
+
+data_plant<- read.csv("Data/Stability_fivespecies.csv")
+data_plant<-data_plant[,-1]
+
+
+# Replace inf with NA
+data_plant[sapply(data_plant, is.infinite)] <- NA
+
+# We can express asynchrony as 1 - φ, 
+#where φ is Loreau and de Mazancourt’s (2008)
+data_plant$asynchrony= 1-data_plant$syncLM
+
+
+
+# model plot (cv_1_visitation~S_total+asynchrony)
+# plot for richness
+plot_stabi_plant <- data_plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+asynchrony,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line(size=1) +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), linetype = 3, alpha=0.1, colour = "black")))
+
+#Cistus crispus
+p1=plot_stabi_plant$plots[[1]] + geom_point(data =data_plant %>% filter(Plant_gen_sp == "Cistus crispus"), 
+  aes(x =  S_total, y = cv_1_visitation),color="coral3",fill="coral2", pch=21, size=2)+ 
+  labs(x = "",y="Stability of visitation rate",subtitle = "Cistus crispus")+scale_x_continuous(limits = c(9, 16))+
+  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+theme( plot.subtitle = element_text(face = "italic"))
+
+#Cistus ladanifer
+p2=plot_stabi_plant$plots[[2]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), 
+  aes(x =  S_total, y = cv_1_visitation),color="yellow4",fill="yellow4",pch=21, size=2)+ 
+  labs(x = "",y=NULL,subtitle = "Cistus ladanifer")+scale_x_continuous(limits = c(3, 16))+ 
[…]

### 2022-10-26 Manuscript/Figures/Plot_1.R
edit

@@ -36,11 +36,13 @@ p1=ggplot(effe_mod_sta, aes(asynchrony, fit)) + geom_line(size=1)+
   scale_y_continuous(limits = c(-0.14, 6))+ labs(color='Plant species')+
   geom_point(data = data_plant, aes(x =  asynchrony, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
   theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
-  labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")
+  labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")+
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))
 
 
 #getting effects for richness
 effe2_mod_sta <-data.frame( effect("S_total", mod1_sta, se = TRUE))
+
 
 
 #plot model of richness
@@ -49,12 +51,14 @@ p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
   scale_y_continuous(limits = c(-0.14, 6))+  labs(color='Plant species')+
   geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
   theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
-  labs(x = "Richness of pollinator",y="")
+  labs(x = "Richness of pollinator",y="") +
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))
 
 
 #join plots
 p_cv_visit=p1+p2+ 
   plot_annotation(tag_levels = "A")& 
   theme(plot.tag.position = c(0, 1),
-        plot.tag = element_text(hjust = -3.5, vjust = 1.5, size=15))& theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))
+        plot.tag = element_text(hjust = -0.5, size=15))& 
+  theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))
 p_cv_visit+ plot_layout(guides = "collect")

### 2022-10-26 Manuscript/Figures/Plot_2.R
Plot 2

@@ -1,0 +1,65 @@
+
+library(tidyverse)
+library(lme4)
+library(effects)
+library(patchwork)
+
+
+# stability data for five plant species present at least in five sites
+# C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata
+
+data_plant<- read.csv("Data/Stability_fivespecies.csv")
+data_plant<-data_plant[,-1]
+
+
+# Replace inf with NA
+data_plant[sapply(data_plant, is.infinite)] <- NA
+
+# We can express asynchrony as 1 - φ, 
+#where φ is Loreau and de Mazancourt’s (2008)
+data_plant$asynchrony= 1-data_plant$syncLM
+
+#model fruit stability ~ visitation rate stability
+mod2_sta= lmer(cv_1_fruit ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID), data = data_plant)
+
+#getting effects 
+effe3_mod_sta <-data.frame( effect("cv_1_visitation", mod2_sta, se = TRUE))
+
+
+#plot model 
+p_mod2=ggplot(effe3_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper),linetype = 3, alpha=0.2, colour = "black")+
+  geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_fruit, color=Plant_gen_sp), size=3)+
+  labs(color='Plant species')+
+  labs(y = "Stability of fruit proportion",x="Visitation rate stability")+
+  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))
+
+
+
+# model seed stability ~ visitation rate stability
+mod3_sta= lmer(cv_1_seed ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID), data = data_plant)
+
+
+#getting effects 
+effe4_mod_sta <-data.frame( effect("cv_1_visitation", mod3_sta, se = TRUE))
+
+
+#plot model 
+p_mod3=ggplot(effe4_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black")+
+  labs(color='Plant species')+
[…]

### 2022-10-26 Manuscript/Figures/Suplementary_Fig1.R
edit

@@ -26,35 +26,35 @@ plot_stabi_plant <- data_plant %>%
   mutate(mod = list(lm(cv_1_visitation~S_total+asynchrony,data))) %>%
   mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
   mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line(size=1) +
-  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), linetype = 3, alpha=0.1, colour = "black")))
+ geom_ribbon(aes(ymin = conf.low, ymax = conf.high), linetype = 3, alpha=0.2, colour = "black")))
 
 #Cistus crispus
 p1=plot_stabi_plant$plots[[1]] + geom_point(data =data_plant %>% filter(Plant_gen_sp == "Cistus crispus"), 
-  aes(x =  S_total, y = cv_1_visitation),color="coral3",fill="coral2", pch=21, size=2)+ 
+  aes(x =  S_total, y = cv_1_visitation),color="coral3",fill="coral2", pch=21, size=8)+ 
   labs(x = "",y="Stability of visitation rate",subtitle = "Cistus crispus")+scale_x_continuous(limits = c(9, 16))+
   theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+theme( plot.subtitle = element_text(face = "italic"))
 
 #Cistus ladanifer
 p2=plot_stabi_plant$plots[[2]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), 
-  aes(x =  S_total, y = cv_1_visitation),color="yellow4",fill="yellow4",pch=21, size=2)+ 
+  aes(x =  S_total, y = cv_1_visitation),color="yellow4",fill="yellow4",pch=21, size=8)+ 
   labs(x = "",y=NULL,subtitle = "Cistus ladanifer")+scale_x_continuous(limits = c(3, 16))+ 
   theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))+theme( plot.subtitle = element_text(face = "italic"))
 
 #Cistus salviifolius
 p3=plot_stabi_plant$plots[[3]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), 
[…]

### 2022-10-26 Manuscript/Figures/Plot_1.R
edit

@@ -37,7 +37,8 @@ p1=ggplot(effe_mod_sta, aes(asynchrony, fit)) + geom_line(size=1)+
   geom_point(data = data_plant, aes(x =  asynchrony, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
   theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
   labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")+
-  guides(colour=guide_legend(nrow=2,byrow=TRUE))
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
+
 
 
 #getting effects for richness
@@ -52,7 +53,9 @@ p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
   geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
   theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
   labs(x = "Richness of pollinator",y="") +
-  guides(colour=guide_legend(nrow=2,byrow=TRUE))
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
+  
+
 
 
 #join plots

### 2022-10-26 Manuscript/Manuscript.Rmd
results and plots

@@
 
+# Abstract
+
+1.
+Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions is important for predicting changes in both community structure and ecosystem function.
+While community stability can be influenced by species richness and asynchrony of species,  the relation with the stability of ecosystem functioning is less explored, and specially for functions involving several trophic levels such as plant pollination.
+
+2.
+Using a 5-year time dataset in Mediterranean woodland patches, we assessed the effect of the richness and asynchrony pollinators as drivers of the stability of visitation rate and the relationship between the stability of visitation rate and the stability of the plants reproductive success.
+In addition, we analyzed whether the year together with richness and visitation rate affected the proportion of fruits and the number of seeds.
+
+3.
+The stability of visitation rate is affected by the asynchrony of species while richness shows different responses depending on the plant species.
+As for the stability of the plant reproductive success, we found no relationship between the stability of the proportion of fruits and the number of seeds and the stability of the visitation rate.
+When we analyzed year as a factor, although fruit proportion was saturated, we observed that the effect of richness on fruit proportion depends on the year.
+This relationship is not found with seed number.
+
 # Material and method
@@
 Our study was conducted in the southwest of the Iberian Peninsula (Huelva and Seville - Spain).
-We selected 16 (13) sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby.
+We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby.
 These sites had similarity in plant community composition and some of most abundance plant species provide nectar and pollen that attract flower visitors.
@@
 For a deeper understanding, we also analyzed the respond of the stability for each plant species separately.
+
 For our aim to study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run  linear mixed models using as response variables the stability of fruit proportion or stability of seed number and as explanatory variable the visitation rate stability.
 Site and plant species were included as factor random.
+
 To detect whether the effect of pollinator richness and visitation rate  is different across the years, we use all plant species sampled.
@@
 
+## Stability of visitation rate and its drives: richness and synchrony 
 Stability of visitation rate ranged from 0.71 to 5.63 (mean ± SE: 1.715 ± 0.135), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.98 (0.689 ± 0.036).
-Our results showed that the stability of visitation rate was positively related with de asynchorny (Estimate: 1.236; standard error: 0.658) (Fig 1A), and it was not influenced by the pollinator richness (Estimate: 0.021; standard error: 0.034) (Fig 1B).
-when we analyzed the plant species separately, we observed that the relationship between stability of visitation rate and richness is different in function of plant species.
-*Cistus crispus* and *Cistus salviifolius* showed a negative relation whereas *Cistus ladanifer* and *Lavandula pedunculata* was positive.
-The tendency of the asynchrony was positive in all plant species except to the *Lavandula pedunculata*.
-(Supplementary material-Fig1)
+Our results showed that the stability of visitation rate was positively related with de asynchrony (Estimate: 1.236; standard error: 0.658) (Fig 1A), and it was not influenced by the pollinator richness (Estimate: 0.021; standard error: 0.034) (Fig 1B).
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+The results obtained from visitation rate stability for plant species separately showed that the richness effect is different in function of plant species.
+A negative relation was found in *Cistus crispus* (Estimate: -0.120; std.
+error: 0.05) and *Cistus salviifolius* (Estimate: -0.079; std.
+error: 0.03) whereas a positive relation was found in *Cistus ladanifer* (Estimate: 0.069; std.
+error: 0.04) and *Lavandula pedunculata* (Estimate: 0.302; std.
+error: 0.13).
+The asynchrony was only relation with the visitation rate stability in *C.
+crispu* (Estimate: 1.847; std.
+error: 0.72), although we observed that the tendency of all plant species was positive, except to the *L.
+pedunculata* (Supplementary material-Fig 1).
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 10,fig.width=20, out.width="100%"}
 
@@
 p1=ggplot(effe_mod_sta, aes(asynchrony, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.1, colour = "black")+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,size=1, alpha=0.2, colour = "black")+
   scale_y_continuous(limits = c(-0.14, 6))+ labs(color='Plant species')+
-  geom_point(data = data_plant, aes(x =  asynchrony, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
+  geom_point(data = data_plant, aes(x =  asynchrony, y = cv_1_visitation, color=Plant_gen_sp), size=8)+
   theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
-  labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")
+  labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")+
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
 
@@
 p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.1, colour = "black")+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, size=0.8, alpha=0.2, colour = "black")+
   scale_y_continuous(limits = c(-0.14, 6))+  labs(color='Plant species')+
-  geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
+  geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), size=8)+
   theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
-  labs(x = "Richness of pollinator",y="")
+  labs(x = "Richness of pollinator",y="")+
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
 
@@
   theme(plot.tag.position = c(0, 1),
-        plot.tag = element_text(hjust = -3.5, vjust = 1.5, size=15))& theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))
+        plot.tag = element_text(hjust = -0.3, vjust = 0.5, size=30))& 
+  theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))&theme(text = element_text(size=30))
 p_cv_visit+ plot_layout(guides = "collect")
@@
 ```
+
+## Stability of visitation rate and stability of the plant reproductive success
+
+Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
+When we analyzed whether the stability of the visitation rate affected the stability of the plant reproductive success, we found no relationship between this and the stability of the fruit proportion (Estimate: 4.692; std.
+error: 4.545), and neither with the stability of the number of seeds (Estimate: 0.859; std.
+error: 1.825).
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 10,fig.width=20,out.width="100%"}
+
+#model fruit stability ~ visitation rate stability
+mod2_sta= lmer(cv_1_fruit ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID), data = data_plant)
+
+#getting effects 
+effe3_mod_sta <-data.frame( effect("cv_1_visitation", mod2_sta, se = TRUE))
+
+#plot model 
+p_mod2=ggplot(effe3_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper),linetype = 3, alpha=0.2, colour = "black")+
+  geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_fruit, color=Plant_gen_sp), size=8)+
+  labs(color='Plant species')+
+  labs(y = "Stability of fruit proportion",x="Visitation rate stability")+
+  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+theme(legend.text = element_text(face="italic"))
+
+# model seed stability ~ visitation rate stability
+mod3_sta= lmer(cv_1_seed ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID), data = data_plant)
+
+#getting effects 
+effe4_mod_sta <-data.frame( effect("cv_1_visitation", mod3_sta, se = TRUE))
+
+#plot model 
+p_mod3=ggplot(effe4_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black")+
+  labs(color='Plant species')+
+  geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_seed, color=Plant_gen_sp), size=8)+
+  labs(y = "Stability of seed number",x="Visitation rate stability")+
+  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+theme(legend.text = element_text(face="italic"))
+
+#join plots
+p_plant=p_mod2+p_mod3+ 
+  plot_annotation(tag_levels = "A")& 
+  theme(plot.tag.position = c(0, 1),
+        plot.tag = element_text(hjust = -0.3, vjust = 0.5,size=30))& 
+  theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))&theme(text = element_text(size=30))
+p_plant+ plot_layout(guides = "collect")
+
+```
+
+\newpage
+
+# Supplementary material
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 15,fig.width=30,out.width="100%"}
+# model plot (cv_1_visitation~S_total+asynchrony)
+# plot for richness
+plot_stabi_plant <- data_plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+asynchrony,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line(size=1) +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), linetype = 3, alpha=0.2, colour = "black")))
+
+#Cistus crispus
+p1=plot_stabi_plant$plots[[1]] + geom_point(data =data_plant %>% filter(Plant_gen_sp == "Cistus crispus"), 
+  aes(x =  S_total, y = cv_1_visitation),color="coral3",fill="coral2", pch=21, size=8)+ 
+  labs(x = "",y="Stability of visitation rate",subtitle = "Cistus crispus")+scale_x_continuous(limits = c(9, 16))+
+  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+theme( plot.subtitle = element_text(face = "italic"))
+
+#Cistus ladanifer
+p2=plot_stabi_plant$plots[[2]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), 
+  aes(x =  S_total, y = cv_1_visitation),color="yellow4",fill="yellow4",pch=21, size=8)+ 
+  labs(x = "",y=NULL,subtitle = "Cistus ladanifer")+scale_x_continuous(limits = c(3, 16))+ 
+  theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))+theme( plot.subtitle = element_text(face = "italic"))
+
+#Cistus salviifolius
+p3=plot_stabi_plant$plots[[3]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), 
+ aes(x =  S_total, y = cv_1_visitation),color= "springgreen3",fill="springgreen3",pch=21, size=8)+ 
+  labs(x = "Richness",y=NULL,subtitle = "Cistus salviifolius")+scale_x_continuous(limits = c(3, 20))+  
+  theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))+theme( plot.subtitle = element_text(face = "italic"))
+
+#Halimium halimifolium
+p4=plot_stabi_plant$plots[[4]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), 
+  aes(x =  S_total, y = cv_1_visitation), color= "cyan3",fill="cyan3", pch=21, size=8)+ 
+  labs(x = "",y=NULL,subtitle = "Halimium halimifolium")+ scale_x_continuous(limits = c(4, 14))+ 
+  theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))+theme( plot.subtitle = element_text(face = "italic"))
+
+#Lavandula pedunculata
+p5=plot_stabi_plant$plots[[5]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), 
+  aes(x =  S_total, y = cv_1_visitation),color="hotpink",fill="hotpink",pch=21, size=8)+ 
+  labs(x = "",y=NULL,subtitle = "Lavandula pedunculata")+  
+  theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))+theme( plot.subtitle = element_text(face = "italic"))
+
+# model plot for asynchrony
+plot_stabi_plant_2 <- data_plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+asynchrony,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "asynchrony"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line(size=1) +
+ geom_ribbon(aes(ymin = conf.low, ymax = conf.high),linetype = 3, alpha=0.2, colour = "black")))
+
+#Cistus crispus
+p1.1=plot_stabi_plant_2$plots[[1]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus crispus"), 
+ aes(x =  asynchrony, y = cv_1_visitation),color="coral3",fill="coral2", pch=21, size=8)+ 
+  labs(x = "",y="Stability of visitaion rate")+
+  theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))
+
+#Cistus ladanifer
+p2.1=plot_stabi_plant_2$plots[[2]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), 
+  aes(x =  asynchrony, y = cv_1_visitation),color="yellow4",fill="yellow4",pch=21, size=8)+ 
+  labs(x = "",y=NULL)+  theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))
+
+#Cistus salviifolius
+p3.1=plot_stabi_plant_2$plots[[3]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), 
+   aes(x =  asynchrony, y = cv_1_visitation),color= "springgreen3",fill="springgreen3",pch=21, size=8)+ 
+  labs(x = "Asynchrony of pollinators",y= NULL)+  theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))
+
+#Halimium halimifolium
+p4.1=plot_stabi_plant_2$plots[[4]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), 
+  aes(x =  asynchrony, y = cv_1_visitation), color= "cyan3",fill="cyan3", pch=21, size=8)+ 
+  labs(x = "",y=NULL)+  theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))
+
+#Lavandula pedunculata
+p5.1=plot_stabi_plant_2$plots[[5]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), 
+ aes(x =  asynchrony, y = cv_1_visitation), color="hotpink",fill="hotpink",pch=21, size=8)+ 
+  labs(x = "",y=NULL)+  theme_classic()+theme(panel.border = element_rect(colour = "black", fill=NA))
+
+#join plot
+p1+p2+p3+p4+p5+p1.1+p2.1+p3.1+p4.1+p5.1+plot_layout(ncol = 5)& theme(axis.title = element_text(face="bold"))&theme(text = element_text(size=30))
+
+```

### 2022-11-02 script/Fruit_set.R
calculate frequecy and visitation rate in 1 minute

@@ -297,6 +297,7 @@ reprod_success0<-arrange(reprod_success0,Site_ID, Plant_gen_sp)
 ### Focal ###
 
 focal <- read.csv("Data_BeeFun/master_focals.csv")
+str(focal)
 
 # remove years (2021,2020)
 levels(factor(focal$Year))
@@ -491,7 +492,20 @@ focal$plant_id = ifelse(focal$Plant_individual=="AFE" |focal$Plant_individual== 
 
 levels(factor(focal$plant_id))
 
-write.csv(focal, "C:/Users/estef/git/stability-and-function/Data/focal.csv")
+# add time of observation 
+# 2015-2016 = observing all visitors during a 5 minute census
+# 2017-2018-2019 = 3 minute census
+focal=focal %>%
+  mutate(time_obs= ifelse(Year== "2015"| Year=="2016", 5,3)) %>%
+  relocate(time_obs, .before = Time)
+
+
+# calculate visitation frequency in 1 minute
+focal=focal%>%
+  mutate(freq_minute= Frequency/time_obs)%>%
+  relocate(freq_minute, .before = Flower_abundance)
+
+#write.csv(focal, "C:/Users/estef/git/stability-and-function/Data/focal.csv")
 
 
 # Flower abundance
@@ -504,10 +518,20 @@ flower_abun<-aggregate(Flower_abundance ~ Year+Site_ID+Plant_gen_sp+plant_id, da
 Pol_frequency<-aggregate(Frequency ~ Year+Site_ID+Plant_gen_sp+plant_id, data = focal, FUN = sum)
 
 
+# pollinator frequency in 1 minute ##
+## pollinator frequency (Total (sum)) per plant individual, species plants, site and year
+Pol_frequency_minut<-aggregate(freq_minute ~ Year+Site_ID+Plant_gen_sp+plant_id, data = focal, FUN = sum)
+
+
+
 #link flower_abun and Pol_frequency (dejando individuos que tienen flores pero no visitas)
-visitation<-merge(x=flower_abun,y=Pol_frequency,by=c("Year","Site_ID", "Plant_gen_sp","plant_id" ),all.x=T, all.y=F)
+visitation=left_join(flower_abun, Pol_frequency, by = c("Year","Site_ID", "Plant_gen_sp","plant_id" ))%>%
+  left_join (., Pol_frequency_minut, by=c("Year","Site_ID", "Plant_gen_sp","plant_id" ))
+
 
[…]

### 2022-11-02 script/models_per_year.R
visitation rate/minute analysed

@@ -15,10 +15,14 @@ library(effects)
 
 
 
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant_Apis_separada.csv") #400 observaciones
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
 Pollinator_Plant<-Pollinator_Plant[,-1]
 Pollinator_Plant$Year= as.factor(Pollinator_Plant$Year)
 str(Pollinator_Plant)
+
+levels(factor(Pollinator_Plant$Site_ID))
+
+
 
 #Species out (plant species only in one site)
 spp_out <- Pollinator_Plant %>%
@@ -35,6 +39,26 @@ Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
 Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
 
 
+
+#number of plant species per site
+num_plant_site= Pollinator_Plant %>%
+  group_by(Site_ID)  %>%
+  summarise(numb= n_distinct(Plant_gen_sp))
+
+ave_plant <- num_plant_site%>% 
+  summarize(mean_plant = mean(numb, na.rm=T),
+            standarderror = sd(numb, na.rm = TRUE)/sqrt(n()))
+
+levels(factor(Pollinator_Plant$Plant_gen_sp))
+
+
+# number of plant individual per plant species
+num_ind_plant= Pollinator_Plant %>%
+  group_by(Plant_gen_sp)  %>%
+  summarise(numb= n_distinct(plant_id))
+
+
+
 #we analyze whether the fruit proportion is affected by richness, 
 #year and its interaction for all data 
 #with plant species nested within site as random effect
@@ -42,6 +66,8 @@ Pollinator_Plant <- mutate_all(Pollinator_Plant, ~replace(., is.na(.), 0))
 mod1_to= glmer(cbind(fruit_formado, Fruit_No) ~ richness * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
 summary(mod1_to)
 vif(mod1_to)
+
+car::Anova(mod1_to,Type="III")
 
 plot_model(mod1_to, type = "pred")
 plot_model(mod1_to, type = "int")
@@ -59,22 +85,26 @@ ggplot(ee, aes(richness,fit, group=Year, color = Year, fill=Year))+
 
 
 
-# and visitation rate, year and its interaction
[…]

### 2022-11-03 script/stability.R
corrected stability and synchrony (round and observation time)

@@ -70,29 +70,21 @@ plots3_seed[[5]]+plots3_seed[[6]]+plots3_seed[[7]]+plots3_seed[[8]]
 plots3_seed[[9]]+plots3_seed[[10]]+plots3_seed[[11]]+plots3_seed[[12]]
 
 
-# plot seed number and year for each plant species and site 
+# plot visitation rate/minute and year for each plant species and site 
 plots3_visitation_rate <- pol_plant2 %>%
   group_by(Plant_gen_sp) %>%
-  group_map(~ ggplot(.) + aes(x=Year, y=visitatio_rate, col =factor(Site_ID), shape=factor(Site_ID)) + 
+  group_map(~ ggplot(.) + aes(x=Year, y=visitation_rate_minute, col =factor(Site_ID), shape=factor(Site_ID)) + 
   scale_shape_manual(values = c(15,16,17,18,6,7,8,9,10,11,12,13,14))+ geom_point(size = 3) + ggtitle(.y[[1]]))
 
 plots3_visitation_rate[[1]]+plots3_visitation_rate[[2]]+plots3_visitation_rate[[3]]+plots3_visitation_rate[[4]]
 plots3_visitation_rate[[5]]+plots3_visitation_rate[[6]]+plots3_visitation_rate[[7]]+plots3_visitation_rate[[8]] 
 plots3_visitation_rate[[9]]+plots3_visitation_rate[[10]]+plots3_visitation_rate[[11]]+plots3_visitation_rate[[12]]
 
+
+
 ## Stability ##
 
 # fruit proportion stability for each plant species per site #
-# con colum plant_id
-
-#cv_1Fruit<-Pollinator_Plant %>%
-#  group_by(Plant_gen_sp,Site_ID) %>%
-#  summarise_at(vars(fruit_proportion),cv_1 <- function(x, ...) {
-#    ( mean(x, ...)/sd(x, ...) )
-#  })%>%
-#  ungroup()
-
-
 # datos por año y sitio para cada sp de planta (sin plant_id)
 cv_1Fruit2<-pol_plant2 %>%
   group_by(Plant_gen_sp,Site_ID) %>%
@@ -103,15 +95,6 @@ cv_1Fruit2<-pol_plant2 %>%
 
 
 # seed number stability for each plant species per site #
-
-#cv_1Seed<-Pollinator_Plant %>%
[…]

### 2022-11-03 Manuscript/Manuscript.Rmd
results and plot
Quick check from Nacho

@@
 1.
-Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions is important for predicting changes in both community structure and ecosystem function.
-While community stability can be influenced by species richness and asynchrony of species,  the relation with the stability of ecosystem functioning is less explored, and specially for functions involving several trophic levels such as plant pollination.
+Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions is important for predicting the resilience of communities to changes in biodiversity.
+While community stability can be influenced by species richness and asynchrony of species,  the relation with the stability of ecosystem functioning provided by this community is less explored, and specially for functions involving several trophic levels such as plant pollination.
 
 2.
-Using a 5-year time dataset in Mediterranean woodland patches, we assessed the effect of the richness and asynchrony pollinators as drivers of the stability of visitation rate and the relationship between the stability of visitation rate and the stability of the plants reproductive success.
-In addition, we analyzed whether the year together with richness and visitation rate affected the proportion of fruits and the number of seeds.
+Using a 5-year dataset across 16 Mediterranean woodland patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and its relationship between the stability of visitation rate and the stability of the plants reproductive success.
+[In addition, we analyzed whether the year together with richness and visitation rate affected the proportion of fruits and the number of seeds.](esto pensamos como ponerlo con los results finales)
 
 3.
-The stability of visitation rate is affected by the asynchrony of species while richness shows different responses depending on the plant species.
-As for the stability of the plant reproductive success, we found no relationship between the stability of the proportion of fruits and the number of seeds and the stability of the visitation rate.
-When we analyzed year as a factor, although fruit proportion was saturated, we observed that the effect of richness on fruit proportion depends on the year.
-This relationship is not found with seed number.
+The stability of plant's visitation rate is mainly affected by the asynchrony of pollinator species abundances while pollinator richness shows contrasting responses depending on the plant species.
+As for the stability of the plant reproductive success, we found no relationship between the stability of fruits or seed set and the stability of the visitation rate.
+This is because for most years, visitation rates are high enough to prevent pollen limitation, but interestingly, in bad[?]() years the effect of pollinator richness on fruit proportion becomes important.
 
@@
 Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean  ± standard error: 5.92  ± 0.54 plant species per site).
-All the floral visitors (from now on referred to as pollinators) that contacted with their flowers  were registered over 5 minutes.
+All the floral visitors (from now on referred to as pollinators) that contacted with their flowers  were registered in visits per flower and minutes by performing timed focal observations to the selected individuals.
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
@@
 ## Stability
-For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were present in at least 5 sites during the 5 years.
-The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot.
+For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites during the 5 years.
+The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following (REF).
 To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot during the five years.
-To synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018).
-All of them were positively correlation in each plant species, therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses.
+For synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018).
+All of them were positively correlated within each plant species, therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses.
 This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous.
@@
 When we analyzed whether the stability of the visitation rate affected the stability of the plant reproductive success, we found no relationship between this and the stability of the fruit proportion (Estimate: 4.692; std.
-error: 4.545), and neither with the stability of the number of seeds (Estimate: 0.859; std.
-error: 1.825).
+error: 4.545) (Fig 2A), and neither with the stability of the number of seeds (Estimate: 0.859; std.
+error: 1.825) (Fig 2B).
 

### 2022-11-03 script/stability.R
calculate synchrony with observation time and effort corrected

@@ -183,31 +183,33 @@ prueba=prueba %>%
   relocate(time_obs, .before = Andrena_agilissima)
 
 # add round per year
-round=focal %>%
-  group_by(Year) %>%
-  summarise_at(vars(8), funs(max(., na.rm=TRUE)))
+round=focal_0 %>%
+  group_by(Year, Plant_gen_sp,Site_ID) %>%
+  summarise(round= n_distinct(Round))
+
 
 prueba=left_join(prueba, round) %>%
-  relocate(Round, .before = Plant_gen_sp)
+  relocate(round, .before = Plant_gen_sp)
 
 
 # calculate sample effort: different rounds per year and different observation time. 
 # We multiply round by time = effort. 
-# The abundance of each pollinator is multiplied by effort and divided by its year's effort.
-
 prueba= prueba %>%
-  mutate(effort= Round*time_obs) %>%
+  mutate(effort= round*time_obs) %>%
   relocate(effort, .before = Andrena_agilissima)
 
-mean(prueba$effort)
+# The abundance of each pollinator is divided by observation time
+prueba_time=prueba %>%
+  mutate_at(vars(c(7:130)),funs(./time_obs))
 
-prueba_2=prueba %>%
-  mutate_at(vars(c(7:130)),funs(.*mean(prueba$effort)/effort))
+# The abundance of each pollinator is divided by effort 
+prueba_effort=prueba %>%
+  mutate_at(vars(c(7:130)),funs(./effort))
 
 
 
 # Richness 
-data_long <- gather(prueba_2, pollinator, frequ, Andrena_agilissima : Xylocopa_violacea , factor_key=T)
+data_long <- gather(prueba, pollinator, frequ, Andrena_agilissima : Xylocopa_violacea , factor_key=T)
 data_long
 
 riqueza= data_long %>%
@@ -227,9 +229,19 @@ log_VR <- function(x){
 
 
 # un dato por sp planta, sitio y año (sin plant_id)
-syn_2=prueba_2%>% 
+# corrected observation time
+syn_1=prueba_time%>% 
   group_by(Plant_gen_sp,Site_ID)%>% 
   do(log_VR=log_VR(.[7:130]))
+
+
[…]

### 2022-11-14 script/Model_Year_2.R
analysis of interaction effect

@@ -1,0 +1,161 @@
+library(tidyverse)
+library(broom.mixed)
+library(broom)
+library(lmerTest)
+library(dplyr)
+library(patchwork)
+library(ggcorrplot)
+library(ggpubr)
+library (lme4)
+library(sjPlot)
+library(car)
+library(effects)
+library(RColorBrewer)
+library(piecewiseSEM)
+library(multcomp)
+
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
+Pollinator_Plant<-Pollinator_Plant[,-1]
+Pollinator_Plant$Year= as.factor(Pollinator_Plant$Year)
+Pollinator_Plant$Site_ID= as.factor(Pollinator_Plant$Site_ID)
+Pollinator_Plant$Plant_gen_sp= as.factor(Pollinator_Plant$Plant_gen_sp)
+
+str(Pollinator_Plant)
+
+
+
+# species out
+#plant species that for each year occur only at one site
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp, Year) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp, Year)
+
+
+Pollinator_Plant= anti_join(Pollinator_Plant, spp_out)
+
+levels(factor(Pollinator_Plant$Plant_gen_sp))
+
+#we analyze whether the fruit proportion is affected by richness, 
+#year and its interaction for all data 
+#with plant species nested within site as random effect
+mod1_to= glmer(cbind(fruit_formado, Fruit_No) ~ S_total * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
+summary(mod1_to)
+car::Anova(mod1_to,Type="III")
+
+
+plot_model(mod1_to, type = "int")
+plot_model(mod1_to, type = "pred")
+
+summary(glht(mod1_to, mcp(Year="Tukey")))
+
+
+#getting effects for the two variables
+ee_mod1 <- as.data.frame(Effect(c("S_total","Year"),mod = mod1_to))
+
+p1=ggplot(ee_mod1, aes(S_total,fit))+
+  geom_line(size=0.8)+ 
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
[…]

### 2022-11-14 Manuscript/Manuscript.Rmd
results and plots

--- 2022-10-26 Manuscript/Manuscript.Rmd
@@
 title: "Title"
-output: pdf_document
 date: '2022-10-26'
+output: 
+  pdf_document :
+header-includes:
+ \usepackage{float}
+ \floatplacement{figure}{H}
+ \usepackage{caption}
+ \renewcommand{\caption}{Figure}
+
 ---
+
+# Abstract
+
+1.
+Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions is important for predicting the resilience of communities to changes in biodiversity.
+While community stability can be influenced by species richness and asynchrony of species,  the relation with the stability of ecosystem functioning provided by this community is less explored, and specially for functions involving several trophic levels such as plant pollination.
+
+2.
+Using a 5-year dataset across 13 Mediterranean woodland patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and its relationship between the stability of visitation rate and the stability of the plants reproductive success.
+[In addition, we analyzed whether the year together with richness and visitation rate affected the proportion of fruits and the number of seeds.](esto pensamos como ponerlo con los results finales)
+
+3.
+The stability of plant's visitation rate is mainly affected by the asynchrony of pollinator species abundances while pollinator richness shows contrasting responses depending on the plant species.
+As for the stability of the plant reproductive success, we found no relationship between the stability of fruits and the stability of the visitation rate, however a negative tendency was observed between stability of seed and the stability of visitation rate.
+[This is because for most years, visitation rates are high enough to prevent pollen limitation, but interestingly, in bad years the effect of pollinator richness on fruit proportion becomes important.]()
 
@@
 ## Stability
-For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were present in at least 5 sites during the 5 years.
-The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot.
-To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot during the five years.
-To synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018).
-All of them were positively correlation in each plant species, therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses.
+For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites.
+The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following (Tilman, 1999).
+To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
+For synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018).
+All of them were positively correlated within each plant species, therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses.
 This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous.
@@
 For a deeper understanding, we also analyzed the respond of the stability for each plant species separately.
+
 For our aim to study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or stability of seed number and as explanatory variable the visitation rate stability.
 Site and plant species were included as factor random.
+
 To detect whether the effect of pollinator richness and visitation rate is different across the years, we use all plant species sampled.
 We analyzed the interaction effect richness and year, and visitation rate and year on fruit proportion using  binomial generalized linear mixed models, and on the number of seeds employing linear mixed model.
-The number of seeds per fruit was centered and scaled to allow meaningful comparisons across species.
+The number of seeds per fruit was centered and scaled per plant species to allow meaningful comparisons across species.
 For all models, we included plant species identity nested within site and site as random effects because of multiple individuals of the same plant species are measured at each site.
@@
 
-Stability of visitation rate ranged from 0.71 to 5.63 (mean ± SE: 1.715 ± 0.135), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.98 (0.689 ± 0.036).
-Our results showed that the stability of visitation rate was positively related with de asynchorny (Estimate: 1.236; standard error: 0.658) (Fig 1A), and it was not influenced by the pollinator richness (Estimate: 0.021; standard error: 0.034) (Fig 1B).
-when we analyzed the plant species separately, we observed that the relationship between stability of visitation rate and richness is different in function of plant species.
-*Cistus crispus* and *Cistus salviifolius* showed a negative relation whereas *Cistus ladanifer* and *Lavandula pedunculata* was positive.
-The tendency of the asynchrony was positive in all plant species except to the *Lavandula pedunculata*.
-(Supplementary material-Fig1)
+## Stability of visitation rate and its drives: richness and synchrony 
+Stability of visitation rate ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
+Our results showed a significant relationship between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate: 4.851; standard error: 1.368) (Fig 1A), whereas the pollinator richness was marginal and negatively related to stability (Estimate: -0.125; standard error: 0.067) (Fig 1B).
+When we analysed the plant species separately, we observed that all plant species follow the general tendency, except to the *L.
+pedunculata* that presented a negative tendency between stability of visitation rate and asynchrony, and positive with the richness (Suplementary material-Fig 1).
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE, out.width="100%"}
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 10,fig.width=20, out.width="80%",fig.align='center', fig.cap =" 1.Relationship between stability of visitation rate (calculated as the inverse of the coefficient of variation) and asynchorny of pollinators (Loreau and de Mazancourt’s index) (A) and richness of pollinators (B).
+Dots represent the different plant species incluided in the analysis."}
 
@@
 
-# stability data for five plant species present at least in five sites
+# staility of visitation rate and richness and asynchrony
+# plant species present at least in five sites
 # C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata
 
-data_plant<- read.csv("../Data/Stability_fivespecies.csv")
+# stability data 
+data_plant<- read.csv("../Data/Stability.csv")
 data_plant<-data_plant[,-1]
 
-# Replace inf with NA
-data_plant[sapply(data_plant, is.infinite)] <- NA
+# eliminar plant species 
+sp_out2=data_plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id <= 4) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in at least 5 sites
+data_plant = data_plant %>% filter(!Plant_gen_sp %in% sp_out2)
+
+data_plant=data_plant %>%
+  filter(!Plant_gen_sp=="Salvia rosmarinus") %>%
+  filter(!Plant_gen_sp=="Halimium calycinum")%>%
+  filter(!Plant_gen_sp=="Lavandula stoechas")
+
+## Replace Inf and -Inf with NA
+data_plant[is.na(data_plant) | data_plant == "Inf"] <- NA 
+data_plant[is.na(data_plant) | data_plant == "-Inf"] <- NA
 
@@
 #where φ is Loreau and de Mazancourt’s (2008)
-data_plant$asynchrony= 1-data_plant$syncLM
+data_plant$asyn_LM= 1-data_plant$syncLM
 
 #model 
-mod1_sta= lmer (cv_1_visitation ~ S_total + asynchrony + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+mod1_sta= lmer (cv_1_visitation ~ S_total + asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
 
 #getting effects for asynchrony
-effe_mod_sta <-data.frame( effect("asynchrony", mod1_sta, se = TRUE))
+effe_mod_sta <-data.frame( effect("asyn_LM", mod1_sta, se = TRUE))
 
 #plot model of asynchrony
-p1=ggplot(effe_mod_sta, aes(asynchrony, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.1, colour = "black")+
-  scale_y_continuous(limits = c(-0.14, 6))+ labs(color='Plant species')+
-  geom_point(data = data_plant, aes(x =  asynchrony, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
-  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
-  labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")
+p1=ggplot(effe_mod_sta, aes(asyn_LM, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.2, colour = "black", size=1)+
+  scale_y_continuous(limits = c(-4, 9.5))+labs(color='Plant species')+
+  geom_point(data = data_plant, aes(x =  asyn_LM, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=7)+
+  scale_colour_brewer(palette = "Set1")+
+   theme_bw ()+
+  labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")+
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
 
@@
 p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.1, colour = "black")+
-  scale_y_continuous(limits = c(-0.14, 6))+  labs(color='Plant species')+
-  geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
-  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
-  labs(x = "Richness of pollinator",y="")
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black", size=1)+
+  scale_y_continuous(limits = c(-4, 9.5))+  labs(color='Plant species')+
+  geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=7)+
+  scale_colour_brewer(palette = "Set1")+
+  theme_bw ()+
+  labs(x = "Richness of pollinator",y="") +
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
 
@@
   theme(plot.tag.position = c(0, 1),
-        plot.tag = element_text(hjust = -3.5, vjust = 1.5, size=15))& theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))
+        plot.tag = element_text(hjust = -0.1, size=30))& 
+  theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))&theme(text = element_text(size=30))
 p_cv_visit+ plot_layout(guides = "collect")
@@
 ```
+
+## Stability of visitation rate and stability of the plant reproductive success
+
+Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
+When we analyzed whether the stability of the visitation rate affected the stability of the plant reproductive success, we did not find relationship between this and the stability of the fruit proportion (Estimate: -1.547; std.
+error: 2.611) (Fig 2A), however, the stability of seed number showed negative tendency with the stability of visitation rate (Estimate: -1.887; std.
+error: 0.959) (Fig 2B).
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 10,fig.width=20,out.width="80%",fig.align='center', fig.cap = " 2.
+Relationship between stability of plant reproductive succes: fruit propotion (A) and seed number (B) and the stability of visitation rate.
+Dots represent the different plant species incluided in the analysis."}
+
+#model fruit stability ~ visitation rate stability
+mod2_sta= lmer(cv_1_fruit ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID), data = data_plant)
+
+#getting effects 
+effe3_mod_sta <-data.frame( effect("cv_1_visitation", mod2_sta, se = TRUE))
+
+#plot model 
+p_mod2=ggplot(effe3_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper),linetype = 3, alpha=0.2, colour = "black",size=1)+
+  geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_fruit, color=Plant_gen_sp),alpha=0.7, size=7)+
+  labs(color='Plant species')+
+  scale_colour_brewer(palette = "Set1")+
+  labs(y = "Stability of fruit proportion",x="Stability of visitation rate")+
+  theme_bw ()+
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
+
+# model seed stability ~ visitation rate stability
+mod3_sta= lmer(cv_1_seed ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID), data = data_plant)
+
+#getting effects 
+effe4_mod_sta <-data.frame( effect("cv_1_visitation", mod3_sta, se = TRUE))
+
+#plot model 
+p_mod3=ggplot(effe4_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black", size=1)+
+  labs(color='Plant species')+
+  geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_seed, color=Plant_gen_sp), alpha=0.7,size=7)+
+  scale_colour_brewer(palette = "Set1")+
+  labs(y = "Stability of seed number",x="Stability of visitation rate")+
+  theme_bw ()+
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
+
+#join plots
+p_plant=p_mod2+p_mod3+ 
+  plot_annotation(tag_levels = "A")& 
+  theme(plot.tag.position = c(0, 1),
+        plot.tag = element_text(hjust = -0.8, vjust = 0.5,size=30))& 
+  theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))&theme(text = element_text(size=30))
+p_plant+ plot_layout(guides = "collect")
+
+```
+
+## Effect of pollinators across years on the plant reproductive success
+
+When we analysed whether the effect of pollinator richness and visitation rate is different across the years, we found that both variables showed a significant interaction effect with the year on fruit proportion.
+Although we observed a saturation of the fruit proportion, in year like 2017 is showed that a greater richness and visitation rate increased the fruit proportion (Richness - Estimate: 0.395; std.
+error: 0.15; Visitation rate - Estimate: 25.238; std.
+error: 5.67).
+However in 2018, the relationship between richness and fruit proportion was negative [(Estimate: -0.147; std.
+error: 0.05)](Los estimate y std error en este caso son en funcion de 2015 ya que el modelo lo pone como intercept.
+El Anova(car) nos da Pr(>Chisq) y df, ¿incluyo esta información??) (Fig 3).
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height =13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 3.
+Interaction effect between richness and year (top row), and visitation rate and year (bottom row) on fruit proportion.
+For the visualization purpose, we omit in the visitation rate (x-axis) the values outside of the 95\\%."}
+
+Pollinator_Plant<- read.csv("../Data/Pollinator_Plant.csv") #400 observaciones
+Pollinator_Plant<-Pollinator_Plant[,-1]
+Pollinator_Plant$Year= as.factor(Pollinator_Plant$Year)
+Pollinator_Plant$Site_ID= as.factor(Pollinator_Plant$Site_ID)
+Pollinator_Plant$Plant_gen_sp= as.factor(Pollinator_Plant$Plant_gen_sp)
+
+# species out
+#plant species that for each year occur only at one site
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp, Year) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp, Year)
+
+Pollinator_Plant= anti_join(Pollinator_Plant, spp_out)
+
+# model 1
+mod1_to= glmer(cbind(fruit_formado, Fruit_No) ~ S_total * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
+
+#getting effects for the two variables
+ee_mod1 <- as.data.frame(Effect(c("S_total","Year"),mod = mod1_to))
+
+p1=ggplot(ee_mod1, aes(S_total,fit))+
+  geom_line(size=0.8)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
+  geom_point(data= Pollinator_Plant, aes(x = S_total , y = fruit_proportion),shape=21, fill="grey", size=6)+
+  labs(x = "Pollinator richness",y="Fruit proportion")+
+  facet_wrap(~Year, nrow = 1) + 
+  theme_bw ()+
+  theme(legend.position = "none")
+
+# model 2
+mod2_to= glmer(cbind(fruit_formado, Fruit_No) ~ visitatio_rate * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
+
+#getting effects for the two variables
+ee_mod2 <- as.data.frame(Effect(c("visitatio_rate","Year"),mod = mod2_to))
+
+p2=ggplot(ee_mod2, aes(visitatio_rate,fit))+
+  geom_line(size=0.8)+  
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
+  geom_point(data= Pollinator_Plant, aes(x =visitatio_rate , y = fruit_proportion),shape=21, fill="grey", size=6)+
+  labs(x = "Visitation rate",y="Fruit proportion")+
+  facet_wrap(~Year, nrow = 1) + 
+  coord_cartesian(xlim=c(0, quantile(Pollinator_Plant$visitatio_rate,0.95)))+
+  theme_bw ()+
+  theme(legend.position = "none")
+
+p1/p2&theme(text = element_text(size=35))
+
+```
+
+For the seed number, we not found the interaction effect to pollinator richness, however we found a marginal significant interaction between visitation rate and year.
+We observed that a higher the visitation rate increased the seed number in 2019 [(Fig 4)](quizas puede ir a material suplementario).
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 4.
+Interaction effect between richness and year (top row), and visitation rate and year (bottom row) on seed number.
+For the visualization purpose, we omit in the visitation rate (x-axis) the values outside of the 95\\%."}
+
+# #scale seed number variable
+Pollinator_Plant=Pollinator_Plant %>% 
+  group_by(Plant_gen_sp) %>%
+  mutate(seed_sc=scale(Seeds, center = T, scale = T))
+
+#model3
+mod3_to= lmer(seed_sc ~S_total * Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
+
+#getting effects for the two variables
+ee_mod3 <- as.data.frame(Effect(c("S_total","Year"),mod = mod3_to))
+
+p3=ggplot(ee_mod3, aes(S_total,fit))+
+  geom_line(size=0.8)+ 
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
+  geom_point(data= Pollinator_Plant, aes(x = S_total , y = seed_sc),shape=21, fill="grey", size=6)+
+  labs(x = "Pollinator richness",y="Seed number")+
+  ylim(-3,3)+
+  facet_wrap(~Year, nrow = 1) + 
+  theme_bw ()+
+  theme(legend.position = "none")
+
+#model4
+mod4_to= lmer(seed_sc ~ visitatio_rate*Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
+
+#getting effects for the two variables
+ee_mod4 <- as.data.frame(Effect(c("visitatio_rate","Year"),mod = mod4_to))
+
+#plot
+
+p4 = ggplot(ee_mod4, aes(visitatio_rate,fit))+
+  geom_line(size=0.8)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
+  geom_point(data= Pollinator_Plant, aes(x =visitatio_rate , y = seed_sc),shape=21, fill="grey",size=6)+
+  labs(x = "Visitation rate",y="Seed number")+
+  facet_wrap(~Year, nrow = 1) + 
+  coord_cartesian(xlim=c(0, quantile(Pollinator_Plant$visitatio_rate,0.95)),ylim = c(-3,3))+
+  theme_bw ()+
+  theme(legend.position="none")
+
+p3/p4 &theme(text = element_text(size=35))
+
+```
+
+\newpage
+
+# Supplementary material
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 1.
+Changes in the stability of visitation rate with the asynchrony (top row) and richness (botton row) are shown for each plant species"}
+# model plot (cv_1_visitation~S_total+asynchrony)
+
+# plot for richness
+plot_stabi_plant <- data_plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+asyn_LM,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line(size=1) +
+  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), linetype = 3, alpha=0.2, colour = "black")))
+
+#Cistus crispus
+p1=plot_stabi_plant$plots[[1]] + geom_point(data =data_plant %>% filter(Plant_gen_sp == "Cistus crispus"), 
+  aes(x =  S_total, y = cv_1_visitation),color="#e41a1c", alpha=0.7,size=7)+ 
+  labs(x = "",y="Stability of visitation rate")+scale_x_continuous(limits = c(9, 16))+
+  scale_y_continuous(limits = c(-5,9.5))+
+  theme_bw ()
+
+#Cistus ladanifer
+p2=plot_stabi_plant$plots[[2]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), 
+  aes(x =  S_total, y = cv_1_visitation),color="#377eb8",alpha=0.7, size=7)+ 
+  labs(x = "",y=NULL)+scale_x_continuous(limits = c(3, 16))+ 
+  scale_y_continuous(limits = c(-1.55,4))+
+  theme_bw()
+
+#Cistus salviifolius
+p3=plot_stabi_plant$plots[[3]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), 
+  aes(x =  S_total, y = cv_1_visitation),color= "#4daf4a",alpha=0.7, size=7)+ 
+  labs(x = "Richness",y=NULL)+scale_x_continuous(limits = c(3, 20))+  
+  scale_y_continuous(limits = c(-3,6))+
+  theme_bw()
+
+#Halimium halimifolium
+p4=plot_stabi_plant$plots[[4]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), 
+  aes(x =  S_total, y = cv_1_visitation), color= "#984ea3",alpha=0.7, size=7)+   labs(x = "",y=NULL)+ scale_x_continuous(limits = c(4, 14))+ 
+  scale_y_continuous(limits = c(-0.7,3))+
+  theme_bw()
+
+#Lavandula pedunculata
+p5=plot_stabi_plant$plots[[5]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), 
+  aes(x =  S_total, y = cv_1_visitation),color="#ff7f00",alpha=0.7, size=7)+ 
+  labs(x = "",y=NULL)+  
+  scale_y_continuous(limits = c(-0.7,4.7))+
+  theme_bw()
+
+# model plot for asynchrony
+plot_stabi_plant_2 <- data_plant %>%
+  nest_by(Plant_gen_sp) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total+asyn_LM,data))) %>%
+  mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "asyn_LM"))) %>%
+  mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line(size=1) +
+ geom_ribbon(aes(ymin = conf.low, ymax = conf.high),linetype = 3, alpha=0.2, colour = "black")))
+
+#Cistus crispus
+p1.1=plot_stabi_plant_2$plots[[1]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus crispus"), 
+  aes(x =  asyn_LM, y = cv_1_visitation),color="#e41a1c",alpha=0.7, size=7)+ 
+  labs(x = "",y="Stability of visitaion rate",subtitle = "Cistus crispus")+
+  scale_y_continuous(limits = c(-5,9.5))+
+   theme_bw()+theme( plot.subtitle = element_text(face = "italic"))
+
+#Cistus ladanifer
+p2.1=plot_stabi_plant_2$plots[[2]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus ladanifer"), 
+  aes(x =  asyn_LM, y = cv_1_visitation),color="#377eb8", alpha=0.7,size=7)+ 
+  labs(x = "",y=NULL,subtitle = "Cistus ladanifer")+ 
+  scale_y_continuous(limits = c(-1.55,4))+
+  theme_bw()+theme( plot.subtitle = element_text(face = "italic"))
+
+#Cistus salviifolius
+p3.1=plot_stabi_plant_2$plots[[3]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Cistus salviifolius"), 
+  aes(x =  asyn_LM, y = cv_1_visitation),color= "#4daf4a",alpha=0.7, size=7)+ 
+  labs(x = "Asynchrony of pollinators",y= NULL,subtitle = "Cistus salviifolius")+ 
+  scale_y_continuous(limits = c(-3,6))+
+  theme_bw()+theme( plot.subtitle = element_text(face = "italic"))
+
+#Halimium halimifolium
+p4.1=plot_stabi_plant_2$plots[[4]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Halimium halimifolium"), 
+  aes(x =  asyn_LM, y = cv_1_visitation), color= "#984ea3", alpha=0.7,size=7)+   labs(x = "",y=NULL,subtitle = "Halimium halimifolium")+ 
+  scale_y_continuous(limits = c(-0.7,3))+
+  theme_bw() +theme( plot.subtitle = element_text(face = "italic"))
+
+#Lavandula pedunculata
+p5.1=plot_stabi_plant_2$plots[[5]] + geom_point(data = data_plant %>% filter(Plant_gen_sp == "Lavandula pedunculata"), 
+  aes(x =  asyn_LM, y = cv_1_visitation), color="#ff7f00",alpha=0.7, size=7)+ 
+  labs(x = "",y=NULL,subtitle = "Lavandula pedunculata")+  
+  scale_y_continuous(limits = c(-0.7,4.7))+
+  theme_bw() +theme( plot.subtitle = element_text(face = "italic"))
+
+#join plot
+p1.1+p2.1+p3.1+p4.1+p5.1+p1+p2+p3+p4+p5+plot_layout(ncol = 5)& theme(axis.title = element_text(face="bold"))&theme(text = element_text(size=30))
+
+```

### 2022-11-15 script/stability_analysisr.R
relation asynchrony and richness

@@ -53,9 +53,9 @@ data_plant[is.na(data_plant) | data_plant == "-Inf"] <- NA
 data_plant$asyn_LM= 1-data_plant$syncLM
 
 
-# correlacion indices de sincronia
+# correlacion asynchrony and richness
 
-syn_cor<-data_plant %>% select(log_VR,syncLM,)
+syn_cor<-data_plant %>% select(asyn_LM,S_total)
 
 ## Replace Inf and -Inf with NA
 syn_cor[is.na(syn_cor) | syn_cor == "Inf"] <- 0 
@@ -132,17 +132,20 @@ ave_seed <- data_plant%>%
 #pollinator abundance is corrected by the sampling effort
 #to calculate the synchrony index
 
-mod1_sta= lmer (cv_1_visitation ~ S_total + asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+mod1_sta= lmer (cv_1_visitation ~ S_total + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+mod1_sta_2= lmer (cv_1_visitation ~ asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
 
 
 summary(mod1_sta)
+summary(mod1_sta_2)
+
 r.squaredGLMM(mod1_sta)
 car::vif(mod1_sta)
 
 car::Anova(mod1_sta,Type="III")
 
  
-plot_model(mod1_sta, type="pred", show.data = T)
+plot_model(mod1_sta_2, type="pred", show.data = T)
 plot_model(mod1_sta, type = "re")
 
 #getting effects for asyncLM 
@@ -172,6 +175,22 @@ p_cv_visit=p1+p2+
         plot.tag = element_text(hjust = -3.5, vjust = 1.5, size=15))& theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))
 p_cv_visit+ plot_layout(guides = "collect")
 
+
+
+# relationship between richness and asynchrony
+mod_rich_asyn= lmer (asyn_LM ~ S_total +  (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+summary(mod_rich_asyn)
+plot_model(mod_rich_asyn,type="pred", show.data = T)
+
+#getting effects for richness
[…]

### 2022-11-15 Manuscript/Manuscript.Rmd
introduction and supplementary fig

@@
 3.
-The stability of plant's visitation rate is mainly affected by the asynchrony of pollinator species abundances while pollinator richness shows contrasting responses depending on the plant species.
-As for the stability of the plant reproductive success, we found no relationship between the stability of fruits and the stability of the visitation rate, however a negative tendency was observed between stability of seed and the stability of visitation rate.
-[This is because for most years, visitation rates are high enough to prevent pollen limitation, but interestingly, in bad years the effect of pollinator richness on fruit proportion becomes important.]()
+The stability of plant's visitation rate is more affected by the asynchrony of pollinator species abundances than by pollinator richness shows a negative tendency.
+As for the stability of the plant reproductive success, we found no relationship between the stability of fruits and the stability of the visitation rate, however a negative relation was observed between stability of seed and the stability of visitation rate.
+However, when years are analysed we found that in some years/[bad years](), the effect of pollinator richness and visitation rate on fruit proportion becomes important.
+
+# Introduction
+
+The role of biodiversity in ecosystem function has long been of great interest to researchers (Hooper et al 2005, Gagic et al., 2015, Lefcheck et al 2015, Oliver et al., 2015, Hong et al 2021).
+We have experimental and observational evidence that biodiversity enhances ecosystem functioning (Cardinale et al., 2006, Cardinale et al., 2012, Tilman et al., 2014), but the role of biodiversity for the stability of ecosystem functioning is less explored (but see Griffin et al., 2009, Grman et al., 2010), specially for functions involving several trophic levels such as plant pollination (Ebeling et al., 2008, Winfree and Kremen 2009, Garibaldi et al 2011, [Lázaro et al 2022](wild Olea europaea communities)).
+Globally, it is estimated that at least 78% of wild plants and 75% of leading crops depend to some extent on pollination by animals (Ollerton et al., 2011; Kleijn et al., 2015).
+Understanding the mechanisms driving pollinator community stability and how this relates to the stability of ecosystem functions and services is important for predicting changes in both community structure and ecosystem function.
+
+Stability can be defined as the inverse of the coefficient of variation of ecosystem properties over time (McCann, 2000; Tilman, 1999).
+Among main driving of stability are the diversity and species asynchrony.
+A higher number of species might provide a wider range of responses to environmental changes, which would result in a higher stability (McCann, 2000, Tilman et al.
+2006, Hector et al.
+2010, Xu et al.
+2021), although non-significant relationships between diversity and stability have also been observed (Hooper et al.
+2005, van der Plas 2019).
+The stability is also influenced by the degree of asynchrony between species.
+In this sense, higher levels of asynchrony in species fluctuation stabilize the community (Loreau et al.
+2002, Ruijven and Berendse 2007, Blüthgen et al.
+2016, Craven et al.
+2018).
+It has been also shown that stability can associate more strongly with the degree of synchrony among dominant species than with species richness (Blüthgen et al 2016, Valencia et al 2020).
+[While community temporal stability should be related to the stability of ecosystem functions and services, there is limited evidence linking both processes on multitrophic systems.]()
+
+Since the reproductive success of the most plant highly depends on pollination by animals, the stability of pollinator communities may increase the plant reproductive success.
+A greater diversity of pollinators has been shown to increase the plant reproductive success as a result of complementary service provision arising from variation across of pollinator effectiveness, including space and time (Hoehn et al.
+2008; Fründ et al.
+2010, Albrecht et al.
+2012, Blüthgen and Klein, 2013, Fründ et al.
+2013).
+Pollinator species may exhibit different ranges of temporal activity (Pisanty et al.
+2016, Rader et al.
+2016) and consequently may provide pollination services at different times of the season.
+Other studies suggesting that a few dominant species are sufficient to provide a higher reproductive success of plants, i.e pollinator communities are dominated by a small number of common species, and that abundance fluctuations of these dominant species are often responsible for a majority of pollination service provision across an ecosystem (Kleijn et al 2015, Winfree et al 2015).
+
+[gap]()
+
+In the current study, we use a 5-year dataset in Mediterranean woodland patches to study the role of richness and synchrony of pollinator species as drivers of stability of visitation rate.
+We also evaluate whether the stability of plant reproductive success, employed the stability of fruit proportion and stability of seed numbers, is affected by the stability of pollinator communities.
+In addition, we analysis whether the effect of the pollinator richness and visitation rate on the reproductive success of the plants varies according to the year.
+
+[Hipotesis]()
 
@@
 ## Stability
+
 For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites.
@@
 ## Statistical analysis
-To evaluate the main drivers of visitation rate stability, we employed linear mixed model to test for relationships between stability and richness and asynchrony including site and plant species as random factor.
-We used variance inflation factors to check for collinearity between explanatory variables.
+
+All the analyses of this study were conducted in R ver.
+4.0.2.
+To evaluate the main drivers of visitation rate stability, first we run correlation test between asynchrony and richness.
+Due to we observed a positive correlation among both variables, linear mixed models were used separately to evaluate the relationships between stability of visitation rate and pollinator richness, and stability of visitation rate and asynchrony of pollinator including site and plant species as random factor.
+We also asses the relationship between asynchrony and pollinator richness with linear mixed model.
 For a deeper understanding, we also analyzed the respond of the stability for each plant species separately.
@@
 ## Stability of visitation rate and its drives: richness and synchrony
+
 Stability of visitation rate ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-Our results showed a significant relationship between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate: 4.851; standard error: 1.368) (Fig 1A), whereas the pollinator richness was marginal and negatively related to stability (Estimate: -0.125; standard error: 0.067) (Fig 1B).
-When we analysed the plant species separately, we observed that all plant species follow the general tendency, except to the *L.
-pedunculata* that presented a negative tendency between stability of visitation rate and asynchrony, and positive with the richness (Suplementary material-Fig 1).
+Our results showed a significant relationship between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate: 2.903; standard error: 1.134) (Fig 1A),
+whereas stability of visitation rate was not influenced by the pollinator richness (Estimate: -0.001; standard error: 0.063) (Fig 1B).
+We also observed a significant and positive relationship between asynchrony and pollinator richness (Estimate: 0.031; standard error: 0.007) (Supplementary material-Fig 1).
+When we analysed the plant species separately, we found no significant differences but we observed positive tendency in asynchrony for *H.
+halimifolium* and *L.
+pedunculata*.
+In the case of richness, *C.
+crispus*, *C.
+ladanifer* and *C.
+salviifolius* was a negative tendecy wile *H.
+halimifolium* and *L.
+pedunculata* was positive (Supplementary material-Fig 2).
 
@@
 #model 
-mod1_sta= lmer (cv_1_visitation ~ S_total + asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+mod1_sta= lmer (cv_1_visitation ~ asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
 
@@
 
+#model richness
+mod1.2_sta= lmer (cv_1_visitation ~ S_total + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+
 #getting effects for richness
-effe2_mod_sta <-data.frame( effect("S_total", mod1_sta, se = TRUE))
+effe2_mod_sta <-data.frame( effect("S_total", mod1.2_sta, se = TRUE))
 
@@
 # Supplementary material
-```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 1.
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 10,fig.width=20,out.width="80%",fig.align='center',fig.cap=" 1.
+Relationship between asynchrony and pollinator richness.
+Dots represent the different plant species incluided in the analysis"}
+
+# relationship between richness and asynchrony
+mod_rich_asyn= lmer (asyn_LM ~ S_total +  (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+
+#getting effects for richness
+effe_rich_mod_sta <-data.frame( effect("S_total", mod_rich_asyn, se = TRUE))
+
+#plot model 
+p1.2=ggplot(effe_rich_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black")+
+  labs(color='Plant species')+
+  scale_colour_brewer(palette = "Set1")+
+  geom_point(data = data_plant, aes(x =  S_total, y = asyn_LM, color=Plant_gen_sp), alpha=0.7,size=7)+
+  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
+  labs(x = "Richness of pollinator",y="Asynchrony")+ theme(legend.text = element_text(face="italic"))
+
+p1.2&theme(text = element_text(size=30))
+```
+
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 2.
 Changes in the stability of visitation rate with the asynchrony (top row) and richness (botton row) are shown for each plant species"}
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(cv_1_visitation~S_total+asyn_LM,data))) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total,data))) %>%
   mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
@@
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(cv_1_visitation~S_total+asyn_LM,data))) %>%
+  mutate(mod = list(lm(cv_1_visitation~asyn_LM,data))) %>%
   mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "asyn_LM"))) %>%

### 2022-11-17 Manuscript/Manuscript.Rmd
Quick comments from Nacho

@@
 While community stability can be influenced by species richness and asynchrony of species,  the relation with the stability of ecosystem functioning provided by this community is less explored, and specially for functions involving several trophic levels such as plant pollination.
+[For J ecol, I will focus on stability of plant reproductive success, and then link that to the theory of community stability, so just the same sentences you usem, but order upside down]()
 
 2.
-Using a 5-year dataset across 13 Mediterranean woodland patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and its relationship between the stability of visitation rate and the stability of the plants reproductive success.
+Using a 5-year dataset across 13 Mediterranean woodland patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and plants reproductive success.
 [In addition, we analyzed whether the year together with richness and visitation rate affected the proportion of fruits and the number of seeds.](esto pensamos como ponerlo con los results finales)
@@
 3.
-The stability of plant's visitation rate is more affected by the asynchrony of pollinator species abundances than by pollinator richness shows a negative tendency.
+The stability of plant's visitation rate is more affected by the asynchrony of pollinator species abundances than by pollinator richness.
+shows a negative tendency.
 As for the stability of the plant reproductive success, we found no relationship between the stability of fruits and the stability of the visitation rate, however a negative relation was observed between stability of seed and the stability of visitation rate.
@@
 Globally, it is estimated that at least 78% of wild plants and 75% of leading crops depend to some extent on pollination by animals (Ollerton et al., 2011; Kleijn et al., 2015).
-Understanding the mechanisms driving pollinator community stability and how this relates to the stability of ecosystem functions and services is important for predicting changes in both community structure and ecosystem function.
+Understanding the mechanisms driving pollinator community stability and how this relates to the stability of ecosystem functions and services delivered (i.e.
+pollination) is important for predicting changes in both community structure and ecosystem function.
 
-Stability can be defined as the inverse of the coefficient of variation of ecosystem properties over time (McCann, 2000; Tilman, 1999).
+Stability can be defined [as the inverse of the coefficient of variation of ecosystem properties over time](irrelevant now) (McCann, 2000; Tilman, 1999).
 Among main driving of stability are the diversity and species asynchrony.
@@
 It has been also shown that stability can associate more strongly with the degree of synchrony among dominant species than with species richness (Blüthgen et al 2016, Valencia et al 2020).
-[While community temporal stability should be related to the stability of ecosystem functions and services, there is limited evidence linking both processes on multitrophic systems.]()
+[While community temporal stability should be related to the stability of ecosystem functions and services, there is limited evidence linking both processes on multitrophic systems.](I like this sentence)
 
-Since the reproductive success of the most plant highly depends on pollination by animals, the stability of pollinator communities may increase the plant reproductive success.
+Since the reproductive success of most plant species highly depends on pollination by animals (Ollerton et al 2012), the stability of pollinator communities may increase the stability of plant reproductive success.
 A greater diversity of pollinators has been shown to increase the plant reproductive success as a result of complementary service provision arising from variation across of pollinator effectiveness, including space and time (Hoehn et al.
@@
 2016) and consequently may provide pollination services at different times of the season.
-Other studies suggesting that a few dominant species are sufficient to provide a higher reproductive success of plants, i.e pollinator communities are dominated by a small number of common species, and that abundance fluctuations of these dominant species are often responsible for a majority of pollination service provision across an ecosystem (Kleijn et al 2015, Winfree et al 2015).
+Other studies suggesting that a few dominant species are sufficient to provide a higher reproductive success of plants, i.e pollinator communities are dominated by a small number of common species, and that abundance fluctuations of these dominant species are often responsible for a majority of pollination service provision across an ecosystem (Kleijn et al 2015, Winfree et al 2015).[not sure this last sentence is supported by the refs, plus, is in crops only]()
 
-[gap]()
+[gap](I think something about temporal variation and pollen limitation)
 
@@
 We also evaluate whether the stability of plant reproductive success, employed the stability of fruit proportion and stability of seed numbers, is affected by the stability of pollinator communities.
-In addition, we analysis whether the effect of the pollinator richness and visitation rate on the reproductive success of the plants varies according to the year.
+In addition, we analyzed whether the effect of the pollinator richness and visitation rate on the reproductive success of the plants varies over time.
 
@@
 Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean  ± standard error: 5.92  ± 0.54 plant species per site).
-All the floral visitors (from now on referred to as pollinators) that contacted with their flowers  were registered in visits per flower and minutes by performing timed focal observations to the selected individuals.
+All the floral visitors (from now on referred to as pollinators) that contacted with their flowers  were registered in visits per flower and minute by performing timed focal observations to the selected individuals.
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
 For each plant individual, we counted the total number of flowers and at the end of the season, we recorded the number of fruit and the seeds per fruit.
+All plants analyzed are at least partially pollinator dependent.
 For each site and year, we calculated the visitation rate of pollinators as the number of visits divided by the number of flowers, pollinator richness, the fruit set as the proportion of fruit, and the seed set as number of seed for each plant individual sampled per site.
@@
 
-For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites.
+For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites [what about years?
+in all years?]().
 The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following (Tilman, 1999).
 To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
-For synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018).
-All of them were positively correlated within each plant species, therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses.
+To calculate synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018).
+All of them were positively correlated to each other within each plant species [sup mat?](), therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses.
 This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous.
@@
 4.0.2.
-To evaluate the main drivers of visitation rate stability, first we run correlation test between asynchrony and richness.
-Due to we observed a positive correlation among both variables, linear mixed models were used separately to evaluate the relationships between stability of visitation rate and pollinator richness, and stability of visitation rate and asynchrony of pollinator including site and plant species as random factor.
-We also asses the relationship between asynchrony and pollinator richness with linear mixed model.
-For a deeper understanding, we also analyzed the respond of the stability for each plant species separately.
+To evaluate the main drivers of visitation rate stability, first we run correlation test between pollinator asynchrony and richness.
+As we observed a positive correlation among both variables [indicate r](), linear mixed models were used separately to evaluate the relationships between stability of visitation rate and pollinator richness, and stability of visitation rate and asynchrony of pollinator including site and plant species as random factor.
+[We also asses the relationship between asynchrony and pollinator richness with linear mixed model.](first you said correlation, now is lm?) For a deeper understanding, we also analyzed the response for each plant species separately.
 
-For our aim to study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or stability of seed number and as explanatory variable the visitation rate stability.
+To study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or stability of seed number and as explanatory variable the visitation rate stability.
 Site and plant species were included as factor random.
@@
 
+All models check with Dharma... cite packages used for plotting, etc...
+
 # Results
@@
 Stability of visitation rate ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-Our results showed a significant relationship between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate: 2.903; standard error: 1.134) (Fig 1A),
-whereas stability of visitation rate was not influenced by the pollinator richness (Estimate: -0.001; standard error: 0.063) (Fig 1B).
-We also observed a significant and positive relationship between asynchrony and pollinator richness (Estimate: 0.031; standard error: 0.007) (Supplementary material-Fig 1).
-When we analysed the plant species separately, we found no significant differences but we observed positive tendency in asynchrony for *H.
+Our results showed a significant relationship between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A),
+whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063)[only need to explain what is what the first time]() (Fig 1B).
+[We also observed a significant and positive relationship between asynchrony and pollinator richness (Estimate: 0.031; standard error: 0.007) (Supplementary material-Fig 1).](decide if this is needed)
+When we analysed the plant species separately, we found [no significant](are we reporting p-values?) differences but we observed positive tendency in asynchrony for *H.
 halimifolium* and *L.
-pedunculata*.
+pedunculata* [and other species has also positive estmate, right?]().
 In the case of richness, *C.
@@
 Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
-When we analyzed whether the stability of the visitation rate affected the stability of the plant reproductive success, we did not find relationship between this and the stability of the fruit proportion (Estimate: -1.547; std.
+When we analyzed whether the stability of the visitation rate affected the stability of the plant reproductive success, we did not find a relationship between this and the stability of the fruit proportion (Estimate: -1.547; std.
 error: 2.611) (Fig 2A), however, the stability of seed number showed negative tendency with the stability of visitation rate (Estimate: -1.887; std.
@@
 error: 0.05)](Los estimate y std error en este caso son en funcion de 2015 ya que el modelo lo pone como intercept.
-El Anova(car) nos da Pr(>Chisq) y df, ¿incluyo esta información??) (Fig 3).
+El Anova(car) nos da Pr(>Chisq) y df, ¿incluyo esta información??) (Fig 3).[Hay que pensar como lo contamos]()
 

### 2022-11-18 Manuscript/Figures/Plot_1.R
edit

@@ -46,7 +46,7 @@ data_plant$asyn_LM= 1-data_plant$syncLM
 
 
 #model 
-mod1_sta= lmer (cv_1_visitation ~ S_total + asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+mod1_sta= lmer (cv_1_visitation ~  asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
 
 
 
@@ -56,36 +56,55 @@ effe_mod_sta <-data.frame( effect("asyn_LM", mod1_sta, se = TRUE))
 
 #plot model of asynchrony
 p1=ggplot(effe_mod_sta, aes(asyn_LM, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.1, colour = "black")+
-  scale_y_continuous(limits = c(-4, 9.5))+labs(color='Plant species')+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.2, colour = "black")+
+  scale_y_continuous(limits = c(-2.5, 9.5))+labs(color='Plant species')+
   geom_point(data = data_plant, aes(x =  asyn_LM, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.5,size=3)+
   scale_colour_brewer(palette = "Set1")+
-   theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
+   theme_bw ()+
   labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")+
   guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
 
 
 
+#model richness
+mod1.2_sta= lmer (cv_1_visitation ~ S_total + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+
+
 #getting effects for richness
-effe2_mod_sta <-data.frame( effect("S_total", mod1_sta, se = TRUE))
-
-
+effe2_mod_sta <-data.frame( effect("S_total", mod1.2_sta, se = TRUE))
 
 #plot model of richness
-p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
+p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1,linetype = "dashed")+
[…]

### 2022-11-22 script/Richness_stability.R
Stability of richness

@@ -1,0 +1,127 @@
+library(tidyverse)
+library(broom.mixed)
+library(broom)
+library(lmerTest)
+library(dplyr)
+library(reshape2)
+library(tidyr)
+library(ggplot2)
+library(ggeffects)
+library(patchwork)
+library(ggcorrplot)
+library(ggpubr)
+library(qqplotr)
+
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
+str(Pollinator_Plant)
+Pollinator_Plant<-Pollinator_Plant[,-1]
+
+
+#Species out
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+
+#Data with species in more than 1 site
+Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
+
+
+# datos sin plant_id (mean de las variables porque hay plantas con 2 indv, otras 3, etc)
+# nos quedamos con sitio - año - plant species
+pol_plant2=Pollinator_Plant %>%
+  group_by(Site_ID,Year, Plant_gen_sp) %>%
+  summarise_if(is.numeric, mean)
+
+levels(factor(pol_plant2$Plant_gen_sp)) #12 plant species 
+
+
+
+## Stability of richness ##
+
+cv_1richness<-pol_plant2 %>%
+  group_by(Plant_gen_sp,Site_ID) %>%
+  summarise_at(vars(S_total),cv_1 <- function(x, ...) {
+    ( mean(x, ...)/sd(x, ...) )
+  })%>%
+  ungroup()
+
+
+# Stability of fruit proportion
+cv_1Fruit2<-pol_plant2 %>%
+  group_by(Plant_gen_sp,Site_ID) %>%
+  summarise_at(vars(fruit_proportion),cv_1 <- function(x, ...) {
+    ( mean(x, ...)/sd(x, ...) )
+  })%>%
+  ungroup()
+
+
+
+
+# seed number stability 
+cv_1Seed2<-pol_plant2 %>%
+  group_by(Plant_gen_sp,Site_ID) %>%
+  summarise_at(vars(Seeds),cv_1 <- function(x, ...) {
+    ( mean(x, ...)/sd(x, ...) )
+  })%>%
+  ungroup()
[…]

### 2022-11-22 Manuscript/Figures/Conceptual_plot.R
Plot conceptual

@@ -1,0 +1,148 @@
+
+library(ggplot2)
+
+
+#First dataset RED
+s1 <- seq(from=0, to=100, by=0.5)
+l1 = log(s1, base = 6)
+d1 = data.frame(l1, s1)
+
+
+#Second dataset BLUE
+s2 <- seq(from=0, to=100, by=0.5)
+l2 = log(s2, base = 8)
+d2 = data.frame(l2, s2)
+
+#Third dataset GREEN
+s3 <- seq(from=0, to=100, by=0.5)
+l3 = log(s3, base = 12)
+d3 = data.frame(l3, s3)
+
+
+
+to=ggplot(d1, aes(s1, l1)) +
+  geom_line(color = "#e41a1c", size=1.3) +
+  geom_line(data =  d2, aes(s2,l2), color = "#377eb8",size=1.3) +
+  geom_line(data =  d3, aes(s3,l3), color = "#4daf4a",size=1.3) +
+  ylab("Reproductive success")+
+  labs(x = "") +
+  theme_classic()+
+  theme(axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())+
+  scale_x_continuous(breaks=seq(from= 0, to= 100, by = 50), labels=c("V1","V2","V3"))+
+  theme(text = element_text(size=15,face="bold"))+
+  theme(axis.ticks.x=element_blank())+
+  annotate("rect", xmin = c(6, 60), xmax = c(15,80), ymin = c(0.6, 1.5), 
+           ymax = c(1.6, 2.6), linetype = 1, fill="gray88", alpha=0.2, colour = "black") +
+  annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R1", "R2", "R3"), size=4)+
+  theme(axis.line.x = element_line(arrow = arrow()))+
+  theme(axis.line.y = element_line(arrow = arrow()))
+
+
+
+##################################
+x <- seq(0, 40, by = 0.1)
+y1 <- sin(x)
+
+da1 <- data.frame( x, y1)
+
+
+R_1=ggplot(da1, aes(x, y1))+
+  geom_line( size=1) +
+  geom_hline(yintercept=0, color= "#e41a1c", size=1) +
+  theme_classic() +
+  xlab("Time") +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) + 
+  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("R3","R1"))+
[…]

### 2022-11-22 Manuscript/Manuscript.Rmd
editing methods

@@
 
-Our study was conducted in the southwest of the Iberian Peninsula (Huelva and Seville - Spain).
+Our study was conducted in the southwest of the Iberian Peninsula (Huelva and Sevilla - Spain).
 We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby.
@@
 Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean  ± standard error: 5.92  ± 0.54 plant species per site).
-All the floral visitors (from now on referred to as pollinators) that contacted with their flowers  were registered in visits per flower and minute by performing timed focal observations to the selected individuals.
+All the floral visitors (from now on referred to as pollinators) that contacted with their flowers were registered by performing focal observations to the selected individuals during five minutes in 2015 -2016 and three minutes from 2017 to 2019.
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
@@
 All plants analyzed are at least partially pollinator dependent.
+Due to the focal time observation was different over years, for each plant individual, the effort of sampling was standardized in frequency per minute dividing the total frequency by total observation time (time observation multiplied by number of round observation).
 For each site and year, we calculated the visitation rate of pollinators as the number of visits divided by the number of flowers, pollinator richness, the fruit set as the proportion of fruit, and the seed set as number of seed for each plant individual sampled per site.
@@
 
-For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites [what about years?
-in all years?]().
+For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites and a minimum of two years per site.
 The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following (Tilman, 1999).
@@
 
-All the analyses of this study were conducted in R ver.
-4.0.2.
-To evaluate the main drivers of visitation rate stability, first we run correlation test between pollinator asynchrony and richness.
-As we observed a positive correlation among both variables [indicate r](), linear mixed models were used separately to evaluate the relationships between stability of visitation rate and pollinator richness, and stability of visitation rate and asynchrony of pollinator including site and plant species as random factor.
-[We also asses the relationship between asynchrony and pollinator richness with linear mixed model.](first you said correlation, now is lm?) For a deeper understanding, we also analyzed the response for each plant species separately.
+Linear mixed models were used to evaluate the relationships between 1) stability of visitation rate and asynchrony of pollinator, 2) stability of visitation rate and pollinator richness, and 3) asynchrony and pollinator richness.
+In all case, site and plant species were included as random factor.
+For a deeper understanding, we also analyzed the response for each plant species separately.
 
@@
 
-All models check with Dharma... cite packages used for plotting, etc...
+All the analyses of this study were conducted in R software (v.
+4.0.2; R Core Team, 2022) and the lme4 (Bates et al., 2015) and ggplot2 (Wickham, 2016) packages.
+DHARMa package was employed for checking all models (Harting 2017)
 
@@
 Stability of visitation rate ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-Our results showed a significant relationship between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A),
-whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063)[only need to explain what is what the first time]() (Fig 1B).
-[We also observed a significant and positive relationship between asynchrony and pollinator richness (Estimate: 0.031; standard error: 0.007) (Supplementary material-Fig 1).](decide if this is needed)
+Our results supported the positive tendency between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A),
+whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 1B).
+We also observed a positively strong relationship between asynchrony and pollinator richness (0.031 ± 0.007) (Fig 1C).
+
 When we analysed the plant species separately, we found [no significant](are we reporting p-values?) differences but we observed positive tendency in asynchrony for *H.
@@
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 10,fig.width=20, out.width="80%",fig.align='center', fig.cap =" 1.Relationship between stability of visitation rate (calculated as the inverse of the coefficient of variation) and asynchorny of pollinators (Loreau and de Mazancourt’s index) (A) and richness of pollinators (B).
-Dots represent the different plant species incluided in the analysis."}
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 8,fig.width=20, out.width="100%",fig.align='center', fig.cap =" 1.Relationships between stability of visitation rate (calculated as the inverse of the coefficient of variation) and asynchorny of pollinators (Loreau and de Mazancourt’s index) (A), stability of visitation rate and pollinator richness (B), and asynchorny of pollinators and richness (C).Dots represent the different plant species incluided in the analysis.Significant models are representing with solid line For the visualization purpose, asynchrony values are represented from 0 to 1."}
 
@@
   geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.2, colour = "black", size=1)+
-  scale_y_continuous(limits = c(-4, 9.5))+labs(color='Plant species')+
+  scale_y_continuous(limits = c(-2.5, 9.5))+labs(color='Plant species')+
   geom_point(data = data_plant, aes(x =  asyn_LM, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=7)+
@@
 #plot model of richness
-p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black", size=1)+
-  scale_y_continuous(limits = c(-4, 9.5))+  labs(color='Plant species')+
+p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1,linetype = "dashed")+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.1, colour = "black", size=1)+
+  scale_y_continuous(limits = c(-2.5, 9.5))+  labs(color='Plant species')+
   geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=7)+
@@
   theme_bw ()+
-  labs(x = "Richness of pollinator",y="") +
+  labs(x = "Richness of pollinator",y="Stability of visitation rate") +
+  guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
+
+# relationship between richness and asynchrony
+mod_rich_asyn= lmer (asyn_LM ~ S_total +  (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+
+#getting effects for richness
+effe_rich_mod_sta <-data.frame( effect("S_total", mod_rich_asyn, se = TRUE))
+#plot model 
+p1.2=ggplot(effe_rich_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black", size=1)+
+  labs(color='Plant species')+
+  coord_cartesian(ylim=c(0,1))+
+  geom_point(data = data_plant, aes(x =  S_total, y = asyn_LM, color=Plant_gen_sp), alpha=0.7,size=7)+
+  scale_colour_brewer(palette = "Set1")+
+  theme_bw ()+
+  labs(x = "Richness of pollinator",y="Asynchrony of pollinator")+
   guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
@@
 #join plots
-p_cv_visit=p1+p2+ 
+p_cv_visit=p1+p2+ p1.2+
   plot_annotation(tag_levels = "A")& 
   theme(plot.tag.position = c(0, 1),
-        plot.tag = element_text(hjust = -0.1, size=30))& 
-  theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))&theme(text = element_text(size=30))
+        plot.tag = element_text(hjust = -0.1,vjust=0.5, size=25))& 
+  theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))&theme(text = element_text(size=25))
 p_cv_visit+ plot_layout(guides = "collect")
@@
 
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 10,fig.width=20,out.width="80%",fig.align='center',fig.cap=" 1.
-Relationship between asynchrony and pollinator richness.
-Dots represent the different plant species incluided in the analysis"}
-
-# relationship between richness and asynchrony
-mod_rich_asyn= lmer (asyn_LM ~ S_total +  (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
-
-#getting effects for richness
-effe_rich_mod_sta <-data.frame( effect("S_total", mod_rich_asyn, se = TRUE))
-
-#plot model 
-p1.2=ggplot(effe_rich_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black")+
-  labs(color='Plant species')+
-  scale_colour_brewer(palette = "Set1")+
-  geom_point(data = data_plant, aes(x =  S_total, y = asyn_LM, color=Plant_gen_sp), alpha=0.7,size=7)+
-  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
-  labs(x = "Richness of pollinator",y="Asynchrony")+ theme(legend.text = element_text(face="italic"))
-
-p1.2&theme(text = element_text(size=30))
-```
-
-```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 2.
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 1.
 Changes in the stability of visitation rate with the asynchrony (top row) and richness (botton row) are shown for each plant species"}

### 2022-11-23 Manuscript/Figures/Suplementary_Fig1.R
edit

@@ -46,7 +46,7 @@ data_plant$asyn_LM= 1-data_plant$syncLM
 # plot for richness
 plot_stabi_plant <- data_plant %>%
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(cv_1_visitation~S_total+asyn_LM,data))) %>%
+  mutate(mod = list(lm(cv_1_visitation~S_total,data))) %>%
   mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "S_total"))) %>%
   mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line(size=1) +
  geom_ribbon(aes(ymin = conf.low, ymax = conf.high), linetype = 3, alpha=0.2, colour = "black")))
@@ -95,7 +95,7 @@ p5=plot_stabi_plant$plots[[5]] + geom_point(data = data_plant %>% filter(Plant_g
 # model plot for asynchrony
 plot_stabi_plant_2 <- data_plant %>%
   nest_by(Plant_gen_sp) %>%
-  mutate(mod = list(lm(cv_1_visitation~S_total+asyn_LM,data))) %>%
+  mutate(mod = list(lm(cv_1_visitation~asyn_LM,data))) %>%
   mutate(mod1 = list(ggeffects::ggpredict(mod, terms = "asyn_LM"))) %>%
   mutate(plots = list(ggplot(mod1, aes(x, predicted)) + geom_line(size=1) +
   geom_ribbon(aes(ymin = conf.low, ymax = conf.high),linetype = 3, alpha=0.2, colour = "black")))

### 2022-11-23 script/stability_analysisr.R
checking outlier

@@ -125,6 +125,8 @@ ave_seed <- data_plant%>%
 
 
 
+
+
 # we analyze whether the stability of visitation rate is affect 
 #by total richness and asynchrony (L & M index) 
 #incorporating site and plant species as random effects 
@@ -191,6 +193,50 @@ p1.2=ggplot(effe_rich_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
   geom_point(data = data_plant, aes(x =  S_total, y = asyn_LM, color=Plant_gen_sp), size=3)+
   theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
   labs(x = "Richness of pollinator",y="Asynchrony")
+
+
+#########################################3
+# out c.crispus el pozo = valor de estabilidad en tasa de visita muy alto
+# ver si cambia el modelo
+
+data_sin_out=data_plant %>%
+  filter(!(Site_ID=="El_pozo" & Plant_gen_sp=="Cistus crispus")) 
+
+
+#model richness
+mod_sta_out= lmer (cv_1_visitation ~ S_total + (1|Site_ID) + (1|Plant_gen_sp), data = data_sin_out)
+summary(mod_sta_out)
+
+#getting effects for richness
+effe2_mod_sta_out <-data.frame( effect("S_total", mod_sta_out, se = TRUE))
+#plor model 
+ggplot(effe2_mod_sta_out, aes(S_total, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.1, colour = "black")+
+  labs(color='Plant species')+
+  geom_point(data = data_sin_out, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), size=3)+
+  theme_classic ()+theme(panel.border = element_rect(colour = "black", fill=NA))+
+  labs(x = "Richness of pollinator",y="Satability of visitaion rate")
+
+
+
+
+# model asynchrony
+mod1_sta_2out= lmer (cv_1_visitation ~ asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_sin_out)
+summary(mod1_sta_2out)
+
+#getting effects for asyncLM 
+effe_mod_sta2_out <-data.frame( effect("asyn_LM", mod1_sta_2out, se = TRUE))
+#plot model 
+ggplot(effe_mod_sta2_out, aes(asyn_LM, fit)) + geom_line(size=1)+
[…]

### 2022-11-24 Manuscript/Figures/Conceptual_plot.R
edit

@@ -1,5 +1,6 @@
 
 library(ggplot2)
+library(patchwork)
 
 
 #First dataset RED
@@ -32,50 +33,49 @@ to=ggplot(d1, aes(s1, l1)) +
   scale_x_continuous(breaks=seq(from= 0, to= 100, by = 50), labels=c("V1","V2","V3"))+
   theme(text = element_text(size=15,face="bold"))+
   theme(axis.ticks.x=element_blank())+
-  annotate("rect", xmin = c(6, 60), xmax = c(15,80), ymin = c(0.6, 1.5), 
+  annotate("rect", xmin = c(2, 60), xmax = c(15,80), ymin = c(0.4, 1.5), 
            ymax = c(1.6, 2.6), linetype = 1, fill="gray88", alpha=0.2, colour = "black") +
-  annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R1", "R2", "R3"), size=4)+
+  annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R3", "R2", "R1"), size=4)+
   theme(axis.line.x = element_line(arrow = arrow()))+
   theme(axis.line.y = element_line(arrow = arrow()))
 
 
 
 ##################################
-x <- seq(0, 40, by = 0.1)
+x <- seq(0, 41, by = 0.1)
 y1 <- sin(x)
+y1.2 <- cos(x+4.3)
 
 da1 <- data.frame( x, y1)
-
+da1.2 <- data.frame( x, y1.2)
 
 R_1=ggplot(da1, aes(x, y1))+
   geom_line( size=1) +
-  geom_hline(yintercept=0, color= "#e41a1c", size=1) +
+  geom_line(data =  da1.2, aes(x, y1.2), color = "#e41a1c",size=1)+
   theme_classic() +
   xlab("Time") +
   theme(axis.text.x=element_blank(),
         axis.ticks.x=element_blank()) + 
-  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("R3","R1"))+
+  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("R1","R3"))+
   theme(text = element_text(size=10, face="bold"))+
   theme(axis.title.y = element_blank()) +
-  annotate("text", x = 42, y = 0.15, label = "Rep", size=3,color="#e41a1c")+
[…]

### 2022-12-01 Manuscript/Figures/Plot_4.R
.

@@ -1,66 +1,0 @@
-
-library(tidyverse)
-library(lme4)
-library(effects)
-library(patchwork)
-
-
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
-Pollinator_Plant<-Pollinator_Plant[,-1]
-Pollinator_Plant$Year= as.factor(Pollinator_Plant$Year)
-Pollinator_Plant$Site_ID= as.factor(Pollinator_Plant$Site_ID)
-Pollinator_Plant$Plant_gen_sp= as.factor(Pollinator_Plant$Plant_gen_sp)
-
-
-# species out
-#plant species that for each year occur only at one site
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp, Year) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp, Year)
-
-
-Pollinator_Plant= anti_join(Pollinator_Plant, spp_out)
-
-# #scale seed number variable
-Pollinator_Plant=Pollinator_Plant %>% 
-  group_by(Plant_gen_sp) %>%
-  mutate(seed_sc=scale(Seeds, center = T, scale = T))
-
-#model3
-mod3_to= lmer(seed_sc ~S_total * Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
-
-#getting effects for the two variables
-ee_mod3 <- as.data.frame(Effect(c("S_total","Year"),mod = mod3_to))
-
-p3=ggplot(ee_mod3, aes(S_total,fit))+
-  geom_line(size=0.8)+ 
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
-  geom_point(data= Pollinator_Plant, aes(x = S_total , y = seed_sc),shape=21, fill="grey")+
-  labs(x = "Pollinator richness",y="Seed number")+
-  ylim(-3,3)+
-  facet_wrap(~Year, nrow = 1) + 
-  theme_bw ()+
-  theme(legend.position = "none")
-
-#model4
-mod4_to= lmer(seed_sc ~ visitatio_rate*Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
-
-
-#getting effects for the two variables
[…]

### 2022-12-01 Manuscript/Figures/Conceptual_plot.R
editing

@@ -30,12 +30,13 @@ to=ggplot(d1, aes(s1, l1)) +
   theme_classic()+
   theme(axis.text.y=element_blank(),
         axis.ticks.y=element_blank())+
-  scale_x_continuous(breaks=seq(from= 0, to= 100, by = 50), labels=c("V1","V2","V3"))+
+  scale_x_continuous(breaks=seq(from= 0, to= 100, by = 20), labels=c("V1","V2","V3", "V4","V5","V6"))+
   theme(text = element_text(size=15,face="bold"))+
   theme(axis.ticks.x=element_blank())+
-  annotate("rect", xmin = c(2, 60), xmax = c(15,80), ymin = c(0.4, 1.5), 
-           ymax = c(1.6, 2.6), linetype = 1, fill="gray88", alpha=0.2, colour = "black") +
+  annotate("rect", xmin = c(0, 60), xmax = c(20,80), ymin = c(0.4, 1.35), 
+           ymax = c(1.75, 2.7), linetype = 1, fill="gray88", alpha=0.3, colour = "black") +
   annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R3", "R2", "R1"), size=4)+
+  annotate("text", x = c(1.25, 61.3), y = c(1.66,2.62), label = c("A", "B"), size=6)+
   theme(axis.line.x = element_line(arrow = arrow()))+
   theme(axis.line.y = element_line(arrow = arrow()))
 
@@ -60,7 +61,8 @@ R_1=ggplot(da1, aes(x, y1))+
   theme(text = element_text(size=10, face="bold"))+
   theme(axis.title.y = element_blank()) +
   annotate("text", x = 42, y = 0.4, label = "Rep", size=3,color="#e41a1c")+
-  annotate("text", x = 42, y = 0, label = "R", size=4)
+  annotate("text", x = 42, y = 0, label = "R", size=4)+ 
+  theme(aspect.ratio=0.5)
 
 
 
@@ -80,13 +82,15 @@ v_1=ggplot(da2, aes(x2, y2))+
   xlab("Time")+
   theme(axis.text.x=element_blank(),
         axis.ticks.x=element_blank())+ 
-  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("V1","V3"))+
+  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("V1","V2"))+
[…]

### 2022-12-01 Manuscript/Figures/Suplementary_Fig2.R
suplementary fig2

@@ -1,0 +1,66 @@
+
+library(tidyverse)
+library(lme4)
+library(effects)
+library(patchwork)
+
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
+Pollinator_Plant<-Pollinator_Plant[,-1]
+Pollinator_Plant$Year= as.factor(Pollinator_Plant$Year)
+Pollinator_Plant$Site_ID= as.factor(Pollinator_Plant$Site_ID)
+Pollinator_Plant$Plant_gen_sp= as.factor(Pollinator_Plant$Plant_gen_sp)
+
+
+# species out
+#plant species that for each year occur only at one site
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp, Year) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp, Year)
+
+
+Pollinator_Plant= anti_join(Pollinator_Plant, spp_out)
+
+# #scale seed number variable
+Pollinator_Plant=Pollinator_Plant %>% 
+  group_by(Plant_gen_sp) %>%
+  mutate(seed_sc=scale(Seeds, center = T, scale = T))
+
+#model3
+mod3_to= lmer(seed_sc ~S_total * Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
+
+#getting effects for the two variables
+ee_mod3 <- as.data.frame(Effect(c("S_total","Year"),mod = mod3_to))
+
+p3=ggplot(ee_mod3, aes(S_total,fit))+
+  geom_line(size=0.8)+ 
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
+  geom_point(data= Pollinator_Plant, aes(x = S_total , y = seed_sc),shape=21, fill="grey")+
+  labs(x = "Pollinator richness",y="Seed number")+
+  ylim(-3,3)+
+  facet_wrap(~Year, nrow = 1) + 
+  theme_bw ()+
+  theme(legend.position = "none")
+
+#model4
+mod4_to= lmer(seed_sc ~ visitatio_rate*Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
+
+
+#getting effects for the two variables
[…]

### 2022-12-01 Manuscript/Manuscript.Rmd
editing introduction

@@
 
+bibliography: library.bib
+csl: journalofecol.csl
+
 ---
@@
 1.
+Community stability can be influenced by species richness and asynchrony of species, however the relation with the stability of ecosystem functioning provided by this community is less explored, and specially for functions involving several trophic levels such as plant pollination.
 Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions is important for predicting the resilience of communities to changes in biodiversity.
-While community stability can be influenced by species richness and asynchrony of species,  the relation with the stability of ecosystem functioning provided by this community is less explored, and specially for functions involving several trophic levels such as plant pollination.
-[For J ecol, I will focus on stability of plant reproductive success, and then link that to the theory of community stability, so just the same sentences you usem, but order upside down]()
 
 2.
-Using a 5-year dataset across 13 Mediterranean woodland patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and plants reproductive success.
+Using a 5-year dataset across 13 Mediterranean shrub patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and plants reproductive success.
 [In addition, we analyzed whether the year together with richness and visitation rate affected the proportion of fruits and the number of seeds.](esto pensamos como ponerlo con los results finales)
@@
 
-The role of biodiversity in ecosystem function has long been of great interest to researchers (Hooper et al 2005, Gagic et al., 2015, Lefcheck et al 2015, Oliver et al., 2015, Hong et al 2021).
-We have experimental and observational evidence that biodiversity enhances ecosystem functioning (Cardinale et al., 2006, Cardinale et al., 2012, Tilman et al., 2014), but the role of biodiversity for the stability of ecosystem functioning is less explored (but see Griffin et al., 2009, Grman et al., 2010), specially for functions involving several trophic levels such as plant pollination (Ebeling et al., 2008, Winfree and Kremen 2009, Garibaldi et al 2011, [Lázaro et al 2022](wild Olea europaea communities)).
-Globally, it is estimated that at least 78% of wild plants and 75% of leading crops depend to some extent on pollination by animals (Ollerton et al., 2011; Kleijn et al., 2015).
+Global environmental changes and the biodiversity loss have highlighted the interest for better understanding the role of biodiversity in ecosystem function [@Hooper2005; @Lefcheck2015; @Oliver2015; @Hong2022].
+We have experimental and observational evidence that biodiversity enhances ecosystem functioning [@Cardinale2006; @Cardinale2012; @Tilman2014], but the role of biodiversity for the stability of ecosystem functioning is less explored (but see @Griffin2009; @Grman2010), specially for functions involving several trophic levels such as plant pollination [@Ebeling2008; @Winfree2009a; @Garibaldi2011; @Lazaro2022].
+Globally, it is estimated that at least 78% of wild plants and 75% of leading crops depend to some extent on pollination by animals [@Ollerton2011; @Kleijn2015].
 Understanding the mechanisms driving pollinator community stability and how this relates to the stability of ecosystem functions and services delivered (i.e.
@@
 
-Stability can be defined [as the inverse of the coefficient of variation of ecosystem properties over time](irrelevant now) (McCann, 2000; Tilman, 1999).
+Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
 Among main driving of stability are the diversity and species asynchrony.
-A higher number of species might provide a wider range of responses to environmental changes, which would result in a higher stability (McCann, 2000, Tilman et al.
-2006, Hector et al.
-2010, Xu et al.
-2021), although non-significant relationships between diversity and stability have also been observed (Hooper et al.
-2005, van der Plas 2019).
+A higher number of species might provide a wider range of responses to environmental changes, which would result in a higher stability [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
 The stability is also influenced by the degree of asynchrony between species.
-In this sense, higher levels of asynchrony in species fluctuation stabilize the community (Loreau et al.
-2002, Ruijven and Berendse 2007, Blüthgen et al.
-2016, Craven et al.
-2018).
-It has been also shown that stability can associate more strongly with the degree of synchrony among dominant species than with species richness (Blüthgen et al 2016, Valencia et al 2020).
-[While community temporal stability should be related to the stability of ecosystem functions and services, there is limited evidence linking both processes on multitrophic systems.](I like this sentence)
+In this sense, higher levels of asynchrony in species fluctuation stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018].
+It has been also shown that stability can associate more strongly with the degree of synchrony among dominant species than with species richness [@Bluthgen2016; @Valencia2020].
+While community temporal stability should be related to the stability of ecosystem functions and services, there is limited evidence linking both processes on multitrophic systems.
 
-Since the reproductive success of most plant species highly depends on pollination by animals (Ollerton et al 2012), the stability of pollinator communities may increase the stability of plant reproductive success.
-A greater diversity of pollinators has been shown to increase the plant reproductive success as a result of complementary service provision arising from variation across of pollinator effectiveness, including space and time (Hoehn et al.
+Since the reproductive success of most plant species highly depends on pollination by animal [@Ollerton2012], the stability of pollinator communities may increase the stability of plant reproductive success.
+A greater diversity of pollinators has been shown to increase the plant reproductive success as a result of complementary service provision arising from variation across of pollinator effectiveness, including space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013] (Hoehn et al.
 2008; Fründ et al.
@@
 2013).
-Pollinator species may exhibit different ranges of temporal activity (Pisanty et al.
+Pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] (Pisanty et al.
 2016, Rader et al.
 2016) and consequently may provide pollination services at different times of the season.
-Other studies suggesting that a few dominant species are sufficient to provide a higher reproductive success of plants, i.e pollinator communities are dominated by a small number of common species, and that abundance fluctuations of these dominant species are often responsible for a majority of pollination service provision across an ecosystem (Kleijn et al 2015, Winfree et al 2015).[not sure this last sentence is supported by the refs, plus, is in crops only]()
+on the other hand, few studies link the visitation rate directly with plant reproductive but they generally find positive association.
+Sites with more visitation show higher pollen deposition and fruit set (Garibaldi et al., 2014; Kaiser‐Bunbury et al., 2017).
 
@@
 
-In the current study, we use a 5-year dataset in Mediterranean woodland patches to study the role of richness and synchrony of pollinator species as drivers of stability of visitation rate.
+Although most plant species rely on animals for pollination, it has calculated that between 60% and 73% of populations suffer significant pollen limitation (Ashman et al.
+2004; Burd 1994; Knight et al.
+2005)
+plants visited by many pollinators species are less pollen limited than those visited by one or few species (Knight et al.
+2005), however other research found no relationship between pollinator diversity and pollen limitation (Hegland and Totland 2008; Davila et al 2012)
+
+the occurrence and magnitude of pollen limitation varies among years for individual populations (Burd 1994, Ashman et al.
+2004), primarily because of variation in pollinator service (Aizen and Harder 2007).
+
+In the current study, we use a 5-year dataset in Mediterranean woodland patches to study the role of richness and asynchrony of pollinator species as drivers of stability of visitation rate.
 We also evaluate whether the stability of plant reproductive success, employed the stability of fruit proportion and stability of seed numbers, is affected by the stability of pollinator communities.
@@
 Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean  ± standard error: 5.92  ± 0.54 plant species per site).
-All the floral visitors (from now on referred to as pollinators) that contacted with their flowers were registered by performing focal observations to the selected individuals during five minutes in 2015 -2016 and three minutes from 2017 to 2019.
+All the floral visitors (from now on referred to as pollinators) that contacted with their flowers were registered by performing focal observations to the selected individuals during five minutes in 2015-2016 and three minutes from 2017 to 2019.
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
@@
 All plants analyzed are at least partially pollinator dependent.
-Due to the focal time observation was different over years, for each plant individual, the effort of sampling was standardized in frequency per minute dividing the total frequency by total observation time (time observation multiplied by number of round observation).
-For each site and year, we calculated the visitation rate of pollinators as the number of visits divided by the number of flowers, pollinator richness, the fruit set as the proportion of fruit, and the seed set as number of seed for each plant individual sampled per site.
+Due to the focal time observation was different over years, for each plant individual, the effort of sampling was standardized in number of visits per minute dividing the total visits observed by total observation time (time observation multiplied by number of survey per year).
+For each site and year, we calculated the visitation rate of pollinators as the number of visits divided by the number of flowers, pollinator richness, the fruit set as the proportion of fruit, and the seed set as number of seed per fruit for each plant individual sampled per site.
 
@@
 For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites and a minimum of two years per site.
-The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following (Tilman, 1999).
+The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
 To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
@@
 Stability of visitation rate ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-Our results supported the positive tendency between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A),
+Our results showed a positive tendency between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A),
 whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 1B).
-We also observed a positively strong relationship between asynchrony and pollinator richness (0.031 ± 0.007) (Fig 1C).
+We also found a positively strong relationship between asynchrony and pollinator richness (0.020 ± 0.005) (Fig 1C).
+We observed one data with high leverage of visitation rate stability (*C.crispus*) however when we removed this point the tendencies are the same.
 
-When we analysed the plant species separately, we found [no significant](are we reporting p-values?) differences but we observed positive tendency in asynchrony for *H.
-halimifolium* and *L.
-pedunculata* [and other species has also positive estmate, right?]().
+When we analysed the plant species separately, we observed positive tendency in asynchrony for *C.
+crispus*, *H.
+halimifoliun* and *L.
+pedunculata* and milder tendency in *C.
+salviifolious* being the slightly negative tendency in *C.ladanifer*.
 In the case of richness, *C.
@@
 ladanifer* and *C.
-salviifolius* was a negative tendecy wile *H.
+salviifolius* showed a negative tendency wile *H.
 halimifolium* and *L.
-pedunculata* was positive (Supplementary material-Fig 2).
+pedunculata* was positive (Supplementary material-Fig 1).
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 8,fig.width=20, out.width="100%",fig.align='center', fig.cap =" 1.Relationships between stability of visitation rate (calculated as the inverse of the coefficient of variation) and asynchorny of pollinators (Loreau and de Mazancourt’s index) (A), stability of visitation rate and pollinator richness (B), and asynchorny of pollinators and richness (C).Dots represent the different plant species incluided in the analysis.Significant models are representing with solid line For the visualization purpose, asynchrony values are represented from 0 to 1."}
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 8,fig.width=20, out.width="100%",fig.align='center', fig.cap =" 1.Relationships between stability of visitation rate (calculated as the inverse of the coefficient of variation) and asynchorny of pollinators (Loreau and de Mazancourt’s index) (A), stability of visitation rate and pollinator richness (B), and asynchorny of pollinators and richness (C).Dots represent the different plant species incluided in the analysis.Significant models are representing with solid line."}
 
@@
 p1=ggplot(effe_mod_sta, aes(asyn_LM, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.2, colour = "black", size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper),alpha=0.2)+
   scale_y_continuous(limits = c(-2.5, 9.5))+labs(color='Plant species')+
-  geom_point(data = data_plant, aes(x =  asyn_LM, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=7)+
+  geom_point(data = data_plant, aes(x =  asyn_LM, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=6)+
   scale_colour_brewer(palette = "Set1")+
@@
 p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1,linetype = "dashed")+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.1, colour = "black", size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.1)+
   scale_y_continuous(limits = c(-2.5, 9.5))+  labs(color='Plant species')+
-  geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=7)+
+  geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=6)+
   scale_colour_brewer(palette = "Set1")+
@@
 # relationship between richness and asynchrony
-mod_rich_asyn= lmer (asyn_LM ~ S_total +  (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+mod_rich_asyn= lmer (asyn_LM ~ S_total +  (1|Site_ID) + (1|Plant_gen_sp), weights = asyn_LM, data = data_plant)
 
@@
 p1.2=ggplot(effe_rich_mod_sta, aes(S_total, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black", size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.2)+
   labs(color='Plant species')+
-  coord_cartesian(ylim=c(0,1))+
-  geom_point(data = data_plant, aes(x =  S_total, y = asyn_LM, color=Plant_gen_sp), alpha=0.7,size=7)+
+  geom_point(data = data_plant, aes(x =  S_total, y = asyn_LM, color=Plant_gen_sp), alpha=0.7,size=6)+
   scale_colour_brewer(palette = "Set1")+
@@
 Relationship between stability of plant reproductive succes: fruit propotion (A) and seed number (B) and the stability of visitation rate.
-Dots represent the different plant species incluided in the analysis."}
+Dots represent the different plant species incluided in the analysis.Significant models are representing with solid line."}
 
@@
 #plot model 
-p_mod2=ggplot(effe3_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper),linetype = 3, alpha=0.2, colour = "black",size=1)+
+p_mod2=ggplot(effe3_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1,linetype = "dashed")+
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.1)+
   geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_fruit, color=Plant_gen_sp),alpha=0.7, size=7)+
@@
 p_mod3=ggplot(effe4_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black", size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.2)+
   labs(color='Plant species')+
@@
 
-When we analysed whether the effect of pollinator richness and visitation rate is different across the years, we found that both variables showed a significant interaction effect with the year on fruit proportion.
-Although we observed a saturation of the fruit proportion, in year like 2017 is showed that a greater richness and visitation rate increased the fruit proportion (Richness - Estimate: 0.395; std.
-error: 0.15; Visitation rate - Estimate: 25.238; std.
-error: 5.67).
-However in 2018, the relationship between richness and fruit proportion was negative [(Estimate: -0.147; std.
-error: 0.05)](Los estimate y std error en este caso son en funcion de 2015 ya que el modelo lo pone como intercept.
-El Anova(car) nos da Pr(>Chisq) y df, ¿incluyo esta información??) (Fig 3).[Hay que pensar como lo contamos]()
+When we analysed whether the effect of pollinator richness and visitation rate is different across the years, we found that both variables showed a significant interaction effect with the year on fruit proportion [(richness:year p = <0.0001; visitation rate:year p = <0.0001)](tengo que poner Anova tipo III???
+y algun dato mas como df??).
+Although we observed a saturation of the fruit proportion, in year like 2017 is showed that a greater richness and visitation rate increased the fruit proportion.
+We also observed a positive tendency between richness and fruit proportion in 2019.
+However in 2018, the relationship between richness and fruit proportion was negative (Fig 3).
+
+For the seed number, we not found the interaction effect to pollinator richness (p = 0.628), however we found a marginal significant interaction between visitation rate and year (p = 0.058).
+We observed that a higher the visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).
 
@@
 p1/p2&theme(text = element_text(size=35))
-
-```
-
-For the seed number, we not found the interaction effect to pollinator richness, however we found a marginal significant interaction between visitation rate and year.
-We observed that a higher the visitation rate increased the seed number in 2019 [(Fig 4)](quizas puede ir a material suplementario).
-
-```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 4.
-Interaction effect between richness and year (top row), and visitation rate and year (bottom row) on seed number.
-For the visualization purpose, we omit in the visitation rate (x-axis) the values outside of the 95\\%."}
-
-# #scale seed number variable
-Pollinator_Plant=Pollinator_Plant %>% 
-  group_by(Plant_gen_sp) %>%
-  mutate(seed_sc=scale(Seeds, center = T, scale = T))
-
-#model3
-mod3_to= lmer(seed_sc ~S_total * Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
-
-#getting effects for the two variables
-ee_mod3 <- as.data.frame(Effect(c("S_total","Year"),mod = mod3_to))
-
-p3=ggplot(ee_mod3, aes(S_total,fit))+
-  geom_line(size=0.8)+ 
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
-  geom_point(data= Pollinator_Plant, aes(x = S_total , y = seed_sc),shape=21, fill="grey", size=6)+
-  labs(x = "Pollinator richness",y="Seed number")+
-  ylim(-3,3)+
-  facet_wrap(~Year, nrow = 1) + 
-  theme_bw ()+
-  theme(legend.position = "none")
-
-#model4
-mod4_to= lmer(seed_sc ~ visitatio_rate*Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
-
-#getting effects for the two variables
-ee_mod4 <- as.data.frame(Effect(c("visitatio_rate","Year"),mod = mod4_to))
-
-#plot
-
-p4 = ggplot(ee_mod4, aes(visitatio_rate,fit))+
-  geom_line(size=0.8)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
-  geom_point(data= Pollinator_Plant, aes(x =visitatio_rate , y = seed_sc),shape=21, fill="grey",size=6)+
-  labs(x = "Visitation rate",y="Seed number")+
-  facet_wrap(~Year, nrow = 1) + 
-  coord_cartesian(xlim=c(0, quantile(Pollinator_Plant$visitatio_rate,0.95)),ylim = c(-3,3))+
-  theme_bw ()+
-  theme(legend.position="none")
-
-p3/p4 &theme(text = element_text(size=35))
 
@@
 ```
+
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 2.
+Interaction effect between richness and year (top row), and visitation rate and year (bottom row) on seed number.
+For the visualization purpose, we omit in the visitation rate (x-axis) the values outside of the 95\\%."}
+
+# #scale seed number variable
+Pollinator_Plant=Pollinator_Plant %>% 
+  group_by(Plant_gen_sp) %>%
+  mutate(seed_sc=scale(Seeds, center = T, scale = T))
+
+#model3
+mod3_to= lmer(seed_sc ~S_total * Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
+
+#getting effects for the two variables
+ee_mod3 <- as.data.frame(Effect(c("S_total","Year"),mod = mod3_to))
+
+p3=ggplot(ee_mod3, aes(S_total,fit))+
+  geom_line(size=0.8)+ 
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
+  geom_point(data= Pollinator_Plant, aes(x = S_total , y = seed_sc),shape=21, fill="grey", size=6)+
+  labs(x = "Pollinator richness",y="Seed number")+
+  ylim(-3,3)+
+  facet_wrap(~Year, nrow = 1) + 
+  theme_bw ()+
+  theme(legend.position = "none")
+
+#model4
+mod4_to= lmer(seed_sc ~ visitatio_rate*Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
+
+#getting effects for the two variables
+ee_mod4 <- as.data.frame(Effect(c("visitatio_rate","Year"),mod = mod4_to))
+
+#plot
+
+p4 = ggplot(ee_mod4, aes(visitatio_rate,fit))+
+  geom_line(size=0.8)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
+  geom_point(data= Pollinator_Plant, aes(x =visitatio_rate , y = seed_sc),shape=21, fill="grey",size=6)+
+  labs(x = "Visitation rate",y="Seed number")+
+  facet_wrap(~Year, nrow = 1) + 
+  coord_cartesian(xlim=c(0, quantile(Pollinator_Plant$visitatio_rate,0.95)),ylim = c(-3,3))+
+  theme_bw ()+
+  theme(legend.position="none")
+
+p3/p4 &theme(text = element_text(size=35))
+
+```
+
+# References

### 2022-12-12 Manuscript/Manuscript.Rmd
working introduction

@@
 3.
-The stability of plant's visitation rate is more affected by the asynchrony of pollinator species abundances than by pollinator richness.
-shows a negative tendency.
-As for the stability of the plant reproductive success, we found no relationship between the stability of fruits and the stability of the visitation rate, however a negative relation was observed between stability of seed and the stability of visitation rate.
+The stability of plant's visitation rate is affected by the asynchrony of pollinator species abundances but not by the pollinator richness.
+However, we found a strong positive relationship between richness and asynchrony of pollinators.
+As for the stability of the plant reproductive success, the stability of fruits is not influenced by the stability of the visitation rate but a negative relation was observed between stability of seed and the stability of visitation rate.
 However, when years are analysed we found that in some years/[bad years](), the effect of pollinator richness and visitation rate on fruit proportion becomes important.
@@
 
-Since the reproductive success of most plant species highly depends on pollination by animal [@Ollerton2012], the stability of pollinator communities may increase the stability of plant reproductive success.
-A greater diversity of pollinators has been shown to increase the plant reproductive success as a result of complementary service provision arising from variation across of pollinator effectiveness, including space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013] (Hoehn et al.
-2008; Fründ et al.
-2010, Albrecht et al.
-2012, Blüthgen and Klein, 2013, Fründ et al.
-2013).
-Pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] (Pisanty et al.
-2016, Rader et al.
-2016) and consequently may provide pollination services at different times of the season.
-on the other hand, few studies link the visitation rate directly with plant reproductive but they generally find positive association.
-Sites with more visitation show higher pollen deposition and fruit set (Garibaldi et al., 2014; Kaiser‐Bunbury et al., 2017).
+Since the reproductive success of most plant species highly depends on pollination by animal [@Ollerton2011], the stability of pollinator communities may increase the stability of plant reproductive success.
+A greater diversity of pollinators has been shown to increase the plant reproductive success as a result of complementary service provision arising from variation across of pollinator effectiveness, including space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013].
+Pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] and consequently may provide pollination services at different times of the season.
+On the other hand, few studies link the visitation rate directly with plant reproductive.
+In some case, sites with more visitation show higher plant reproductive and in another they do not find relationship (Hegland and Totland 2012, Lundgren et al 2013; Kaiser‐Bunbury et al., 2017).
+Likewise, in more visited sites, it has been observed lower pollen limitation of fruit set and seed production [(Cosacov et al., 2008; Gómez et al., 2010; Williams & Winfree, 2013)]().
+The occurrence and magnitude of pollen limitation can varies among years for individual populations (Burd 1994, Ashman et al.
+2004), primarily because of variation in pollinator service (Aizen and Harder 2007).
 
@@
 
-Although most plant species rely on animals for pollination, it has calculated that between 60% and 73% of populations suffer significant pollen limitation (Ashman et al.
+[?](Although most plant species rely on animals for pollination, it has calculated that between 60% and 73% of populations suffer significant pollen limitation (Ashman et al.
 2004; Burd 1994; Knight et al.
-2005)
-plants visited by many pollinators species are less pollen limited than those visited by one or few species (Knight et al.
-2005), however other research found no relationship between pollinator diversity and pollen limitation (Hegland and Totland 2008; Davila et al 2012)
-
-the occurrence and magnitude of pollen limitation varies among years for individual populations (Burd 1994, Ashman et al.
-2004), primarily because of variation in pollinator service (Aizen and Harder 2007).
+2005).plants visited by many pollinators species are less pollen limited than those visited by one or few species (Knight et al.
+2005), however other research found no relationship between pollinator diversity and pollen limitation (Hegland and Totland 2008; Davila et al 2012))
 

### 2022-12-13 script/stability.R
new calculate Gross synchrony

@@ -17,6 +17,7 @@ library(ggpubr)
 #install.packages("qqplotr")
 library(qqplotr)
 
+
 Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") 
 str(Pollinator_Plant)
 Pollinator_Plant<-Pollinator_Plant[,-1]
@@ -27,22 +28,11 @@ spp_out <- Pollinator_Plant %>%
   group_by(Plant_gen_sp) %>%
   summarise(Unique_Id = n_distinct(Site_ID)) %>%
   filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+  dplyr::select(Plant_gen_sp) %>% pull(Plant_gen_sp)
 
 
 #Data with species in more than 1 site
 Pollinator_Plant = Pollinator_Plant %>% filter(!Plant_gen_sp %in% spp_out)
-
-
-# # plant species with only one year
-# remo=Pollinator_Plant %>%
-#   group_by(Plant_gen_sp,Site_ID) %>%
-#   summarise(Unique_Id = n_distinct(Year)) %>%
-#   filter(Unique_Id == 1) %>%
-#   select(Plant_gen_sp, Site_ID) 
-# 
-# # Data with species in more one year
-# Pollinator_Plant= anti_join(Pollinator_Plant, remo)
 
 
 
@@ -203,6 +193,7 @@ abund_pol_stand=abund_pol %>%
 
 
 
+
 # Richness 
 data_long <- gather(abund_pol, pollinator, frequ, Andrena_agilissima : Xylocopa_violacea , factor_key=T)
 data_long
@@ -225,9 +216,12 @@ log_VR <- function(x){
 
 # un dato por sp planta, sitio y año (sin plant_id)
 # corrected synchrony for sampling effort
+abund_pol_stand=abund_pol_stand  %>% 
+  select(!c(total_time))
+
 syn_1=abund_pol_stand%>% 
   group_by(Plant_gen_sp,Site_ID)%>% 
-  do(log_VR=log_VR(.[5:128]))
+  do(log_VR=log_VR(.[4:127]))
 
 
 
@@ -245,7 +239,7 @@ syncLM <- function(x){
 # corrected synchrony for sampling effort
 syn_LM1=abund_pol_stand%>% 
   group_by(Plant_gen_sp,Site_ID)%>% 
[…]

### 2022-12-13 script/stability_analysisr.R
correlation of synchrony by plant

@@ -28,7 +28,7 @@ sp_out2=data_plant %>%
   group_by(Plant_gen_sp) %>%
   summarise(Unique_Id = n_distinct(Site_ID)) %>%
   filter(Unique_Id <= 4) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+  dplyr::select(Plant_gen_sp) %>% pull(Plant_gen_sp)
 
 #Data with species in at least 5 sites
 data_plant = data_plant %>% filter(!Plant_gen_sp %in% sp_out2)
@@ -48,34 +48,16 @@ data_plant[is.na(data_plant) | data_plant == "-Inf"] <- NA
 
 
 
-# We can express asynchrony as 1 - φ, 
-#where φ is Loreau and de Mazancourt’s (2008)
-data_plant$asyn_LM= 1-data_plant$syncLM
-
-
-# correlacion asynchrony and richness
-
-syn_cor<-data_plant %>% select(asyn_LM,S_total)
-
-## Replace Inf and -Inf with NA
-syn_cor[is.na(syn_cor) | syn_cor == "Inf"] <- 0 
-syn_cor[is.na(syn_cor) | syn_cor == "-Inf"] <- 0 
-
+# correlacion indices de sincronia
+syn_cor<-data_plant %>% select(log_VR,syncLM,av_sync)
 syn_cor <- mutate_all(syn_cor, ~replace(., is.na(.), 0))
-
 cor(syn_cor)
 
-# correlacion synchrony index and richness to different plant species
-correl_syn_richn<-data_plant %>% select(Plant_gen_sp,cv_1_fruit, cv_1_seed,cv_1_visitation,S_total,log_VR,syncLM,av_sync)
+# correlacion por plant species
+syn_cor_pla<-data_plant %>% select(Plant_gen_sp,log_VR,syncLM,av_sync)
+syn_cor_pla <- mutate_all(syn_cor_pla, ~replace(., is.na(.), 0))
 
-## Replace Inf and -Inf with NA
-correl_syn_richn[is.na(correl_syn_richn) | correl_syn_richn == "Inf"] <- NA 
-correl_syn_richn[is.na(correl_syn_richn) | correl_syn_richn == "-Inf"] <- NA 
-
-correl_syn_richn <- mutate_all(correl_syn_richn, ~replace(., is.na(.), 0))
-
-# tabla correlacion 
-b_cor <- correl_syn_richn %>%
[…]

### 2022-12-15 Manuscript/Manuscript.Rmd
editing method

@@
   pdf_document :
+    latex_engine : xelatex
 header-includes:
@@
 The stability of plant's visitation rate is affected by the asynchrony of pollinator species abundances but not by the pollinator richness.
-However, we found a strong positive relationship between richness and asynchrony of pollinators.
+Likewise, we found a strong positive relationship between richness and asynchrony of pollinators.
 As for the stability of the plant reproductive success, the stability of fruits is not influenced by the stability of the visitation rate but a negative relation was observed between stability of seed and the stability of visitation rate.
@@
 In this sense, higher levels of asynchrony in species fluctuation stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018].
-It has been also shown that stability can associate more strongly with the degree of synchrony among dominant species than with species richness [@Bluthgen2016; @Valencia2020].
+It has been also shown that stability can associate more strongly with the degree of asynchrony across species than with species richness [@Bluthgen2016; @Valencia2020].
 While community temporal stability should be related to the stability of ecosystem functions and services, there is limited evidence linking both processes on multitrophic systems.
@@
 
-[?](Although most plant species rely on animals for pollination, it has calculated that between 60% and 73% of populations suffer significant pollen limitation (Ashman et al.
-2004; Burd 1994; Knight et al.
-2005).plants visited by many pollinators species are less pollen limited than those visited by one or few species (Knight et al.
-2005), however other research found no relationship between pollinator diversity and pollen limitation (Hegland and Totland 2008; Davila et al 2012))
-
 In the current study, we use a 5-year dataset in Mediterranean woodland patches to study the role of richness and asynchrony of pollinator species as drivers of stability of visitation rate.
@@
 In addition, we analyzed whether the effect of the pollinator richness and visitation rate on the reproductive success of the plants varies over time.
-
-[Hipotesis]()
+We expect that the stability of visitation rate will increase with higher richness and asynchrony of pollinators.
+In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rate.
 
@@
 To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
-To calculate synchrony, we used the Loreau and de Mazancourt index (2008), the weighted form of the synchrony index (Gross et al., 2014; Blüthgen et al., 2016), and the log of variance ratio (log VR) (Schluter, 1984; Hallett et al., 2014; Lepš et al., 2018).
-All of them were positively correlated to each other within each plant species [sup mat?](), therefore, data for synchrony assessed by Loreau and de Mazancourt index are presented and included in our further analyses.
+[The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:](al final he puesto que utilizamos este solo porque al corregir el esfuerzo de muestreo este y el de Gross ya no estan correlacionados.
+He analizado el de Gross y no hay relacion con la estabilidad de las visitas.
+Muchos trabajos que solo utilizan un indice no dicen que hayan probado otros como es el trabajo de Lazaro, y he visto que muchos ponen la ecuacion, si no te parece bien asi vuelvo a poner los tres y explico lo de la correlacion)
+
+$$
+\begingroup\Large
+\phi =\frac{\sigma_{x_T}^2}{(\sum\sigma_{x_T})^2}
+\endgroup
+$$
+where ${\sigma_{x_T}^2}$ represents the temporal variance of the community times series and ${(\sum\sigma_{x_T})^2}$ represents the sum of the temporal standard deviation of the time series across all species.
 This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous.
-Finally, we express asynchrony as 1-Loreau and de Mazancourt’s index of synchrony.
+Finally, we express asynchrony as $1-\phi$.
 We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.

### 2022-12-16 Manuscript/Manuscript.Rmd
writing

@@
 When we analyzed whether the stability of the visitation rate affected the stability of the plant reproductive success, we did not find a relationship between this and the stability of the fruit proportion (Estimate: -1.547; std.
-error: 2.611) (Fig 2A), however, the stability of seed number showed negative tendency with the stability of visitation rate (Estimate: -1.887; std.
+error: 2.611) (Fig 2A).
+However, the stability of seed number showed negative tendency with the stability of visitation rate (Estimate: -1.887; std.
 error: 0.959) (Fig 2B).
@@
 ```
+
+# Discussion
+
+The results obtained indicate that the stability of visitation rate will increase with higher asynchrony of pollinators and that greater species richness might increase stability of visitation rate indirectly, via enhanced species asynchrony.
+Contrary to expectations, we found no relationship between the stability of visitor rate and the stability of plant reproductive success.
+However, we observed that the effect of visitation rate and richness on the fruit propotions is different depending on the year.
 

### 2023-01-10 Manuscript/Manuscript.Rmd
writing discussion

@@
 In some case, sites with more visitation show higher plant reproductive and in another they do not find relationship (Hegland and Totland 2012, Lundgren et al 2013; Kaiser‐Bunbury et al., 2017).
-Likewise, in more visited sites, it has been observed lower pollen limitation of fruit set and seed production [(Cosacov et al., 2008; Gómez et al., 2010; Williams & Winfree, 2013)]().
+Likewise, in more visited sites, it has been observed lower pollen limitation of fruit set and seed production (Cosacov et al., 2008; Gómez et al., 2010; Williams & Winfree, 2013).
 The occurrence and magnitude of pollen limitation can varies among years for individual populations (Burd 1994, Ashman et al.
@@
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
-For each plant individual, we counted the total number of flowers and at the end of the season, we recorded the number of fruit and the seeds per fruit.
+For each plant individual, we counted the total number of flowers  in each surveyed and at the end of the season, we recorded the number of fruit and the seeds per fruit.
 All plants analyzed are at least partially pollinator dependent.
@@
 \begingroup\Large
-\phi =\frac{\sigma_{x_T}^2}{(\sum\sigma_{x_T})^2}
+\phi =\frac{\sigma_{x_T}^2}{(\sum_{i=1}^S\sigma_{x_i})^2}
 \endgroup
 $$
-where ${\sigma_{x_T}^2}$ represents the temporal variance of the community times series and ${(\sum\sigma_{x_T})^2}$ represents the sum of the temporal standard deviation of the time series across all species.
-This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous.
+where ${\sigma_{x_T}^2}$ is the variance of the community abundance of each plot and ${\sigma_{x_i}}$ is the standard deviation of species i abundance in a community with S species.
+This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous [@Loreau2008].
 Finally, we express asynchrony as $1-\phi$.
@@
 Stability of visitation rate ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-Our results showed a positive tendency between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A),
-whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 1B).
+Our results showed a positive tendency between stability of visitation rate and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 1B).
 We also found a positively strong relationship between asynchrony and pollinator richness (0.020 ± 0.005) (Fig 1C).
@@
 
-When we analysed the plant species separately, we observed positive tendency in asynchrony for *C.
+When we analysed the plant species separately, we observed positive tendency in asynchrony of pollinators for *C.
 crispus*, *H.
@@
 salviifolious* being the slightly negative tendency in *C.ladanifer*.
-In the case of richness, *C.
+In the case of pollinator richness, *C.
 crispus*, *C.
@@
 For the seed number, we not found the interaction effect to pollinator richness (p = 0.628), however we found a marginal significant interaction between visitation rate and year (p = 0.058).
-We observed that a higher the visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).
+We observed that a higher visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).
 
@@
 
-The results obtained indicate that the stability of visitation rate will increase with higher asynchrony of pollinators and that greater species richness might increase stability of visitation rate indirectly, via enhanced species asynchrony.
+The results obtained indicate that the stability of visitation rate will increase with higher asynchrony of pollinators species abundances and that greater species richness might increase stability of visitation rate indirectly, via enhanced species asynchrony.
 Contrary to expectations, we found no relationship between the stability of visitor rate and the stability of plant reproductive success.
-However, we observed that the effect of visitation rate and richness on the fruit propotions is different depending on the year.
+However, we observed that the effect of visitation rate and richness on the fruit proportions is different depending on the year.
+
+While drivers of temporal stability have been well study in plant community [@Ruijven2007; @Gross2014; @Craven2018; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021], relative few studies have evaluated how the drivers can affect the stability in pollinator communities [@Ebeling2008; @Senapathi2021; @Lazaro2022].
+An outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
+This stability–asynchrony relationship has been found by different theoretical and empirical studies(de Mazancourt et al., 2013; Blüthgen et al., 2016; Lepš et al., 2018; Sasaki et al., 2019; Valencia et al, 2020, Kigel et al 2021).
+Lázaro et al.(2022) also found the synchrony like an important driver of stability for for plants, pollinators and their interactions.
+[The fact that species asynchrony increases the temporal stability of the visitation rate may be because a decrease in the abundance of one pollinator species is compensated by an increase of the abundance of another.](escribir mejor la frase)
+On the other hand, species richness is considered one of the strongest drivers of community stability (Tilman et al., 2006; de Mazancourt et al., 2013; Hallett et al., 2014), although Valencia et al.(2020) have reported that this relation is not nearly as strong.
+In the pollinator studies have been observed a positive relationship between richness and stability (Ebeling et al 2008; Senapathi et al 2021), however, our results show that the richness was positively associated with asynchrony, which might positively affect the stability of visitation rate.[This most likely reflects niche variation among species that affect their relative performance over time in a temporally variable environment (Yachi & Loreau,1999; Gross et al., 2014; Craven et al 2018).](??)
+
+Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services (Garibaldi et al.
+2011, Lázaro and Alomar 2019, Hünicken et al 2021, Bishop et al 2022).The majority of these studies were focused on crops, however, to our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
+In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate (Garibaldi et al.
+2011, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship or even observed a negative relationship between seed number stability and visitation rate stability.
 

### 2023-01-13 Manuscript/Manuscript.Rmd
Nacho's edits on ms. Looks great!

--- 2022-12-15 Manuscript/Manuscript.Rmd
@@
 csl: journalofecol.csl
-
+editor_options: 
+  markdown: 
+    wrap: sentence
 ---
@@
 
-1.
-Community stability can be influenced by species richness and asynchrony of species, however the relation with the stability of ecosystem functioning provided by this community is less explored, and specially for functions involving several trophic levels such as plant pollination.
-Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions is important for predicting the resilience of communities to changes in biodiversity.
+1.  The stability of ecological communities over time, often measured as its aggregated abundance or biomass, is mainly influenced by species richness and the asynchrony of the species fluctuations.
+    However, the relation with the stability of ecosystem functioning provided by this community is less explored, specially for functions involving several trophic levels such as plant pollination.
+    Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions provided is important for predicting the resilience of communities to changes in biodiversity.
 
@@
 Using a 5-year dataset across 13 Mediterranean shrub patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and plants reproductive success.
-[In addition, we analyzed whether the year together with richness and visitation rate affected the proportion of fruits and the number of seeds.](esto pensamos como ponerlo con los results finales)
+    In addition, we analyzed whether the effects of species richness and visitation rate on plant reproduction success were consistent among years.
 
-3.
-The stability of plant's visitation rate is affected by the asynchrony of pollinator species abundances but not by the pollinator richness.
-Likewise, we found a strong positive relationship between richness and asynchrony of pollinators.
-As for the stability of the plant reproductive success, the stability of fruits is not influenced by the stability of the visitation rate but a negative relation was observed between stability of seed and the stability of visitation rate.
-However, when years are analysed we found that in some years/[bad years](), the effect of pollinator richness and visitation rate on fruit proportion becomes important.
+3.  The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances but not by the pollinator richness.
+    [Likewise, we found a strong positive relationship between richness and asynchrony of pollinators.](Yo%20esto%20no%20lo%20meteria%20aquí,%20por%20que%20no%20aporta%20mucho,%20no?%20Y%20es%20complejo%20de%20explicar.)
+    In contrast, the stability of the plant reproductive success is not related to the stability of the visitation rate.
+    A year by year analysis revels that plants are unlikely to be limited by pollinator abundances except in specific years with [extreme low levels of pollinator activity](esto%20es%20así?%20Molaria).
+
+4.  CONCLUSION
 
@@
 
-Global environmental changes and the biodiversity loss have highlighted the interest for better understanding the role of biodiversity in ecosystem function [@Hooper2005; @Lefcheck2015; @Oliver2015; @Hong2022].
-We have experimental and observational evidence that biodiversity enhances ecosystem functioning [@Cardinale2006; @Cardinale2012; @Tilman2014], but the role of biodiversity for the stability of ecosystem functioning is less explored (but see @Griffin2009; @Grman2010), specially for functions involving several trophic levels such as plant pollination [@Ebeling2008; @Winfree2009a; @Garibaldi2011; @Lazaro2022].
-Globally, it is estimated that at least 78% of wild plants and 75% of leading crops depend to some extent on pollination by animals [@Ollerton2011; @Kleijn2015].
+Global environmental changes and the consequent loss of biodiversity have highlighted the need for better understanding the role of biodiversity in ecosystem function [@Hooper2005; @Lefcheck2015; @Oliver2015; @Hong2022].
+We have experimental and observational evidence that biodiversity enhances aggregated community-level properties, such as total biomass [@Cardinale2006; @Cardinale2012; @Tilman2014], but the role of biodiversity for the stability of ecosystem functioning is less explored (but see @Griffin2009; @Grman2010), specially for functions involving several trophic levels such as plant pollination [@Ebeling2008; @Winfree2009a; @Garibaldi2011; @Lazaro2022].
+Globally, it is estimated that at least 78% of wild plants depend to some extent on pollination by animals [@Ollerton2011].
 Understanding the mechanisms driving pollinator community stability and how this relates to the stability of ecosystem functions and services delivered (i.e.
@@
 Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
-Among main driving of stability are the diversity and species asynchrony.
-A higher number of species might provide a wider range of responses to environmental changes, which would result in a higher stability [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
-The stability is also influenced by the degree of asynchrony between species.
-In this sense, higher levels of asynchrony in species fluctuation stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018].
-It has been also shown that stability can associate more strongly with the degree of asynchrony across species than with species richness [@Bluthgen2016; @Valencia2020].
-While community temporal stability should be related to the stability of ecosystem functions and services, there is limited evidence linking both processes on multitrophic systems.
+Among the main driving forces of community stability are the diversity of species present and the asynchrony on the species abundance fluctuations.
+A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e.
+the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
+However, a more direct stabilizing mechanisms the degree of asynchrony in species abundance fluctuations.
+In this sense, higher levels of asynchrony stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018].
+In fact, stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016; @Valencia2020].
+While community temporal stability should be related to the stability of ecosystem functions and services provided by such community, there is limited evidence linking both processes on multitrophic systems.
+[comment](aqui%20hecho%20a%20faltar%20la%20alternativa,%20solo%20la%20asyncronia%20entre%20las%20especies%20más%20abundantes%20es%20lo%20que%20cuenta)
 
-Since the reproductive success of most plant species highly depends on pollination by animal [@Ollerton2011], the stability of pollinator communities may increase the stability of plant reproductive success.
-A greater diversity of pollinators has been shown to increase the plant reproductive success as a result of complementary service provision arising from variation across of pollinator effectiveness, including space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013].
-Pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] and consequently may provide pollination services at different times of the season.
-On the other hand, few studies link the visitation rate directly with plant reproductive.
-In some case, sites with more visitation show higher plant reproductive and in another they do not find relationship (Hegland and Totland 2012, Lundgren et al 2013; Kaiser‐Bunbury et al., 2017).
-Likewise, in more visited sites, it has been observed lower pollen limitation of fruit set and seed production [(Cosacov et al., 2008; Gómez et al., 2010; Williams & Winfree, 2013)]().
-The occurrence and magnitude of pollen limitation can varies among years for individual populations (Burd 1994, Ashman et al.
+Since the reproductive success of most plant species highly depends on pollination by animals [@Ollerton2011], the stability of pollinator communities may increase the stability of plant reproductive success.
+A greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementary in service provision arising from variation of pollinator effectiveness across space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013].
+For example, pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] and consequently may provide pollination services at different times of the day or of the season.
+[However, there are not that many studies linking explicitly pollinator visitation rates directly with plant reproductive outputs](de%20esto%20estas%20segura?).
+While some studies report that sites with higher visitation rates show higher plant reproductive outputs (REFS), other studies do not find such relationship (Hegland and Totland 2012, Lundgren et al 2013; Kaiser‐Bunbury et al., 2017).
+Interestingly, studies looking at pollen limitation show that sites with higher visitation rates show no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant (Fig.
+1; Cosacov et al., 2008; Gómez et al., 2010; Williams & Winfree, 2013).
+However, the occurrence and magnitude of pollen limitation can vary among years for individual populations (Burd 1994, Ashman et al.
 2004), primarily because of variation in pollinator service (Aizen and Harder 2007).
 
-[gap](I think something about temporal variation and pollen limitation)
+[gap](I%20think%20something%20about%20temporal%20variation%20and%20pollen%20limitation)
 
-In the current study, we use a 5-year dataset in Mediterranean woodland patches to study the role of richness and asynchrony of pollinator species as drivers of stability of visitation rate.
-We also evaluate whether the stability of plant reproductive success, employed the stability of fruit proportion and stability of seed numbers, is affected by the stability of pollinator communities.
-In addition, we analyzed whether the effect of the pollinator richness and visitation rate on the reproductive success of the plants varies over time.
-We expect that the stability of visitation rate will increase with higher richness and asynchrony of pollinators.
+Here, we use a 5-year dataset collected across X Mediterranean woodland patches to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates to X plant speices.
+Further, we evaluate whether more stable pollinator communities foster a more stabale plant reproductive success along years, measuring both the stability of fruit and seed set.
+We expect that the stability of visitation rates will increase with higher richness and asynchrony of pollinators.
 In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rate.
+However, given the lack of a clear relationship between pollinator and plant reproductive output stability, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.
 
@@
 We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby.
-These sites had similarity in plant community composition and some of most abundance plant species provide nectar and pollen that attract flower visitors.
+These sites are similar in the plant community composition and the most abundant plant species are known to be attractive to flower visitors and to depend on pollinators to maximize its reproduction (e.g.
+dominated by X, y and Z).
 Each site was surveyed at least 7 times per year during the flowering season from 2015 to 2019 (from March to June).
 Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean ± standard error: 5.92 ± 0.54 plant species per site).
-All the floral visitors (from now on referred to as pollinators) that contacted with their flowers were registered by performing focal observations to the selected individuals during five minutes in 2015-2016 and three minutes from 2017 to 2019.
+We performed focal observations where all the floral visitors (from now on referred to as pollinators) that contacted with their flowers were registered.
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
-For each plant individual, we counted the total number of flowers and at the end of the season, we recorded the number of fruit and the seeds per fruit.
-All plants analyzed are at least partially pollinator dependent.
-Due to the focal time observation was different over years, for each plant individual, the effort of sampling was standardized in number of visits per minute dividing the total visits observed by total observation time (time observation multiplied by number of survey per year).
-For each site and year, we calculated the visitation rate of pollinators as the number of visits divided by the number of flowers, pollinator richness, the fruit set as the proportion of fruit, and the seed set as number of seed per fruit for each plant individual sampled per site.
+For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed and the number of seeds per fruit in a subsample of X fruits.
+Focal observations had a duration of five minutes per individual in 2015-2016 and three minutes from 2017 to 2019.
+Hence, for each plant individual, the sampling effort was standardized in number of visits per flower per minute.
+To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time observation multiplied by number of survey per year).
+Pollinator richness is calculated as the number of different species observed, fruit set as the proportion of fruits developed, and the seed set as the mean?
+number of seed per fruit for each plant individual sampled per site.
 
@@
 
-For the study of stability, we used 5 plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) because of they were recorded in at least 5 sites and a minimum of two years per site.
-The stability of visitation rate was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
+We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites in a minimum of two years per site (show mean sites / years per plant).
+The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
 To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
-[The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:](al final he puesto que utilizamos este solo porque al corregir el esfuerzo de muestreo este y el de Gross ya no estan correlacionados.
-He analizado el de Gross y no hay relacion con la estabilidad de las visitas.
-Muchos trabajos que solo utilizan un indice no dicen que hayan probado otros como es el trabajo de Lazaro, y he visto que muchos ponen la ecuacion, si no te parece bien asi vuelvo a poner los tres y explico lo de la correlacion)
+[The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:](al%20final%20he%20puesto%20que%20utilizamos%20este%20solo%20porque%20al%20corregir%20el%20esfuerzo%20de%20muestreo%20este%20y%20el%20de%20Gross%20ya%20no%20estan%20correlacionados.%20He%20analizado%20el%20de%20Gross%20y%20no%20hay%20relacion%20con%20la%20estabilidad%20de%20las%20visitas.%20Muchos%20trabajos%20que%20solo%20utilizan%20un%20indice%20no%20dicen%20que%20hayan%20probado%20otros%20como%20es%20el%20trabajo%20de%20Lazaro,%20y%20he%20visto%20que%20muchos%20ponen%20la%20ecuacion,%20si%20no%20te%20parece%20bien%20asi%20vuelvo%20a%20poner%20los%20tres%20y%20explico%20lo%20de%20la%20correlacion)
 
@@
 \begingroup\Large
-\phi =\frac{\sigma_{x_T}^2}{(\sum\sigma_{x_T})^2}
+\phi =\frac{\sigma_{x_T}^2}{(\sum_{i=1}^S\sigma_{x_i})^2}
 \endgroup
-$$
-where ${\sigma_{x_T}^2}$ represents the temporal variance of the community times series and ${(\sum\sigma_{x_T})^2}$ represents the sum of the temporal standard deviation of the time series across all species.
-This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous.
+$$ where ${\sigma_{x_T}^2}$ is the variance of the community abundance of each plot and ${\sigma_{x_i}}$ is the standard deviation of species i abundance in a community with S species.
+This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous [@Loreau2008].
 Finally, we express asynchrony as $1-\phi$.
-We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.
+We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot using the same index.
 
@@
 Linear mixed models were used to evaluate the relationships between 1) stability of visitation rate and asynchrony of pollinator, 2) stability of visitation rate and pollinator richness, and 3) asynchrony and pollinator richness.
-In all case, site and plant species were included as random factor.
+In all cases, site and plant species were included as random factor.
 For a deeper understanding, we also analyzed the response for each plant species separately.
+[a bit of why three models could help the reader]
 
-To study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or stability of seed number and as explanatory variable the visitation rate stability.
+To study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or the stability of seed number and as explanatory variable the visitation rate stability.
 Site and plant species were included as factor random.
 
-To detect whether the effect of pollinator richness and visitation rate is different across the years, we use all plant species sampled.
-We analyzed the interaction effect richness and year, and visitation rate and year on fruit proportion using binomial generalized linear mixed models, and on the number of seeds employing linear mixed model.
+To detect whether the effect of pollinator richness and visitation rate is different across the years, we use all X plant species sampled.
+We analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using binomial generalized linear mixed model, and on the number of seeds employing linear mixed model.
 The number of seeds per fruit was centered and scaled per plant species to allow meaningful comparisons across species.
@@
 
-All the analyses of this study were conducted in R software (v.
-4.0.2; R Core Team, 2022) and the lme4 (Bates et al., 2015) and ggplot2 (Wickham, 2016) packages.
+All the analyses of this study were conducted in R software (v. 4.0.2; R Core Team, 2022) and the lme4 (Bates et al., 2015) and ggplot2 (Wickham, 2016) packages.
 DHARMa package was employed for checking all models (Harting 2017)
@@
 
-## Stability of visitation rate and its drives: richness and synchrony
+## Stability of visitation rate and its drivers: richness and asynchrony
 
-Stability of visitation rate ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-Our results showed a positive tendency between stability of visitation rate and asynchrony with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A),
-whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 1B).
-We also found a positively strong relationship between asynchrony and pollinator richness (0.020 ± 0.005) (Fig 1C).
-We observed one data with high leverage of visitation rate stability (*C.crispus*) however when we removed this point the tendencies are the same.
+Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
+There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 1B).
+We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005) (Fig 1C).
+However, note that despite one data point has a high leverage on this last analysis?
+(*C.crispus*), when we removed this point the tendencie remain unchanged.
 
-When we analysed the plant species separately, we observed positive tendency in asynchrony for *C.
+When we analysed each plant species separately, we observed positive relationship between asynchrony of pollinators and visitation rate for *C.
 crispus*, *H.
 halimifoliun* and *L.
-pedunculata* and milder tendency in *C.
-salviifolious* being the slightly negative tendency in *C.ladanifer*.
-In the case of richness, *C.
+pedunculata*, weak relationship for *C.
+salviifolious* and a weak negative relationship for *C.ladanifer*.
+For the relationship with pollinator richness, *C.
 crispus*, *C.
 ladanifer* and *C.
-salviifolius* showed a negative tendency wile *H.
+salviifolius* showed a negative relationships wile *H.
 halimifolium* and *L.
-pedunculata* was positive (Supplementary material-Fig 1).
+pedunculata* showed positiverelationships, explaining the overall lack of relationship across all five plants (Supplementary material-Fig 1).
 
@@
 
-Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
-When we analyzed whether the stability of the visitation rate affected the stability of the plant reproductive success, we did not find a relationship between this and the stability of the fruit proportion (Estimate: -1.547; std.
-error: 2.611) (Fig 2A), however, the stability of seed number showed negative tendency with the stability of visitation rate (Estimate: -1.887; std.
-error: 0.959) (Fig 2B).
+Stability of fruit set [llamale siempre igual, yo propongo fruit y seed number] varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
+When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit set (Estimate: -1.547; std.
+error: 2.611) (Fig 2A).
+However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (Estimate: -1.887; std. error: 0.959) (Fig 2B).
 
@@
 
-## Effect of pollinators across years on the plant reproductive success
+## Effect of pollinators across years on plant reproductive success
 
-When we analysed whether the effect of pollinator richness and visitation rate is different across the years, we found that both variables showed a significant interaction effect with the year on fruit proportion [(richness:year p = <0.0001; visitation rate:year p = <0.0001)](tengo que poner Anova tipo III???
-y algun dato mas como df??).
-Although we observed a saturation of the fruit proportion, in year like 2017 is showed that a greater richness and visitation rate increased the fruit proportion.
-We also observed a positive tendency between richness and fruit proportion in 2019.
+When we analysed whether the effect of pollinator richness and visitation rate on fruit proportion is different across the years, we found that both variables showed a significant interaction with year [(richness:year p = \<0.0001; visitation rate:year p = \<0.0001)](tengo%20que%20poner%20Anova%20tipo%20III???%20y%20algun%20dato%20mas%20como%20df??).[Aqui me pones p-values?]
+Although we observed a general saturation of the proportion of fruits developed with most species consistently over 80% of fruit set, in years like 2017 we showed that a greater richness and visitation rate increased the fruit proportion.
+We also observed a positive relationship between richness and fruit proportion in 2019.
 However in 2018, the relationship between richness and fruit proportion was negative (Fig 3).
+[esto requiere un poco más de story telling.
+Por ejemplo, estos años son años altos o bajos en polinizadores?]
 
 For the seed number, we not found the interaction effect to pollinator richness (p = 0.628), however we found a marginal significant interaction between visitation rate and year (p = 0.058).
-We observed that a higher the visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).
+We observed that a higher visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).
+[idem, p-values ahora?]
 
@@
 ```
+
+# Discussion
+
+We show that pollinator's visitation rate stability increase with higher asynchrony of pollinators species abundances and that greater species richness only increase stability of visitation rate indirectly, via enhanced species asynchrony.
+However, contrary to expectations, we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
+This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with lower pollinator abundances.
+However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years [seria ideal decir quales...
+los que tienen poco polinizador?
+Los secos, quizas?]
+the relationship between pollinator activity and plant's reproductive output kicks in as important.
+When and where pollinators are limiting is the key question then.
+[esta frase a lo mejor puede ser una conclusing sentence del paper, por ahora la dejo aquí]
+
+While drivers of temporal stability have been well study in plant communities [@Ruijven2007; @Gross2014; @Craven2018; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021], relatively few studies have evaluated how this same drivers can affect community stability in mobile organisms such as pollinators [@Ebeling2008; @Senapathi2021; @Lazaro2022].
+A first clear outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
+This stability--asynchrony relationship has been found by different theoretical and empirical studies (de Mazancourt et al., 2013; Blüthgen et al., 2016; Lepš et al., 2018; Sasaki et al., 2019; Valencia et al, 2020, Kigel et al 2021).
+For example, Lázaro et al.(2022) also found that plants or pollinators?
+temporal or spatial?
+asynchrony is an important driver of stability for for plants, pollinators and their interactions.
+[The fact that species asynchrony increases the temporal stability of the visitation rate is likely because a decrease in the abundance of one pollinator species is compensated by an increase of the abundance of another.](escribir%20mejor%20la%20frase)
+[mirate los appaers de Winfree sobre esto que lo explica muy bien y explica mecanismos] On the other hand, species richness is considered one of the strongest drivers of community stability [in plants?]
+(Tilman et al., 2006; de Mazancourt et al., 2013; Hallett et al., 2014), although Valencia et al.(2020) have reported that this relation is not nearly as strong [where?]
+.
+Pollinator studies have observed a positive relationship between richness and stability of what?
+in crops??
+(Ebeling et al 2008; Senapathi et al 2021), however, our results show that richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly.
+[This most likely reflects niche variation among species that affect their relative performance over time in a temporally variable environment (Yachi & Loreau,1999; Gross et al., 2014; Craven et al 2018).](??)
+
+Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems [right?]
+(Garibaldi et al.
+2011, Lázaro and Alomar 2019, Hünicken et al 2021, Bishop et al 2022).The majority of these studies were focused on crops, however, to our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
+In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate (Garibaldi et al.
+2011, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship or even observed a negative relationship between seed number stability and visitation rate stability.
 

### 2023-01-16 Manuscript/Manuscript.Rmd
editing

@@
 output:
-  pdf_document :
-    latex_engine : xelatex
-header-includes:
- \usepackage{float}
- \floatplacement{figure}{H}
- \usepackage{caption}
+  pdf_document:
+    latex_engine: xelatex
+  word_document: default
+header-includes: \usepackage{float} \floatplacement{figure}{H} \usepackage{caption}
   \renewcommand{\caption}{Figure}
-
 bibliography: library.bib
@@
 3.  The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances but not by the pollinator richness.
-    [Likewise, we found a strong positive relationship between richness and asynchrony of pollinators.](Yo%20esto%20no%20lo%20meteria%20aquí,%20por%20que%20no%20aporta%20mucho,%20no?%20Y%20es%20complejo%20de%20explicar.)
     In contrast, the stability of the plant reproductive success is not related to the stability of the visitation rate.
-    A year by year analysis revels that plants are unlikely to be limited by pollinator abundances except in specific years with [extreme low levels of pollinator activity](esto%20es%20así?%20Molaria).
+    A year by year analysis revels that plants are unlikely to be limited by pollinator abundances except in specific years with [extreme low levels of pollinator activity](esto es así Molaria).
 
@@
 While community temporal stability should be related to the stability of ecosystem functions and services provided by such community, there is limited evidence linking both processes on multitrophic systems.
-[comment](aqui%20hecho%20a%20faltar%20la%20alternativa,%20solo%20la%20asyncronia%20entre%20las%20especies%20más%20abundantes%20es%20lo%20que%20cuenta)
+[comment](aqui hecho a faltar la alternativa, solo la asyncronia entre las especies más abundantes es lo que cuenta)
 
@@
 For example, pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] and consequently may provide pollination services at different times of the day or of the season.
-[However, there are not that many studies linking explicitly pollinator visitation rates directly with plant reproductive outputs](de%20esto%20estas%20segura?).
-While some studies report that sites with higher visitation rates show higher plant reproductive outputs (REFS), other studies do not find such relationship (Hegland and Totland 2012, Lundgren et al 2013; Kaiser‐Bunbury et al., 2017).
+While some studies report that sites with higher visitation rates show higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
 Interestingly, studies looking at pollen limitation show that sites with higher visitation rates show no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant (Fig.
@@
 
-[gap](I%20think%20something%20about%20temporal%20variation%20and%20pollen%20limitation)
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 8,fig.width=10,out.width="60%",fig.align='center'}
+library(ggplot2)
+library(patchwork)
 
-Here, we use a 5-year dataset collected across X Mediterranean woodland patches to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates to X plant speices.
+#First dataset RED
+s1 <- seq(from=0, to=100, by=0.5)
+l1 = log(s1, base = 6)
+d1 = data.frame(l1, s1)
+
+#Second dataset BLUE
+s2 <- seq(from=0, to=100, by=0.5)
+l2 = log(s2, base = 8)
+d2 = data.frame(l2, s2)
+
+#Third dataset GREEN
+s3 <- seq(from=0, to=100, by=0.5)
+l3 = log(s3, base = 12)
+d3 = data.frame(l3, s3)
+
+to=ggplot(d1, aes(s1, l1)) +
+  geom_line(color = "#e41a1c", linewidth=1.3) +
+  geom_line(data =  d2, aes(s2,l2), color = "#377eb8",linewidth=1.3) +
+  geom_line(data =  d3, aes(s3,l3), color = "#4daf4a",linewidth=1.3) +
+  ylab("Reproductive success")+
+  labs(x = "") +
+  theme_classic()+
+  theme(axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())+
+  scale_x_continuous(breaks=seq(from= 0, to= 100, by = 20), labels=c("V1","V2","V3", "V4","V5","V6"))+
+  theme(text = element_text(size=18,face="bold"))+
+  theme(axis.ticks.x=element_blank())+
+  annotate("rect", xmin = c(0, 60), xmax = c(20,80), ymin = c(0.4, 1.35), 
+           ymax = c(1.75, 2.7), linetype = 1, fill="gray88", alpha=0.3, colour = "black") +
+  annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R3", "R2", "R1"), size=5)+
+  annotate("text", x = c(1.25, 61.3), y = c(1.62,2.58), label = c("A", "B"), size=6)+
+  theme(axis.line.x = element_line(arrow = arrow()))+
+  theme(axis.line.y = element_line(arrow = arrow()))
+
+##################################
+x <- seq(0, 41, by = 0.1)
+y1 <- sin(x)
+y1.2 <- cos(x+4.3)
+
+da1 <- data.frame( x, y1)
+da1.2 <- data.frame( x, y1.2)
+
+R_1=ggplot(da1, aes(x, y1))+
+  geom_line( size=1) +
+  geom_line(data =  da1.2, aes(x, y1.2), color = "#e41a1c",size=1)+
+  theme_classic() +
+  xlab("Time") +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) + 
+  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("R1","R3"))+
+  theme(text = element_text(size=15, face="bold"))+
+  theme(axis.title.y = element_blank()) +
+  annotate("text", x = 44, y = 0.4, label = "Rep", size=4,color="#e41a1c")+
+  annotate("text", x = 43, y = 0, label = "R", size=4)+ 
+  theme(aspect.ratio=0.5)
+
+###################################
+
+x2 <- seq(0, 41, by = 0.1)
+y2 <- sin(x2)
+y3 = sin(x2/2.5)
+
+da2 <- data.frame(x2, y2)
+da2.1 = data.frame(x2,y3)
+
+v_1=ggplot(da2, aes(x2, y2))+
+  geom_line( size=1) +
+  geom_line(data =  da2.1, aes(x2,y3), color = "#e41a1c",size=1)+
+  theme_classic() +
+  xlab("Time")+
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+ 
+  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("V1","V2"))+
+  theme(text = element_text(size=15, face="bold"))+
+  theme(axis.title.y = element_blank())+
+  annotate("text", x = 44, y = -0.5, label = "Rep", size=4, color="#e41a1c")+
+  annotate("text", x = 42.5, y = 0, label = "V", size=4) + 
+  theme(aspect.ratio=0.5)
+
+po1=v_1/R_1
+
+######################
+x3 <- seq(0, 57, by = 0.1)
+y3 <- sin(x3)
+y3.1 <- cos(x3+4.3)
+
+da3 <- data.frame(x3, y3)
+da3.1 <- data.frame(x3, y3.1)
+
+v_2=ggplot(da3, aes(x3, y3))+
+  geom_line( size=1) +
+  geom_line(data =  da3.1, aes(x3,y3.1), color = "#e41a1c",size=1)+
+  theme_classic() +
+  xlab("Time") +
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank()) + 
+  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("V4","V5"))+
+  theme(text = element_text(size=15, face="bold"))+
+  theme(axis.title.y = element_blank()) +
+  annotate("text", x = 61, y = 0, label = "Rep", size=4,color="#e41a1c")+
+  annotate("text", x = 59, y = 0.3, label = "V", size=4)+ 
+  theme(aspect.ratio=0.5)
+
+########################################
+x4 <- seq(0, 57, by = 0.1)
+y4 <- sin(x4)
+y5 = sin(x4/2.5)
+
+da4 <- data.frame(x4, y4)
+da5 = data.frame(x4,y5)
+
+R_2=ggplot(da4, aes(x4, y4))+
+  geom_line( size=1) +
+  geom_line(data =  da5, aes(x4,y5), color = "#e41a1c",size=1)+
+  theme_classic() +
+  xlab("Time")+
+  theme(axis.text.x=element_blank(),
+        axis.ticks.x=element_blank())+ 
+  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("R1","R3"))+
+  theme(text = element_text(size=15, face="bold"))+
+  theme(axis.title.y = element_blank())+
+  annotate("text", x = 61, y = -0.6, label = "Rep", size=4, color="#e41a1c")+
+  annotate("text", x = 59, y = 0.4, label = "R", size=4)+ 
+  theme(aspect.ratio=0.5)
+
+po2=v_2/R_2
+
+to/ (po1 |po2)
+```
+
+Here, we use a 5-year dataset collected across X Mediterranean woodland patches to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates to X plant species.
 Further, we evaluate whether more stable pollinator communities foster a more stabale plant reproductive success along years, measuring both the stability of fruit and seed set.
@@
 We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby.
-These sites are similar in the plant community composition and the most abundant plant species are known to be attractive to flower visitors and to depend on pollinators to maximize its reproduction (e.g.
-dominated by X, y and Z).
+These sites are similar in the plant community composition and the most abundant plant species are known to be attractive to flower visitors and to depend on pollinators to maximize its reproduction [(e.g.
+dominated by X, y and Z).]()
 Each site was surveyed at least 7 times per year during the flowering season from 2015 to 2019 (from March to June).
@@
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
-For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed and the number of seeds per fruit in a subsample of X fruits.
+For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed and the number of seeds per fruit in a subsample of [X fruits.]()
 Focal observations had a duration of five minutes per individual in 2015-2016 and three minutes from 2017 to 2019.
@@
 
-We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites in a minimum of two years per site (show mean sites / years per plant).
+We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites in a minimum of two years per site [(show mean sites / years per plant).]()
 The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
 To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
-[The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:](al%20final%20he%20puesto%20que%20utilizamos%20este%20solo%20porque%20al%20corregir%20el%20esfuerzo%20de%20muestreo%20este%20y%20el%20de%20Gross%20ya%20no%20estan%20correlacionados.%20He%20analizado%20el%20de%20Gross%20y%20no%20hay%20relacion%20con%20la%20estabilidad%20de%20las%20visitas.%20Muchos%20trabajos%20que%20solo%20utilizan%20un%20indice%20no%20dicen%20que%20hayan%20probado%20otros%20como%20es%20el%20trabajo%20de%20Lazaro,%20y%20he%20visto%20que%20muchos%20ponen%20la%20ecuacion,%20si%20no%20te%20parece%20bien%20asi%20vuelvo%20a%20poner%20los%20tres%20y%20explico%20lo%20de%20la%20correlacion)
-
+The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:
 $$
@@
 [mirate los appaers de Winfree sobre esto que lo explica muy bien y explica mecanismos] On the other hand, species richness is considered one of the strongest drivers of community stability [in plants?]
-(Tilman et al., 2006; de Mazancourt et al., 2013; Hallett et al., 2014), although Valencia et al.(2020) have reported that this relation is not nearly as strong [where?]
-.
+(Tilman et al., 2006; de Mazancourt et al., 2013; Hallett et al., 2014), although Valencia et al.(2020) have reported that this relation is not nearly as strong [where?].
 Pollinator studies have observed a positive relationship between richness and stability of what?

### 2023-01-17 Manuscript/Manuscript.Rmd
editing

@@
 
-Here, we use a 5-year dataset collected across X Mediterranean woodland patches to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates to X plant species.
-Further, we evaluate whether more stable pollinator communities foster a more stabale plant reproductive success along years, measuring both the stability of fruit and seed set.
+Here, we use a 5-year dataset collected across 13 Mediterranean woodland patches to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates to 5 plant species.
+Further, we evaluate whether more stable pollinator communities foster a more stable plant reproductive success along years, measuring both the stability of fruit and seed set.
 We expect that the stability of visitation rates will increase with higher richness and asynchrony of pollinators.
@@
 We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby.
-These sites are similar in the plant community composition and the most abundant plant species are known to be attractive to flower visitors and to depend on pollinators to maximize its reproduction [(e.g.
-dominated by X, y and Z).]()
+These sites are similar in the plant community composition and the most abundant plant species are known to be attractive to flower visitors and to depend on pollinators to maximize its reproduction (e.g.
+dominated by *Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*).
 Each site was surveyed at least 7 times per year during the flowering season from 2015 to 2019 (from March to June).
@@
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
-For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed and the number of seeds per fruit in a subsample of [X fruits.]()
+For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed and the number of seeds per fruit in a subsample of [3 fruits.](en algunos casos solo habia contado para dos frutos pero la mayoria son 3)
 Focal observations had a duration of five minutes per individual in 2015-2016 and three minutes from 2017 to 2019.
@@
 To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time observation multiplied by number of survey per year).
-Pollinator richness is calculated as the number of different species observed, fruit set as the proportion of fruits developed, and the seed set as the mean?
-number of seed per fruit for each plant individual sampled per site.
+Pollinator richness is calculated as the number of different species observed, fruit set as the proportion of fruits developed, and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.
 
@@
 
-To detect whether the effect of pollinator richness and visitation rate is different across the years, we use all X plant species sampled.
+To detect whether the effect of pollinator richness and visitation rate is different across the years, we use all 12 plant species sampled.
 We analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using binomial generalized linear mixed model, and on the number of seeds employing linear mixed model.
+*P* values were obtained using the type III Anova (package: car)
 The number of seeds per fruit was centered and scaled per plant species to allow meaningful comparisons across species.
@@
 Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 1A), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 1B).
-We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005) (Fig 1C).
-However, note that despite one data point has a high leverage on this last analysis?
-(*C.crispus*), when we removed this point the tendencie remain unchanged.
+There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 2A), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 2B).
+We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005) (Fig 2C).
+However, note that despite one data point has a high leverage on the stability analysis
+(*C.crispus*), when we removed this point the tendencies remain unchanged.
 
@@
 halimifolium* and *L.
-pedunculata* showed positiverelationships, explaining the overall lack of relationship across all five plants (Supplementary material-Fig 1).
+pedunculata* showed positive relationships, explaining the overall lack of relationship across all five plants (Supplementary material-Fig 1).
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 8,fig.width=20, out.width="100%",fig.align='center', fig.cap =" 1.Relationships between stability of visitation rate (calculated as the inverse of the coefficient of variation) and asynchorny of pollinators (Loreau and de Mazancourt’s index) (A), stability of visitation rate and pollinator richness (B), and asynchorny of pollinators and richness (C).Dots represent the different plant species incluided in the analysis.Significant models are representing with solid line."}
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 8,fig.width=20, out.width="100%",fig.align='center', fig.cap =" 2.Relationships between stability of visitation rate (calculated as the inverse of the coefficient of variation) and asynchorny of pollinators (Loreau and de Mazancourt’s index) (A), stability of visitation rate and pollinator richness (B), and asynchorny of pollinators and richness (C).Dots represent the different plant species incluided in the analysis.Significant models are representing with solid line."}
 
@@
 
-Stability of fruit set [llamale siempre igual, yo propongo fruit y seed number] varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
-When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit set (Estimate: -1.547; std.
-error: 2.611) (Fig 2A).
-However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (Estimate: -1.887; std. error: 0.959) (Fig 2B).
+Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
+When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit proportion (Estimate: -1.547; std.
+error: 2.611) (Fig 3A).
+However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (Estimate: -1.887; std.
+error: 0.959) (Fig 3B).Although this tendency is influenced by a high value in the stability of seed number of *H.
+halimifolium* since when we removed this point the relationship disappears.
 
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 10,fig.width=20,out.width="80%",fig.align='center', fig.cap = " 2.
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 10,fig.width=20,out.width="80%",fig.align='center', fig.cap = " 3.
 Relationship between stability of plant reproductive succes: fruit propotion (A) and seed number (B) and the stability of visitation rate.
@@
 
-When we analysed whether the effect of pollinator richness and visitation rate on fruit proportion is different across the years, we found that both variables showed a significant interaction with year [(richness:year p = \<0.0001; visitation rate:year p = \<0.0001)](tengo%20que%20poner%20Anova%20tipo%20III???%20y%20algun%20dato%20mas%20como%20df??).[Aqui me pones p-values?]
+When we analysed whether the effect of pollinator richness and visitation rate on fruit proportion is different across the years, we found that both variables showed a significant interaction with year (richness interaction with year: $\chi 2$ =  28.976, df = 4, *p* = \<0.0001; visitation rate interaction with year: $\chi 2$ =  40.691, df = 4, *p* = \<0.0001)
 Although we observed a general saturation of the proportion of fruits developed with most species consistently over 80% of fruit set, in years like 2017 we showed that a greater richness and visitation rate increased the fruit proportion.

### 2023-01-17 script/stability_analysisr.R
checking outlier

@@ -16,6 +16,7 @@ library(effects)
 library(MuMIn)
 library(sjPlot)
 library(RColorBrewer)
+library(Hmisc)
 
 
 # stability data 
@@ -52,6 +53,9 @@ data_plant[is.na(data_plant) | data_plant == "-Inf"] <- NA
 syn_cor<-data_plant %>% select(log_VR,syncLM,av_sync)
 syn_cor <- mutate_all(syn_cor, ~replace(., is.na(.), 0))
 cor(syn_cor)
+cor_1 <- rcorr(as.matrix(syn_cor))
+cor_1
+
 
 # correlacion por plant species
 syn_cor_pla<-data_plant %>% select(Plant_gen_sp,log_VR,syncLM,av_sync)
@@ -130,7 +134,6 @@ summary(mod1_sta)
 summary(mod1_sta_2)
 
 r.squaredGLMM(mod1_sta)
-car::vif(mod1_sta)
 
 car::Anova(mod1_sta,Type="III")
 
@@ -247,7 +250,27 @@ p3=ggplot(effe3_mod_sta, aes(cv_1_visitation, fit)) + geom_line()+
   geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_fruit, color=Plant_gen_sp), size=3)+
   labs(y = "fruit set stability",x="visitation rate stability")
  
+#########################################3
+# out c.salviifolius la cunya = valor de estabilidad en fruit proportion muy alto
+# ver si cambia el modelo
 
+data_slavi_out=data_plant %>%
+  filter(!(Site_ID=="La_cunya" & Plant_gen_sp=="Cistus salviifolius")) 
+
+mod2_sta_out= lmer(cv_1_fruit ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID), data = data_slavi_out)
+summary(mod2_sta_out)
+
+#getting effects 
+effe_mod_sta_out <-data.frame( effect("cv_1_visitation", mod2_sta_out, se = TRUE))
+#plot model 
+p4_out=ggplot(effe_mod_sta_out, aes(cv_1_visitation, fit)) + geom_line()+
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
+  geom_point(data = data_slavi_out, aes(x =  cv_1_visitation, y = cv_1_fruit, color=Plant_gen_sp), size=3)+
+  labs(y = "fruit set stability",x="visitation rate stability")
+
+
+
+#########################################3
 
[…]

### 2023-02-02 script/media_anual.R
boxplot year

@@ -1,0 +1,73 @@
+
+
+# pollinator richness per year
+ggplot(data = Pollinator_Plant, aes(x = Year, y = S_total)) + 
+    geom_boxplot ()
+
+
+ave_S <- Pollinator_Plant%>% 
+  group_by(Year) %>% 
+  summarize(mean_S = mean(S_total, na.rm=T),
+            standarderror = sd(S_total, na.rm = TRUE)/sqrt(n()))
+
+
+
+
+# visitation rate per year
+ggplot(data = Pollinator_Plant, aes(x = Year, y = visitatio_rate)) + 
+  geom_boxplot ()
+
+
+ave_VR <- Pollinator_Plant%>% 
+  group_by(Year) %>% 
+  summarize(mean_VR = mean(visitatio_rate, na.rm=T),
+            standarderror = sd(visitatio_rate, na.rm = TRUE)/sqrt(n()))
+
+
+# FOCAL
+
+focal<- read.csv("Data/focal.csv") 
+focal<-focal[,-1]
+
+
+focal <- focal[!(focal$Pollinator_gen_sp == "NA NA"),] #eliminar polinizadores NA NA
+
+#Data with species in more than 1 site
+focal = focal %>% filter(!Plant_gen_sp %in% spp_out)
+
+focal$Pollinator_gen_sp <- sub(" ", "_", focal$Pollinator_gen_sp )
+
+levels(factor(focal$Plant_gen_sp))
+
+focal<-subset(focal, Plant_gen_sp != 'Ulex australis') #remove ulex
+
+
+# temperature mean per year during sampling
+focal$Year <- as.factor(focal$Year)
+
+ave_tem <- focal%>% 
+  group_by(Year) %>% 
+  summarize(mean_tem = mean(Temperature, na.rm=T),
+            standarderror = sd(Temperature, na.rm = TRUE)/sqrt(n()))
+
+
+
+ggplot(data = focal, aes(x = Year, y = Temperature)) + 
+  geom_boxplot ()
+
+
+
+# humidity mean per year during sampling
+ave_hu <- focal%>% 
+  group_by(Year) %>% 
+  summarize(mean_hu= mean(Humidity, na.rm=T),
+            standarderror = sd(Humidity, na.rm = TRUE)/sqrt(n()))
+
+
+ggplot(data = focal, aes(x = Year, y = Humidity)) + 
+  geom_boxplot ()
+
+
+
+
+

### 2023-02-02 script/stability.R
dylyr::select

@@ -157,7 +157,7 @@ levels(factor(full2$Plant_gen_sp))
 focal<-subset(focal, Plant_gen_sp != 'Ulex australis') #remove ulex
 
 plant_polli<-data.frame(focal[,c(1,2,6,31,32)])
-
+plant_polli$Year <- as.factor(plant_polli$Year)
 
 df.result <- left_join(Pollinator_Plant, plant_polli, c('Plant_gen_sp', 'Site_ID','Year','plant_id'))
 
@@ -165,7 +165,7 @@ df.result1<-data.frame(df.result[,c(1,2,3,4,16,17,21)])
 df.result2 <- dcast(df.result, formula = Site_ID + Year + n_round + time_obs + plant_id+Plant_gen_sp ~ Pollinator_gen_sp)
 
 # remove column NA
-df.result2= select(df.result2, -131)
+df.result2= dplyr::select(df.result2, -123)
 
 
 # corrected abundance of pollinator by sampling effort (total time of observation)
@@ -178,7 +178,7 @@ df.result2= select(df.result2, -131)
 abund_pol=df.result2 %>%
   mutate(total_time= n_round*time_obs) %>%
   relocate(total_time, .before = plant_id) %>%
-  select(!c(n_round, time_obs)) %>%
+  dplyr::select(!c(n_round, time_obs)) %>%
   group_by(Site_ID, Year, Plant_gen_sp) %>%
   summarise_if(is.numeric, sum) %>%
   ungroup()
@@ -188,7 +188,7 @@ abund_pol=df.result2 %>%
 # y multiplicado por el tiempo max de observacion 
 # hay una especie que se ha observado un max de 90 min
 abund_pol_stand=abund_pol %>% 
-  mutate_at (vars (c(5:128)), funs((./total_time)*90))
+  mutate_at (vars (c(5:120)), funs((./total_time)*90))
 
 
 

### 2023-02-02 script/Model_Year_2.R
dplyr::select and Anova type III

@@ -31,19 +31,20 @@ spp_out <- Pollinator_Plant %>%
   group_by(Plant_gen_sp, Year) %>%
   summarise(Unique_Id = n_distinct(Site_ID)) %>%
   filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp, Year)
+  dplyr::select(Plant_gen_sp, Year)
 
 
 Pollinator_Plant= anti_join(Pollinator_Plant, spp_out)
 
 levels(factor(Pollinator_Plant$Plant_gen_sp))
 
+
 #we analyze whether the fruit proportion is affected by richness, 
 #year and its interaction for all data 
 #with plant species nested within site as random effect
 mod1_to= glmer(cbind(fruit_formado, Fruit_No) ~ S_total * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
 summary(mod1_to)
-car::Anova(mod1_to,Type="III")
+car::Anova(mod1_to,type="III")
 
 
 plot_model(mod1_to, type = "int")
@@ -71,10 +72,11 @@ p1=ggplot(ee_mod1, aes(S_total,fit))+
 # and visitation rate (in one minute), year and its interaction
 mod2_to= glmer(cbind(fruit_formado, Fruit_No) ~ visitatio_rate * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
 summary(mod2_to)
-car::Anova(mod2_to,Type="III")
+car::Anova(mod2_to,type="III")
 
 
 plot_model(mod2_to, type = "int")
+plot_model(mod2_to, type = "pred")
 
 
 #getting effects for the two variables
@@ -108,7 +110,7 @@ Pollinator_Plant=Pollinator_Plant %>%
 #model
 mod3_to= lmer(seed_sc ~S_total * Year + (1|Site_ID/Plant_gen_sp),data=Pollinator_Plant)
 summary(mod3_to)
-car::Anova(mod3_to,Type="III")
+car::Anova(mod3_to,type="III")
 
 plot_model(mod3_to, type = "int", show.data = F)
 plot_model(mod3_to, type="pred")

### 2023-02-02 Manuscript/Figures/Conceptual_plot.R
edit

@@ -22,9 +22,9 @@ d3 = data.frame(l3, s3)
 
 
 to=ggplot(d1, aes(s1, l1)) +
-  geom_line(color = "#e41a1c", size=1.3) +
-  geom_line(data =  d2, aes(s2,l2), color = "#377eb8",size=1.3) +
-  geom_line(data =  d3, aes(s3,l3), color = "#4daf4a",size=1.3) +
+  geom_line(color = "#e41a1c", linewidth=1.3) +
+  geom_line(data =  d2, aes(s2,l2), color = "#377eb8",linewidth=1.3) +
+  geom_line(data =  d3, aes(s3,l3), color = "#4daf4a",linewidth=1.3) +
   ylab("Reproductive success")+
   labs(x = "") +
   theme_classic()+
@@ -90,8 +90,8 @@ v_1=ggplot(da2, aes(x2, y2))+
   theme(aspect.ratio=0.5)
 
 
-po1=R_1/v_1 & theme(plot.background = element_rect(color = "black", size = 1))
 
+po1=R_1/v_1& theme(plot.background = element_rect(color = "black", size = 1))
 
 ######################
 x3 <- seq(0, 57, by = 0.1)
@@ -142,13 +142,13 @@ R_2=ggplot(da4, aes(x4, y4))+
   theme(aspect.ratio=0.5)
 
 
-po2=v_2/R_2
+po2=v_2/R_2& theme(plot.background = element_rect(color = "black", size = 1))
 
 ########################################
 
 design <- "
-  11#
-  24#
+  AA#
+  BC#
 "
 
 to+po1+v_2+R_2+ plot_layout(heights  = c(3,1,1),design = design)
@@ -157,3 +157,4 @@ to / ((v_1 / R_1)|(v_2 / R_2))
 
 to/ (po1 |po2)
  
+to - (po1 | po2) + plot_layout(ncol=1)

### 2023-02-02 Manuscript/Manuscript.Rmd
edit

@@
 ---
-title: "Title"
+title: "Stability of flower visitation rate over time is driven by asynchrony of pollinator abundances but does not determine the stability of plant reproductive success."
+author: "Estefanía Tobajas, Virginia Domínguez-García, Francisco P. Molina, Ignasi Bartomeus"
 date: '2022-10-26'
@@
 
-1.  The stability of ecological communities over time, often measured as its aggregated abundance or biomass, is mainly influenced by species richness and the asynchrony of the species fluctuations.
+1.
+The stability of ecological communities over time, often quantified using its aggregated abundance or biomass, is mainly influenced by species richness and the asynchrony of the species fluctuations.
     However, the relation with the stability of ecosystem functioning provided by this community is less explored, specially for functions involving several trophic levels such as plant pollination.
@@
 Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
-Among the main driving forces of community stability are the diversity of species present and the asynchrony on the species abundance fluctuations.
+The temporal stability of community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
 A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e.
 the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
-However, a more direct stabilizing mechanisms the degree of asynchrony in species abundance fluctuations.
+The degree of asynchrony in species abundance fluctuations is also a stabilizing mechanisms.
 In this sense, higher levels of asynchrony stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018].
-In fact, stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016; @Valencia2020].
+Species asynchrony has been found to be a key factor driving positive relationships between diversity and stability [@Loreau2008;@Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016;@Huang2020].
+Other studies have indicated that temporal stability of the dominant species or asynchrony among these dominant species is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020].
 While community temporal stability should be related to the stability of ecosystem functions and services provided by such community, there is limited evidence linking both processes on multitrophic systems.
-[comment](aqui hecho a faltar la alternativa, solo la asyncronia entre las especies más abundantes es lo que cuenta)
 
@@
 While some studies report that sites with higher visitation rates show higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
-Interestingly, studies looking at pollen limitation show that sites with higher visitation rates show no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant (Fig.
-1; Cosacov et al., 2008; Gómez et al., 2010; Williams & Winfree, 2013).
-However, the occurrence and magnitude of pollen limitation can vary among years for individual populations (Burd 1994, Ashman et al.
-2004), primarily because of variation in pollinator service (Aizen and Harder 2007).
+Interestingly, studies looking at pollen limitation show that sites with higher visitation rates show no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant [Fig.
+1; @Cosacov2008; @Williams2013].
+However, the occurrence and magnitude of pollen limitation can vary among years for individual populations [@Burd1994; @Ashman2004], primarily because of variation in pollinator service [@Aizen2007].
 
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 8,fig.width=10,out.width="60%",fig.align='center'}
+```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 8,fig.width=10,out.width="60%",fig.align='center', fig.cap =" 1.
+Conceptual figure showing the general relationship between visitation rate of pollinators and plant reproductive success to different species richness.
+As the number of visits from pollinators increases, the plant reproductive success is expected to increase until than above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success."}
 library(ggplot2)
@@
 
-Here, we use a 5-year dataset collected across 13 Mediterranean woodland patches to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates to 5 plant species.
+Here, [we use a 5-year dataset collected for a total of 12 plant species across 13 Mediterranean woodland patches but to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates we use the 5 most represented plant species.](no se si asi se entendera que tenemos un total de 12 especies pero que para la estabilidad solo empleamos 5)
 Further, we evaluate whether more stable pollinator communities foster a more stable plant reproductive success along years, measuring both the stability of fruit and seed set.
@@
 To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time observation multiplied by number of survey per year).
-Pollinator richness is calculated as the number of different species observed, fruit set as the proportion of fruits developed, and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.
+Pollinator richness is calculated as the number of pollinator species observed visiting the plant, fruit set as the proportion of fruits developed, and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.
 
@@
 The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
-To examine the role of richness and synchrony of pollinator species as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
+To examine the role of richness and synchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
 The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:
@@
 Finally, we express asynchrony as $1-\phi$.
-We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot using the same index.
+We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.
 
@@
 
-Linear mixed models were used to evaluate the relationships between 1) stability of visitation rate and asynchrony of pollinator, 2) stability of visitation rate and pollinator richness, and 3) asynchrony and pollinator richness.
+To discover the main drivers of visitation rate stability on the five plant species studied, we carried out two linear mixed models using as response variable the stability of visitation rate and as explanatory variables pollinator asynchrony and richness, respectively.
+Similarly, linear mixed model was used to test the influence of pollinator richness on asynchrony of pollinator species abundances.
 In all cases, site and plant species were included as random factor.
-For a deeper understanding, we also analyzed the response for each plant species separately.
-[a bit of why three models could help the reader]
+For a deeper understanding of the processes stabilizing visitation rate, we also analyzed the response for each plant species separately.
 
@@
 
-To detect whether the effect of pollinator richness and visitation rate is different across the years, we use all 12 plant species sampled.
-We analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using binomial generalized linear mixed model, and on the number of seeds employing linear mixed model.
+Finally, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.
+For this we employed all plant species sampled and we analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using binomial generalized linear mixed model, and on the number of seeds employing linear mixed model.
 *P* values were obtained using the type III Anova (package: car)
@@
 Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases (Estimate ± standard error: 2.903 ± 1.134) (Fig 2A), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 2B).
+There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134) (Fig 2A)](Virginia me ha comentado en reportar el R2 de los modelos pero al tratarse de modelos mixtos tendriamos que poner el marginal o el condicional.He revisado articulos que utilizan estos modleos y normalmente no ponen R2.
+Lo incluyo??), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 2B).
 We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005) (Fig 2C).
-However, note that despite one data point has a high leverage on the stability analysis
-(*C.crispus*), when we removed this point the tendencies remain unchanged.
+Furthermore, we observed one data point has a high leverage on the stability analysis (*C.crispus*, Fig 2A-B), when we remove this point the tendency of asynchrony is  weaker but still positive (0.968 ± 0.745).
 
-When we analysed each plant species separately, we observed positive relationship between asynchrony of pollinators and visitation rate for *C.
+When we analysed each plant species separately, we observed positive relationship between asynchrony of pollinators and stability of visitation rate for *C.
 crispus*, *H.
@@
 Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
-When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit proportion (Estimate: -1.547; std.
-error: 2.611) (Fig 3A).
-However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (Estimate: -1.887; std.
-error: 0.959) (Fig 3B).Although this tendency is influenced by a high value in the stability of seed number of *H.
-halimifolium* since when we removed this point the relationship disappears.
+When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611) (Fig 3A).
+However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959) (Fig 3B).Although this tendency is influenced by a high value in the stability of seed number of *H.
+halimifolium* (Fig 3B) since when we removed this point the relationship disappears (0.561 ± 0.535).
 
@@
 
-## Effect of pollinators across years on plant reproductive success
+##  The effect of pollinators on reproductive success depends on the year
 
-When we analysed whether the effect of pollinator richness and visitation rate on fruit proportion is different across the years, we found that both variables showed a significant interaction with year (richness interaction with year: $\chi 2$ =  28.976, df = 4, *p* = \<0.0001; visitation rate interaction with year: $\chi 2$ =  40.691, df = 4, *p* = \<0.0001)
-Although we observed a general saturation of the proportion of fruits developed with most species consistently over 80% of fruit set, in years like 2017 we showed that a greater richness and visitation rate increased the fruit proportion.
+When we analysed whether the variability of pollinator richness and visitation rate across years affected to the reproductive success of plants, we found that both year and interaction of pollinator richness and visitation rate with year affected on fruit proportion (richness interaction with year: $\chi 2$ =  28.976, df = 4, *p* = \<0.0001; visitation rate interaction with year: $\chi 2$ =  40.691, df = 4, *p* = \<0.0001)
+Although we observed a general saturation of the proportion of fruits developed with most species consistently over 80% of fruit set, in years like 2017 we found that a greater richness and visitation rate increased the fruit proportion.
 We also observed a positive relationship between richness and fruit proportion in 2019.
@@
 
-```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height =13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 3.
+```{r,echo=FALSE, warning=FALSE,message=FALSE,fig.height =13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 4.
 Interaction effect between richness and year (top row), and visitation rate and year (bottom row) on fruit proportion.

### 2023-02-03 script/meteo.R
meteo Almonte

@@ -1,0 +1,111 @@
+library(tidyverse)
+
+
+# Datos estacion meteorologia Almonte
+met<- read_delim("Data/Almonte.csv", delim = ";", escape_double = FALSE, trim_ws = TRUE)
+str(met)
+
+# separate column date
+met=met %>% separate(FECHA, c("dia", "mes", "año"), sep = "/")
+
+#change data types
+met$Hu10Precip <- as.numeric(met$Hu10Precip)
+met$Hu10Rad <- as.numeric(met$Hu10Rad)
+met$Hu10HumMed <- as.numeric(met$Hu10HumMed)
+met$Hu10TMed <- as.numeric(met$Hu10TMed)
+
+str(met)
+
+
+#remove june, july and august. 
+
+met=met %>% filter(!mes %in% c("06","07", "08"))
+
+
+# new column
+#data for 2015 is from sept 2014 to may 2015. 
+#the same for the rest year
+met=met %>%
+  mutate(new_year = case_when(mes %in% c(01,02,03,04,05) | año %in% c(19) ~ 2019,
+                              mes%in% c("09","10","11","12") & año %in% c(18) ~ 2019,
+                              mes %in% c(01,02,03,04,05) | año %in% c(18) ~ 2018,
+                              mes%in% c("09","10","11","12") & año %in% c(17) ~ 2018,
+                              mes %in% c(01,02,03,04,05) | año %in% c(17) ~ 2017,
+                              mes%in% c("09","10","11","12") & año %in% c(16) ~ 2017,
+                              mes %in% c(01,02,03,04,05) | año %in% c(16) ~ 2016,
+                              mes%in% c("09","10","11","12") & año %in% c(15) ~ 2016,
+                              mes %in% c(01,02,03,04,05) | año %in% c(15) ~ 2015,
+                              mes%in% c("09","10","11","12") & año %in% c(14) ~ 2015,
+                              TRUE~0))
+
+
+met$new_year <- as.factor(met$new_year)
+
+
+#box plot precipitacion 
+ggplot(data = met, aes(x = new_year, y =  Hu10Precip)) + 
+  geom_boxplot ()
+
+
+# plot precipitacion media mensual por años 
+met %>%
+  group_by(mes, new_year) %>%
[…]

### 2023-02-06 script/meteo.R
accumulated precipitation

@@ -59,6 +59,25 @@ met %>%
   facet_grid(new_year~.)
 
 
+# plot precipitacion acumulada mensual por años 
+met %>%
+  group_by(mes, new_year) %>%
+  summarise(acum_precip = sum(Hu10Precip, na.rm = TRUE)) %>%
+  mutate(mes = factor(mes,c("09","10","11","12","01","02","03", "04", "05"))) %>%
+  ggplot(aes(x=mes,
+             y = acum_precip,group = 1)) +
+  geom_point()+
+  geom_line()+
+  facet_grid(new_year~.)
+
+
+met %>%
+  group_by(new_year) %>%
+  summarise(acum_precip = sum(Hu10Precip, na.rm = TRUE)) %>%
+  ggplot(aes(x=new_year,
+             y = acum_precip,group = 1)) +
+  geom_point()+
+  geom_line()
 
 #box plot radiacion 
 ggplot(data = met, aes(x = new_year, y =  Hu10Rad)) + 

### 2023-02-06 script/Model_Year_2.R
plot_model

@@ -137,6 +137,7 @@ summary(mod4_to)
 car::Anova(mod4_to, type="III")
 
 plot_model(mod4_to, type = "int", show.data = F)
+plot_model(mod4_to, type="pred")
 
 
 #getting effects for the two variables

### 2023-02-06 Manuscript/Manuscript.Rmd
edit

@@
     In contrast, the stability of the plant reproductive success is not related to the stability of the visitation rate.
-    A year by year analysis revels that plants are unlikely to be limited by pollinator abundances except in specific years with [extreme low levels of pollinator activity](esto es así Molaria).
+    A year by year analysis revels that plants are unlikely to be limited by pollinator abundances except in specific years.
+[extreme low levels of pollinator activity](esto es así Molaria- esto no podemos asegurarlo, al mirar la riqueza y tasa de visitas en los diferentes años es bastante similar)
 
@@
 Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134) (Fig 2A)](Virginia me ha comentado en reportar el R2 de los modelos pero al tratarse de modelos mixtos tendriamos que poner el marginal o el condicional.He revisado articulos que utilizan estos modleos y normalmente no ponen R2.
-Lo incluyo??), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063) (Fig 2B).
-We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005) (Fig 2C).
-Furthermore, we observed one data point has a high leverage on the stability analysis (*C.crispus*, Fig 2A-B), when we remove this point the tendency of asynchrony is  weaker but still positive (0.968 ± 0.745).
+There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)](Virginia me ha comentado en reportar el R2 de los modelos pero al tratarse de modelos mixtos tendriamos que poner el marginal o el condicional.He revisado articulos que utilizan estos modleos y normalmente no ponen R2.
+Lo incluyo??), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
+We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
+Furthermore, we observed one data point has a high leverage on the stability analysis (*C.crispus*, Fig 2A-B), when we remove this point, although the relationship is not significant, the tendency is still positive (0.968 ± 0.745; *p* = 0.215).
 
@@
 Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
-When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611) (Fig 3A).
-However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959) (Fig 3B).Although this tendency is influenced by a high value in the stability of seed number of *H.
-halimifolium* (Fig 3B) since when we removed this point the relationship disappears (0.561 ± 0.535).
+When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
+However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).Although this tendency is influenced by a high value in the stability of seed number of *H.
+halimifolium* (Fig 3B) since when we removed this point the relationship disappears (0.561 ± 0.535; *p* = 0.306).
 
@@
 
-When we analysed whether the variability of pollinator richness and visitation rate across years affected to the reproductive success of plants, we found that both year and interaction of pollinator richness and visitation rate with year affected on fruit proportion (richness interaction with year: $\chi 2$ =  28.976, df = 4, *p* = \<0.0001; visitation rate interaction with year: $\chi 2$ =  40.691, df = 4, *p* = \<0.0001)
+For analyses whether the variability of pollinator richness and visitation rate across years affected to the reproductive success of plants we employed total plant species sampled.
+When we analysed the fruit proportion, we found that the interaction between year and pollinator richness, and year and visitation rate affected the fruit proportion (richness and year: $\chi 2$ =  28.976, df = 4, *p* = \<0.0001; visitation rate and year: $\chi 2$ =  40.691, df = 4, *p* = \<0.0001).
+Furthermore, we observed a significant effect of year by itself, not so of pollinator richness or visitation rate.
 Although we observed a general saturation of the proportion of fruits developed with most species consistently over 80% of fruit set, in years like 2017 we found that a greater richness and visitation rate increased the fruit proportion.
@@
 However in 2018, the relationship between richness and fruit proportion was negative (Fig 3).
-[esto requiere un poco más de story telling.
-Por ejemplo, estos años son años altos o bajos en polinizadores?]
+[esto requiere un poco más de story telling.Por ejemplo, estos años son años altos o bajos en polinizadores?](con los datos que tenemos la riqueza y la tasa de visitas es similar en los diferentes años.
+Tambien he mirado datos meteorologicos descargados de la estacion de Almonte-precipitacion, radiacion, humedad y temperatura,y no parace que haya diferencias entre años)
 
-For the seed number, we not found the interaction effect to pollinator richness (p = 0.628), however we found a marginal significant interaction between visitation rate and year (p = 0.058).
+For the seed number, we found an effect of year in both models in addition to the interaction between visitation rate and year ($\chi 2$ =  9.113, df = 4, *p* = 0.058) but not the interaction between pollinator richness and year ($\chi 2$ =  2.592, df = 4, *p* = 0.628).
 We observed that a higher visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).
-[idem, p-values ahora?]
 
@@
 However, contrary to expectations, we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
-This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with lower pollinator abundances.
-However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years [seria ideal decir quales...
+This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with [lower pollinator abundances.](quizas decir lower richness and visitation rate??)
+However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.[seria ideal decir quales...
 los que tienen poco polinizador?
-Los secos, quizas?]
-the relationship between pollinator activity and plant's reproductive output kicks in as important.
+Los secos, quizas?](los años no tienen menor actividad ni riqueza de polinizadores, tampoco son los años mas secos, no se ven diferencias en precipitacion, temperatura, humedad o radiacion)
 When and where pollinators are limiting is the key question then.
@@
 A first clear outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
-This stability--asynchrony relationship has been found by different theoretical and empirical studies (de Mazancourt et al., 2013; Blüthgen et al., 2016; Lepš et al., 2018; Sasaki et al., 2019; Valencia et al, 2020, Kigel et al 2021).
-For example, Lázaro et al.(2022) also found that plants or pollinators?
-temporal or spatial?
-asynchrony is an important driver of stability for for plants, pollinators and their interactions.
+This stability-asynchrony relationship has been found by different theoretical and empirical studies [@DeMazancourt2013; @Bluthgen2016; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021].
+For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities being more temporal stable.
 [The fact that species asynchrony increases the temporal stability of the visitation rate is likely because a decrease in the abundance of one pollinator species is compensated by an increase of the abundance of another.](escribir%20mejor%20la%20frase)

### 2023-02-13 Manuscript/Manuscript.Rmd
edit discussion

@@
 the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
-The degree of asynchrony in species abundance fluctuations is also a stabilizing mechanisms.
+Species asynchrony represents the intrinsic differences in species response to disturbances and natural fluctuations [@Loreau2013] which has been suggested as a key driver for community temporal stability [@Loreau2008].
 In this sense, higher levels of asynchrony stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018].
-Species asynchrony has been found to be a key factor driving positive relationships between diversity and stability [@Loreau2008;@Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016;@Huang2020].
+Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008;@Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016;@Huang2020].
 Other studies have indicated that temporal stability of the dominant species or asynchrony among these dominant species is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020].
@@
 While drivers of temporal stability have been well study in plant communities [@Ruijven2007; @Gross2014; @Craven2018; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021], relatively few studies have evaluated how this same drivers can affect community stability in mobile organisms such as pollinators [@Ebeling2008; @Senapathi2021; @Lazaro2022].
-A first clear outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
+A first outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
 This stability-asynchrony relationship has been found by different theoretical and empirical studies [@DeMazancourt2013; @Bluthgen2016; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021].
 For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities being more temporal stable.
-[The fact that species asynchrony increases the temporal stability of the visitation rate is likely because a decrease in the abundance of one pollinator species is compensated by an increase of the abundance of another.](escribir%20mejor%20la%20frase)
-[mirate los appaers de Winfree sobre esto que lo explica muy bien y explica mecanismos] On the other hand, species richness is considered one of the strongest drivers of community stability [in plants?]
-(Tilman et al., 2006; de Mazancourt et al., 2013; Hallett et al., 2014), although Valencia et al.(2020) have reported that this relation is not nearly as strong [where?].
-Pollinator studies have observed a positive relationship between richness and stability of what?
-in crops??
-(Ebeling et al 2008; Senapathi et al 2021), however, our results show that richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly.
-[This most likely reflects niche variation among species that affect their relative performance over time in a temporally variable environment (Yachi & Loreau,1999; Gross et al., 2014; Craven et al 2018).](??)
+In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species, density compensation (Winfree & Kremen, 2009;Mukherjee et al 2019); or also in response to the same environmental changes, response diversity (Walker et al.
+1999; Winfree 2013).[aunque nosotros no sabemos si estos cambios son debido a perturbaciones ambientales, We believe it is important to test the degree to which these stabilizing mechanisms are at work.](Quizas añadir algo asi??)
 
-Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems [right?]
+On the other hand, species richness is considered one of the strongest drivers of community stability in plants (Tilman et al., 2006; Hallett et al., 2014), although Valencia et al.
+(2020), analyzing a large number of plant community datasets, have reported that this relationship is not as strong.
+Pollinator studies, carried out in crop systems, have observed a positive relationship between species richness and stability of floral visits (Ebeling et al 2008) or stability of abundance and richness (Senapathi et al 2021).
+However, our results show that pollinator richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly.
+Species richness may increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability (Craven et al., 2018; McCann, 2000; Yachi & Loreau, 1999).
+
+Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems
 (Garibaldi et al.
@@
 In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate (Garibaldi et al.
-2011, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship or even observed a negative relationship between seed number stability and visitation rate stability.
+2011, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship.
 

### 2023-03-01 Manuscript/Manuscript.Rmd
Discussion

@@
 (Garibaldi et al.
-2011, Lázaro and Alomar 2019, Hünicken et al 2021, Bishop et al 2022).The majority of these studies were focused on crops, however, to our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
+2011, Lázaro and Alomar 2019, Hünicken et al 2021, Bishop et al 2022).To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
 In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate (Garibaldi et al.
 2011, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship.
+
+We observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, even if there is a saturation of the proportion of fruits in most of the plant species.
+As the number of pollinator visits received by a plant increases from zero, the reproductive success of the plant is expected to rise initially but then to level off or possibly decline (Young 1988, Young and Young 1992).
+Bees can remove 70–80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits.
+Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion (Thomson 2001).
+
+NOTA: the plants studied are totally or partially self-incompatible plant species that depend on pollinators to maximize their reproduction (Magrach et al 2022)
 

### 2023-03-09 Manuscript/Manuscript.Rmd
Discussion

@@
 
-We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites in a minimum of two years per site [(show mean sites / years per plant).]()
+We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites in a minimum of two years per site.
 The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
@@
 ladanifer* and *C.
-salviifolius* showed a negative relationships wile *H.
+salviifolius* showed a negative relationships while *H.
 halimifolium* and *L.
@@
 (Garibaldi et al.
-2011, Lázaro and Alomar 2019, Hünicken et al 2021, Bishop et al 2022).To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
+2011, 2013, Lázaro and Alomar 2019, Hünicken et al 2021, Bishop et al 2022).To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
 In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate (Garibaldi et al.
-2011, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship.
+2011, 2013, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship.
 
@@
 Bees can remove 70–80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits.
-Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion (Thomson 2001).
+Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion (Thomson 2001).Even so, in certain years, the pollinator activity (visitation rate and richness) increases the fruit proportion.
+
+One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, although this has not been directly measured in the plots.
+These factors can mediate pollination through impacts on pollinator densities (Steffan-Dewenter and Westphal 2008; Williams et al.
+2015), foraging dynamics (Kunin and Iwasa 1996; Kunin 1993), visitation rates (Van Nuland et al.
+2013, Veddeler et al.
+2006), and pollen deposition (Lortie and Aarssen 1999; Evans et al.
+2017).When high-resource patches recruit more foragers to a site, increase visits per plant (concentration effect)(Kunin and Iwasa 1996; Totland and Matthews 1996), which has implications for plant reproductive success (Blaauw and Isaacs 2014; Cohen et al 2021).
+Furthermore, some plant species increase pollinator visits to the coflowering plant, which subsequently contributes to the reproductive success of neighbouring individuals (Schemske 1981; Moeller 2004; Ghazoul 2006).
+
+Another possible explanation to this might be difference in abiotic factors between years??
 

### 2023-03-13 Manuscript/Manuscript.Rmd
Discussion

--- 2023-02-13 Manuscript/Manuscript.Rmd
@@
 For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities being more temporal stable.
-In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species, density compensation (Winfree & Kremen, 2009;Mukherjee et al 2019); or also in response to the same environmental changes, response diversity (Walker et al.
-1999; Winfree 2013).[aunque nosotros no sabemos si estos cambios son debido a perturbaciones ambientales, We believe it is important to test the degree to which these stabilizing mechanisms are at work.](Quizas añadir algo asi??)
+In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species, density compensation [@Winfree2009a; @Mukherjee2019]; or also in response to the same environmental changes, response diversity [@Walker99; @Winfree2013].[Aunque nosotros no sabemos si estos cambios son debido a perturbaciones ambientales, We believe it is important to test the degree to which these stabilizing mechanisms are at work.](Quizas añadir algo asi??)
 
-On the other hand, species richness is considered one of the strongest drivers of community stability in plants (Tilman et al., 2006; Hallett et al., 2014), although Valencia et al.
+On the other hand, species richness is considered one of the strongest drivers of community stability in plants [@Tilman2006; @Hallett2014], although Valencia et al.
 (2020), analyzing a large number of plant community datasets, have reported that this relationship is not as strong.
-Pollinator studies, carried out in crop systems, have observed a positive relationship between species richness and stability of floral visits (Ebeling et al 2008) or stability of abundance and richness (Senapathi et al 2021).
+Pollinator studies, carried out in crop systems, have observed a positive relationship between species richness and stability of floral visits [@Ebeling2008] or stability of abundance and richness [@Senapathi2021].
 However, our results show that pollinator richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly.
-Species richness may increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability (Craven et al., 2018; McCann, 2000; Yachi & Loreau, 1999).
+Species richness may increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999].
 
-Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems
-(Garibaldi et al.
-2011, Lázaro and Alomar 2019, Hünicken et al 2021, Bishop et al 2022).The majority of these studies were focused on crops, however, to our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
-In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate (Garibaldi et al.
-2011, Hünicken et al 2021), however in our study system (wild plants), we did not find this relationship.
+Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems [@Garibaldi2011; @Garibaldi2013; @Lazaro2019; @Hunicken2021].
+To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
+In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate [@Garibaldi2011; @Garibaldi2013; @Hunicken2021], although in our study system (wild plants), we did not find this relationship.
+However, we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, even if there is a saturation of the proportion of fruits in most of the plant species analysed.
+As the number of pollinator visits received by a plant increases from zero, the reproductive success of the plant is expected to rise initially but then to level off or possibly decline [@Young1992; @Morris2010].
+Bees can remove 70–80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits.
+Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion [@Thomson2001].
+Even so, in certain years, the pollinator activity (visitation rate and richness) increases the fruit proportion.
+One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, [although we have not measured this directly in the plots](quiero decir que nosotros no sabemos si esos años los plots tenian mas abundancia y diversidad de flores, nosotros tenemos las flores de las especies analizadas pero no del resto).
+These factors can mediate pollination through impacts on pollinator densities [@Steffan-Dewenter2008a; @Williams2015], foraging dynamics [@Kunin1996], visitation rates [@VanNuland2013; @Veddeler2006], and pollen deposition [@Lortie1999; @Evans2017].
+The concentration effect, which occurs when foragers visit a location in greater numbers due to high resource availability [@Kunin1996; @Totland1998], has an impact on the reproductive success of plants [@Blaauw2014; @Cohen2021].
+Furthermore, some plant species increase pollinator visits to the coflowering plant, which subsequently contributes to the reproductive success of neighbouring individuals [@Schemske1981; @Moeller2004; @Ghazoul2006].
+Another possible explanation to this might be the variations in abiotic factors.
+Since the weather conditions can vary significantly between years, the abundance of pollinators during the flowering season of a plant can show annual variations, which may have an impact on the plant reproductive success [@Vicens2000; @Ivey2003].
+In addition, the environmental conditions also affect to host plants.
+For instance,  the variation of temperature conditions lead to alterations in nectar production, composition and concentration [@Pacini2003], which can affect to the pollinator activity.
 

### 2023-03-15 Manuscript/Manuscript.Rmd
Discussion

@@
 Even so, in certain years, the pollinator activity (visitation rate and richness) increases the fruit proportion.
-One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, [although we have not measured this directly in the plots](quiero decir que nosotros no sabemos si esos años los plots tenian mas abundancia y diversidad de flores, nosotros tenemos las flores de las especies analizadas pero no del resto).
+One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, [although we have not measured this directly in the plots](quiero decir que nosotros no sabemos si esos años los plots tenian mas abundancia y diversidad de flores, recursos disponibles, nosotros tenemos las flores de las especies analizadas pero no del resto).
 These factors can mediate pollination through impacts on pollinator densities [@Steffan-Dewenter2008a; @Williams2015], foraging dynamics [@Kunin1996], visitation rates [@VanNuland2013; @Veddeler2006], and pollen deposition [@Lortie1999; @Evans2017].
@@
 For instance,  the variation of temperature conditions lead to alterations in nectar production, composition and concentration [@Pacini2003], which can affect to the pollinator activity.
+Although we have not taken these factors into account in our study, we believe it is important to include them in order to better understand the relationships between pollinators and plant reproductive success over time.
+
+In summary, our study highlights the importance of pollinator species' asynchrony in maintaining the temporal stability of these communities in natural environments.
+However, this stability did not contribute to the stability of the function.
+In this sense, we believe that further studies are needed to better understand these mechanisms in natural communities by assessing the reproductive success of a wider variety of plant species.
+The variations seen between years suggest that in our study system, plant reproduction is not typically limited by pollinators.
+However in certain years the relationship between pollinator activity and plant reproductive success is important.
+This study contributes to understanding the mechanisms driving the temporal stability of pollinator communities in natural systems and how the relationships between pollinators and plant reproductive success may vary from year to year.
 

### 2023-04-20 Manuscript/Manuscript.Rmd
Second round finished. Looks amaizing!

--- 2023-03-13 Manuscript/Manuscript.Rmd
@@
 ---
-title: "Stability of flower visitation rate over time is driven by asynchrony of pollinator abundances but does not determine the stability of plant reproductive success."
-author: "Estefanía Tobajas, Virginia Domínguez-García, Francisco P. Molina, Ignasi Bartomeus"
+title: "The temporal stability in flower visitation rates is driven by the asynchrony of pollinator abundances but does not necesarely explain plant reproductive success stability."
+author: "Estefanía Tobajas^1, Virginia Domínguez-García^1, Francisco P. Molina^1, Ignasi Bartomeus^1"
 date: '2022-10-26'
@@
 
+\^1 Estación Biológica de Doñana (EBD-CSIC).
+Sevilla, Spain.
+
 # Abstract
@@
 1.
-The stability of ecological communities over time, often quantified using its aggregated abundance or biomass, is mainly influenced by species richness and the asynchrony of the species fluctuations.
-    However, the relation with the stability of ecosystem functioning provided by this community is less explored, specially for functions involving several trophic levels such as plant pollination.
+The stability of ecological communities over time, often quantified using its aggregated abundance or biomass, is though to be influenced by species richness and the asynchrony of species abundance fluctuations.
+    However, the relation between community stability and the stability of the ecosystem functioning provided by this community has been little explored, specially for functions involving several trophic levels such as plant pollination.
     Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions provided is important for predicting the resilience of communities to changes in biodiversity.
@@
 2.
-Using a 5-year dataset across 13 Mediterranean shrub patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and plants reproductive success.
+Using a 5-year dataset across 13 Mediterranean shrublands and X plant species, we assessed the effect of pollinator richness and asynchrony as drivers of the stability of plant's visitation rate and plants reproductive success.
     In addition, we analyzed whether the effects of species richness and visitation rate on plant reproduction success were consistent among years.
 
-3.  The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances but not by the pollinator richness.
-    In contrast, the stability of the plant reproductive success is not related to the stability of the visitation rate.
-    A year by year analysis revels that plants are unlikely to be limited by pollinator abundances except in specific years.
-[extreme low levels of pollinator activity](esto es así Molaria- esto no podemos asegurarlo, al mirar la riqueza y tasa de visitas en los diferentes años es bastante similar)
+3.
+The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances but the effect of species richness is only indirect, as richer communities also tend to show more asynchronous populations.
+    In contrast, the stability of the plant reproductive success is not related to the stability of its pollinator visitation rates.
+    A year by year analysis revels that in the studied system plants are unlikely to be limited by pollinator abundances except in specific years, blurring any potential effect of visitation rates stability on the stability of reproductive success.
 
-4.  CONCLUSION
+4.  We highlight the importance of maintaining a redundancy of pollinators that visit the same plant species, given that its presence can buffer from pollinators temporal fluctuations.
+    This is particularly important for pollinators with contsarting responses to environmental fluctuations, as this creates the needed asynchrony of their populations to guarantee stable levels of flower visitation rates.
+    However, we warn that more complex ecosystem functions such as reproductive success, which not only depends on pollinators, but on plant competition or resource availability, might be decoupled from first order ecosystem functions (i.e.
+visitation rates and pollen deposition) when pollination is not a limiting factor.
 
@@
 Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
-The temporal stability of community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
+The temporal stability of a community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
 A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e.
@@
 Species asynchrony represents the intrinsic differences in species response to disturbances and natural fluctuations [@Loreau2013] which has been suggested as a key driver for community temporal stability [@Loreau2008].
-In this sense, higher levels of asynchrony stabilize the community [@Ruijven2007; @Bluthgen2016; @Craven2018].
-Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008;@Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016;@Huang2020].
+In this sense, higher levels of species asynchrony stabilize the overall community dynamics [@Ruijven2007; @Bluthgen2016; @Craven2018].
+Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008; @Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016; @Huang2020].
 Other studies have indicated that temporal stability of the dominant species or asynchrony among these dominant species is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020].
@@
 Since the reproductive success of most plant species highly depends on pollination by animals [@Ollerton2011], the stability of pollinator communities may increase the stability of plant reproductive success.
-A greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementary in service provision arising from variation of pollinator effectiveness across space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013].
-For example, pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] and consequently may provide pollination services at different times of the day or of the season.
-While some studies report that sites with higher visitation rates show higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
-Interestingly, studies looking at pollen limitation show that sites with higher visitation rates show no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant [Fig.
+Evidence emerging from single-years studies suggest that different factors such as species richness and abundance might be important for muti-year stability too.
+For example, a greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementary in service provision arising from variation of pollinator effectiveness across space and time of the day [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013; @Magrach2021].
+For example, pollinator species may exhibit different ranges of daily temporal activity [@Pisanty2016; @Rader2016, @zaragoza-trello2023] and consequently may provide pollination services at different times of the day or of the season.
+In addition, higher overall visitation rates are often assumed to insure reproductive success.
+However, while some studies report that higher visitation rates are correlated with higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017, @vázquez2005], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
+Interestingly, studies looking at pollen limitation show that higher visitation rates are often associated with no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant [Fig.
 1; @Cosacov2008; @Williams2013].
-However, the occurrence and magnitude of pollen limitation can vary among years for individual populations [@Burd1994; @Ashman2004], primarily because of variation in pollinator service [@Aizen2007].
+However, the occurrence and magnitude of pollen limitation can vary among years for individual populations [@Burd1994; @Ashman2004], primarily because of variation in pollinator service delivery [@Aizen2007].
+All this lines of evidence suggest that results found for single year studies should scale up to muti-year stability studies [CITAR GARIBALDI Y SENADAPATY CRFOP STUDIES], but evidence is mostly lacking for natural plant-pollinator systems.
 
 ```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 8,fig.width=10,out.width="60%",fig.align='center', fig.cap =" 1.
-Conceptual figure showing the general relationship between visitation rate of pollinators and plant reproductive success to different species richness.
-As the number of visits from pollinators increases, the plant reproductive success is expected to increase until than above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success."}
+Conceptual figure showing the general relationship between visitation rate of pollinators and plant reproductive success to different species richness (R1, R2, ...).
+As the number of visits (V1, V2, ...) from pollinators increases, the plant reproductive success is expected to increase until than above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success."}
 library(ggplot2)
 library(patchwork)
+
+####IB: ESTEFANIA, necesitamos un A y B en plots de abajo, para que la gente los reconozca.
+EN esos paneles yo escribiria Repreocution y Visitation /Richness entro.
+Y los paneles A y B necesitan explicación en la leyenda, de hecho, yo creo que ahora estan girados...
+o eso o estoy espeso.
+Lo hablamos por video.
 
@@
 
-Here, [we use a 5-year dataset collected for a total of 12 plant species across 13 Mediterranean woodland patches but to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates we use the 5 most represented plant species.](no se si asi se entendera que tenemos un total de 12 especies pero que para la estabilidad solo empleamos 5)
+Here, we use a 5-year dataset collected for a total of 12 plant species across 13 Mediterranean shrubland sites.
+However, to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates we only use the 5 most represented plant species across years and sites.
 Further, we evaluate whether more stable pollinator communities foster a more stable plant reproductive success along years, measuring both the stability of fruit and seed set.
 We expect that the stability of visitation rates will increase with higher richness and asynchrony of pollinators.
-In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rate.
-However, given the lack of a clear relationship between pollinator and plant reproductive output stability, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.
+In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rates.
+However, given the lack of a clear relationship between pollinator and plant reproductive output stability in our dataset, we further analyzed the variability on the yearly effect of pollinator richness and visitation rates on the reproductive success of the plants.
 
-# Material and method
+# Material and methods
 
@@
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
-For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed and the number of seeds per fruit in a subsample of [3 fruits.](en algunos casos solo habia contado para dos frutos pero la mayoria son 3)
+For each plant individual, we counted the total number of flowers observed in each survey and we recorded the number of fruits developed / aborted and the number of seeds per fruit in a subsample of 3 fruits at the end of the season.
 Focal observations had a duration of five minutes per individual in 2015-2016 and three minutes from 2017 to 2019.
-Hence, for each plant individual, the sampling effort was standardized in number of visits per flower per minute.
-To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time observation multiplied by number of survey per year).
-Pollinator richness is calculated as the number of pollinator species observed visiting the plant, fruit set as the proportion of fruits developed, and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.
+Hence, for each plant individual, the sampling effort was standardized to the number of visits per flower per minute.
+To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time of each observation multiplied by number of survey rounds per year).
+Pollinator richness is calculated as the number of different pollinator species observed visiting the plant over all rounds, fruit set as the proportion of fruits developed (developed / aborted+developed), and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.
 
@@
 
-We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites in a minimum of two years per site.
+We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites (mean = X sites) in a minimum of two years per site (mean = X years per plant).
 The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
-To examine the role of richness and synchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
-The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:
-$$
+This is an adequate index given that in our dataset, as in most ecological studies, the mean and the variance scale with each other.
+To examine the role of richness and asynchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate pollinator richness as the total number of diferent pollinator species that visit each plant species in each plot.
+The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as: $$
 \begingroup\Large
@@
 $$ where ${\sigma_{x_T}^2}$ is the variance of the community abundance of each plot and ${\sigma_{x_i}}$ is the standard deviation of species i abundance in a community with S species.
+[ESTEFANIA: Abundance = numero individuos, visitation rate = visitas hechas por esos individuos o usas visitation rate como proxy de abundancias.
+Si es lo primero, yo especificaria.
+"Note that we calulated abundance as the number of individuals observed, while visitation rate is the sum of their visits" o algo así, quizás tambien en metodos más arriba, mejor ser redundante, sino, o lo dejas así, o clarificas que we use visitation rates as proxies of abundances].
 This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous [@Loreau2008].
 Finally, we express asynchrony as $1-\phi$.
-We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot.
+We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot following the same methods.
 
@@
 
-To discover the main drivers of visitation rate stability on the five plant species studied, we carried out two linear mixed models using as response variable the stability of visitation rate and as explanatory variables pollinator asynchrony and richness, respectively.
+To evaluate the main drivers of visitation rate stability on the five plant species studied, we carried out two linear mixed models using as response variable the stability of visitation rate and as explanatory variables pollinator asynchrony and richness, respectively.
 Similarly, linear mixed model was used to test the influence of pollinator richness on asynchrony of pollinator species abundances.
 In all cases, site and plant species were included as random factor.
-For a deeper understanding of the processes stabilizing visitation rate, we also analyzed the response for each plant species separately.
+For a deeper understanding of the processes, we also analyzed the response for each plant species separately.
 
-To study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or the stability of seed number and as explanatory variable the visitation rate stability.
-Site and plant species were included as factor random.
+To study whether the stability of pollinator visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or the stability of seed number and as explanatory variable the visitation rate stability.
+Site and plant species were included as random factors.
 
 Finally, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.
-For this we employed all plant species sampled and we analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using binomial generalized linear mixed model, and on the number of seeds employing linear mixed model.
-*P* values were obtained using the type III Anova (package: car)
+For this we employed all plant species sampled and we analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using a binomial generalized linear mixed model, and on the number of seeds employing a linear mixed model.
+*P* values were obtained using the type III Anova (package: car CITAR) as recommended for tetsing interactions.
 The number of seeds per fruit was centered and scaled per plant species to allow meaningful comparisons across species.
@@
 Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)](Virginia me ha comentado en reportar el R2 de los modelos pero al tratarse de modelos mixtos tendriamos que poner el marginal o el condicional.He revisado articulos que utilizan estos modleos y normalmente no ponen R2.
-Lo incluyo??), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
-We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
-Furthermore, we observed one data point has a high leverage on the stability analysis (*C.crispus*, Fig 2A-B), when we remove this point, although the relationship is not significant, the tendency is still positive (0.968 ± 0.745; *p* = 0.215).
+There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)](Virginia%20me%20ha%20comentado%20en%20reportar%20el%20R2%20de%20los%20modelos%20pero%20al%20tratarse%20de%20modelos%20mixtos%20tendriamos%20que%20poner%20el%20marginal%20o%20el%20condicional.He%20revisado%20articulos%20que%20utilizan%20estos%20modleos%20y%20normalmente%20no%20ponen%20R2.%20Lo%20incluyo??) [IB: por mi esta bien así], whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
+However, we also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
+We observed one data point has a high leverage on the stability analysis (*C.crispus*, Fig 2A-B), when we remove this point, the slope is still positive (0.968 ± 0.745).
 
-When we analysed each plant species separately, we observed positive relationship between asynchrony of pollinators and stability of visitation rate for *C.
+When we analysed each plant species separately, we observed a positive relationship between asynchrony of pollinators and stability of visitation rate for *C.
 crispus*, *H.
 halimifoliun* and *L.
-pedunculata*, weak relationship for *C.
+pedunculata*, a weak positive relationship for *C.
 salviifolious* and a weak negative relationship for *C.ladanifer*.
@@
 Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
-When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
-However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).Although this tendency is influenced by a high value in the stability of seed number of *H.
-halimifolium* (Fig 3B) since when we removed this point the relationship disappears (0.561 ± 0.535; *p* = 0.306).
+When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find any relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
+However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).
+Although this tendency is influenced by a high value in the stability of seed number of *H.
+halimifolium* (Fig 3B) since when we removed this point the relationship disappears and if anything, show a positive slope (0.561 ± 0.535).
+[quito los p val de los tests sin outlyers, para no caer en multiple testing]
 
@@
 
-##  The effect of pollinators on reproductive success depends on the year
+## Yearly variability on the effect of pollinators on reproductive success
 
-For analyses whether the variability of pollinator richness and visitation rate across years affected to the reproductive success of plants we employed total plant species sampled.
-When we analysed the fruit proportion, we found that the interaction between year and pollinator richness, and year and visitation rate affected the fruit proportion (richness and year: $\chi 2$ =  28.976, df = 4, *p* = \<0.0001; visitation rate and year: $\chi 2$ =  40.691, df = 4, *p* = \<0.0001).
-Furthermore, we observed a significant effect of year by itself, not so of pollinator richness or visitation rate.
-Although we observed a general saturation of the proportion of fruits developed with most species consistently over 80% of fruit set, in years like 2017 we found that a greater richness and visitation rate increased the fruit proportion.
+To analyse whether the variability of pollinator richness and visitation rate across years affected the reproductive success of plants we used all plant species sampled.
+When we analysed the variable fruit proportion, we found that the interactions between year and pollinator richness, and year and visitation rate affected the fruit proportion (richness x year: $\chi 2$ = 28.976, df = 4, *p* = \<0.0001; visitation rate x year: $\chi 2$ = 40.691, df = 4, *p* = \<0.0001).
+Furthermore, we observed a significant effect of year by itself, but not so of pollinator richness or visitation rate.
+Note that we observed a general saturation of the proportion of fruits developed with most species consistently showing over 80% of fruit set, however, in years like 2017, for which the hydrological year was very dry, we found that a greater richness and visitation rate increased the fruit proportion.
 We also observed a positive relationship between richness and fruit proportion in 2019.
-However in 2018, the relationship between richness and fruit proportion was negative (Fig 3).
-[esto requiere un poco más de story telling.Por ejemplo, estos años son años altos o bajos en polinizadores?](con los datos que tenemos la riqueza y la tasa de visitas es similar en los diferentes años.
-Tambien he mirado datos meteorologicos descargados de la estacion de Almonte-precipitacion, radiacion, humedad y temperatura,y no parace que haya diferencias entre años)
+However in 2018, an specially wet year, the relationship between richness and fruit proportion was negative (Fig 3).
 
-For the seed number, we found an effect of year in both models in addition to the interaction between visitation rate and year ($\chi 2$ =  9.113, df = 4, *p* = 0.058) but not the interaction between pollinator richness and year ($\chi 2$ =  2.592, df = 4, *p* = 0.628).
+For the seed number analysis, we found an effect of year in both models in addition to the interaction between visitation rate and year ($\chi 2$ = 9.113, df = 4, *p* = 0.058) but not the interaction between pollinator richness and year ($\chi 2$ = 2.592, df = 4, *p* = 0.628).
 We observed that a higher visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).
@@
 For the visualization purpose, we omit in the visitation rate (x-axis) the values outside of the 95\\%."}
+
+##IB: Yo cortaba todos los plots a zero (o a -1) El de arriba tambien.
 
@@
 However, contrary to expectations, we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
-This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with [lower pollinator abundances.](quizas decir lower richness and visitation rate??)
-However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.[seria ideal decir quales...
-los que tienen poco polinizador?
-Los secos, quizas?](los años no tienen menor actividad ni riqueza de polinizadores, tampoco son los años mas secos, no se ven diferencias en precipitacion, temperatura, humedad o radiacion)
+This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with [lower pollinator abundances.](quizas%20decir%20lower%20richness%20and%20visitation%20rate??)
+However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.
 When and where pollinators are limiting is the key question then.
-[esta frase a lo mejor puede ser una conclusing sentence del paper, por ahora la dejo aquí]
 
@@
 This stability-asynchrony relationship has been found by different theoretical and empirical studies [@DeMazancourt2013; @Bluthgen2016; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021].
-For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities being more temporal stable.
-In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species, density compensation [@Winfree2009a; @Mukherjee2019]; or also in response to the same environmental changes, response diversity [@Walker99; @Winfree2013].[Aunque nosotros no sabemos si estos cambios son debido a perturbaciones ambientales, We believe it is important to test the degree to which these stabilizing mechanisms are at work.](Quizas añadir algo asi??)
+For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities are more temporally stable.
+In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species (i.e.
+density compensation [@Winfree2009a; @Mukherjee2019]); or also when they respond differently to the same environmental changes (i.e.
+response diversity [@Walker99; @Winfree2013]).
+While we do not evaluate the causes of this response diversity, we do show that the asynchronous fluctuating species are redundant in its visitation patterns, a known requisite for response diversity to matter for ecosystem functioning stability [@stavert2017].
 
@@
 (2020), analyzing a large number of plant community datasets, have reported that this relationship is not as strong.
-Pollinator studies, carried out in crop systems, have observed a positive relationship between species richness and stability of floral visits [@Ebeling2008] or stability of abundance and richness [@Senapathi2021].
-However, our results show that pollinator richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly.
-Species richness may increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999].
+Pollinator studies carried out in crop systems have observed a positive relationship between species richness and stability of floral visits [@Ebeling2008] or the stability of pollinator abundance [@Senapathi2021].
+However, our results show that pollinator richness effects were mostly indirect.
+Pollinator richness was positively associated with asynchrony, which positively affect the stability of visitation rate, but not associated directly with more stable visitation rates.
+Species richness is suggested to increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999], but the asynchrony of a few dominant species might be more relevant in pollinator systems than richness per se [ref about pollinator dominance, maighbe winfree or kleijn (the nat comm paper) has something].
 
-Despite the stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator visits frequency on pollination services, and those who did used agricultural systems [@Garibaldi2011; @Garibaldi2013; @Lazaro2019; @Hunicken2021].
+Despite temporal stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator abundances on pollination services, and those who did used agricultural systems [@Garibaldi2011; @Garibaldi2013; @Lazaro2019; @Hunicken2021].
 To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
-In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate [@Garibaldi2011; @Garibaldi2013; @Hunicken2021], although in our study system (wild plants), we did not find this relationship.
-However, we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, even if there is a saturation of the proportion of fruits in most of the plant species analysed.
-As the number of pollinator visits received by a plant increases from zero, the reproductive success of the plant is expected to rise initially but then to level off or possibly decline [@Young1992; @Morris2010].
-Bees can remove 70–80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits.
+In pollinator-dependent crops it has been observed that a greater yield stability is related to pollinator diversity and the stability of visitation rates [@Garibaldi2011; @Garibaldi2013; @Hunicken2021] but in our study system (wild plants), we did not find this relationship.
+Despite we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, for most plants and years there is a general saturation of the proportion of fruits developed, with fruitsets above 80%.
+As shown in figure 1, an initial increase in the number of pollinator visits is predicted to increase the reproductive success of the plant but as visitation rates continue to increase, its effect will level off or even decline [@Young1992; @Morris2010].
+Bees can remove 70--80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits [REF?]
+.
 Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion [@Thomson2001].
-Even so, in certain years, the pollinator activity (visitation rate and richness) increases the fruit proportion.
-One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, [although we have not measured this directly in the plots](quiero decir que nosotros no sabemos si esos años los plots tenian mas abundancia y diversidad de flores, nosotros tenemos las flores de las especies analizadas pero no del resto).
-These factors can mediate pollination through impacts on pollinator densities [@Steffan-Dewenter2008a; @Williams2015], foraging dynamics [@Kunin1996], visitation rates [@VanNuland2013; @Veddeler2006], and pollen deposition [@Lortie1999; @Evans2017].
+Several factors can mediate the shape of this relationships.
+First [Aqui has de elegir tres hipotesis y ponerlas en plan first, second, third,..., ahora queda un batiburrillo hasta el final del parrafo] through impacts on pollinator densities [@Steffan-Dewenter2008a; @Williams2015], foraging dynamics [@Kunin1996], visitation rates [@VanNuland2013; @Veddeler2006], and pollen deposition [@Lortie1999; @Evans2017].
 The concentration effect, which occurs when foragers visit a location in greater numbers due to high resource availability [@Kunin1996; @Totland1998], has an impact on the reproductive success of plants [@Blaauw2014; @Cohen2021].
@@
 In addition, the environmental conditions also affect to host plants.
-For instance,  the variation of temperature conditions lead to alterations in nectar production, composition and concentration [@Pacini2003], which can affect to the pollinator activity.
+For instance, the variation of temperature conditions lead to alterations in nectar production, composition and concentration [@Pacini2003], which can affect to the pollinator activity [hasta aquí hay que guiar al lector, resume tus opciones de por que hay variacion interanual en tres categorias una frase por categoria y listos].
+Although investigating this factors is beyond the aim of the study, future research should clarify when and where pollinators are limiting.
+For example @herbertsson2021 show in a recent meta-analysis a large variability on the effects of different pollinators on seed set, but the causes of this variability remain to be explored.
+
+In summary, our study highlights the importance of pollinator species' asynchrony in maintaining the temporal stability of their visitation rates to wild plants in natural environments.
+However, visitation rates stability did not directly contribute to the stability of the final plant reproductive success function.
+In this sense, we believe that further studies are needed to better understand these mechanisms in natural communities by assessing the reproductive success along time of a wider variety of plant species [citar aqui algun estudio a largo plazo de la reproduccion de una sola espcie de plantas Thomson tendra algo?
+(alguno de los thomsons :) no?]
+.
+The variations seen between years suggest that in our study system, plant reproduction is not typically limited by pollinators.
+However in certain years the relationship between pollinator activity and plant reproductive success is important.
+This study contributes to understanding the mechanisms driving the temporal stability of pollinator communities in natural systems and how the relationships between pollinators and plant reproductive success may vary from year to year.
 

### 2023-04-20 Manuscript/Manuscript.Rmd
.

--- 2023-03-15 Manuscript/Manuscript.Rmd
@@
 ---
-title: "Stability of flower visitation rate over time is driven by asynchrony of pollinator abundances but does not determine the stability of plant reproductive success."
-author: "Estefanía Tobajas, Virginia Domínguez-García, Francisco P. Molina, Ignasi Bartomeus"
+title: "Stability of flower visitation rate over time is driven by the asynchrony of pollinator abundances but does not determine the stability of plant reproductive success."
+author: "Estefanía Tobajas^1, Virginia Domínguez-García^1, Francisco P. Molina^1, Ignasi Bartomeus^1"
 date: '2022-10-26'
@@
 1.
-The stability of ecological communities over time, often quantified using its aggregated abundance or biomass, is mainly influenced by species richness and the asynchrony of the species fluctuations.
-    However, the relation with the stability of ecosystem functioning provided by this community is less explored, specially for functions involving several trophic levels such as plant pollination.
+The stability of ecological communities over time, often quantified using its aggregated abundance or biomass, is though to be influenced by species richness and the asynchrony of the species fluctuations.
+    However, the relation between community stability and the stability of the ecosystem functioning provided by this community is less explored, specially for functions involving several trophic levels such as plant pollination.
     Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions provided is important for predicting the resilience of communities to changes in biodiversity.
@@
 2.
-Using a 5-year dataset across 13 Mediterranean shrub patches, we assessed the effect of the richness and asynchrony of pollinators as drivers of the stability of plant's visitation rate and plants reproductive success.
+Using a 5-year dataset across 13 Mediterranean shrublands and X plant species, we assessed the effect of pollinator richness and asynchrony as drivers of the stability of plant's visitation rate and plants reproductive success.
     In addition, we analyzed whether the effects of species richness and visitation rate on plant reproduction success were consistent among years.
@@
 3.  The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances but not by the pollinator richness.
-    In contrast, the stability of the plant reproductive success is not related to the stability of the visitation rate.
+    In contrast, the stability of the plant reproductive success is not related to the stability of its pollinator visitation rates.
     A year by year analysis revels that plants are unlikely to be limited by pollinator abundances except in specific years.
-[extreme low levels of pollinator activity](esto es así Molaria- esto no podemos asegurarlo, al mirar la riqueza y tasa de visitas en los diferentes años es bastante similar)
 
-4.  CONCLUSION
+4.  We highlight the importance of maintaining a redundancy of pollinators that visit the same plant species, given that its presence can buffer from species temporal fluctuations.
+    This is particularly important for pollinators with contsarting responses to environmental fluctuations, as this creates the needed asynchrony of their populations to guarantee stable levels of flower visitation rates.
+    However, we warn that more complex ecosystem functions such as reproductive success, which not only depends on pollinators, but on plant competition or resource availability, might be decoupled from primary functions (i.e.
+visitation rates and pollen deposition) when pollination is not a limiting factor.
 
@@
 Since the reproductive success of most plant species highly depends on pollination by animals [@Ollerton2011], the stability of pollinator communities may increase the stability of plant reproductive success.
-A greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementary in service provision arising from variation of pollinator effectiveness across space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013].
-For example, pollinator species may exhibit different ranges of temporal activity [@Pisanty2016; @Rader2016] and consequently may provide pollination services at different times of the day or of the season.
-While some studies report that sites with higher visitation rates show higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
-Interestingly, studies looking at pollen limitation show that sites with higher visitation rates show no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant [Fig.
+A greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementary in service provision arising from variation of pollinator effectiveness across space and time [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013; @Magrach2021].
+For example, pollinator species may exhibit different ranges of daily temporal activity [@Pisanty2016; @Rader2016, @zaragoza-trello2023] and consequently may provide pollination services at different times of the day or of the season.
+In any case, higher overall visitation rates are often assumed to insure reproductive success.
+However, while some studies report that higher visitation rates are correlated with higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017, @vázquez2005], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
+Interestingly, studies looking at pollen limitation show that higher visitation rates are often associated with no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant [Fig.
 1; @Cosacov2008; @Williams2013].
@@
 ```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 8,fig.width=10,out.width="60%",fig.align='center', fig.cap =" 1.
-Conceptual figure showing the general relationship between visitation rate of pollinators and plant reproductive success to different species richness.
-As the number of visits from pollinators increases, the plant reproductive success is expected to increase until than above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success."}
+Conceptual figure showing the general relationship between visitation rate of pollinators and plant reproductive success to different species richness (R1, R2, ...).
+As the number of visits (V1, V2, ...) from pollinators increases, the plant reproductive success is expected to increase until than above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success."}
 library(ggplot2)
 library(patchwork)
+
+####IB: ESTEFANIA, necesitamos un A y B en plots de abajo, para que la gente los reconozca.
+EN esos paneles yo escribiria Repreocution y Visitation /Richness entro.
+Y los paneles A y B necesitan explicación en la leyenda, de hecho, yo creo que ahora estan girados...
+o eso o estoy espeso.
+Lo hablamos por video.
 
@@
 
-Here, [we use a 5-year dataset collected for a total of 12 plant species across 13 Mediterranean woodland patches but to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates we use the 5 most represented plant species.](no se si asi se entendera que tenemos un total de 12 especies pero que para la estabilidad solo empleamos 5)
+Here, we use a 5-year dataset collected for a total of 12 plant species across 13 Mediterranean shrubland sites.
+However, to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates we only use the 5 most represented plant species across years and sites.
 Further, we evaluate whether more stable pollinator communities foster a more stable plant reproductive success along years, measuring both the stability of fruit and seed set.
 We expect that the stability of visitation rates will increase with higher richness and asynchrony of pollinators.
-In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rate.
+In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rates.
 However, given the lack of a clear relationship between pollinator and plant reproductive output stability, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.
@@
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
-For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed and the number of seeds per fruit in a subsample of [3 fruits.](en algunos casos solo habia contado para dos frutos pero la mayoria son 3)
+For each plant individual, we counted the total number of flowers observed in each survey and at the end of the season, we recorded the number of fruits developed / aborted and the number of seeds per fruit in a subsample of 3 fruits.
 Focal observations had a duration of five minutes per individual in 2015-2016 and three minutes from 2017 to 2019.
-Hence, for each plant individual, the sampling effort was standardized in number of visits per flower per minute.
-To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time observation multiplied by number of survey per year).
+Hence, for each plant individual, the sampling effort was standardized to the number of visits per flower per minute.
+To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time of each observation multiplied by number of survey rounds per year).
 Pollinator richness is calculated as the number of pollinator species observed visiting the plant, fruit set as the proportion of fruits developed, and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.
@@
 The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
+This is an adequate index given that in our dataset the mean and the variance scale with each other.
 To examine the role of richness and synchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate the richness as the total number of pollinator species that visit each plant species in each plot.
-The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as:
-$$
+The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as: $$
 \begingroup\Large
@@
 
-To study whether the stability of the visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or the stability of seed number and as explanatory variable the visitation rate stability.
-Site and plant species were included as factor random.
+To study whether the stability of pollinator visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or the stability of seed number and as explanatory variable the visitation rate stability.
+Site and plant species were included as random factors.
 
 Finally, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.
-For this we employed all plant species sampled and we analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using binomial generalized linear mixed model, and on the number of seeds employing linear mixed model.
-*P* values were obtained using the type III Anova (package: car)
+For this we employed all plant species sampled and we analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using a binomial generalized linear mixed model, and on the number of seeds employing a linear mixed model.
+*P* values were obtained using the type III Anova (package: car CITAR) as recomended for tetsing interactions.
 The number of seeds per fruit was centered and scaled per plant species to allow meaningful comparisons across species.
@@
 Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)](Virginia me ha comentado en reportar el R2 de los modelos pero al tratarse de modelos mixtos tendriamos que poner el marginal o el condicional.He revisado articulos que utilizan estos modleos y normalmente no ponen R2.
-Lo incluyo??), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
+There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)](Virginia%20me%20ha%20comentado%20en%20reportar%20el%20R2%20de%20los%20modelos%20pero%20al%20tratarse%20de%20modelos%20mixtos%20tendriamos%20que%20poner%20el%20marginal%20o%20el%20condicional.He%20revisado%20articulos%20que%20utilizan%20estos%20modleos%20y%20normalmente%20no%20ponen%20R2.%20Lo%20incluyo??), whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
 We also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
@@
 When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find a clear relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
-However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).Although this tendency is influenced by a high value in the stability of seed number of *H.
+However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).
+Although this tendency is influenced by a high value in the stability of seed number of *H.
 halimifolium* (Fig 3B) since when we removed this point the relationship disappears (0.561 ± 0.535; *p* = 0.306).
@@
 
-For analyses whether the variability of pollinator richness and visitation rate across years affected to the reproductive success of plants we employed total plant species sampled.
-When we analysed the fruit proportion, we found that the interaction between year and pollinator richness, and year and visitation rate affected the fruit proportion (richness and year: $\chi 2$ =  28.976, df = 4, *p* = \<0.0001; visitation rate and year: $\chi 2$ =  40.691, df = 4, *p* = \<0.0001).
-Furthermore, we observed a significant effect of year by itself, not so of pollinator richness or visitation rate.
+To analyse whether the variability of pollinator richness and visitation rate across years affected the reproductive success of plants we used all plant species sampled.
+When we analysed the fruit proportion (set?
+unify terminology), we found that the interaction between year and pollinator richness, and year and visitation rate affected the fruit proportion (richness and year: $\chi 2$ = 28.976, df = 4, *p* = \<0.0001; visitation rate and year: $\chi 2$ = 40.691, df = 4, *p* = \<0.0001).
+Furthermore, we observed a significant effect of year by itself, but not so of pollinator richness or visitation rate.
 Although we observed a general saturation of the proportion of fruits developed with most species consistently over 80% of fruit set, in years like 2017 we found that a greater richness and visitation rate increased the fruit proportion.
@@
 However in 2018, the relationship between richness and fruit proportion was negative (Fig 3).
-[esto requiere un poco más de story telling.Por ejemplo, estos años son años altos o bajos en polinizadores?](con los datos que tenemos la riqueza y la tasa de visitas es similar en los diferentes años.
-Tambien he mirado datos meteorologicos descargados de la estacion de Almonte-precipitacion, radiacion, humedad y temperatura,y no parace que haya diferencias entre años)
+[esto requiere un poco más de story telling.Por ejemplo, estos años son años altos o bajos en polinizadores?](con%20los%20datos%20que%20tenemos%20la%20riqueza%20y%20la%20tasa%20de%20visitas%20es%20similar%20en%20los%20diferentes%20años.%20Tambien%20he%20mirado%20datos%20meteorologicos%20descargados%20de%20la%20estacion%20de%20Almonte-precipitacion,%20radiacion,%20humedad%20y%20temperatura,y%20no%20parace%20que%20haya%20diferencias%20entre%20años)
 
-For the seed number, we found an effect of year in both models in addition to the interaction between visitation rate and year ($\chi 2$ =  9.113, df = 4, *p* = 0.058) but not the interaction between pollinator richness and year ($\chi 2$ =  2.592, df = 4, *p* = 0.628).
+For the seed number analysis, we found an effect of year in both models in addition to the interaction between visitation rate and year ($\chi 2$ = 9.113, df = 4, *p* = 0.058) but not the interaction between pollinator richness and year ($\chi 2$ = 2.592, df = 4, *p* = 0.628).
 We observed that a higher visitation rate increased the seed number in 2019 (Supplementary material-Fig 2).
@@
 
-We show that pollinator's visitation rate stability increase with higher asynchrony of pollinators species abundances and that greater species richness only increase stability of visitation rate indirectly, via enhanced species asynchrony.
+We show that pollinator's visitation rate stability increase with higher asynchrony of pollinators species abundances and that greater species richness only increase stability of visitation rate indirectly, via enhanced species asynchrony [IB: esto a abstract!]
+.
 However, contrary to expectations, we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
-This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with [lower pollinator abundances.](quizas decir lower richness and visitation rate??)
+This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with [lower pollinator abundances.](quizas%20decir%20lower%20richness%20and%20visitation%20rate??)
 However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.[seria ideal decir quales...
 los que tienen poco polinizador?
-Los secos, quizas?](los años no tienen menor actividad ni riqueza de polinizadores, tampoco son los años mas secos, no se ven diferencias en precipitacion, temperatura, humedad o radiacion)
+Los secos, quizas?](los%20años%20no%20tienen%20menor%20actividad%20ni%20riqueza%20de%20polinizadores,%20tampoco%20son%20los%20años%20mas%20secos,%20no%20se%20ven%20diferencias%20en%20precipitacion,%20temperatura,%20humedad%20o%20radiacion)
 When and where pollinators are limiting is the key question then.
-[esta frase a lo mejor puede ser una conclusing sentence del paper, por ahora la dejo aquí]
 
@@
 For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities being more temporal stable.
-In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species, density compensation [@Winfree2009a; @Mukherjee2019]; or also in response to the same environmental changes, response diversity [@Walker99; @Winfree2013].[Aunque nosotros no sabemos si estos cambios son debido a perturbaciones ambientales, We believe it is important to test the degree to which these stabilizing mechanisms are at work.](Quizas añadir algo asi??)
+In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species (i.e.
+density compensation [@Winfree2009a; @Mukherjee2019]); or also when they respond differently to the same environmental changes (i.e.
+response diversity [@Walker99; @Winfree2013]).
+[Aunque nosotros no sabemos si estos cambios son debido a perturbaciones ambientales, We believe it is important to test the degree to which these stabilizing mechanisms are at work.](Quizas%20añadir%20algo%20asi??)
 
@@
 (2020), analyzing a large number of plant community datasets, have reported that this relationship is not as strong.
-Pollinator studies, carried out in crop systems, have observed a positive relationship between species richness and stability of floral visits [@Ebeling2008] or stability of abundance and richness [@Senapathi2021].
+Pollinator studies carried out in crop systems have observed a positive relationship between species richness and stability of floral visits [@Ebeling2008] or stability of abundance and richness [@Senapathi2021].
 However, our results show that pollinator richness was positively associated with asynchrony, which might positively affect the stability of visitation rate, but indirectly.
@@
 To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
-In pollinator-dependent crops have been observed a greater yield stability with the pollinator diversity and the stability of visitation rate [@Garibaldi2011; @Garibaldi2013; @Hunicken2021], although in our study system (wild plants), we did not find this relationship.
+In pollinator-dependent crops it has been observed that a greater yield stability is related to pollinator diversity and the stability of visitation rates [@Garibaldi2011; @Garibaldi2013; @Hunicken2021] but in our study system (wild plants), we did not find this relationship.
 However, we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, even if there is a saturation of the proportion of fruits in most of the plant species analysed.
 As the number of pollinator visits received by a plant increases from zero, the reproductive success of the plant is expected to rise initially but then to level off or possibly decline [@Young1992; @Morris2010].
-Bees can remove 70–80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits.
+Bees can remove 70--80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits.
 Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion [@Thomson2001].
-Even so, in certain years, the pollinator activity (visitation rate and richness) increases the fruit proportion.
-One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, [although we have not measured this directly in the plots](quiero decir que nosotros no sabemos si esos años los plots tenian mas abundancia y diversidad de flores, recursos disponibles, nosotros tenemos las flores de las especies analizadas pero no del resto).
+Even so, in certain years, the pollinator activity (visitation rate and richness) increases the fruit proportion.\
+
+One possible explanation for this is that there was greater floral diversity and abundance in the plots these years, [although we have not measured this directly in the plots](quiero%20decir%20que%20nosotros%20no%20sabemos%20si%20esos%20años%20los%20plots%20tenian%20mas%20abundancia%20y%20diversidad%20de%20flores,%20recursos%20disponibles,%20nosotros%20tenemos%20las%20flores%20de%20las%20especies%20analizadas%20pero%20no%20del%20resto).
 These factors can mediate pollination through impacts on pollinator densities [@Steffan-Dewenter2008a; @Williams2015], foraging dynamics [@Kunin1996], visitation rates [@VanNuland2013; @Veddeler2006], and pollen deposition [@Lortie1999; @Evans2017].

### 2023-05-04 Manuscript/Figures/Plot_1.R
cut y-axis in figure a and b

@@ -57,10 +57,11 @@ effe_mod_sta <-data.frame( effect("asyn_LM", mod1_sta, se = TRUE))
 #plot model of asynchrony
 p1=ggplot(effe_mod_sta, aes(asyn_LM, fit)) + geom_line(size=1)+
   geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.2, colour = "black")+
-  scale_y_continuous(limits = c(-2.5, 9.5))+labs(color='Plant species')+
+  labs(color='Plant species')+
+  coord_cartesian(ylim=c(-0.5,9.5))+
   geom_point(data = data_plant, aes(x =  asyn_LM, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.5,size=3)+
   scale_colour_brewer(palette = "Set1")+
-   theme_bw ()+
+  theme_bw ()+
   labs(x = "Asynchrony of pollinator",y="Stability of visitation rate")+
   guides(colour=guide_legend(nrow=2,byrow=TRUE))+ theme(legend.text = element_text(face="italic"))
 
@@ -76,7 +77,7 @@ effe2_mod_sta <-data.frame( effect("S_total", mod1.2_sta, se = TRUE))
 #plot model of richness
 p2=ggplot(effe2_mod_sta, aes(S_total, fit)) + geom_line(size=1,linetype = "dashed")+
   geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.1, colour = "black")+
-  scale_y_continuous(limits = c(-2.5, 9.5))+  labs(color='Plant species')+
+  scale_y_continuous(limits = c(-0.5, 9.5))+  labs(color='Plant species')+
   geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.5,size=3)+
   scale_colour_brewer(palette = "Set1")+
   theme_bw ()+

### 2023-05-04 Manuscript/Manuscript.Rmd
editando

--- 2023-04-20 Manuscript/Manuscript.Rmd
@@
 ---
-title: "The temporal stability in flower visitation rates is driven by the asynchrony of pollinator abundances but does not necesarely explain plant reproductive success stability."
+title: "The temporal stability in flower visitation rates is driven by the asynchrony of pollinator abundances but does not necessarely explain plant reproductive success stability."
 author: "Estefanía Tobajas^1, Virginia Domínguez-García^1, Francisco P. Molina^1, Ignasi Bartomeus^1"
@@
 1.
-The stability of ecological communities over time, often quantified using its aggregated abundance or biomass, is though to be influenced by species richness and the asynchrony of species abundance fluctuations.
-    However, the relation between community stability and the stability of the ecosystem functioning provided by this community has been little explored, specially for functions involving several trophic levels such as plant pollination.
+The stability of ecological communities over time, often quantified using its aggregated abundance or biomass, is thought to be influenced by species richness and the asynchrony of species abundance fluctuations.
+    However, the relationship between community stability and the stability of the ecosystem functioning provided by this community has been little explored, specially for functions involving several trophic levels such as plant pollination.
     Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions provided is important for predicting the resilience of communities to changes in biodiversity.
@@
 2.
-Using a 5-year dataset across 13 Mediterranean shrublands and X plant species, we assessed the effect of pollinator richness and asynchrony as drivers of the stability of plant's visitation rate and plants reproductive success.
+Using a 5-year dataset across 13 Mediterranean shrublands and 12 plant species, we assessed the effect of pollinator richness and asynchrony as drivers of the stability of plant's visitation rate and plants reproductive success.
     In addition, we analyzed whether the effects of species richness and visitation rate on plant reproduction success were consistent among years.
@@
 3.
-The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances but the effect of species richness is only indirect, as richer communities also tend to show more asynchronous populations.
+The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances, but the effect of species richness is only indirect, as richer communities also tend to show more asynchronous populations.
     In contrast, the stability of the plant reproductive success is not related to the stability of its pollinator visitation rates.
-    A year by year analysis revels that in the studied system plants are unlikely to be limited by pollinator abundances except in specific years, blurring any potential effect of visitation rates stability on the stability of reproductive success.
+    A year-by-year analysis reveals that in the studied system plants are unlikely to be limited by pollinator abundances except in specific years, blurring any potential effect of visitation rates stability on the stability of reproductive success.
 
 4.  We highlight the importance of maintaining a redundancy of pollinators that visit the same plant species, given that its presence can buffer from pollinators temporal fluctuations.
-    This is particularly important for pollinators with contsarting responses to environmental fluctuations, as this creates the needed asynchrony of their populations to guarantee stable levels of flower visitation rates.
-    However, we warn that more complex ecosystem functions such as reproductive success, which not only depends on pollinators, but on plant competition or resource availability, might be decoupled from first order ecosystem functions (i.e.
-visitation rates and pollen deposition) when pollination is not a limiting factor.
+    This is particularly important for pollinators with contrasting responses to environmental fluctuations, as this creates the needed asynchrony of their populations to guarantee stable levels of flower visitation rates.
+    However, we warn that more complex ecosystem functions such as reproductive success, which not only depends on pollinators but on plant competition or resource availability, might be decoupled from first order ecosystem functions (i.e., visitation rates and pollen deposition) when pollination is not a limiting factor.
 
@@
 Global environmental changes and the consequent loss of biodiversity have highlighted the need for better understanding the role of biodiversity in ecosystem function [@Hooper2005; @Lefcheck2015; @Oliver2015; @Hong2022].
-We have experimental and observational evidence that biodiversity enhances aggregated community-level properties, such as total biomass [@Cardinale2006; @Cardinale2012; @Tilman2014], but the role of biodiversity for the stability of ecosystem functioning is less explored (but see @Griffin2009; @Grman2010), specially for functions involving several trophic levels such as plant pollination [@Ebeling2008; @Winfree2009a; @Garibaldi2011; @Lazaro2022].
+We have experimental and observational evidence that biodiversity enhances aggregated community-level properties, such as total biomass [@Cardinale2006; @Cardinale2012; @Tilman2014], but the role of biodiversity for the stability of ecosystem functioning is less explored (but see @Griffin2009; @Grman2010), specially in functions involving several trophic levels such as plant pollination [@Ebeling2008; @Winfree2009a; @Garibaldi2011; @Lazaro2022].
 Globally, it is estimated that at least 78% of wild plants depend to some extent on pollination by animals [@Ollerton2011].
@@
 Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
-The temporal stability of a community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
+The temporal stability of the community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
 A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e.
@@
 In this sense, higher levels of species asynchrony stabilize the overall community dynamics [@Ruijven2007; @Bluthgen2016; @Craven2018].
-Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008; @Xu2015] or even that stability is often more strongly associated with the degree of asynchrony across species than with species richness [@Bluthgen2016; @Huang2020].
-Other studies have indicated that temporal stability of the dominant species or asynchrony among these dominant species is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020].
+Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008; @Xu2015], and often stability is more strongly associated with the degree of asynchrony across species than with species richness itself [@Bluthgen2016; @Huang2020].
+Other studies have indicated that the temporal stability of the dominant species or the asynchrony among these dominant species are important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020].
 While community temporal stability should be related to the stability of ecosystem functions and services provided by such community, there is limited evidence linking both processes on multitrophic systems.
@@
 Evidence emerging from single-years studies suggest that different factors such as species richness and abundance might be important for muti-year stability too.
-For example, a greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementary in service provision arising from variation of pollinator effectiveness across space and time of the day [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013; @Magrach2021].
-For example, pollinator species may exhibit different ranges of daily temporal activity [@Pisanty2016; @Rader2016, @zaragoza-trello2023] and consequently may provide pollination services at different times of the day or of the season.
+For example, a greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementarity in service provision arising from the variation of pollinator effectiveness across space and time of the day [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013; @Magrach2021].
+Pollinator species may exhibit different ranges of daily temporal activity [@Pisanty2016; @Rader2016; @Zaragoza-Trello2023] and consequently may provide pollination services at different times of the day or of the season.
 In addition, higher overall visitation rates are often assumed to insure reproductive success.
-However, while some studies report that higher visitation rates are correlated with higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017, @vázquez2005], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
+However, while some studies report that higher visitation rates are correlated with higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017, @Vazquez2005], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
 Interestingly, studies looking at pollen limitation show that higher visitation rates are often associated with no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant [Fig.
@@
 However, the occurrence and magnitude of pollen limitation can vary among years for individual populations [@Burd1994; @Ashman2004], primarily because of variation in pollinator service delivery [@Aizen2007].
-All this lines of evidence suggest that results found for single year studies should scale up to muti-year stability studies [CITAR GARIBALDI Y SENADAPATY CRFOP STUDIES], but evidence is mostly lacking for natural plant-pollinator systems.
+All this lines of evidence suggest that results found for single year studies should scale up to muti-year stability studies [@Garibaldi2011a; @Senapathi2021], but evidence is mostly lacking for natural plant-pollinator systems.
 
@@
 Hence, for each plant individual, the sampling effort was standardized to the number of visits per flower per minute.
-To that end, we divided the total visits observed by the number of flowers observed and by the total observation time (time of each observation multiplied by number of survey rounds per year).
+To that end, we calculated the visitation rate by dividing the total visits observed by the number of flowers observed and by the total observation time (time of each observation multiplied by number of survey rounds per year).
 Pollinator richness is calculated as the number of different pollinator species observed visiting the plant over all rounds, fruit set as the proportion of fruits developed (developed / aborted+developed), and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.
@@
 
-We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites (mean = X sites) in a minimum of two years per site (mean = X years per plant).
-The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman, 1999.
+We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites [(mean = 7 ± 0.71 sites)](lavandula aparece en 5 sitios, halimiun en 6, los citus estan entre 7 y 9 sitios) in a minimum of two years per site (mean = 3.25 ± 0.16 years per plant).
+The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman (1999).
 This is an adequate index given that in our dataset, as in most ecological studies, the mean and the variance scale with each other.
-To examine the role of richness and asynchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate pollinator richness as the total number of diferent pollinator species that visit each plant species in each plot.
+To examine the role of richness and asynchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate pollinator richness as the total number of different pollinator species that visit each plant species in each plot.
 The synchrony index for each plant species in the plot was calculated following Loreau and de Mazancourt (2008), as: $$
@@
 $$ where ${\sigma_{x_T}^2}$ is the variance of the community abundance of each plot and ${\sigma_{x_i}}$ is the standard deviation of species i abundance in a community with S species.
-[ESTEFANIA: Abundance = numero individuos, visitation rate = visitas hechas por esos individuos o usas visitation rate como proxy de abundancias.
-Si es lo primero, yo especificaria.
-"Note that we calulated abundance as the number of individuals observed, while visitation rate is the sum of their visits" o algo así, quizás tambien en metodos más arriba, mejor ser redundante, sino, o lo dejas así, o clarificas que we use visitation rates as proxies of abundances].
+
+Note that we determined abundance as the total number of individuals that were observed, whereas the visitation rate is the total number of their visits.
 This synchrony measurement varies from zero, when fluctuations are perfectly asynchronous, to one, when fluctuations are perfectly synchronous [@Loreau2008].
@@
 For this we employed all plant species sampled and we analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using a binomial generalized linear mixed model, and on the number of seeds employing a linear mixed model.
-*P* values were obtained using the type III Anova (package: car CITAR) as recommended for tetsing interactions.
+*P* values were obtained using the type III Anova (package: car [@Fox2011]) as recommended for testing interactions.
 The number of seeds per fruit was centered and scaled per plant species to allow meaningful comparisons across species.
@@
 
-All the analyses of this study were conducted in R software (v. 4.0.2; R Core Team, 2022) and the lme4 (Bates et al., 2015) and ggplot2 (Wickham, 2016) packages.
-DHARMa package was employed for checking all models (Harting 2017)
+All the analyses of this study were conducted in R software (v. 4.0.2; R Core Team, 2022) and the lme4 [@Bates2015] and ggplot2 [@Wickham2016] packages.
+DHARMa package was employed for checking all models [@Hartig2017].
 
@@
 Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)](Virginia%20me%20ha%20comentado%20en%20reportar%20el%20R2%20de%20los%20modelos%20pero%20al%20tratarse%20de%20modelos%20mixtos%20tendriamos%20que%20poner%20el%20marginal%20o%20el%20condicional.He%20revisado%20articulos%20que%20utilizan%20estos%20modleos%20y%20normalmente%20no%20ponen%20R2.%20Lo%20incluyo??) [IB: por mi esta bien así], whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
+There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)], whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
 However, we also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
@@
   geom_ribbon(aes(ymin = lower, ymax = upper),alpha=0.2)+
-  scale_y_continuous(limits = c(-2.5, 9.5))+labs(color='Plant species')+
+  labs(color='Plant species')+
+  coord_cartesian(ylim=c(-0.5,9.5))+
   geom_point(data = data_plant, aes(x =  asyn_LM, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=6)+
@@
   geom_ribbon(aes(ymin = lower, ymax = upper), alpha=0.1)+
-  scale_y_continuous(limits = c(-2.5, 9.5))+  labs(color='Plant species')+
+  scale_y_continuous(limits = c(-0.5, 9.5))+  labs(color='Plant species')+
   geom_point(data = data_plant, aes(x =  S_total, y = cv_1_visitation, color=Plant_gen_sp), alpha=0.7,size=6)+
@@
 
-Stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged 1.28 to 55.86 (7.018 ± 1.441).
+The stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged from 1.28 to 55.86 (7.018 ± 1.441).
 When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find any relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
@@
 Although this tendency is influenced by a high value in the stability of seed number of *H.
-halimifolium* (Fig 3B) since when we removed this point the relationship disappears and if anything, show a positive slope (0.561 ± 0.535).
-[quito los p val de los tests sin outlyers, para no caer en multiple testing]
+halimifolium* (Fig 3B) since when if the point is removed the relationship disappears and if anything, shows a positive slope (0.561 ± 0.535).
 

### 2023-05-08 Manuscript/Figures/Plot_2.R
editing figure

@@ -45,7 +45,7 @@ data_plant$asyn_LM= 1-data_plant$syncLM
 
 
 #model fruit stability ~ visitation rate stability
-mod2_sta= lmer(cv_1_fruit ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID), data = data_plant)
+mod2_sta= lmer(cv_1_fruit ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID),data = data_plant)
 
 #getting effects 
 effe3_mod_sta <-data.frame( effect("cv_1_visitation", mod2_sta, se = TRUE))
@@ -56,6 +56,7 @@ p_mod2=ggplot(effe3_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
   geom_ribbon(aes(ymin = lower, ymax = upper),linetype = 3, alpha=0.2, colour = "black")+
   geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_fruit, color=Plant_gen_sp),alpha=0.5, size=3)+
   labs(color='Plant species')+
+  coord_cartesian(ylim=c(-10,120))+
   scale_colour_brewer(palette = "Set1")+
   labs(y = "Stability of fruit proportion",x="Stability of visitation rate")+
   theme_bw ()+
@@ -77,6 +78,7 @@ effe4_mod_sta <-data.frame( effect("cv_1_visitation", mod3_sta, se = TRUE))
 p_mod3=ggplot(effe4_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
   geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3, alpha=0.2, colour = "black")+
   labs(color='Plant species')+
+  coord_cartesian(ylim=c(-10,60))+
   geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_seed, color=Plant_gen_sp), alpha=0.5,size=3)+
   scale_colour_brewer(palette = "Set1")+
   labs(y = "Stability of seed number",x="Stability of visitation rate")+

### 2023-05-08 Manuscript/Manuscript.Rmd
corrected comments in the discussion

@@
 $$ where ${\sigma_{x_T}^2}$ is the variance of the community abundance of each plot and ${\sigma_{x_i}}$ is the standard deviation of species i abundance in a community with S species.
-
 Note that we determined abundance as the total number of individuals that were observed, whereas the visitation rate is the total number of their visits.
@@
 Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-There is a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increases [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)], whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
+There was a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increased [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)], whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
 However, we also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
@@
 The stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged from 1.28 to 55.86 (7.018 ± 1.441).
-When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find any relationship when analyzing the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
-However, contrary to expected, the stability of seed number did show a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).
+When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find any relationship considering the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
+However, contrary to expected, the stability of seed number showed a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).
 Although this tendency is influenced by a high value in the stability of seed number of *H.
@@
   labs(color='Plant species')+
+  coord_cartesian(ylim=c(-10,120))+
   scale_colour_brewer(palette = "Set1")+
@@
   labs(color='Plant species')+
+  coord_cartesian(ylim=c(-5,60))+
   geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_seed, color=Plant_gen_sp), alpha=0.7,size=7)+
@@
 For the visualization purpose, we omit in the visitation rate (x-axis) the values outside of the 95\\%."}
-
-##IB: Yo cortaba todos los plots a zero (o a -1) El de arriba tambien.
 
@@
 
-We show that pollinator's visitation rate stability increase with higher asynchrony of pollinators species abundances and that greater species richness only increase stability of visitation rate indirectly, via enhanced species asynchrony.
-However, contrary to expectations, we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
-This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with [lower pollinator abundances.](quizas%20decir%20lower%20richness%20and%20visitation%20rate??)
+In this study we show that the pollinator's visitation rate stability increase with higher asynchrony of pollinators species abundances and that greater species richness only increase stability of visitation rate indirectly, via enhanced species asynchrony.
+However, contrary to what could be expected we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
+This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with lower pollinator abundances.
 However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.
@@
 response diversity [@Walker99; @Winfree2013]).
-While we do not evaluate the causes of this response diversity, we do show that the asynchronous fluctuating species are redundant in its visitation patterns, a known requisite for response diversity to matter for ecosystem functioning stability [@stavert2017].
+While we do not evaluate the causes of this response diversity, we do show that the asynchronous fluctuating species are redundant in their visitation patterns, a known requisite for response diversity to matter for ecosystem functioning stability [@Stavert2017].
 
@@
 Pollinator richness was positively associated with asynchrony, which positively affect the stability of visitation rate, but not associated directly with more stable visitation rates.
-Species richness is suggested to increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999], but the asynchrony of a few dominant species might be more relevant in pollinator systems than richness per se [ref about pollinator dominance, maighbe winfree or kleijn (the nat comm paper) has something].
+Species richness is suggested to increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999], but the asynchrony of a few dominant species might be more relevant in pollinator systems than richness per se [@Winfree2015; @Kleijn2015].
 
@@
 In pollinator-dependent crops it has been observed that a greater yield stability is related to pollinator diversity and the stability of visitation rates [@Garibaldi2011; @Garibaldi2013; @Hunicken2021] but in our study system (wild plants), we did not find this relationship.
-Despite we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, for most plants and years there is a general saturation of the proportion of fruits developed, with fruitsets above 80%.
-As shown in figure 1, an initial increase in the number of pollinator visits is predicted to increase the reproductive success of the plant but as visitation rates continue to increase, its effect will level off or even decline [@Young1992; @Morris2010].
-Bees can remove 70--80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits [REF?]
-.
+Despite we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, for most plants and years there is a general saturation of the proportion of fruits developed, with fruit sets above 80%.
+As shown in Figure 1, an initial increase in the number of pollinator visits is predicted to increase the reproductive success of the plant but as visitation rates continue to increase, its effect will level off or even decline [@Young1992; @Morris2010].
+Bees can remove 70--80% of the pollen that is presented in a flower and a flower's pollen can be exhausted after only a few visits [@harder90; @Kudo2005].
 Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion [@Thomson2001].
 Several factors can mediate the shape of this relationships.
-First [Aqui has de elegir tres hipotesis y ponerlas en plan first, second, third,..., ahora queda un batiburrillo hasta el final del parrafo] through impacts on pollinator densities [@Steffan-Dewenter2008a; @Williams2015], foraging dynamics [@Kunin1996], visitation rates [@VanNuland2013; @Veddeler2006], and pollen deposition [@Lortie1999; @Evans2017].
-The concentration effect, which occurs when foragers visit a location in greater numbers due to high resource availability [@Kunin1996; @Totland1998], has an impact on the reproductive success of plants [@Blaauw2014; @Cohen2021].
-Furthermore, some plant species increase pollinator visits to the coflowering plant, which subsequently contributes to the reproductive success of neighbouring individuals [@Schemske1981; @Moeller2004; @Ghazoul2006].
-Another possible explanation to this might be the variations in abiotic factors.
-Since the weather conditions can vary significantly between years, the abundance of pollinators during the flowering season of a plant can show annual variations, which may have an impact on the plant reproductive success [@Vicens2000; @Ivey2003].
-In addition, the environmental conditions also affect to host plants.
-For instance, the variation of temperature conditions lead to alterations in nectar production, composition and concentration [@Pacini2003], which can affect to the pollinator activity [hasta aquí hay que guiar al lector, resume tus opciones de por que hay variacion interanual en tres categorias una frase por categoria y listos].
-Although investigating this factors is beyond the aim of the study, future research should clarify when and where pollinators are limiting.
-For example @herbertsson2021 show in a recent meta-analysis a large variability on the effects of different pollinators on seed set, but the causes of this variability remain to be explored.
+Firstly, greater availability of floral resources in the plots these years can impact pollinator densities, visitation rates and pollen deposition [@Williams2015; @VanNuland2013; @Veddeler2006; @Evans2017].
+Secondly, variations in abiotic factors can affect both pollinator abundance and host plants [@Vicens2000; @Ivey2003].
+For instance, the variation of temperature conditions leads to alterations in nectar production, composition, and concentration [@Pacini2003], which can affect to the pollinator.
+Although investigating these factors is beyond the aim of the study, future research should clarify when and where pollinators are limited.
+For example, Herbertsson et al.
+(2021) showed in a recent meta-analysis a large variability in the effects of different pollinators on seed sets, but the causes of this variability remain to be explored.
 
@@
 However, visitation rates stability did not directly contribute to the stability of the final plant reproductive success function.
-In this sense, we believe that further studies are needed to better understand these mechanisms in natural communities by assessing the reproductive success along time of a wider variety of plant species [citar aqui algun estudio a largo plazo de la reproduccion de una sola espcie de plantas Thomson tendra algo?
-(alguno de los thomsons :) no?]
-.
+In this sense, we believe that further studies are needed to better understand these mechanisms in natural communities by assessing the reproductive success along time of a wider variety of plant species [@Thomson2019].
 The variations seen between years suggest that in our study system, plant reproduction is not typically limited by pollinators.

### 2023-05-11 Manuscript/Manuscript.Rmd
acknowledgement, conflict and author contributions. Grammarly in abstract and introduction

@@
 ---
-title: "The temporal stability in flower visitation rates is driven by the asynchrony of pollinator abundances but does not necessarely explain plant reproductive success stability."
-author: "Estefanía Tobajas^1, Virginia Domínguez-García^1, Francisco P. Molina^1, Ignasi Bartomeus^1"
+title: "The temporal stability in flower visitation rates is driven by the asynchrony of pollinator abundances but does not necessarily explain plant reproductive success stability."
+author: "Estefanía Tobajas^1, Virginia Domínguez-García^2, Francisco P. Molina^2, Ignasi Bartomeus^2"
 date: '2022-10-26'
 output:
+  word_document: default
   pdf_document:
     latex_engine: xelatex
-  word_document: default
 header-includes: \usepackage{float} \floatplacement{figure}{H} \usepackage{caption}
@@
 
-\^1 Estación Biológica de Doñana (EBD-CSIC).
+\^1 Departamento de Biología Animal, Facultad de Biología, Universidad de Salamanca, Salamanca, Spain \^2 Estación Biológica de Doñana (EBD-CSIC).
 Sevilla, Spain.
@@
 2.
-Using a 5-year dataset across 13 Mediterranean shrublands and 12 plant species, we assessed the effect of pollinator richness and asynchrony as drivers of the stability of plant's visitation rate and plants reproductive success.
-    In addition, we analyzed whether the effects of species richness and visitation rate on plant reproduction success were consistent among years.
+Using a 5-year dataset across 13 Mediterranean shrublands and 12 plant species, we assessed the effect of pollinator richness and asynchrony as drivers of stability in plant visitation rates and plant reproductive success.
+    In addition, we analyzed whether the effects of species richness and visitation rate on plant reproduction success were consistent across the years.
 
 3.
-The stability of plant's visitation rate is driven by the asynchrony of pollinator species abundances, but the effect of species richness is only indirect, as richer communities also tend to show more asynchronous populations.
-    In contrast, the stability of the plant reproductive success is not related to the stability of its pollinator visitation rates.
-    A year-by-year analysis reveals that in the studied system plants are unlikely to be limited by pollinator abundances except in specific years, blurring any potential effect of visitation rates stability on the stability of reproductive success.
+The stability of plant visitation rates is driven by the asynchrony of pollinator species abundances, but the effect of species richness is only indirect, as richer communities also tend to have more asynchronous populations.
+    In contrast, the stability of plant reproductive success is not related to the stability of its pollinator visitation rates.
+   A year-by-year analysis reveals that plants in the system studied are unlikely to be limited by pollinator abundance except in specific years, blurring any potential effect of visitation rate stability on reproductive success stability.
 
-4.  We highlight the importance of maintaining a redundancy of pollinators that visit the same plant species, given that its presence can buffer from pollinators temporal fluctuations.
+4.  We highlight the importance of maintaining a redundancy of pollinators that visit the same plant species, given that their presence can buffer the temporal fluctuations of pollinators.
     This is particularly important for pollinators with contrasting responses to environmental fluctuations, as this creates the needed asynchrony of their populations to guarantee stable levels of flower visitation rates.
@@
 
-Global environmental changes and the consequent loss of biodiversity have highlighted the need for better understanding the role of biodiversity in ecosystem function [@Hooper2005; @Lefcheck2015; @Oliver2015; @Hong2022].
-We have experimental and observational evidence that biodiversity enhances aggregated community-level properties, such as total biomass [@Cardinale2006; @Cardinale2012; @Tilman2014], but the role of biodiversity for the stability of ecosystem functioning is less explored (but see @Griffin2009; @Grman2010), specially in functions involving several trophic levels such as plant pollination [@Ebeling2008; @Winfree2009a; @Garibaldi2011; @Lazaro2022].
+Global environmental changes and the consequent loss of biodiversity have highlighted the need for a better understanding of the role of biodiversity in ecosystem function [@Hooper2005; @Lefcheck2015; @Oliver2015; @Hong2022].
+We have experimental and observational evidence that biodiversity enhances aggregated community-level properties, such as total biomass [@Cardinale2006; @Cardinale2012; @Tilman2014], but the role of biodiversity in the stability of ecosystem functioning is less explored (but see @Griffin2009; @Grman2010), specially in functions involving several trophic levels such as plant pollination [@Ebeling2008; @Winfree2009a; @Garibaldi2011; @Lazaro2022].
 Globally, it is estimated that at least 78% of wild plants depend to some extent on pollination by animals [@Ollerton2011].
-Understanding the mechanisms driving pollinator community stability and how this relates to the stability of ecosystem functions and services delivered (i.e.
-pollination) is important for predicting changes in both community structure and ecosystem function.
+Understanding the mechanisms driving pollinator community stability and how this relates to the stability of ecosystem functions and services delivered (i.e., pollination) is important for predicting changes in both community structure and ecosystem function.
 
 Temporal stability is defined as the capacity of an ecosystem to dampen environmental perturbations over time while retaining ecological functions of interest [@Ives2007; @Pimm1984].
-The temporal stability of the community can be influenced by the diversity of species present and the asynchrony on the species abundance fluctuations.
+The temporal stability of the community can be influenced by the diversity of species present and the asynchrony of species abundance fluctuations.
 A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e.
@@
 Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008; @Xu2015], and often stability is more strongly associated with the degree of asynchrony across species than with species richness itself [@Bluthgen2016; @Huang2020].
-Other studies have indicated that the temporal stability of the dominant species or the asynchrony among these dominant species are important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020].
-While community temporal stability should be related to the stability of ecosystem functions and services provided by such community, there is limited evidence linking both processes on multitrophic systems.
+Other studies have indicated that the temporal stability of the dominant species, or the asynchrony among these dominant species, is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020].
+While community temporal stability should be related to the stability of ecosystem functions and services provided by such a community, there is limited evidence linking both processes in multitrophic systems.
 
 Since the reproductive success of most plant species highly depends on pollination by animals [@Ollerton2011], the stability of pollinator communities may increase the stability of plant reproductive success.
-Evidence emerging from single-years studies suggest that different factors such as species richness and abundance might be important for muti-year stability too.
+Evidence from single-year studies suggests that different factors such as species richness and abundance may also be important for multi-year stability.
 For example, a greater diversity of pollinators has been shown to increase plant reproductive success as a result of complementarity in service provision arising from the variation of pollinator effectiveness across space and time of the day [@Hoehn2008; @Frund2010; @Albrecht2012; @Bluthgen2011; @Frund2013; @Magrach2021].
 Pollinator species may exhibit different ranges of daily temporal activity [@Pisanty2016; @Rader2016; @Zaragoza-Trello2023] and consequently may provide pollination services at different times of the day or of the season.
-In addition, higher overall visitation rates are often assumed to insure reproductive success.
-However, while some studies report that higher visitation rates are correlated with higher plant reproductive outputs [@Garibaldi2013; @Kaiser-Bunbury2017, @Vazquez2005], other studies do not find such relationship [@Hegland2012; @Lundgren2013].
-Interestingly, studies looking at pollen limitation show that higher visitation rates are often associated with no pollen limitation, indicating than above a certain threshold, changes in visitation rates are no longer relevant [Fig.
+In addition, higher overall visitation rates are often assumed to ensure reproductive success.
+However, while some studies report that higher visitation rates are correlated with higher plant reproductive output [@Garibaldi2013; @Kaiser-Bunbury2017; @Vazquez2005], other studies find no such relationship [@Hegland2012; @Lundgren2013].
+Interestingly, studies looking at pollen limitation show that higher visitation rates are often associated with no pollen limitation, indicating that above a certain threshold, changes in visitation rates are no longer relevant [Fig.
 1; @Cosacov2008; @Williams2013].
-However, the occurrence and magnitude of pollen limitation can vary among years for individual populations [@Burd1994; @Ashman2004], primarily because of variation in pollinator service delivery [@Aizen2007].
-All this lines of evidence suggest that results found for single year studies should scale up to muti-year stability studies [@Garibaldi2011a; @Senapathi2021], but evidence is mostly lacking for natural plant-pollinator systems.
+However, the occurrence and magnitude of pollen limitation can vary from year to year for individual populations [@Burd1994; @Ashman2004], mainly because of variations in pollinator service delivery [@Aizen2007].
+All these  lines of evidence suggest that results found for single year studies should scale up to muti-year stability studies [@Garibaldi2011a; @Senapathi2021], but the evidence is mostly lacking for natural plant-pollinator systems.
 
-```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 8,fig.width=10,out.width="60%",fig.align='center', fig.cap =" 1.
-Conceptual figure showing the general relationship between visitation rate of pollinators and plant reproductive success to different species richness (R1, R2, ...).
-As the number of visits (V1, V2, ...) from pollinators increases, the plant reproductive success is expected to increase until than above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success."}
-library(ggplot2)
-library(patchwork)
-
-####IB: ESTEFANIA, necesitamos un A y B en plots de abajo, para que la gente los reconozca.
-EN esos paneles yo escribiria Repreocution y Visitation /Richness entro.
-Y los paneles A y B necesitan explicación en la leyenda, de hecho, yo creo que ahora estan girados...
-o eso o estoy espeso.
-Lo hablamos por video.
-
-#First dataset RED
-s1 <- seq(from=0, to=100, by=0.5)
-l1 = log(s1, base = 6)
-d1 = data.frame(l1, s1)
-
-#Second dataset BLUE
-s2 <- seq(from=0, to=100, by=0.5)
-l2 = log(s2, base = 8)
-d2 = data.frame(l2, s2)
-
-#Third dataset GREEN
-s3 <- seq(from=0, to=100, by=0.5)
-l3 = log(s3, base = 12)
-d3 = data.frame(l3, s3)
-
-to=ggplot(d1, aes(s1, l1)) +
-  geom_line(color = "#e41a1c", linewidth=1.3) +
-  geom_line(data =  d2, aes(s2,l2), color = "#377eb8",linewidth=1.3) +
-  geom_line(data =  d3, aes(s3,l3), color = "#4daf4a",linewidth=1.3) +
-  ylab("Reproductive success")+
-  labs(x = "") +
-  theme_classic()+
-  theme(axis.text.y=element_blank(),
-        axis.ticks.y=element_blank())+
-  scale_x_continuous(breaks=seq(from= 0, to= 100, by = 20), labels=c("V1","V2","V3", "V4","V5","V6"))+
-  theme(text = element_text(size=18,face="bold"))+
-  theme(axis.ticks.x=element_blank())+
-  annotate("rect", xmin = c(0, 60), xmax = c(20,80), ymin = c(0.4, 1.35), 
-           ymax = c(1.75, 2.7), linetype = 1, fill="gray88", alpha=0.3, colour = "black") +
-  annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R3", "R2", "R1"), size=5)+
-  annotate("text", x = c(1.25, 61.3), y = c(1.62,2.58), label = c("A", "B"), size=6)+
-  theme(axis.line.x = element_line(arrow = arrow()))+
-  theme(axis.line.y = element_line(arrow = arrow()))
-
-##################################
-x <- seq(0, 41, by = 0.1)
-y1 <- sin(x)
-y1.2 <- cos(x+4.3)
-
-da1 <- data.frame( x, y1)
-da1.2 <- data.frame( x, y1.2)
-
-R_1=ggplot(da1, aes(x, y1))+
-  geom_line( size=1) +
-  geom_line(data =  da1.2, aes(x, y1.2), color = "#e41a1c",size=1)+
-  theme_classic() +
-  xlab("Time") +
-  theme(axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) + 
-  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("R1","R3"))+
-  theme(text = element_text(size=15, face="bold"))+
-  theme(axis.title.y = element_blank()) +
-  annotate("text", x = 44, y = 0.4, label = "Rep", size=4,color="#e41a1c")+
-  annotate("text", x = 43, y = 0, label = "R", size=4)+ 
-  theme(aspect.ratio=0.5)
-
-###################################
-
-x2 <- seq(0, 41, by = 0.1)
-y2 <- sin(x2)
-y3 = sin(x2/2.5)
-
-da2 <- data.frame(x2, y2)
-da2.1 = data.frame(x2,y3)
-
-v_1=ggplot(da2, aes(x2, y2))+
-  geom_line( size=1) +
-  geom_line(data =  da2.1, aes(x2,y3), color = "#e41a1c",size=1)+
-  theme_classic() +
-  xlab("Time")+
-  theme(axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+ 
-  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("V1","V2"))+
-  theme(text = element_text(size=15, face="bold"))+
-  theme(axis.title.y = element_blank())+
-  annotate("text", x = 44, y = -0.5, label = "Rep", size=4, color="#e41a1c")+
-  annotate("text", x = 42.5, y = 0, label = "V", size=4) + 
-  theme(aspect.ratio=0.5)
-
-po1=v_1/R_1
-
-######################
-x3 <- seq(0, 57, by = 0.1)
-y3 <- sin(x3)
-y3.1 <- cos(x3+4.3)
-
-da3 <- data.frame(x3, y3)
-da3.1 <- data.frame(x3, y3.1)
-
-v_2=ggplot(da3, aes(x3, y3))+
-  geom_line( size=1) +
-  geom_line(data =  da3.1, aes(x3,y3.1), color = "#e41a1c",size=1)+
-  theme_classic() +
-  xlab("Time") +
-  theme(axis.text.x=element_blank(),
-        axis.ticks.x=element_blank()) + 
-  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("V4","V5"))+
-  theme(text = element_text(size=15, face="bold"))+
-  theme(axis.title.y = element_blank()) +
-  annotate("text", x = 61, y = 0, label = "Rep", size=4,color="#e41a1c")+
-  annotate("text", x = 59, y = 0.3, label = "V", size=4)+ 
-  theme(aspect.ratio=0.5)
-
-########################################
-x4 <- seq(0, 57, by = 0.1)
-y4 <- sin(x4)
-y5 = sin(x4/2.5)
-
-da4 <- data.frame(x4, y4)
-da5 = data.frame(x4,y5)
-
-R_2=ggplot(da4, aes(x4, y4))+
-  geom_line( size=1) +
-  geom_line(data =  da5, aes(x4,y5), color = "#e41a1c",size=1)+
-  theme_classic() +
-  xlab("Time")+
-  theme(axis.text.x=element_blank(),
-        axis.ticks.x=element_blank())+ 
-  scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("R1","R3"))+
-  theme(text = element_text(size=15, face="bold"))+
-  theme(axis.title.y = element_blank())+
-  annotate("text", x = 61, y = -0.6, label = "Rep", size=4, color="#e41a1c")+
-  annotate("text", x = 59, y = 0.4, label = "R", size=4)+ 
-  theme(aspect.ratio=0.5)
-
-po2=v_2/R_2
-
-to/ (po1 |po2)
-```
+![ Conceptual figure showing the general relationship between the visitation rate of pollinators and plant reproductive success to different species richness (R1, R2, ...).
+As the number of pollinator visits increases (V1, V2, …), plant reproductive success is expected to increase until that above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success.
+According to this, A-square shows that temporal variation in plant reproductive success depends on variation in visitation, while B-square shows that reproductive success varies with the variation in richness.](Figures/conceptual_plot2.png){width="400"}
 
@@
 However, to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates we only use the 5 most represented plant species across years and sites.
-Further, we evaluate whether more stable pollinator communities foster a more stable plant reproductive success along years, measuring both the stability of fruit and seed set.
-We expect that the stability of visitation rates will increase with higher richness and asynchrony of pollinators.
-In addition, a greater stability of plant reproductive success is expected with higher stability of visitation rates.
-However, given the lack of a clear relationship between pollinator and plant reproductive output stability in our dataset, we further analyzed the variability on the yearly effect of pollinator richness and visitation rates on the reproductive success of the plants.
+We also assess whether more stable pollinator communities foster a more stable plant reproductive success across years, measuring both fruit and seed set stability.
+We expect that the stability of visitation rates will increase with higher pollinator richness and asynchrony.
+In addition, greater stability of plant reproductive success is expected with higher stability of visitation rates.
+However, given the lack of a clear relationship between pollinator and plant reproductive output stability in our dataset, we further analyzed the variability in the yearly effect of pollinator richness and visitation rates on plant reproductive success.
 
@@
 
-We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites [(mean = 7 ± 0.71 sites)](lavandula aparece en 5 sitios, halimiun en 6, los citus estan entre 7 y 9 sitios) in a minimum of two years per site (mean = 3.25 ± 0.16 years per plant).
+We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites [(mean = 7 ± 0.71 sites)](lavandula%20aparece%20en%205%20sitios,%20halimiun%20en%206,%20los%20citus%20estan%20entre%207%20y%209%20sitios) in a minimum of two years per site (mean = 3.25 ± 0.16 years per plant).
 The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman (1999).
@@
 
+# Aknowledgements
+
+This study was supported by the XXXXX.Estefania Tobajas thanks the Bartomeus lab and Estacion Biologica de Doñana (EBD-CSIC) for hosting during the research stay.
+Estefanía Tobajas was funded by a "Postdoc contract" (Ayudas Margarita Salas. Ministerio de Universidades-Universidad de Salamanca).
+
+# Author contributions
+
+All authors designed the idea.
+Francisco P. Molina collected the data.
+Estefanía Tobajas conducted the analyses with the contributions of Virginia Domínguez-García and the guidance of Ignasi Bartomeus.
+Estefanía Tobajas wrote the manuscript with contributions of all authors.
+
+# Conflict of interest
+
+The authors declare no conflict of interest.
+
 # Supplementary material

### 2023-05-16 Manuscript/Manuscript.Rmd
Discussion and grammar review

@@
 output:
-  word_document: default
   pdf_document:
     latex_engine: xelatex
+  word_document: default
 header-includes: \usepackage{float} \floatplacement{figure}{H} \usepackage{caption}
@@
 The temporal stability of the community can be influenced by the diversity of species present and the asynchrony of species abundance fluctuations.
-A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e.
-the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
+A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e., the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
 Species asynchrony represents the intrinsic differences in species response to disturbances and natural fluctuations [@Loreau2013] which has been suggested as a key driver for community temporal stability [@Loreau2008].
 In this sense, higher levels of species asynchrony stabilize the overall community dynamics [@Ruijven2007; @Bluthgen2016; @Craven2018].
-Species asynchrony has been found to be a factor driving positive relationships between diversity and stability [@Loreau2008; @Xu2015], and often stability is more strongly associated with the degree of asynchrony across species than with species richness itself [@Bluthgen2016; @Huang2020].
+Species asynchrony is a factor driving positive relationships between diversity and stability [@Loreau2008; @Xu2015], and often stability is more strongly associated with the degree of asynchrony across species than with species richness itself [@Bluthgen2016; @Huang2020].
 Other studies have indicated that the temporal stability of the dominant species, or the asynchrony among these dominant species, is important in maintaining the stability of ecosystems [@Sasaki2011; @Valencia2020].
@@
 ![ Conceptual figure showing the general relationship between the visitation rate of pollinators and plant reproductive success to different species richness (R1, R2, ...).
-As the number of pollinator visits increases (V1, V2, …), plant reproductive success is expected to increase until that above a certain threshold, changes in visitation rates are no longer relevant to plant reproductive success.
-According to this, A-square shows that temporal variation in plant reproductive success depends on variation in visitation, while B-square shows that reproductive success varies with the variation in richness.](Figures/conceptual_plot2.png){width="400"}
+As the number of pollinator visits increases (V1, V2, …), plant reproductive success is expected to increase until that above a certain threshold, the changes in visitation rates are no longer relevant to plant reproductive success.
+According to this, A-square shows that temporal variation in plant reproductive success depends on variation in visitation, while B-square shows that reproductive success varies with the variation in richness.](Figures/conceptual_plot.png){width="400"}
 
@@
 We selected 13 sites in Mediterranean shrub ecosystems that ranged from sites with little to no disturbances to more modified ones with crops and urban areas nearby.
-These sites are similar in the plant community composition and the most abundant plant species are known to be attractive to flower visitors and to depend on pollinators to maximize its reproduction (e.g.
-dominated by *Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*).
+These sites are similar in the plant community composition and the most abundant plant species are known to be attractive to flower visitors and dependent on pollinators to maximize their reproduction (e.g., dominated by *Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*).
 Each site was surveyed at least 7 times per year during the flowering season from 2015 to 2019 (from March to June).
 Within each site, we selected 3-4 individuals belonging to 3-9 plant species (mean ± standard error: 5.92 ± 0.54 plant species per site).
-We performed focal observations where all the floral visitors (from now on referred to as pollinators) that contacted with their flowers were registered.
+We conducted focal observations, recording all flower visitors (from now on referred to as pollinators) that made contact with their flowers.
 Only pollinators that could not be identified in the field were captured, stored, and identified to species level in the laboratory.
-For each plant individual, we counted the total number of flowers observed in each survey and we recorded the number of fruits developed / aborted and the number of seeds per fruit in a subsample of 3 fruits at the end of the season.
-Focal observations had a duration of five minutes per individual in 2015-2016 and three minutes from 2017 to 2019.
+For each plant individual, we counted the total number of flowers observed in each survey and we recorded the number of fruits developed/aborted and the number of seeds per fruit in a subsample of 3 fruits at the end of the season.
+Focal observations had a duration of five minutes per individual from 2015-2016 and three minutes from 2017 to 2019.
 Hence, for each plant individual, the sampling effort was standardized to the number of visits per flower per minute.
-To that end, we calculated the visitation rate by dividing the total visits observed by the number of flowers observed and by the total observation time (time of each observation multiplied by number of survey rounds per year).
+To that end, we calculated the visitation rate by dividing the total visits observed by the number of flowers observed and by the total observation time (time of each observation multiplied by the number of survey rounds per year).
 Pollinator richness is calculated as the number of different pollinator species observed visiting the plant over all rounds, fruit set as the proportion of fruits developed (developed / aborted+developed), and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.
@@
 
-We analyze five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites [(mean = 7 ± 0.71 sites)](lavandula%20aparece%20en%205%20sitios,%20halimiun%20en%206,%20los%20citus%20estan%20entre%207%20y%209%20sitios) in a minimum of two years per site (mean = 3.25 ± 0.16 years per plant).
+We analyse five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites [(mean = 7 ± 0.71 sites)](lavandula%20aparece%20en%205%20sitios,%20halimiun%20en%206,%20los%20citus%20estan%20entre%207%20y%209%20sitios) in a minimum of two years per site (mean = 3.25 ± 0.16 years per plant).
 The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman (1999).
-This is an adequate index given that in our dataset, as in most ecological studies, the mean and the variance scale with each other.
+This is an adequate index given that in our dataset, as in most ecological studies, the mean and the variance are scaled to each other.
 To examine the role of richness and asynchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate pollinator richness as the total number of different pollinator species that visit each plant species in each plot.
@@
 Finally, we express asynchrony as $1-\phi$.
-We also calculated the stability of fruit proportion and of the seed number for each plant species in each plot following the same methods.
+We also calculated the stability of fruit proportion and the seed number for each plant species in each plot following the same methods.
 
@@
 Similarly, linear mixed model was used to test the influence of pollinator richness on asynchrony of pollinator species abundances.
-In all cases, site and plant species were included as random factor.
-For a deeper understanding of the processes, we also analyzed the response for each plant species separately.
+In all cases, site and plant species were included as random factors.
+For a deeper understanding of the processes, we also analysed the response for each plant species separately.
 
-To study whether the stability of pollinator visitation rate influenced in the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or the stability of seed number and as explanatory variable the visitation rate stability.
+To study whether the stability of pollinator visitation rate influences the stability of the plant reproductive success, we run linear mixed models using as response variables the stability of fruit proportion or the stability of seed number and as explanatory variable the visitation rate stability.
 Site and plant species were included as random factors.
 
-Finally, we further analyzed the variability on the yearly effect of pollinator richness and visitation rate on the reproductive success of the plants.
-For this we employed all plant species sampled and we analyzed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using a binomial generalized linear mixed model, and on the number of seeds employing a linear mixed model.
+Finally, we further analysed the variability in the yearly effect of pollinator richness and visitation rate on plant reproductive success.
+For this, we employed all plant species sampled and we analysed the interactive effect between richness and year, and between visitation rate and year on fruit proportion using a binomial generalized linear mixed model, and on the number of seeds employing a linear mixed model.
 *P* values were obtained using the type III Anova (package: car [@Fox2011]) as recommended for testing interactions.
-The number of seeds per fruit was centered and scaled per plant species to allow meaningful comparisons across species.
+The number of seeds per fruit was centred and scaled per plant species to allow meaningful comparisons across species.
 For all models, we included plant species identity nested within site and site as random effects because of multiple individuals of the same plant species are measured at each site.
@@
 Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-There was a strong positive relationship between stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increased [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)], whereas stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
+There was a strong positive relationship between the stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increased [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)], whereas the stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
 However, we also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
@@
 
-When we analysed each plant species separately, we observed a positive relationship between asynchrony of pollinators and stability of visitation rate for *C.
+When we analysed each plant species separately, we observed a positive relationship between the asynchrony of pollinators and stability of visitation rate for *C.
 crispus*, *H.
@@
 pedunculata*, a weak positive relationship for *C.
-salviifolious* and a weak negative relationship for *C.ladanifer*.
+salviifolious* and a weak negative relationship for *C.
+ladanifer*.
 For the relationship with pollinator richness, *C.
@@
 ladanifer* and *C.
-salviifolius* showed a negative relationships while *H.
+salviifolius* showed a negative relationship while *H.
 halimifolium* and *L.
@@
 
-```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 8,fig.width=20, out.width="100%",fig.align='center', fig.cap =" 2.Relationships between stability of visitation rate (calculated as the inverse of the coefficient of variation) and asynchorny of pollinators (Loreau and de Mazancourt’s index) (A), stability of visitation rate and pollinator richness (B), and asynchorny of pollinators and richness (C).Dots represent the different plant species incluided in the analysis.Significant models are representing with solid line."}
+```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 8,fig.width=20, out.width="100%",fig.align='center', fig.cap =" 2.
+Relationships between the stability of visitation rate (calculated as the inverse of the coefficient of variation) and asynchrony  of pollinators (Loreau and de Mazancourt’s index) (A), stability of visitation rate and pollinator richness (B), and asynchrony of pollinators and richness (C).
+Dots represent the different plant species included in the analysis.
+Significant models are represented with a solid line."}
 
@@
 The stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged from 1.28 to 55.86 (7.018 ± 1.441).
-When we analyzed whether the stability of the pollinator's visitation rate affected the stability of the plant reproductive success, we did not find any relationship considering the fruit proportion (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
-However, contrary to expected, the stability of seed number showed a negative relationship with the stability of pollinator's visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).
+When we analysed whether the stability of the pollinator visitation rate affected the stability of plant reproductive success, we found no relationship when fruit proportion was considered (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
+However, contrary to expectations, the stability of seed number showed a negative relationship with the stability of pollinator visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).
 Although this tendency is influenced by a high value in the stability of seed number of *H.
@@
 ```{r,echo=FALSE, warning=FALSE,message=FALSE, fig.height = 10,fig.width=20,out.width="80%",fig.align='center', fig.cap = " 3.
-Relationship between stability of plant reproductive succes: fruit propotion (A) and seed number (B) and the stability of visitation rate.
-Dots represent the different plant species incluided in the analysis.Significant models are representing with solid line."}
+Relationship between the stability of plant reproductive success: fruit proportion (A) and seed number (B) and the stability of visitation rate.
+Dots represent the different plant species included in the analysis.
+Significant models are represented with a solid line."}
 
@@
 When we analysed the variable fruit proportion, we found that the interactions between year and pollinator richness, and year and visitation rate affected the fruit proportion (richness x year: $\chi 2$ = 28.976, df = 4, *p* = \<0.0001; visitation rate x year: $\chi 2$ = 40.691, df = 4, *p* = \<0.0001).
-Furthermore, we observed a significant effect of year by itself, but not so of pollinator richness or visitation rate.
+Furthermore, we observed a significant effect of the year by itself, but not so of pollinator richness or visitation rate.
 Note that we observed a general saturation of the proportion of fruits developed with most species consistently showing over 80% of fruit set, however, in years like 2017, for which the hydrological year was very dry, we found that a greater richness and visitation rate increased the fruit proportion.
 We also observed a positive relationship between richness and fruit proportion in 2019.
-However in 2018, an specially wet year, the relationship between richness and fruit proportion was negative (Fig 3).
+However, in 2018, a specially wet year, the relationship between richness and fruit proportion was negative (Fig 3).
 
@@
 Interaction effect between richness and year (top row), and visitation rate and year (bottom row) on fruit proportion.
-For the visualization purpose, we omit in the visitation rate (x-axis) the values outside of the 95\\%."}
+For visualization purposes, we omit from the visitation rate (x-axis) the values that are outside 95\\%."}
 
@@
 
-In this study we show that the pollinator's visitation rate stability increase with higher asynchrony of pollinators species abundances and that greater species richness only increase stability of visitation rate indirectly, via enhanced species asynchrony.
+In this study, we show that the stability of pollinator visitation rate increases with higher asynchrony of pollinator species abundances and that greater species richness increases the stability of visitation rate only indirectly, via enhanced species asynchrony.
 However, contrary to what could be expected we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
 This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with lower pollinator abundances.
-However, this do not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.
+However, this does not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.
 When and where pollinators are limiting is the key question then.
 
-While drivers of temporal stability have been well study in plant communities [@Ruijven2007; @Gross2014; @Craven2018; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021], relatively few studies have evaluated how this same drivers can affect community stability in mobile organisms such as pollinators [@Ebeling2008; @Senapathi2021; @Lazaro2022].
-A first outcome of our analysis is that asynchrony of species abundances is a key driver of visitation rate stability.
+While drivers of temporal stability have been well-studied in plant communities [@Ruijven2007; @Gross2014; @Craven2018; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021], relatively few studies have evaluated how these same drivers can affect community stability in mobile organisms such as pollinators [@Ebeling2008; @Senapathi2021; @Lazaro2022].
+The first outcome of our analysis is that the asynchrony of species abundances is a key driver of visitation rate stability.
 This stability-asynchrony relationship has been found by different theoretical and empirical studies [@DeMazancourt2013; @Bluthgen2016; @Leps2018; @Sasaki2019; @Valencia2020; @Kigel2021].
 For example, Lázaro et al.(2022) also found for plants, pollinators and their interactions that more asynchronous communities are more temporally stable.
-In this sense, species asynchrony can increase temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species (i.e.
-density compensation [@Winfree2009a; @Mukherjee2019]); or also when they respond differently to the same environmental changes (i.e.
-response diversity [@Walker99; @Winfree2013]).
+In this sense, species asynchrony can increase the temporal stability of visitation rate when the abundance of one species increases as a result of decreases in the abundance of another species (i.e., density compensation [@Winfree2009a; @Mukherjee2019]); or also when they respond differently to the same environmental changes (i.e., response diversity [@Walker99; @Winfree2013]).
 While we do not evaluate the causes of this response diversity, we do show that the asynchronous fluctuating species are redundant in their visitation patterns, a known requisite for response diversity to matter for ecosystem functioning stability [@Stavert2017].
@@
 On the other hand, species richness is considered one of the strongest drivers of community stability in plants [@Tilman2006; @Hallett2014], although Valencia et al.
-(2020), analyzing a large number of plant community datasets, have reported that this relationship is not as strong.
+(2020), analysing a large number of plant community datasets, have reported that this relationship is not as strong.
 Pollinator studies carried out in crop systems have observed a positive relationship between species richness and stability of floral visits [@Ebeling2008] or the stability of pollinator abundance [@Senapathi2021].
 However, our results show that pollinator richness effects were mostly indirect.
-Pollinator richness was positively associated with asynchrony, which positively affect the stability of visitation rate, but not associated directly with more stable visitation rates.
-Species richness is suggested to increase the probability that community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999], but the asynchrony of a few dominant species might be more relevant in pollinator systems than richness per se [@Winfree2015; @Kleijn2015].
+Pollinator richness was positively associated with asynchrony, which positively affects the stability of the visitation rate, but not associated directly with more stable visitation rates.
+Species richness is suggested to increase the probability that a community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999], but the asynchrony of a few dominant species might be more relevant in pollinator systems than richness per se [@Winfree2015; @Kleijn2015].
 
-Despite temporal stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator abundances on pollination services, and those who did used agricultural systems [@Garibaldi2011; @Garibaldi2013; @Lazaro2019; @Hunicken2021].
-To the best of our knowledge, how the stability of pollinator community affect to the reproductive success of the wild plant community remaining largely unknown.
-In pollinator-dependent crops it has been observed that a greater yield stability is related to pollinator diversity and the stability of visitation rates [@Garibaldi2011; @Garibaldi2013; @Hunicken2021] but in our study system (wild plants), we did not find this relationship.
+Despite temporal stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator abundances on pollination services, and those who did use agricultural systems [@Garibaldi2011; @Garibaldi2013; @Lazaro2019; @Hunicken2021].
+To the best of our knowledge, how the stability of the pollinator community affects the reproductive success of the wild plant community remains largely unknown.
+In pollinator-dependent crops, it has been observed that greater yield stability is related to pollinator diversity and the stability of visitation rates [@Garibaldi2011; @Garibaldi2013; @Hunicken2021] but in our study system (wild plants), we did not find this relationship.
 Despite we observed that in specific years a higher visitation rate or richness of pollinators increases the proportion of fruits, for most plants and years there is a general saturation of the proportion of fruits developed, with fruit sets above 80%.
@@
 Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion [@Thomson2001].
-Several factors can mediate the shape of this relationships.
-Firstly, greater availability of floral resources in the plots these years can impact pollinator densities, visitation rates and pollen deposition [@Williams2015; @VanNuland2013; @Veddeler2006; @Evans2017].
+Several factors can mediate the shape of this relationship.
+First, greater availability of floral resources in the plots these years.
+Floral quantity, diversity and composition at local scales can concentrate pollinator activity [@VanNuland2013; @Veddeler2006] and can influence plant constancy [@Kunin1996], and pollen deposition [@Evans2017].
 Secondly, variations in abiotic factors can affect both pollinator abundance and host plants [@Vicens2000; @Ivey2003].
@@
 For example, Herbertsson et al.
-(2021) showed in a recent meta-analysis a large variability in the effects of different pollinators on seed sets, but the causes of this variability remain to be explored.
+(2021) showed in a recent meta-analysis a large variability in the effects of different pollinators on seed sets,and Ryan et al.
+(2023) found interannual variation in fruit yields in raspberries crops, but the causes of this variability remain to be explored.
 
 In summary, our study highlights the importance of pollinator species' asynchrony in maintaining the temporal stability of their visitation rates to wild plants in natural environments.
-However, visitation rates stability did not directly contribute to the stability of the final plant reproductive success function.
-In this sense, we believe that further studies are needed to better understand these mechanisms in natural communities by assessing the reproductive success along time of a wider variety of plant species [@Thomson2019].
+However, visitation rate stability did not directly contribute to the stability of the final plant reproductive success function.
+In this sense, we believe that further studies are needed to better understand these mechanisms in natural communities by assessing the reproductive success of a wider variety of plant species over time [@Thomson2019].
 The variations seen between years suggest that in our study system, plant reproduction is not typically limited by pollinators.
-However in certain years the relationship between pollinator activity and plant reproductive success is important.
+However, the relationship between pollinator activity and plant reproductive success is important in certain years.
 This study contributes to understanding the mechanisms driving the temporal stability of pollinator communities in natural systems and how the relationships between pollinators and plant reproductive success may vary from year to year.
@@
 
-# Aknowledgements
+# Acknowledgements
 
-This study was supported by the XXXXX.Estefania Tobajas thanks the Bartomeus lab and Estacion Biologica de Doñana (EBD-CSIC) for hosting during the research stay.
+This study was supported by the XXXXX. Estefania Tobajas thanks the Bartomeus lab and Estacion Biologica de Doñana (EBD-CSIC) for hosting during the research stay.
 Estefanía Tobajas was funded by a "Postdoc contract" (Ayudas Margarita Salas. Ministerio de Universidades-Universidad de Salamanca).
@@
 Estefanía Tobajas conducted the analyses with the contributions of Virginia Domínguez-García and the guidance of Ignasi Bartomeus.
-Estefanía Tobajas wrote the manuscript with contributions of all authors.
+Estefanía Tobajas wrote the manuscript with the contributions of all authors.
 
@@
 ```{r, echo=FALSE, warning=FALSE,message=FALSE,fig.height = 13,fig.width=30,out.width="100%", fig.align='center',fig.cap=" 1.
-Changes in the stability of visitation rate with the asynchrony (top row) and richness (botton row) are shown for each plant species"}
+Changes in the stability of visitation rate with the asynchrony (top row) and richness (bottom row) are shown for each plant species."}
 # model plot (cv_1_visitation~S_total+asynchrony)
@@
 Interaction effect between richness and year (top row), and visitation rate and year (bottom row) on seed number.
-For the visualization purpose, we omit in the visitation rate (x-axis) the values outside of the 95\\%."}
+For visualization purposes, we omit from the visitation rate (x-axis) the values that are outside 95\\%."}
 

### 2023-05-16 Manuscript/Figures/Conceptual_plot.R
editing plot

@@ -1,5 +1,6 @@
 
 library(ggplot2)
+library(tidyverse)
 library(patchwork)
 
 
@@ -31,12 +32,12 @@ to=ggplot(d1, aes(s1, l1)) +
   theme(axis.text.y=element_blank(),
         axis.ticks.y=element_blank())+
   scale_x_continuous(breaks=seq(from= 0, to= 100, by = 20), labels=c("V1","V2","V3", "V4","V5","V6"))+
-  theme(text = element_text(size=15,face="bold"))+
+  theme(text = element_text(size=18,face="bold"))+
   theme(axis.ticks.x=element_blank())+
   annotate("rect", xmin = c(0, 60), xmax = c(20,80), ymin = c(0.4, 1.35), 
            ymax = c(1.75, 2.7), linetype = 1, fill="gray88", alpha=0.3, colour = "black") +
-  annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R3", "R2", "R1"), size=4)+
-  annotate("text", x = c(1.25, 61.3), y = c(1.66,2.62), label = c("A", "B"), size=6)+
+  annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R3", "R2", "R1"), size=5)+
+  annotate("text", x = c(1.25, 61.3), y = c(1.62,2.58), label = c("A", "B"), size=6)+
   theme(axis.line.x = element_line(arrow = arrow()))+
   theme(axis.line.y = element_line(arrow = arrow()))
 
@@ -58,10 +59,10 @@ R_1=ggplot(da1, aes(x, y1))+
   theme(axis.text.x=element_blank(),
         axis.ticks.x=element_blank()) + 
   scale_y_continuous(breaks=seq(from= -1, to= 1, by = 2), labels=c("R1","R3"))+
-  theme(text = element_text(size=10, face="bold"))+
+  theme(text = element_text(size=15, face="bold"))+
   theme(axis.title.y = element_blank()) +
-  annotate("text", x = 42, y = 0.4, label = "Rep", size=3,color="#e41a1c")+
-  annotate("text", x = 42, y = 0, label = "R", size=4)+ 
+  annotate("text", x = 44, y = 0.4, label = "Rep", size=4,color="#e41a1c")+
+  annotate("text", x = 43, y = 0, label = "R", size=4)+ 
   theme(aspect.ratio=0.5)
 
 
[…]

### 2023-05-16 Manuscript/Manuscript.Rmd
Discussion and grammar review

@@
 Here, we use a 5-year dataset collected for a total of 12 plant species across 13 Mediterranean shrubland sites.
-However, to study the role of pollinator richness and asynchrony as drivers of stability of its visitation rates we only use the 5 most represented plant species across years and sites.
+However, to study the role of pollinator richness and asynchrony as drivers of the stability of visitation rates we use only the 5 most represented plant species across years and sites.
 We also assess whether more stable pollinator communities foster a more stable plant reproductive success across years, measuring both fruit and seed set stability.

### 2023-05-18 Manuscript/Manuscript.Rmd
mistakes corrected

@@
 However, while some studies report that higher visitation rates are correlated with higher plant reproductive output [@Garibaldi2013; @Kaiser-Bunbury2017; @Vazquez2005], other studies find no such relationship [@Hegland2012; @Lundgren2013].
-Interestingly, studies looking at pollen limitation show that higher visitation rates are often associated with no pollen limitation, indicating that above a certain threshold, changes in visitation rates are no longer relevant [Fig.
-1; @Cosacov2008; @Williams2013].
+Interestingly, studies looking at pollen limitation show that higher visitation rates are often associated with no pollen limitation, indicating that above a certain threshold, changes in visitation rates are no longer relevant (Fig.
+1) [@Cosacov2008; @Williams2013].
 However, the occurrence and magnitude of pollen limitation can vary from year to year for individual populations [@Burd1994; @Ashman2004], mainly because of variations in pollinator service delivery [@Aizen2007].
@@
 The stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged from 1.28 to 55.86 (7.018 ± 1.441).
-When we analysed whether the stability of the pollinator visitation rate affected the stability of plant reproductive success, we found no relationship when fruit proportion was considered (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
+When we analysed whether the pollinator visitation rate's stability affected plant reproductive success, we found no relationship when fruit proportion was considered(Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
 However, contrary to expectations, the stability of seed number showed a negative relationship with the stability of pollinator visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).
@@
 However, contrary to what could be expected we found no relationship between the stability of visitation rates and the stability of plant reproductive success.
-This is because in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with lower pollinator abundances.
+This is because, in our study system, plant reproduction is not pollinator limited in most years, with most plants reaching maximum reproductive success even in the sites with lower pollinator abundances.
 However, this does not imply that pollinators are not important or that are always in enough numbers to disregard them, because for specific years the relationship between pollinator activity and plant's reproductive output kicks in as important.
@@
 However, our results show that pollinator richness effects were mostly indirect.
-Pollinator richness was positively associated with asynchrony, which positively affects the stability of the visitation rate, but not associated directly with more stable visitation rates.
+Pollinator richness was positively associated with asynchrony, which positively affects the stability of the visitation rate, but is not associated directly with more stable visitation rates.
 Species richness is suggested to increase the probability that a community contains species with different responses to environmental conditions and perturbations, leading to asynchrony (compensation) among species abundance and thus, to an increase in community stability [@Craven2018; @McCann2000; @Yachi1999], but the asynchrony of a few dominant species might be more relevant in pollinator systems than richness per se [@Winfree2015; @Kleijn2015].

### 2023-05-26 Manuscript/Manuscript.Rmd
Final comments!

@@
   However, the relationship between community stability and the stability of the ecosystem functioning provided by this community has been little explored, specially for functions involving several trophic levels such as plant pollination.
-  Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions provided is important for predicting the resilience of communities to changes in biodiversity.
+  Understanding the mechanisms driving community stability and whether this stability should be related to the stability of ecosystem functions provided is important for predicting the resilience of communities in front of the increasing threats to biodiversity.
 
@@
 3.
-The stability of plant visitation rates is driven by the asynchrony of pollinator species abundances, but the effect of species richness is only indirect, as richer communities also tend to have more asynchronous populations.
-  In contrast, the stability of plant reproductive success is not related to the stability of its pollinator visitation rates.
+The stability of plant visitation rates is driven by the asynchrony of pollinator species abundances, but the effect of pollinator species richness is only indirect, as richer communities also tend to have more asynchronous populations.
+  In contrast, the stability of plant reproductive success is not related to the stability of their pollinator visitation rates.
   A year-by-year analysis reveals that plants in the system studied are unlikely to be limited by pollinator abundance except in specific years, blurring any potential effect of visitation rate stability on reproductive success stability.
@@
   This is particularly important for pollinators with contrasting responses to environmental fluctuations, as this creates the needed asynchrony of their populations to guarantee stable levels of flower visitation rates.
-   However, we warn that more complex ecosystem functions such as reproductive success, which not only depends on pollinators but on plant competition or resource availability, might be decoupled from first order ecosystem functions (i.e., visitation rates and pollen deposition) when pollination is not a limiting factor.
+   However, we warn that final ecosystem functions such as plant reproductive success, which not only depends on pollinators but on plant competition or resource availability, might be decoupled from first order ecosystem functions (i.e., visitation rates and pollen deposition) when pollination is not a limiting factor.
 
@@
 A higher number of species might stabilize community level functions by increasing the range of species level potential responses to environmental changes (i.e., the portfolio effect) [@McCann2000; @Tilman2006; @Hector2010; @Xu2021], although non-significant relationships between diversity and stability have also been observed [@Hooper2005; @VanderPlas2019].
-Species asynchrony represents the intrinsic differences in species response to disturbances and natural fluctuations [@Loreau2013] which has been suggested as a key driver for community temporal stability [@Loreau2008].
+Species asynchrony represents the intrinsic differences in species response to disturbances and/or environmental fluctuations [@Loreau2013] which has been suggested as a key driver for community temporal stability [@Loreau2008].
 In this sense, higher levels of species asynchrony stabilize the overall community dynamics [@Ruijven2007; @Bluthgen2016; @Craven2018].
@@
 
-![ Conceptual figure showing the general relationship between the visitation rate of pollinators and plant reproductive success to different species richness (R1, R2, ...).
+![ Conceptual figure showing the expected general relationship between the visitation rate of pollinators and plant reproductive success to different species richness (R1, R2, ...).
 As the number of pollinator visits increases (V1, V2, …), plant reproductive success is expected to increase until that above a certain threshold, the changes in visitation rates are no longer relevant to plant reproductive success.
-According to this, A-square shows that temporal variation in plant reproductive success depends on variation in visitation, while B-square shows that reproductive success varies with the variation in richness.](Figures/conceptual_plot.png){width="400"}
+Similarly, higer species richess is expected to increase reproductive success due to complmentary efffects among pollinators.
+According to this, the expected relationship between pollinator biodiversity and estability pollination depends on where we are along this curve.
+In point A, that temporal variation in plant reproductive success depends mainly on the variation in visitation, while in point B the reproductive success varies with the variation in richness.](Figures/conceptual_plot.png){width="400"}
 
@@
 Hence, for each plant individual, the sampling effort was standardized to the number of visits per flower per minute.
-To that end, we calculated the visitation rate by dividing the total visits observed by the number of flowers observed and by the total observation time (time of each observation multiplied by the number of survey rounds per year).
+To that end, we calculated plant's visitation rate by dividing the total visits observed by the number of flowers observed and by the total observation time (time of each observation multiplied by the number of survey rounds per year).
 Pollinator richness is calculated as the number of different pollinator species observed visiting the plant over all rounds, fruit set as the proportion of fruits developed (developed / aborted+developed), and the seed set as the mean number of seeds per fruit for each plant individual sampled per site.
@@
 The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman (1999).
-This is an adequate index given that in our dataset, as in most ecological studies, the mean and the variance are scaled to each other.
+This is an adequate index given that in our dataset, as in most ecological studies, the variance scales with the mean.
 To examine the role of richness and asynchrony of pollinator species abundances as drivers of stability of visitation rate, we calculate pollinator richness as the total number of different pollinator species that visit each plant species in each plot.
@@
 However, we also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
-We observed one data point has a high leverage on the stability analysis (*C.crispus*, Fig 2A-B), when we remove this point, the slope is still positive (0.968 ± 0.745).
+We observed one data point has a high leverage on the stability analysis (*C.crispus*, Fig 2A-B), but when we remove this point, the slope is still positive (0.968 ± 0.745).
 
-When we analysed each plant species separately, we observed a positive relationship between the asynchrony of pollinators and stability of visitation rate for *C.
+When we further analysed each plant species separately, we observed, as expected based on the previous analysis, a consisting positive relationship between the asynchrony of pollinators and stability of visitation rate for *C.
 crispus*, *H.
@@
 halimifolium* and *L.
-pedunculata* showed positive relationships, explaining the overall lack of relationship across all five plants (Supplementary material-Fig 1).
+pedunculata* showed positive relationships, explaining the overall lack of relationship between richness and XXXXX across all five plants (Supplementary material-Fig 1).
 
@@
 The stability of fruit proportion varied from 2.62 to 120.66 (mean ± SE: 19.806 ± 3.615), whereas the stability of seed number ranged from 1.28 to 55.86 (7.018 ± 1.441).
-When we analysed whether the pollinator visitation rate's stability affected plant reproductive success, we found no relationship when fruit proportion was considered(Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
+When we analysed whether the pollinator visitation rate's stability affected plant reproductive success, we found no relationship when fruit proportion was considered (Estimate ± standard error: -1.547 ± 2.611; *p* = 0.558) (Fig 3A).
 However, contrary to expectations, the stability of seed number showed a negative relationship with the stability of pollinator visitation rate (-1.887 ± 0.959; *p* = 0.061) (Fig 3B).
-Although this tendency is influenced by a high value in the stability of seed number of *H.
-halimifolium* (Fig 3B) since when if the point is removed the relationship disappears and if anything, shows a positive slope (0.561 ± 0.535).
+However, this relationship is influenced by a single high value in the stability of seed number of *H.
+halimifolium* (Fig 3B) and when this point is removed the relationship disappears and if anything, shows a positive slope (0.561 ± 0.535).
 
@@
 On the other hand, species richness is considered one of the strongest drivers of community stability in plants [@Tilman2006; @Hallett2014], although Valencia et al.
-(2020), analysing a large number of plant community datasets, have reported that this relationship is not as strong.
+(2020), analysing a large number of plant community datasets, have reported that this relationship is not as strong as initially shown.
 Pollinator studies carried out in crop systems have observed a positive relationship between species richness and stability of floral visits [@Ebeling2008] or the stability of pollinator abundance [@Senapathi2021].
@@
 Despite temporal stability is crucial to the sustainability of ecosystem functions, relatively few studies have evaluated the stability of the pollinator abundances on pollination services, and those who did use agricultural systems [@Garibaldi2011; @Garibaldi2013; @Lazaro2019; @Hunicken2021].
-To the best of our knowledge, how the stability of the pollinator community affects the reproductive success of the wild plant community remains largely unknown.
+To the best of our knowledge, how the stability of the pollinator community affects the reproductive success of wild plant communities remains largely unknown.
 In pollinator-dependent crops, it has been observed that greater yield stability is related to pollinator diversity and the stability of visitation rates [@Garibaldi2011; @Garibaldi2013; @Hunicken2021] but in our study system (wild plants), we did not find this relationship.
@@
 Therefore, its reproductive success may not continue to increase with increased visitation, but instead may saturate quickly because of pollen depletion [@Thomson2001].
-Several factors can mediate the shape of this relationship.
-First, greater availability of floral resources in the plots these years.
-Floral quantity, diversity and composition at local scales can concentrate pollinator activity [@VanNuland2013; @Veddeler2006] and can influence plant constancy [@Kunin1996], and pollen deposition [@Evans2017].
-Secondly, variations in abiotic factors can affect both pollinator abundance and host plants [@Vicens2000; @Ivey2003].
-For instance, the variation of temperature conditions leads to alterations in nectar production, composition, and concentration [@Pacini2003], which can affect to the pollinator.
-Although investigating these factors is beyond the aim of the study, future research should clarify when and where pollinators are limited.
+As pollen limitation can be more common in crop systems with large pulses of monospecific floral resources, this might explain the discrepancies among our findings and crop studies.
+However, several factors can mediate the degree of pollen limitation in natural communities.
+Most importantly, variations in abiotic factors can affect both pollinator abundance and host plants [@Vicens2000; @Ivey2003] affecting the ratio of flowers per pollinator.
+The availability of floral resources determines the pollinator demand, and floral quantity, diversity and composition at local scales can concentrate or dilute pollinator activity [@VanNuland2013; @Veddeler2006] as well as influence plant constancy [@Kunin1996], and pollen deposition [@Evans2017].
+For instance, the variation of temperature conditions leads to alterations in nectar production, composition, and concentration [@Pacini2003], which can affect to the pollinator behaviour.
+Although investigating these factors is beyond the aim of the study, future research should clarify when and where pollinators are limiting.
 For example, Herbertsson et al.
-(2021) showed in a recent meta-analysis a large variability in the effects of different pollinators on seed sets,and Ryan et al.
+(2021) showed in a recent meta-analysis a large variability in the effects of different pollinators on seed sets, and Ryan et al.
 (2023) found interannual variation in fruit yields in raspberries crops, but the causes of this variability remain to be explored.
@@
 In this sense, we believe that further studies are needed to better understand these mechanisms in natural communities by assessing the reproductive success of a wider variety of plant species over time [@Thomson2019].
-The variations seen between years suggest that in our study system, plant reproduction is not typically limited by pollinators.
-However, the relationship between pollinator activity and plant reproductive success is important in certain years.
+The variations seen between years suggest that in our study system, plant reproduction is not typically limited by pollinators, but other systems might be much more pollinator limited.
+However, it is important that the relationship between pollinator activity and plant reproductive success is important in certain years.
 This study contributes to understanding the mechanisms driving the temporal stability of pollinator communities in natural systems and how the relationships between pollinators and plant reproductive success may vary from year to year.
@@
 
-This study was supported by the XXXXX. Estefania Tobajas thanks the Bartomeus lab and Estacion Biologica de Doñana (EBD-CSIC) for hosting during the research stay.
+This study was supported by the BeeFun project (PCIG14-GA-2013-631653). Estefania Tobajas thanks the Bartomeus lab and Estacion Biologica de Doñana (EBD-CSIC) for hosting during the research stay.
 Estefanía Tobajas was funded by a "Postdoc contract" (Ayudas Margarita Salas. Ministerio de Universidades-Universidad de Salamanca).
@@
 All authors designed the idea.
-Francisco P. Molina collected the data.
+Francisco P. Molina and Ignasi Bartomeus collected the data.
 Estefanía Tobajas conducted the analyses with the contributions of Virginia Domínguez-García and the guidance of Ignasi Bartomeus.

### 2023-05-30 Manuscript/Manuscript.Rmd
final version

@@
 output:
+  word_document: default
   pdf_document:
     latex_engine: xelatex
-  word_document: default
 header-includes: \usepackage{float} \floatplacement{figure}{H} \usepackage{caption}
@@
 
+# Keywords
+asynchrony, fruit set, pollinator richness, seed set, temporal stability.
+
 # Introduction
@@
 Similarly, higer species richess is expected to increase reproductive success due to complmentary efffects among pollinators.
-According to this, the expected relationship between pollinator biodiversity and estability pollination depends on where we are along this curve.
+According to this, the expected relationship between pollinator biodiversity and stability pollination depends on where we are along this curve.
 In point A, that temporal variation in plant reproductive success depends mainly on the variation in visitation, while in point B the reproductive success varies with the variation in richness.](Figures/conceptual_plot.png){width="400"}
@@
 
-We analyse five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites [(mean = 7 ± 0.71 sites)](lavandula%20aparece%20en%205%20sitios,%20halimiun%20en%206,%20los%20citus%20estan%20entre%207%20y%209%20sitios) in a minimum of two years per site (mean = 3.25 ± 0.16 years per plant).
+We analyse five plant species (*Cistus crispus*, *Cistus ladanifer*, *Cistus salviifolius*, *Halimium halimifolium*, and *Lavandula pedunculata*) that were recorded in at least 5 sites (mean = 7 ± 0.71 sites) in a minimum of two years per site (mean = 3.25 ± 0.16 years per plant).
 The stability of pollinator visitation rates was quantified as the inverse of the coefficient of variation (mean/SD) for each plant species in each plot following Tilman (1999).
@@
 Stability of visitation rates ranged from 0.64 to 9.24 (mean ± SE: 1.928 ± 0.232), whereas pollinator richness ranged from 2 to 20 species (8.128 ± 0.686) and the pollinator asynchrony varied from 0 to 0.998 (0.754 ± 0.032).
-There was a strong positive relationship between the stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increased [(Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A)], whereas the stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
+There was a strong positive relationship between the stability of visitation rates and asynchrony of pollinator species abundances with greater visitation rate stability when pollinator asynchrony increased (Estimate ± standard error: 2.903 ± 1.134; *p* = 0.017) (Fig 2A), whereas the stability of visitation rate was not influenced by the pollinator richness (-0.001 ± 0.063; *p* = 0.986) (Fig 2B).
 However, we also found a positive relationship between asynchrony and pollinator richness (0.020 ± 0.005, *p* = 0.001) (Fig 2C).
@@
 halimifolium* and *L.
-pedunculata* showed positive relationships, explaining the overall lack of relationship between richness and XXXXX across all five plants (Supplementary material-Fig 1).
+pedunculata* showed positive relationships, explaining the overall lack of relationship between he richness and stability of visitation rates across all five plants (Supplementary material-Fig 1).
 
@@
   theme(legend.position = "bottom",legend.background = element_blank(),legend.box.background = element_rect(colour = "black"))&theme(text = element_text(size=25))
+
 p_cv_visit+ plot_layout(guides = "collect")
@@
 We also observed a positive relationship between richness and fruit proportion in 2019.
-However, in 2018, a specially wet year, the relationship between richness and fruit proportion was negative (Fig 3).
+However, in 2018, a specially wet year, the relationship between richness and fruit proportion was negative (Fig 4).
 

### 2023-05-30 Manuscript/Figures/Figure2.R
Figure 2

@@ -1,0 +1,113 @@
+
+library(tidyverse)
+library(lme4)
+library(effects)
+library(patchwork)
+
+
+# staility of visitation rate and richness and asynchrony
+# plant species present at least in five sites
+# C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata
+
+# stability data 
+data_plant<- read.csv("Data/Stability.csv")
+data_plant<-data_plant[,-1]
+
+
+# eliminar plant species 
+sp_out2=data_plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id <= 4) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in at least 5 sites
+data_plant = data_plant %>% filter(!Plant_gen_sp %in% sp_out2)
+
+levels(factor(data_plant$Plant_gen_sp))
+
+
+data_plant=data_plant %>%
+  filter(!Plant_gen_sp=="Salvia rosmarinus") %>%
+  filter(!Plant_gen_sp=="Halimium calycinum")%>%
+  filter(!Plant_gen_sp=="Lavandula stoechas")
+
+
+
+## Replace Inf and -Inf with NA
+data_plant[is.na(data_plant) | data_plant == "Inf"] <- NA 
+data_plant[is.na(data_plant) | data_plant == "-Inf"] <- NA 
+
+
+
+# We can express asynchrony as 1 - φ, 
+#where φ is Loreau and de Mazancourt’s (2008)
+data_plant$asyn_LM= 1-data_plant$syncLM
+
+
+#model 
+mod1_sta= lmer (cv_1_visitation ~  asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
+
+
+
+#getting effects for asynchrony
+effe_mod_sta <-data.frame( effect("asyn_LM", mod1_sta, se = TRUE))
+
+
+#plot model of asynchrony
+p1=ggplot(effe_mod_sta, aes(asyn_LM, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.2, colour = "black")+
+  labs(color='Plant species')+
+  coord_cartesian(ylim=c(-0.5,9.5))+
[…]

### 2023-05-30 Manuscript/Figures/Plot_1.R
.

@@ -1,113 +1,0 @@
-
-library(tidyverse)
-library(lme4)
-library(effects)
-library(patchwork)
-
-
-# staility of visitation rate and richness and asynchrony
-# plant species present at least in five sites
-# C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata
-
-# stability data 
-data_plant<- read.csv("Data/Stability.csv")
-data_plant<-data_plant[,-1]
-
-
-# eliminar plant species 
-sp_out2=data_plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id <= 4) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in at least 5 sites
-data_plant = data_plant %>% filter(!Plant_gen_sp %in% sp_out2)
-
-levels(factor(data_plant$Plant_gen_sp))
-
-
-data_plant=data_plant %>%
-  filter(!Plant_gen_sp=="Salvia rosmarinus") %>%
-  filter(!Plant_gen_sp=="Halimium calycinum")%>%
-  filter(!Plant_gen_sp=="Lavandula stoechas")
-
-
-
-## Replace Inf and -Inf with NA
-data_plant[is.na(data_plant) | data_plant == "Inf"] <- NA 
-data_plant[is.na(data_plant) | data_plant == "-Inf"] <- NA 
-
-
-
-# We can express asynchrony as 1 - φ, 
-#where φ is Loreau and de Mazancourt’s (2008)
-data_plant$asyn_LM= 1-data_plant$syncLM
-
-
-#model 
-mod1_sta= lmer (cv_1_visitation ~  asyn_LM + (1|Site_ID) + (1|Plant_gen_sp), data = data_plant)
-
-
-
-#getting effects for asynchrony
-effe_mod_sta <-data.frame( effect("asyn_LM", mod1_sta, se = TRUE))
-
-
-#plot model of asynchrony
-p1=ggplot(effe_mod_sta, aes(asyn_LM, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), linetype = 3,alpha=0.2, colour = "black")+
-  labs(color='Plant species')+
-  coord_cartesian(ylim=c(-0.5,9.5))+
[…]

### 2023-05-30 Manuscript/Figures/Figure3.R
Figure 3

@@ -1,0 +1,97 @@
+
+library(tidyverse)
+library(lme4)
+library(effects)
+library(patchwork)
+
+
+# stability data for five plant species present at least in five sites
+# C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata
+
+# stability data 
+data_plant<- read.csv("Data/Stability.csv")
+data_plant<-data_plant[,-1]
+
+
+# eliminar plant species 
+sp_out2=data_plant %>%
+  group_by(Plant_gen_sp) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id <= 4) %>%
+  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
+
+#Data with species in at least 5 sites
+data_plant = data_plant %>% filter(!Plant_gen_sp %in% sp_out2)
+
+levels(factor(data_plant$Plant_gen_sp))
+
+
+data_plant=data_plant %>%
+  filter(!Plant_gen_sp=="Salvia rosmarinus") %>%
+  filter(!Plant_gen_sp=="Halimium calycinum")%>%
+  filter(!Plant_gen_sp=="Lavandula stoechas")
+
+
+
+## Replace Inf and -Inf with NA
+data_plant[is.na(data_plant) | data_plant == "Inf"] <- NA 
+data_plant[is.na(data_plant) | data_plant == "-Inf"] <- NA 
+
+
+
+# We can express asynchrony as 1 - φ, 
+#where φ is Loreau and de Mazancourt’s (2008)
+data_plant$asyn_LM= 1-data_plant$syncLM
+
+
+#model fruit stability ~ visitation rate stability
+mod2_sta= lmer(cv_1_fruit ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID),data = data_plant)
+
+#getting effects 
+effe3_mod_sta <-data.frame( effect("cv_1_visitation", mod2_sta, se = TRUE))
+
+
+#plot model 
+p_mod2=ggplot(effe3_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
+  geom_ribbon(aes(ymin = lower, ymax = upper),linetype = 3, alpha=0.2, colour = "black")+
+  geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_fruit, color=Plant_gen_sp),alpha=0.5, size=3)+
+  labs(color='Plant species')+
[…]

### 2023-05-30 Manuscript/Figures/Plot_2.R
.

@@ -1,97 +1,0 @@
-
-library(tidyverse)
-library(lme4)
-library(effects)
-library(patchwork)
-
-
-# stability data for five plant species present at least in five sites
-# C.crispu, C. ladanifer, C. salviifolius, H.halimifolium and L. pedunculata
-
-# stability data 
-data_plant<- read.csv("Data/Stability.csv")
-data_plant<-data_plant[,-1]
-
-
-# eliminar plant species 
-sp_out2=data_plant %>%
-  group_by(Plant_gen_sp) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id <= 4) %>%
-  select(Plant_gen_sp) %>% pull(Plant_gen_sp)
-
-#Data with species in at least 5 sites
-data_plant = data_plant %>% filter(!Plant_gen_sp %in% sp_out2)
-
-levels(factor(data_plant$Plant_gen_sp))
-
-
-data_plant=data_plant %>%
-  filter(!Plant_gen_sp=="Salvia rosmarinus") %>%
-  filter(!Plant_gen_sp=="Halimium calycinum")%>%
-  filter(!Plant_gen_sp=="Lavandula stoechas")
-
-
-
-## Replace Inf and -Inf with NA
-data_plant[is.na(data_plant) | data_plant == "Inf"] <- NA 
-data_plant[is.na(data_plant) | data_plant == "-Inf"] <- NA 
-
-
-
-# We can express asynchrony as 1 - φ, 
-#where φ is Loreau and de Mazancourt’s (2008)
-data_plant$asyn_LM= 1-data_plant$syncLM
-
-
-#model fruit stability ~ visitation rate stability
-mod2_sta= lmer(cv_1_fruit ~ cv_1_visitation + (1|Plant_gen_sp)+(1|Site_ID),data = data_plant)
-
-#getting effects 
-effe3_mod_sta <-data.frame( effect("cv_1_visitation", mod2_sta, se = TRUE))
-
-
-#plot model 
-p_mod2=ggplot(effe3_mod_sta, aes(cv_1_visitation, fit)) + geom_line(size=1)+
-  geom_ribbon(aes(ymin = lower, ymax = upper),linetype = 3, alpha=0.2, colour = "black")+
-  geom_point(data = data_plant, aes(x =  cv_1_visitation, y = cv_1_fruit, color=Plant_gen_sp),alpha=0.5, size=3)+
-  labs(color='Plant species')+
[…]

### 2023-05-30 Manuscript/Figures/Plot_3.R
.

@@ -1,63 +1,0 @@
-
-library(tidyverse)
-library(lme4)
-library(effects)
-library(patchwork)
-
-
-Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
-Pollinator_Plant<-Pollinator_Plant[,-1]
-Pollinator_Plant$Year= as.factor(Pollinator_Plant$Year)
-Pollinator_Plant$Site_ID= as.factor(Pollinator_Plant$Site_ID)
-Pollinator_Plant$Plant_gen_sp= as.factor(Pollinator_Plant$Plant_gen_sp)
-
-
-# species out
-#plant species that for each year occur only at one site
-spp_out <- Pollinator_Plant %>%
-  group_by(Plant_gen_sp, Year) %>%
-  summarise(Unique_Id = n_distinct(Site_ID)) %>%
-  filter(Unique_Id == 1) %>%
-  select(Plant_gen_sp, Year)
-
-
-Pollinator_Plant= anti_join(Pollinator_Plant, spp_out)
-
-
-
-# model 1
-mod1_to= glmer(cbind(fruit_formado, Fruit_No) ~ S_total * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
-
-#getting effects for the two variables
-ee_mod1 <- as.data.frame(Effect(c("S_total","Year"),mod = mod1_to))
-
-p1=ggplot(ee_mod1, aes(S_total,fit))+
-  geom_line(size=0.8)+
-  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
-  geom_point(data= Pollinator_Plant, aes(x = S_total , y = fruit_proportion),shape=21, fill="grey")+
-  labs(x = "Pollinator richness",y="Fruit proportion")+
-  facet_wrap(~Year, nrow = 1) + 
-  theme_bw ()+
-  theme(legend.position = "none")
-
-
-
-# model 2
-mod2_to= glmer(cbind(fruit_formado, Fruit_No) ~ visitatio_rate * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
-
-#getting effects for the two variables
-ee_mod2 <- as.data.frame(Effect(c("visitatio_rate","Year"),mod = mod2_to))
-
-p2=ggplot(ee_mod2, aes(visitatio_rate,fit))+
-  geom_line(size=0.8)+  
[…]

### 2023-05-30 Manuscript/Figures/Figure4.R
Figure 4

@@ -1,0 +1,63 @@
+
+library(tidyverse)
+library(lme4)
+library(effects)
+library(patchwork)
+
+
+Pollinator_Plant<- read.csv("Data/Pollinator_Plant.csv") #400 observaciones
+Pollinator_Plant<-Pollinator_Plant[,-1]
+Pollinator_Plant$Year= as.factor(Pollinator_Plant$Year)
+Pollinator_Plant$Site_ID= as.factor(Pollinator_Plant$Site_ID)
+Pollinator_Plant$Plant_gen_sp= as.factor(Pollinator_Plant$Plant_gen_sp)
+
+
+# species out
+#plant species that for each year occur only at one site
+spp_out <- Pollinator_Plant %>%
+  group_by(Plant_gen_sp, Year) %>%
+  summarise(Unique_Id = n_distinct(Site_ID)) %>%
+  filter(Unique_Id == 1) %>%
+  select(Plant_gen_sp, Year)
+
+
+Pollinator_Plant= anti_join(Pollinator_Plant, spp_out)
+
+
+
+# model 1
+mod1_to= glmer(cbind(fruit_formado, Fruit_No) ~ S_total * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
+
+#getting effects for the two variables
+ee_mod1 <- as.data.frame(Effect(c("S_total","Year"),mod = mod1_to))
+
+p1=ggplot(ee_mod1, aes(S_total,fit))+
+  geom_line(size=0.8)+
+  geom_ribbon(aes(ymin = lower, ymax = upper), alpha = .2)+
+  geom_point(data= Pollinator_Plant, aes(x = S_total , y = fruit_proportion),shape=21, fill="grey")+
+  labs(x = "Pollinator richness",y="Fruit proportion")+
+  facet_wrap(~Year, nrow = 1) + 
+  theme_bw ()+
+  theme(legend.position = "none")
+
+
+
+# model 2
+mod2_to= glmer(cbind(fruit_formado, Fruit_No) ~ visitatio_rate * Year + (1|Site_ID/Plant_gen_sp),family=binomial,data=Pollinator_Plant)
+
+#getting effects for the two variables
+ee_mod2 <- as.data.frame(Effect(c("visitatio_rate","Year"),mod = mod2_to))
+
+p2=ggplot(ee_mod2, aes(visitatio_rate,fit))+
+  geom_line(size=0.8)+  
[…]

### 2023-05-30 Manuscript/Figures/Conceptual_plot.R
.

@@ -1,163 +1,0 @@
-
-library(ggplot2)
-library(tidyverse)
-library(patchwork)
-
-
-#First dataset RED
-s1 <- seq(from=0, to=100, by=0.5)
-l1 = log(s1, base = 6)
-d1 = data.frame(l1, s1)
-
-
-#Second dataset BLUE
-s2 <- seq(from=0, to=100, by=0.5)
-l2 = log(s2, base = 8)
-d2 = data.frame(l2, s2)
-
-#Third dataset GREEN
-s3 <- seq(from=0, to=100, by=0.5)
-l3 = log(s3, base = 12)
-d3 = data.frame(l3, s3)
-
-
-
-to=ggplot(d1, aes(s1, l1)) +
-  geom_line(color = "#e41a1c", linewidth=1.3) +
-  geom_line(data =  d2, aes(s2,l2), color = "#377eb8",linewidth=1.3) +
-  geom_line(data =  d3, aes(s3,l3), color = "#4daf4a",linewidth=1.3) +
-  ylab("Reproductive success")+
-  labs(x = "") +
-  theme_classic()+
-  theme(axis.text.y=element_blank(),
-        axis.ticks.y=element_blank())+
-  scale_x_continuous(breaks=seq(from= 0, to= 100, by = 20), labels=c("V1","V2","V3", "V4","V5","V6"))+
-  theme(text = element_text(size=18,face="bold"))+
-  theme(axis.ticks.x=element_blank())+
-  annotate("rect", xmin = c(0, 60), xmax = c(20,80), ymin = c(0.4, 1.35), 
-           ymax = c(1.75, 2.7), linetype = 1, fill="gray88", alpha=0.3, colour = "black") +
-  annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R3", "R2", "R1"), size=5)+
-  annotate("text", x = c(1.25, 61.3), y = c(1.62,2.58), label = c("A", "B"), size=6)+
-  theme(axis.line.x = element_line(arrow = arrow()))+
-  theme(axis.line.y = element_line(arrow = arrow()))
-
-
-
-##################################
-x <- seq(0, 41, by = 0.1)
-y1 <- sin(x)
-y1.2 <- cos(x+4.3)
-
-da1 <- data.frame( x, y1)
-da1.2 <- data.frame( x, y1.2)
-
-R_1=ggplot(da1, aes(x, y1))+
-  geom_line( size=1) +
[…]

### 2023-05-30 Manuscript/Figures/Fig.1-Conceptual_plot.R
Figure 1 (conceptual)

@@ -1,0 +1,165 @@
+
+library(ggplot2)
+library(tidyverse)
+library(patchwork)
+
+
+#First dataset RED
+s1 <- seq(from=0, to=100, by=0.5)
+l1 = log(s1, base = 8)
+d1 = data.frame(l1, s1)
+
+
+#Second dataset BLUE
+s2 <- seq(from=0, to=100, by=0.5)
+l2 = log(s2, base = 9)
+d2 = data.frame(l2, s2)
+
+#Third dataset GREEN
+s3 <- seq(from=0, to=100, by=0.5)
+l3 = log(s3, base = 10)
+d3 = data.frame(l3, s3)
+
+
+
+ggplot(d1, aes(s1, l1)) +
+  geom_line(color = "#e41a1c", linewidth=1) +
+  geom_line(data =  d2, aes(s2,l2), color = "#377eb8",linewidth=1) +
+  geom_line(data =  d3, aes(s3,l3), color = "#4daf4a",linewidth=1) +
+  ylab("Reproductive success")+
+  labs(x = "") +
+  theme_classic()+
+  theme(axis.text.y=element_blank(),
+        axis.ticks.y=element_blank())+
+  scale_x_continuous(breaks=seq(from= 0, to= 100, by = 20), labels=c("V1","V2","V3", "V4","V5","V6"))+
+  theme(text = element_text(size=15,face="bold"))+
+  theme(axis.ticks.x=element_blank())+
+  annotate("rect", xmin = c(0, 60), xmax = c(20,80), ymin = c(0.4, 1.35), 
+           ymax = c(1.75, 2.7), linetype = 1, fill="gray88", alpha=0.3, colour = "black") +
+  annotate("text", x = c(98, 98,98), y = c(2.67, 2.31,1.95), label = c("R3", "R2", "R1"), size=5)+
+  annotate("text", x = c(1.25, 61.3), y = c(1.62,2.58), label = c("A", "B"), size=5)+
+  theme(axis.line.x = element_line(arrow = arrow()))+
+  theme(axis.line.y = element_line(arrow = arrow()))
+
+
+
+
+##################################
+x <- seq(0, 41, by = 0.1)
+y1 <- sin(x)
+y1.2 <- cos(x+4.3)
+
+da1 <- data.frame( x, y1)
+da1.2 <- data.frame( x, y1.2)
+
+R_1=ggplot(da1, aes(x, y1))+
+  geom_line( size=1) +
[…]
